### 2016-01-05 Paper/Draft.tex
Initialized paper branch

 \documentclass{article}
 \usepackage[utf8]{inputenc}
 \usepackage[titletoc]{appendix}
 \title{Ontology Matching with Word2Vec}
 \author{Harmen Prins}

 \begin{document}
 \maketitle

 \section*{Summary}

 \tableofcontents

 \section{Introduction}

 \section{Problem}
 \subsection{Short Context}
 \subsection{Problem}
 \subsection{Research questions}
 \subsection{Hypotheses}
 \subsection{Justification}
 Consider moving this up

 \section{Context}
 \subsection{The Semantic Web}
 \subsubsection{Goal}
 \subsubsection{Current state}
 \subsubsection{Technologies}
 \subsection{Ontologies}
 \subsubsection{OWL}
 \subsubsection{Role}
 \subsection{Current merging strategies}
 \subsection{Other related research}
 \subsection{Used technology}
 \subsubsection{Ontology constructor}
 \subsubsection{AgreementMaker}
 \subsubsection{MapReduce}

 \section{Method}
 \subsection{Evaluation methods}
 \subsection{Data}

 \section{Algorithm}
 \subsection{Idea}
 \subsection{Theory}
 \subsection{Product}

 \section{Results}

 \section{Conclusions}
 \subsection{Recap research questions}
 \subsection{Recap hypotheses}
 \subsection{Conclusion per hypothesis}
 \subsection{Overview of results}
 \subsection{Final conclusion}

 \section{Discussion}
 \subsection{Interpretation}
 \subsection{Unexpected results}
 \subsection{Expected results}
 \subsection{Future research}

 \begin{appendices}
  \section{Appendix 1}
  \section{Appendix 2}
 \end{appendices}

 \section*{References}

 \end{document}

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-BatchMode/src/main/java/am/extension/batchmode/Activator.java
Reinstalled agreementmaker

@@ -1,0 +1,33 @@
+package am.extension.batchmode;
+
+import am.extension.batchmode.api.BatchModeFileReader;
+import am.extension.batchmode.api.BatchModeRunner;
+import am.extension.batchmode.internal.BatchModeFileReaderImpl;
+import am.extension.batchmode.simpleBatchMode.SimpleBatchModeRunner;
+import org.osgi.framework.BundleActivator;
+import org.osgi.framework.BundleContext;
+import org.osgi.framework.ServiceRegistration;
+
+public class Activator implements BundleActivator {
+
+	private static BundleContext context;
+    private ServiceRegistration<BatchModeFileReader> fileReaderServiceRegistration;
+    private ServiceRegistration<BatchModeRunner> runnerServiceRegistration;
+
+	public static BundleContext getContext() {
+		return context;
+	}
+
+	public void start(BundleContext bundleContext) throws Exception {
+		Activator.context = bundleContext;
+        fileReaderServiceRegistration = context.registerService(BatchModeFileReader.class, new BatchModeFileReaderImpl(), null);
+        runnerServiceRegistration = context.registerService(BatchModeRunner.class, new SimpleBatchModeRunner(), null);
+	}
+
+	public void stop(BundleContext bundleContext) throws Exception {
+        fileReaderServiceRegistration.unregister();
+        runnerServiceRegistration.unregister();
+		Activator.context = null;
+	}
+
+}

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-BatchMode/src/main/java/am/extension/batchmode/simpleBatchMode/SimpleBatchModeRunner.java

@@ -1,0 +1,215 @@
+package am.extension.batchmode.simpleBatchMode;
+
+import java.io.File;
+import java.io.FileNotFoundException;
+import java.io.IOException;
+
+import am.app.mappingEngine.DefaultMatcherParameters;
+import am.app.mappingEngine.DefaultSelectionParameters;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.SelectionAlgorithm;
+import am.extension.batchmode.api.BatchModeRunner;
+import am.extension.batchmode.api.BatchModeSpec;
+import am.extension.batchmode.api.BatchModeTask;
+import org.apache.log4j.Level;
+import org.apache.log4j.Logger;
+import am.app.mappingEngine.AbstractMatcher;
+
+import am.app.mappingEngine.Alignment;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.ReferenceEvaluationData;
+import am.app.mappingEngine.referenceAlignment.ReferenceAlignmentMatcher;
+import am.app.mappingEngine.referenceAlignment.ReferenceAlignmentParameters;
+import am.app.mappingEngine.referenceAlignment.ReferenceEvaluator;
+
+import am.app.ontology.Ontology;
+import am.app.ontology.ontologyParser.OntoTreeBuilder;
+import am.matcher.oaei.oaei2011.OAEI2011Matcher;
+import am.matcher.oaei.oaei2011.OAEI2011MatcherParameters;
+import am.output.console.ConsoleProgressDisplay;
+
+/**
+ * This class takes runs a batch mode from the given SimpleBatchMode XML file.
+ * 
+ * The structure of the SimpleBatchMode XML file is described in data/SimpleBatchMode.xsd.
+ * 
+ * @author Cosmin Stroe - Nov 7, 2011
+ *
+ */
+public class SimpleBatchModeRunner implements BatchModeRunner {
+
+    @Override
+    public void run(BatchModeSpec spec) throws Exception {
+        for(BatchModeTask task : spec.getTasks()) {
+            // load the Ontologies.
+            checkOntologyFiles(task.getSourceOntology(), task.getTargetOntology());
+
+            final Ontology sourceOntology = OntoTreeBuilder.loadOWLOntology(task.getSourceOntology());
+            final Ontology targetOntology = OntoTreeBuilder.loadOWLOntology(task.getTargetOntology());
+
+            AbstractMatcher matcher = task.getMatcher().getMatcher();
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-Core/src/am/app/Core.java

@@ -1,0 +1,649 @@
+package am.app;
+
+import java.io.File;
+import java.util.ArrayList;
+import java.util.Iterator;
+import java.util.LinkedList;
+import java.util.List;
+
+import javax.management.InstanceAlreadyExistsException;
+
+import org.apache.commons.io.FilenameUtils;
+import org.apache.log4j.LogManager;
+import org.apache.log4j.Logger;
+import org.osgi.framework.Bundle;
+import org.osgi.framework.BundleContext;
+import org.osgi.framework.BundleException;
+
+import am.AMException;
+import am.app.mappingEngine.AbstractMatcher;
+import am.app.mappingEngine.LexiconStore;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MatcherChangeListener;
+import am.app.mappingEngine.MatcherRegistry;
+import am.app.mappingEngine.MatcherResult;
+import am.app.mappingEngine.MatchersRegistry;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.MatchingTaskChangeEvent;
+import am.app.mappingEngine.MatchingTaskChangeEvent.EventType;
+import am.app.mappingEngine.SelectionAlgorithm;
+import am.app.ontology.Node;
+import am.app.ontology.Ontology;
+import am.app.ontology.OntologyChangeEvent;
+import am.app.ontology.OntologyChangeListener;
+import am.app.ontology.profiling.OntologyProfiler;
+import am.app.osgi.AMHost;
+import am.app.osgi.OSGiRegistry;
+import am.utility.AppPreferences;
+
+import com.hp.hpl.jena.rdf.model.Model;
+
+/**
+ * SINGLETON JAVA PATTERN
+ * There will be only one instance of this class in the whole application
+ * All classes can access it without having any reference to it, just invoking the static method
+ * Core.getInstance()
+ * All model information of the system will be accessible from this class:
+ * ontologies, matchings and so on.
+ * 
+ * TODO: I think this class should be removed.  It's a crutch and a better design is needed. -- Cosmin, Oct. 20, 2013.
+ *
+ */
+public class Core {
+	
+	private final Logger log = LogManager.getLogger(Core.class);
+	
+	// Program wide DEBUG flag. -- Deprecated, these flags will be removed and replaced with log4j!!! -- Cosmin Aug. 3, 2012.
+	@Deprecated public static final boolean DEBUG = false;
+	@Deprecated public static final boolean DEBUG_STACK_TRACE_MSG = false;
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-Core/src/am/app/mappingEngine/DefaultMatcherParameters.java

@@ -1,0 +1,198 @@
+package am.app.mappingEngine;
+
+import java.io.Serializable;
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.List;
+
+import am.app.mappingEngine.threaded.AbstractMatcherRunner;
+import am.app.ontology.Ontology;
+
+/**
+ * This class contains all the common matcher parameters:
+ * <ul>
+ * <li>The {@link #ontologies} to be matched.</li>
+ * <li>The {@link #threshold} and cardinality ({@link #maxSourceAlign},
+ * {@link #maxTargetAlign}).</li>
+ * <li>Parameters to control threaded execution of the matching algorithm (
+ * {@link #threadedExecution}, {@link #threadedOverlap},
+ * {@link #threadedExecution}).
+ * <li>Other experimental parameters.</li>
+ * </ul>
+ * 
+ * @author Cosmin Stroe <cstroe@gmail.com>
+ * 
+ */
+public class DefaultMatcherParameters implements Serializable {
+
+	private static final long serialVersionUID = -5278587933670353897L;
+	
+	/**
+	 * <p>
+	 * If this list contains two ontologies, the first ontology is taken to be
+	 * the source ontology and the second ontology is taken to be the target
+	 * ontology. If the list contains more than two ontologies, then it is
+	 * assumed that this is a multi-ontology matching task.
+	 * </p>
+	 */
+	public Ontology[] ontologies;
+	
+	// fields are initialized to their defaults.
+	public double threshold = 0.6;
+	public int maxSourceAlign = 1;
+	public int maxTargetAlign = 1;
+	
+	/**
+	 * <p>
+	 * Enable "completion mode" which tries to avoid matching concepts that have
+	 * been previously matched by an input matcher. The logic for the completion
+	 * mode is implemented in {@link AbstractMatcher}.
+	 * </p>
+	 * 
+	 * <p>
+	 * <b>Currently, completion mode does not work with threaded execution
+	 * mode.</b>
+	 * </p>
+	 */
+	public boolean completionMode = false;
+	
+	/**
+	 * Enable the storing of provenance for each mapping created. The individual
+	 * matching algorithm is currently responsible for creating the provenance,
+	 * although in the future a uniform way of representing provenance should be
+	 * introduced in AgreementMaker.
+	 */
+	public boolean storeProvenance = false; // whether the matcher stores provenance information for mappings.
+	
+	/**
+	 * Enable certain optimizations to deal with large ontologies. This feature
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-Core/src/am/app/mappingEngine/MatchingTask.java

@@ -1,0 +1,108 @@
+package am.app.mappingEngine;
+
+import java.util.ArrayList;
+import java.util.List;
+
+
+/**
+ * A matching task contains:
+ * 	- A matching algorithm.
+ * 	- Parameters for the matching algorithm.
+ * 	- A selection algorithm.
+ * 	- Parameters for the selection algorithm.
+ *  - The MatcherResult after the matcher has executed.
+ *  - The SelectionResult after the selection algorithm has executed.
+ * 
+ * @author Cosmin Stroe
+ *
+ * TODO: Make the property change support work. - Cosmin
+ */
+public class MatchingTask {
+	public AbstractMatcher 				matchingAlgorithm;
+	public DefaultMatcherParameters 	matcherParameters;
+	public SelectionAlgorithm 			selectionAlgorithm;
+	public DefaultSelectionParameters 	selectionParameters;
+	public MatcherResult				matcherResult;
+	public SelectionResult				selectionResult;
+	public int ID;
+	
+	public List<MatchingTask>			inputMatchingTasks;
+	
+	/**
+	 * A short label for this MatchingTask.
+	 */
+	public String shortLabel;
+	
+	/**
+	 * A longer description for this matching task.
+	 */
+	public String description;
+	
+	public MatchingTask(AbstractMatcher matcher, DefaultMatcherParameters matcherParams,
+						 SelectionAlgorithm selectionAlgorithm, DefaultSelectionParameters selectionParams) {
+		super();
+		
+		this.matchingAlgorithm = matcher;
+		this.matcherParameters = matcherParams;
+		this.selectionAlgorithm = selectionAlgorithm;
+		this.selectionParameters = selectionParams;
+	}
+		
+	/**
+	 * Run the matching algorithm.
+	 */
+	public void match() {
+		try {
+			matchingAlgorithm.setParameters(matcherParameters);
+			matchingAlgorithm.match();
+			matcherResult = matchingAlgorithm.getResult();
+		}
+		catch( Exception e ) {
+			e.printStackTrace();
+		}
+	}
+	
+	/**
+	 * After the matching algorithm runs, run the selection algorithm.
+	 */
+	public void select() {
+		try {
+			selectionParameters.inputResult = matcherResult;
+			selectionAlgorithm.setParameters(selectionParameters);
+			selectionAlgorithm.select();
+			selectionResult = selectionAlgorithm.getResult();
+		}
+		catch( Exception e ) {
+			e.printStackTrace();
+		}
+	}
+	
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-Core/src/am/app/mappingEngine/qualityEvaluation/metrics/ufl/shi/ContentionPoint.java

@@ -1,0 +1,102 @@
+package am.app.mappingEngine.qualityEvaluation.metrics.ufl.shi;
+
+
+import java.util.ArrayList;
+import java.util.List;
+
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.qualityEvaluation.AbstractQualityMetric;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+
+public class ContentionPoint  extends AbstractQualityMetric{
+		
+	private double threshold;
+	List<Mapping> lst=new ArrayList<>();
+	SimilarityMatrix ufl;
+	List<MatchingTask> amInput=new ArrayList<>();
+	
+	public ContentionPoint(SimilarityMatrix am, List<MatchingTask> inputMatchers, alignType type, double threshold)
+	{
+		super();
+		this.threshold=threshold;
+		this.ufl=am;
+		this.amInput=inputMatchers;
+		double sim=0.0;
+		int countP=0;
+		int countN=0;
+		for (int i=0;i<am.getRows();i++)
+			for(int j=0;j<am.getColumns();j++)
+			{
+				countP=0;
+				countN=0;
+				for (int k=0; k<inputMatchers.size();k++)
+				{
+					if (type.equals(alignType.aligningClasses))
+						sim=inputMatchers.get(k).matcherResult.getClassesMatrix().getSimilarity(i, j);
+					else
+						sim=inputMatchers.get(k).matcherResult.getPropertiesMatrix().getSimilarity(i, j);
+					
+					if(sim>threshold)
+						countP++;
+					else
+						countN++;
+				}
+				
+				if ((countP!=0) & (countN!=0))
+					lst.add(am.get(i, j));
+				
+			}
+		
+	}
+	
+	/**
+	 * @param type
+	 *            This parameter is ignored for this quality metric.
+	 */
+	@Override
+	public double getQuality(alignType type, int i, int j) 
+	{		
+
+		Mapping m=ufl.get(i, j);
+		if (!lst.contains(m))
+			return 1.0d;
+		
+		double max=Double.MIN_VALUE;
+		double p_max=Double.MIN_VALUE;
+		for (int k=0;k<amInput.size();k++)
+		{
+			double tmp=0;
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-Core/src/am/app/ontology/profiling/classification/OntologyClassifier.java

@@ -1,0 +1,1668 @@
+package am.app.ontology.profiling.classification;
+
+import java.io.BufferedReader;
+import java.io.DataInputStream;
+import java.io.File;
+import java.io.FileInputStream;
+import java.io.FileReader;
+import java.io.IOException;
+import java.io.InputStreamReader;
+import java.io.LineNumberReader;
+import java.util.Iterator;
+import java.util.LinkedList;
+import java.util.List;
+import java.util.Random;
+
+import weka.classifiers.Classifier;
+import weka.classifiers.Evaluation;
+import weka.classifiers.lazy.KStar;
+import weka.core.Attribute;
+import weka.core.FastVector;
+import weka.core.Instance;
+import weka.core.Instances;
+import weka.core.Utils;
+import am.app.Core;
+import am.app.ontology.Ontology;
+import am.app.ontology.ontologyParser.OntoTreeBuilder;
+import am.app.ontology.profiling.classification.trainingGeneration.OutputTrainingGenerator;
+import am.app.ontology.profiling.classification.trainingGeneration.Winner;
+import am.app.ontology.profiling.ontologymetrics.CoupleOntologyMetrics;
+import am.app.ontology.profiling.ontologymetrics.OntologyEvaluation;
+import am.app.ontology.profiling.ontologymetrics.OntologyMetrics;
+
+public class OntologyClassifier {
+
+    private FastVector fvClassVal;
+    private Classifier cModel;
+
+    public enum OAEI2011Configuration {
+        GENERAL_PURPOSE,
+        GENERAL_PURPOSE_ADVANCED,
+        GENERAL_PURPOSE_FILTERED,
+        LARGE_LEXICAL,
+        GENERAL_MULTI,
+        LARGE_LEXICAL_WITH_LOCALNAMES,;
+    }
+
+    /*
+	 * constructor of the object ontologyclassificator
+	 * 
+	 */
+    public OntologyClassifier(OutputTrainingGenerator o) {
+        LinkedList<String> classList = o.getClassList();
+        fvClassVal = new FastVector(classList.size());
+
+        for (Iterator<String> it = classList.iterator(); it.hasNext(); ) {
+            String string = (String) it.next();
+            fvClassVal.addElement(string);
+        }
+
+        cModel = (Classifier) new KStar();
+    }
+
+    public FastVector getFvClassVal() {
+        return fvClassVal;
+    }
+
+    public void setFvClassVal(FastVector fvClassVal) {
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-Core/src/am/app/ontology/profiling/classification/trainingGeneration/OutputTrainingGenerator.java

@@ -1,0 +1,427 @@
+package am.app.ontology.profiling.classification.trainingGeneration;
+
+import java.io.File;
+import java.io.FileNotFoundException;
+import java.io.FileOutputStream;
+import java.io.IOException;
+import java.io.PrintStream;
+import java.util.Iterator;
+import java.util.LinkedList;
+
+import javax.xml.parsers.DocumentBuilder;
+import javax.xml.parsers.DocumentBuilderFactory;
+import javax.xml.parsers.ParserConfigurationException;
+import javax.xml.transform.OutputKeys;
+import javax.xml.transform.Transformer;
+import javax.xml.transform.TransformerFactory;
+import javax.xml.transform.dom.DOMSource;
+import javax.xml.transform.stream.StreamResult;
+
+import org.w3c.dom.Document;
+import org.w3c.dom.Element;
+import org.w3c.dom.NodeList;
+import org.xml.sax.SAXException;
+
+
+
+
+public class OutputTrainingGenerator {
+
+	private LinkedList<String> classList;
+	private LinkedList<Result> resultList;
+	private LinkedList<Winner> winnerList;
+	
+	public OutputTrainingGenerator() {
+		this.classList = new LinkedList<String>();
+		this.resultList = new LinkedList<Result>();
+		this.winnerList = new LinkedList<Winner>();
+	}
+	
+	
+	public OutputTrainingGenerator(String fileName) throws IOException {
+		this.classList= new LinkedList<String>();
+		this.resultList = new LinkedList<Result>();
+		this.winnerList = new LinkedList<Winner>();
+		
+		// open and parse the benchmark XML file
+		//System.out.println("Reading batch file.");
+		File batchFile = new File( fileName );
+
+		DocumentBuilderFactory dbf = DocumentBuilderFactory.newInstance();
+		DocumentBuilder db = null;
+		Document doc= null;
+		try {
+			db = dbf.newDocumentBuilder();
+		} catch (ParserConfigurationException e) {
+			// TODO Auto-generated catch block
+			e.printStackTrace();
+		}
+
+		try {
+			doc = db.parse(batchFile);
+		} catch (SAXException e) {
+			// TODO Auto-generated catch block
+			e.printStackTrace();
+		}
+
+		doc.getDocumentElement().normalize();
+		//System.out.println("Root element " + doc.getDocumentElement().getNodeName());
+
+		
+
+
+		// parse the Classes
+		NodeList classNodeList = doc.getElementsByTagName("class");
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-Core/src/am/evaluation/clustering/ClusterFactoryDialog.java

@@ -1,0 +1,118 @@
+package am.evaluation.clustering;
+
+import java.awt.BorderLayout;
+import java.awt.FlowLayout;
+import java.awt.GridLayout;
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+import java.util.List;
+
+import javax.swing.JButton;
+import javax.swing.JCheckBox;
+import javax.swing.JDialog;
+import javax.swing.JPanel;
+
+import org.apache.log4j.LogManager;
+import org.apache.log4j.Logger;
+
+import am.app.mappingEngine.MatcherResult;
+import am.app.mappingEngine.MatchingTask;
+
+
+public class ClusterFactoryDialog extends JDialog implements ActionListener {
+
+	private static final long serialVersionUID = -6675553141084080729L;
+	
+	private static final Logger LOG = LogManager.getLogger(ClusterFactoryDialog.class);
+
+	private ClusteringParametersPanel clusterPanel = null;
+	
+	private JButton btnCancel;
+	private JButton btnOK;
+	private JCheckBox[] matcherCheckboxes;
+	private List<MatchingTask> matchers;
+	private boolean userCanceled = false;
+	
+	public ClusterFactoryDialog( ClusteringMethod method ) {
+		super();
+		
+		matchers = method.getAvailableMatchers();
+		
+		setLayout(new BorderLayout());
+		
+		// Build the matchers selection panel
+		matcherCheckboxes = new JCheckBox[matchers.size()];
+		JPanel selectionPanel = new JPanel();
+		
+		selectionPanel.setLayout( new GridLayout( matchers.size(), 1) );
+		
+		for( int i = 0; i < matchers.size(); i++ ) {
+			MatchingTask currentMatcher = matchers.get(i);
+			JCheckBox chkMatcher = new JCheckBox(currentMatcher.getShortLabel());
+			chkMatcher.setSelected(true);
+			matcherCheckboxes[i] = chkMatcher;
+			selectionPanel.add(chkMatcher);
+		}
+		
+		add(selectionPanel, BorderLayout.NORTH);		
+		
+		
+		if( method != null ) {
+			clusterPanel = method.getParametersPanel();
+			if( clusterPanel != null ) add(clusterPanel, BorderLayout.CENTER);
+		}
+		
+		
+		btnCancel = new JButton("Cancel");
+		btnCancel.addActionListener(this);
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-Core/src/am/evaluation/clustering/ClusteringParameters.java

@@ -1,0 +1,17 @@
+package am.evaluation.clustering;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import am.app.mappingEngine.MatchingTask;
+
+public abstract class ClusteringParameters {
+	
+	private List<MatchingTask> matchersToConsider = new ArrayList<MatchingTask>();
+	
+	public ClusteringParameters() {}
+	
+	public void addMatcher(MatchingTask abstractMatcher) { matchersToConsider.add(abstractMatcher); }
+	public List<MatchingTask> getMatchers() { return matchersToConsider; }
+	public void setMatchers( List<MatchingTask> m ) { matchersToConsider = m; }
+}

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-Core/src/am/evaluation/clustering/globalfixed/GlobalFixedMethod.java

@@ -1,0 +1,55 @@
+package am.evaluation.clustering.globalfixed;
+
+import java.util.List;
+
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MatchingTask;
+import am.evaluation.clustering.Cluster;
+import am.evaluation.clustering.ClusteringMethod;
+import am.evaluation.clustering.ClusteringParameters;
+import am.evaluation.clustering.ClusteringParametersPanel;
+
+public class GlobalFixedMethod extends ClusteringMethod {
+
+	public GlobalFixedMethod(List<MatchingTask> availableMatchers) {
+		super(availableMatchers);
+	}
+
+	@Override
+	public ClusteringParameters getParameters() {
+		// TODO Auto-generated method stub
+		return null;
+	}
+
+	@Override
+	public ClusteringParametersPanel getParametersPanel() {
+		// TODO Auto-generated method stub
+		return null;
+	}
+
+	@Override
+	public Cluster<Mapping> getCluster(int row, int col, alignType t) {
+		// TODO Auto-generated method stub
+		return null;
+	}
+
+	@Override
+	public void setParameters(ClusteringParameters params) {
+		// TODO Auto-generated method stub
+		
+	}
+
+	@Override
+	public Cluster<Mapping> getCluster(Mapping mapping) {
+		// TODO Auto-generated method stub
+		return null;
+	}
+
+	@Override
+	public void cluster() {
+		// TODO Auto-generated method stub
+		
+	}
+
+}

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-Core/src/am/evaluation/clustering/localByThreshold/LocalByThresholdMethod.java

@@ -1,0 +1,137 @@
+package am.evaluation.clustering.localByThreshold;
+
+import java.awt.Point;
+import java.util.ArrayList;
+import java.util.List;
+import java.util.TreeSet;
+
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+import am.evaluation.clustering.Cluster;
+import am.evaluation.clustering.ClusteringMethod;
+import am.evaluation.clustering.ClusteringParameters;
+import am.evaluation.clustering.ClusteringParametersPanel;
+import am.utility.PointComparator;
+
+/**
+ * This method implements the local-by-threshold clustering method.
+ * 
+ * @author Cosmin Stroe
+ */
+public class LocalByThresholdMethod extends ClusteringMethod {
+
+	protected LocalByThresholdParameters 		params;
+	
+	public LocalByThresholdMethod(List<MatchingTask> availableMatchers) {
+		super(availableMatchers);
+		
+	}
+	
+	@Override 
+	public void cluster() {}
+	
+	@Override public void setParameters(ClusteringParameters params) { this.params = (LocalByThresholdParameters) params; }
+	@Override public ClusteringParameters getParameters() { return params; }
+	@Override public ClusteringParametersPanel getParametersPanel() { return new LocalByThresholdPanel(); }
+
+	@Override
+	public Cluster<Mapping> getCluster(int row, int col, alignType t) {
+
+		// build all the sets
+		ArrayList<TreeSet<Point>> setList = new ArrayList<TreeSet<Point>>();
+		
+		List<MatchingTask> matcherList = params.getMatchers();
+		for( MatchingTask m : matcherList ) {
+			setList.add( buildSet( m, t, row, col ) );
+		}
+		
+		// find the intersection of the sets
+		TreeSet<Point> intersectionSet = null;
+		
+		if( setList.size() == 0 ) {
+			// no sets, leave intersectionSet == null
+		}
+		if( setList.size() == 1 ) {
+			// one set
+			intersectionSet = setList.get(0);
+		} else {
+			// more than one set, must compute intersection.
+			intersectionSet = computeIntersection( setList.get(0), setList.get(1) ); // the first two sets
+			
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-Core/src/am/evaluation/disagreement/variance/VarianceDisagreement.java

@@ -1,0 +1,92 @@
+package am.evaluation.disagreement.variance;
+
+import static am.evaluation.disagreement.variance.VarianceComputation.computeVariance;
+
+import java.util.List;
+
+import am.app.Core;
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.similarityMatrix.ArraySimilarityMatrix;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+import am.evaluation.disagreement.DisagreementCalculationMethod;
+import am.evaluation.disagreement.DisagreementParameters;
+import am.evaluation.disagreement.DisagreementParametersPanel;
+
+public class VarianceDisagreement extends DisagreementCalculationMethod {
+
+	private VarianceDisagreementParameters params;
+
+	@Override
+	public DisagreementParametersPanel getParametersPanel() { return new VarianceDisagreementPanel(); }
+
+	@Override public DisagreementParameters getParameters() {	return params; }
+	@Override public void setParameters(DisagreementParameters params) { 
+		this.params = (VarianceDisagreementParameters) params; 
+	}
+	
+	@Override
+	public SimilarityMatrix getDisagreementMatrix(alignType t) {
+		List<MatchingTask> matchersToConsider = params.getMatchers();
+		double weight=0.0;
+		if( matchersToConsider.size() == 0 ) return null;
+		
+		if( t == alignType.aligningClasses ) {
+		
+			MatchingTask firstTask = matchersToConsider.get(0);
+			
+			int rows = firstTask.matcherResult.getClassesMatrix().getRows();
+			int cols = firstTask.matcherResult.getClassesMatrix().getColumns();
+			
+			SimilarityMatrix disagreementMatrix = new ArraySimilarityMatrix(firstTask.matcherParameters.getSourceOntology(), 
+					firstTask.matcherParameters.getTargetOntology(), alignType.aligningClasses );
+			
+			for( int i = 0; i < rows; i++ ) {
+				for( int j = 0; j < cols; j++ ) {
+					
+					double[] signatureVector = new double[matchersToConsider.size()];
+					for( int k = 0; k < matchersToConsider.size(); k++ ) {
+						signatureVector[k] = matchersToConsider.get(k).matcherResult.getClassesMatrix().getSimilarity(i, j);
+					}
+					
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-Core/src/am/parsing/AlignmentOutput.java

@@ -1,0 +1,312 @@
+package am.parsing;
+
+import java.io.File;
+import java.io.FileNotFoundException;
+import java.io.IOException;
+import java.io.RandomAccessFile;
+import java.io.Writer;
+import java.util.ArrayList;
+
+import org.apache.commons.lang.StringEscapeUtils;
+
+import am.app.mappingEngine.Alignment;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.Mapping.MappingRelation;
+
+import com.hp.hpl.jena.rdf.model.Resource;
+
+public class AlignmentOutput
+{
+    private Alignment<Mapping> alignmentSet = null;
+    private RandomAccessFile raf = null;  // Why is this a RandomAccessFile? Can be a BufferedWriter for faster writing. - Cosmin.
+    private String filepath = null;
+    private ArrayList<String> writeList = null;  // TODO: REMOVE THIS!!!!!! VERY VERY VERY INEFFICIENT USE OF MEMORY - Cosmin.
+    private StringBuilder buffer;
+
+    /**
+     * This constructor is used for saving as a String, not to a file.  Use only with compileString().
+     * @param as The set of mappings between two ontologies.
+     */
+    public AlignmentOutput( Alignment<Mapping> as ) {
+    	alignmentSet = as;
+    	filepath = "";
+    	buffer = new StringBuilder();
+    }
+    
+    /**
+     * This method saves the AlignmentSet in OAEI format in a string in memory, then returns the string.
+     * @param onto1 The URI of the source ontology. Can be empty.
+     * @param onto2 The URI of the target ontology. Can be empty.
+     * @param uri1 The URI of the source ontology.
+     * @param uri2 The URI of the target ontology.
+     * @return The OAEI formatted XML string.
+     */
+    public String compileString(String onto1, String onto2, String uri1, String uri2)
+    {
+        stringNS();
+        stringStart("yes", "0", "11", onto1, onto2, uri1, uri2);
+        for (int i = 0, n = alignmentSet.size(); i < n; i++) {
+            Mapping alignment = (Mapping) alignmentSet.get(i);
+            String e1 = alignment.getEntity1().getUri();
+            String e2 = alignment.getEntity2().getUri();
+            String measure = Double.toString(alignment.getSimilarity());
+            String prov = alignment.getProvenance();
+            if( prov != null ) stringElement(e1, e2, measure, prov);
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UI/src/main/java/am/ui/MatchersChooser.java

@@ -1,0 +1,283 @@
+package am.ui;
+
+import java.awt.BorderLayout;
+import java.awt.FlowLayout;
+import java.awt.GridLayout;
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+import java.util.ArrayList;
+import java.util.List;
+
+import javax.swing.AbstractAction;
+import javax.swing.Action;
+import javax.swing.ButtonGroup;
+import javax.swing.InputMap;
+import javax.swing.JButton;
+import javax.swing.JCheckBox;
+import javax.swing.JComponent;
+import javax.swing.JDialog;
+import javax.swing.JLabel;
+import javax.swing.JPanel;
+import javax.swing.JRadioButton;
+import javax.swing.JRootPane;
+import javax.swing.KeyStroke;
+
+import am.app.Core;
+import am.app.mappingEngine.MatchingTask;
+
+
+/**
+ * This class implements functions to allow developers a quick and easy
+ * dialog for selecting matchers.
+ * 
+ * @author cosmin
+ *
+ */
+
+public class MatchersChooser {
+
+	/**
+	 * This function presents a dialog to the user with a checkbox for each
+	 * active matcher in the system.  The user then selects the checkboxes
+	 * and a list of the matchers corresponding to the checkboxes is returned.
+	 * @return Null if the dialog is canceled.  Empty list if nothing is selected.
+	 */
+	public static List<MatchingTask> getManyMatchers(String message) {
+		
+		MatchersChooserCheckboxPanel checkBoxPanel = new MatchersChooserCheckboxPanel();
+		MatchersChooserDialog dialog = new MatchersChooserDialog(checkBoxPanel);
+		dialog.setMessage(message);
+		dialog.setVisible(true);
+		
+		return dialog.getMatchers();
+	}
+	
+	/**
+	 * This function presents a radio button dialog of all the matchers
+	 * in the system so the user can choose a single one.
+	 * @return Null if the dialog is canceled, or if nothing is selected.
+	 */
+	public static MatchingTask getOneMatcher(String message) {
+		MatchersChooserRadioPanel radioPanel = new MatchersChooserRadioPanel();
+		MatchersChooserDialog dialog = new MatchersChooserDialog(radioPanel);
+		dialog.setMessage(message);
+		dialog.setVisible(true);
+		
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UI/src/main/java/am/visualization/ClusteringEvaluation/ClusteringEvaluationPanel.java

@@ -1,0 +1,86 @@
+package am.visualization.ClusteringEvaluation;
+
+import java.awt.BorderLayout;
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+import java.beans.PropertyChangeEvent;
+import java.beans.PropertyChangeListener;
+import java.util.List;
+
+import javax.swing.JButton;
+
+import am.app.mappingEngine.AbstractMatcher;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MatcherResult;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.ReferenceEvaluationData;
+import am.app.mappingEngine.referenceAlignment.ReferenceEvaluator;
+import am.evaluation.clustering.Cluster;
+import am.evaluation.clustering.localByThreshold.LocalByThresholdMethod;
+import am.evaluation.clustering.localByThreshold.LocalByThresholdParameters;
+import am.ui.MatchersChooser;
+import am.ui.api.impl.AMTabSupportPanel;
+
+public class ClusteringEvaluationPanel 	extends AMTabSupportPanel 
+										implements ActionListener, PropertyChangeListener {
+
+	private static final long serialVersionUID = -5491977894442159008L;
+
+	public ClusteringEvaluationPanel() {
+		super("Clustering Evaluation", "A panel to evaluate our clustering algorithms.");
+		initComponents();
+	}
+	
+	private void initComponents() {
+		
+		setLayout( new BorderLayout() );
+		
+		JButton btnStart = new JButton("Start");
+		btnStart.addActionListener(this);
+		btnStart.setActionCommand("start");
+		
+		add( btnStart, BorderLayout.NORTH );
+	}
+
+	@Override
+	public void actionPerformed(ActionEvent e) {
+		if( e.getActionCommand() == "start" ) {
+			// start button was pressed
+			MatchingTask reference  = MatchersChooser.getOneMatcher("Please select the reference alignment matcher:");
+			List<MatchingTask> matchers = MatchersChooser.getManyMatchers("Please select the matchers for computing the clusters:");
+			
+			evaluateLocalbyThresholdClustering( reference, matchers);
+		}
+		
+	}
+
+	private void evaluateLocalbyThresholdClustering(MatchingTask reference, List<MatchingTask> matchers) {
+
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UI/src/main/java/am/visualization/MatcherAnalyticsEvent.java

@@ -1,0 +1,33 @@
+package am.visualization;
+
+import java.util.EventObject;
+
+public class MatcherAnalyticsEvent extends EventObject {
+
+	private static final long serialVersionUID = 4508844257680133138L;
+
+	public static enum EventType {
+		SELECT_MAPPING,  // implies that the payload is a Point, representing the row, and column of the mapping.
+		CLEAR_MAPPING_SELECTION, // unselect any mappings
+		SET_REFERENCE,	 // Set this matcher as the reference matcher.  Implies that the payload is an AbstractMatcher.
+		MATRIX_UPDATED,   // when a matrix is updated
+		DISPLAY_CLUSTER,	  // display a cluster, payload is inferred to be the cluster
+		CLEAR_CLUSTER,		// clear the cluster display
+		REMOVE_PLOT,			// remove the plot from the analytics panel
+		SET_FEEDBACK,		// set the feedback matcher that will be updated when the user generates feedback (payload == the matcher)
+		VIEW_ORDERED_PLOT,	// event is fired when adding the ordered matrix plot (payload == MatrixPlotPanel of the unordered plot)
+		LOG_MESSAGE
+	}
+	
+	public final EventType type;
+	public final Object payload;
+	
+	public MatcherAnalyticsEvent(Object source, EventType type, Object payload) {
+		super(source);
+		this.type = type;
+		this.payload = payload;
+	}
+	
+	
+	
+}

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UI/src/main/java/am/visualization/MatcherAnalyticsEventListener.java

@@ -1,0 +1,10 @@
+package am.visualization;
+
+import am.app.mappingEngine.MatchingTask;
+
+public interface MatcherAnalyticsEventListener {
+
+	public void receiveEvent(MatcherAnalyticsEvent e);
+	
+	public MatchingTask getMatcher();
+}

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UI/src/main/java/am/visualization/MatcherAnalyticsPanel.java

@@ -1,0 +1,687 @@
+package am.visualization;
+
+import java.awt.BorderLayout;
+import java.awt.Color;
+import java.awt.FlowLayout;
+import java.awt.Point;
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+import java.util.ArrayList;
+import java.util.List;
+
+import javax.swing.BorderFactory;
+import javax.swing.Box;
+import javax.swing.JButton;
+import javax.swing.JComboBox;
+import javax.swing.JLabel;
+import javax.swing.JPanel;
+import javax.swing.JScrollPane;
+import javax.swing.JTextField;
+import javax.swing.SwingUtilities;
+
+import am.app.Core;
+import am.app.mappingEngine.AbstractMatcher;
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.Alignment;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MatcherChangeListener;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.MatchingTaskChangeEvent;
+import am.app.mappingEngine.similarityMatrix.ArraySimilarityMatrix;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+import am.app.ontology.Node;
+import am.app.ontology.Ontology;
+import am.evaluation.clustering.Cluster;
+import am.evaluation.clustering.ClusterFactory;
+import am.evaluation.clustering.ClusterFactory.ClusteringType;
+import am.evaluation.clustering.ClusteringMethod;
+import am.evaluation.disagreement.DisagreementCalculationDialog;
+import am.evaluation.disagreement.DisagreementCalculationMethod;
+import am.evaluation.disagreement.variance.VarianceDisagreement;
+import am.ui.UIUtility;
+import am.utility.WrapLayout;
+import am.visualization.MatcherAnalyticsEvent.EventType;
+import am.visualization.matrixplot.MatrixPlotPanel;
+import am.visualization.matrixplot.OrderedMatrixPlot;
+
+public class MatcherAnalyticsPanel extends JPanel implements MatcherChangeListener, MatcherAnalyticsEventDispatch, ActionListener {
+	
+	private static final long serialVersionUID = -5538266168231508803L;
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UI/src/main/java/am/visualization/matrixplot/MatrixPlotPanel.java

@@ -1,0 +1,457 @@
+package am.visualization.matrixplot;
+
+import java.awt.Color;
+import java.awt.Point;
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+import java.awt.event.MouseEvent;
+import java.awt.event.MouseListener;
+
+import javax.swing.BorderFactory;
+import javax.swing.GroupLayout;
+import javax.swing.ImageIcon;
+import javax.swing.JLabel;
+import javax.swing.JPanel;
+import javax.swing.SpringLayout;
+import javax.swing.SwingUtilities;
+
+import am.Utility;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+import am.evaluation.clustering.Cluster;
+import am.evaluation.clustering.ClusterFactory;
+import am.evaluation.clustering.ClusterFactory.ClusteringType;
+import am.ui.api.impl.AMTabSupportPanel;
+import am.visualization.Gradient;
+import am.visualization.MatcherAnalyticsEvent;
+import am.visualization.MatcherAnalyticsEvent.EventType;
+import am.visualization.MatcherAnalyticsEventDispatch;
+import am.visualization.MatcherAnalyticsEventListener;
+
+public class MatrixPlotPanel extends AMTabSupportPanel 
+                             implements MouseListener, MatcherAnalyticsEventListener, ActionListener {
+
+	private static final long serialVersionUID = -8579270363759208673L;
+
+	private final MatcherAnalyticsEventDispatch dispatch;
+	private final MatrixPlot plot;
+	private final JLabel lblName;
+	private final JLabel lblSimilaritySelected;
+	private final MatchingTask matchingTask;
+	
+	private MatchingTask referenceMatcher = null;
+
+	private String tooltip;
+
+	private String label;
+
+	private ImageIcon icon; 
+	
+	//private boolean popupMenuActive = false;
+	
+	//private VisualizationType type;
+	
+	public MatrixPlotPanel(MatchingTask a, SimilarityMatrix mtx, MatcherAnalyticsEventDispatch d ) {
+		super("MatrixPlot");
+		dispatch = d;
+
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UI/src/main/java/am/visualization/matrixplot/OrderedMatrixPlot.java

@@ -1,0 +1,187 @@
+package am.visualization.matrixplot;
+
+import java.awt.Color;
+import java.awt.Graphics;
+import java.awt.Graphics2D;
+import java.util.ArrayList;
+import java.util.Collections;
+import java.util.List;
+
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+import am.app.ontology.Node;
+import am.app.ontology.Ontology;
+
+import com.hp.hpl.jena.ontology.OntClass;
+import com.hp.hpl.jena.ontology.OntProperty;
+
+public class OrderedMatrixPlot extends MatrixPlot {
+
+	private static final long serialVersionUID = -6639837299305451033L;
+	
+	int[] rowTransform;
+	int[] colTransform;
+	
+	int[] rowInverseTransform;
+	int[] colInverseTransform;
+	
+	ArrayList<Integer> colLines;
+	ArrayList<Integer> rowLines;	
+	
+	public OrderedMatrixPlot(MatchingTask matcher, SimilarityMatrix mtx, MatrixPlotPanel mpnl) {
+		super(matcher, mtx, mpnl);
+		autoDrawCrosshairs = false;
+		
+	}
+	
+	private void createColTransform() {
+		Ontology targetOntology = matrix.getTargetOntology();
+		List<Node> nodes = null;
+		
+		colLines = new ArrayList<Integer>();
+		
+		if(matrix.getAlignType() == alignType.aligningClasses)
+			nodes = targetOntology.getClassesList();
+		else nodes = targetOntology.getPropertiesList();
+		
+		colTransform = new int[nodes.size()];
+		colInverseTransform = new int[nodes.size()];
+		
+//		System.out.println("PREORDERING");
+//		
+//		for (int i = 0; i < nodes.size(); i++) {
+//			System.out.println(nodes.get(i).getLocalName());
+//		}
+		
+		List<Node> ordered = new ArrayList<Node>(nodes);
+		Collections.sort(ordered, new NodeComparator());
+		
+//		System.out.println("POSTORDERING");
+//		
+//		for (int i = 0; i < ordered.size(); i++) {
+//			System.out.println(ordered.get(i).getLocalName());
+//		}
+		
+		createTransformAndLines(colLines, ordered, colTransform);
+		
+		boolean found;
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UIGlue/src/main/java/am/ui/glue/BatchModeMenuItem.java

@@ -1,0 +1,111 @@
+package am.ui.glue;
+
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+import java.io.File;
+import java.io.FileInputStream;
+import java.io.IOException;
+import java.util.prefs.Preferences;
+
+import javax.swing.JFileChooser;
+import javax.swing.JMenuItem;
+import javax.swing.JOptionPane;
+import javax.swing.filechooser.FileFilter;
+
+import am.extension.batchmode.api.BatchModeFileReader;
+import am.extension.batchmode.api.BatchModeRunner;
+import am.extension.batchmode.api.BatchModeSpec;
+import am.ui.UICore;
+import am.ui.UIMenu;
+import am.ui.api.AMMenuItem;
+import org.osgi.framework.ServiceReference;
+
+public class BatchModeMenuItem extends JMenuItem implements AMMenuItem {
+
+	private static final long serialVersionUID = -7679368085474956610L;
+	
+	private static final String PREF_LAST_FILE = "BATCHMODE_LAST_FILE";
+	
+	
+	public BatchModeMenuItem() {
+		super("Batch Mode");
+		
+		addActionListener(new ActionListener() {
+			@Override
+			public void actionPerformed(ActionEvent e) {
+				BatchModeMenuItem.this.runBatchMode();
+			}
+		});
+	}
+	
+	@Override public String getMenuLocation() { return UIMenu.MENU_MATCHERS + "/"; }
+	@Override public JMenuItem getMenuItem() { return this; }
+	
+	/**
+	 * Asks for an input for the BatchModeFile and then runs the batch mode.
+	 */
+	private void runBatchMode() {
+		
+		Preferences prefs = Preferences.userNodeForPackage(this.getClass());
+		String previousFile = prefs.get(PREF_LAST_FILE, "");
+		
+		// ask user to select the xml file
+		final JFileChooser fd = new JFileChooser();
+		
+		if( !previousFile.isEmpty() )
+			fd.setSelectedFile(new File(previousFile));
+		
+		fd.setDialogTitle("Select BatchMode JSON File");
+		
+		FileFilter xmlFileFilter = new FileFilter() {
+			@Override public boolean accept(File f) {
+				return f.isDirectory() || f.getName().toLowerCase().endsWith(".json");
+			}
+
+			@Override public String getDescription() {
+				return "JSON File (*.json)";
+			}
+		};
+		
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/multiUserFeedback/initialization/SignatureVectorStats.java

@@ -1,0 +1,94 @@
+package am.extension.multiUserFeedback.initialization;
+
+import java.io.BufferedWriter;
+import java.io.File;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.util.HashMap;
+import java.util.List;
+
+import am.app.Core;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+import am.extension.multiUserFeedback.experiment.MUExperiment;
+import am.extension.userfeedback.utility.UFLutility;
+
+public class SignatureVectorStats {
+	
+	MUExperiment experiment;
+	HashMap<Integer, List<Mapping>> cluster=new HashMap<>();
+	public SignatureVectorStats (MUExperiment exp)
+	{
+		this.experiment=exp;
+	}
+	
+	public void printSV(SimilarityMatrix sm, alignType type) throws IOException
+	{
+		
+		File directory = new File(Core.getInstance().getRoot() + "settings/tmp/SignatureVector");
+		// if file doesnt exists, then create it
+		if (!directory.exists()) directory.mkdirs();
+		
+		File file = new File( directory.getAbsolutePath() + "/similarityMatrix"+type.toString()+".txt");
+		if( !file.exists() ) {
+			file.createNewFile();
+		}
+
+		FileWriter fw = new FileWriter(file.getAbsoluteFile());
+		BufferedWriter bw = new BufferedWriter(fw);
+
+		int row=sm.getRows();
+		int col=sm.getColumns();
+		for (int i=0;i<row;i++)
+		{
+			for(int j=0;j<col;j++)
+			{
+				Mapping mp = sm.get(i, j);
+				double[] sv = UFLutility.getSignatureVector(mp, experiment.initialMatcher.getComponentMatchers());
+				if (UFLutility.validSsv(sv))
+				{
+
+
+					for (int k=0;k<sv.length;k++)
+					{
+						if(k<sv.length-1)
+							bw.write(sv[k]+",");
+						else
+							bw.write(sv[k]+"");
+					}
+					bw.write("\n");
+
+				}
+
+				
+			}
+		}
+
+		bw.close();
+		fw.close();
+	}
+	
+	private void clusterize()
+	{
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/multiUserFeedback/propagation/ServerFeedbackPropagation.java

@@ -1,0 +1,414 @@
+package am.extension.multiUserFeedback.propagation;
+/*
+ * 	Francesco Loprete December 2013
+ */
+
+
+import java.io.IOException;
+import java.util.List;
+
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.Alignment;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.qualityEvaluation.metrics.InverseOf;
+import am.app.mappingEngine.qualityEvaluation.metrics.ufl.ConsensusQuality;
+import am.app.mappingEngine.qualityEvaluation.metrics.ufl.PropagationImpactMetric;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+import am.app.mappingEngine.similarityMatrix.SparseMatrix;
+import am.app.ontology.Node;
+import am.extension.multiUserFeedback.experiment.MUExperiment;
+import am.extension.userfeedback.UserFeedback.Validation;
+import am.extension.userfeedback.MLutility.WekaUtility;
+import am.extension.userfeedback.experiments.UFLExperimentParameters.Parameter;
+import am.extension.userfeedback.propagation.FeedbackPropagation;
+import am.extension.userfeedback.rankingStrategies.MultiSelectedRanking;
+import am.extension.userfeedback.utility.UFLutility;
+
+
+public class ServerFeedbackPropagation extends FeedbackPropagation<MUExperiment>{
+
+
+	final double log_multiplier=1.2;
+	final double dist_perc=3.0;
+	
+	private MUExperiment experiment;
+	private List<MatchingTask> inputMatchers;
+	
+	public static final String PROPAGATION_NONE 		= "none";
+	public static final String PROPAGATION_EUCLIDEAN 	= "euzero";
+	public static final String PROPAGATION_LOG 			= "logdist";
+	public static final String PROPAGATION_REGRESSION 	= "regression";
+	public static final String PROPAGATION_QUALITY 		= "quality";
+	public static final String PROPAGATION_CRC 	= "crc";
+	
+	private double[] getSignatureVector(Mapping mp)
+	{
+		int size=inputMatchers.size();
+		Node sourceNode=mp.getEntity1();
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/multiUserFeedback/selection/BMCandidateSelection.java

@@ -1,0 +1,345 @@
+package am.extension.multiUserFeedback.selection;
+
+import java.util.ArrayList;
+import java.util.Collections;
+import java.util.List;
+
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.Alignment;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MappingSimilarityComparator;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+import am.evaluation.disagreement.variance.VarianceDisagreement;
+import am.evaluation.disagreement.variance.VarianceDisagreementParameters;
+import am.extension.multiUserFeedback.experiment.BMexperiment;
+import am.extension.userfeedback.selection.CandidateSelection;
+
+public class BMCandidateSelection extends CandidateSelection<BMexperiment>{
+	private String id;
+	private SimilarityMatrix classesMatrix;
+	private SimilarityMatrix propertiesMatrix;
+	private final double weight_um=0.5;
+	private final double weight_mm=0.3;
+	private BMexperiment experiment;
+	List<Mapping> allRanked=new ArrayList<Mapping>();
+	
+	@Override
+	public void rank(BMexperiment exp) {
+		this.experiment=exp;
+
+		//Inizialization
+		classesMatrix = experiment.getUflClassMatrix();
+		propertiesMatrix = experiment.getUflPropertyMatrix();
+		
+		//one time ranking methods
+		if(exp.getIterationNumber() == 1)
+		{
+			uncertainMappingRetrieval();
+		}
+		//every time ranking methods
+		almostCertainMappingRetrieval();
+		disagreementRanking();
+				
+		String id = Integer.toString(experiment.currentUser);
+		Mapping m;
+		switch (experiment.usersGroup.get(id)) 
+		{
+    	case 0:  
+    		m = getCandidateMapping(id, allRanked);
+    		if( m != null ) {
+    			selectedMapping = m;
+    			break;
+    		};
+        case 1:  
+        	m = getCandidateMapping(id, experiment.uncertainRanking);
+            if( m != null ) {
+            	selectedMapping = m;
+            	break;
+            }
+        case 2:  
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/multiUserFeedback/selection/ParametricCandidateSelection.java

@@ -1,0 +1,124 @@
+package am.extension.multiUserFeedback.selection;
+
+import java.util.Arrays;
+import java.util.List;
+
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.Mapping;
+import am.app.ontology.Ontology;
+import am.extension.multiUserFeedback.experiment.MUExperiment;
+import am.extension.userfeedback.experiments.UFLExperimentParameters.Parameter;
+import am.extension.userfeedback.rankingStrategies.RevalidationRanking;
+import am.extension.userfeedback.rankingStrategies.StrategyInterface;
+import am.extension.userfeedback.selection.CandidateSelection;
+
+public class ParametricCandidateSelection extends CandidateSelection<MUExperiment> {
+	
+	MUExperiment experiment;
+	int[] count={0,0,0};
+	int total=0;
+	
+	protected StrategyInterface[] strategies;
+	
+	public void setStrategies(StrategyInterface ... strategies) {
+		this.strategies = strategies;
+		
+		// compute all selection percentages
+		double specifiedPercentage = 0;
+		int notSpecifiedCount = 0;
+		for(StrategyInterface st : strategies) {
+			if( st.getPercentage() > 0d ) { 
+				specifiedPercentage += st.getPercentage();
+			}
+			else {
+				notSpecifiedCount++;
+			}
+		}
+		
+		double leftOverPercentage = 1.0 - specifiedPercentage;
+		if( leftOverPercentage > 0d ) {
+			double balancedPercentage = leftOverPercentage / notSpecifiedCount;
+			for(StrategyInterface st : strategies) {
+				if( st.getPercentage() == 0d )
+					st.setPercentage(balancedPercentage);
+			}
+		}
+
+		Arrays.sort(strategies);
+	}
+	
+	@Override
+	public void rank(MUExperiment exp) {
+		this.experiment=exp;
+		
+		total = 0;
+		for( StrategyInterface currentStrategy : strategies ) {
+			total += currentStrategy.getCount();
+		}
+		
+		boolean staticCS = experiment.setup.parameters.getBooleanParameter(Parameter.STATIC_CANDIDATE_SELECTION);
+		
+		for( StrategyInterface currentStrategy : strategies ) {
+			double currentRate = total == 0 ? 0d : currentStrategy.getCount() / (double)total;
+			if( currentRate <= currentStrategy.getPercentage() ) {
+				currentStrategy.incrementCount();
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/multiUserFeedback/selection/ServerCandidateSelection.java

@@ -1,0 +1,367 @@
+package am.extension.multiUserFeedback.selection;
+
+import java.util.ArrayList;
+import java.util.Collections;
+import java.util.HashSet;
+import java.util.List;
+
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.Alignment;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MappingSimilarityComparator;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.qualityEvaluation.metrics.ufl.CrossCountQuality;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+import am.app.mappingEngine.similarityMatrix.SparseMatrix;
+import am.evaluation.disagreement.variance.VarianceDisagreement;
+import am.evaluation.disagreement.variance.VarianceDisagreementParameters;
+import am.extension.multiUserFeedback.experiment.MUExperiment;
+import am.extension.userfeedback.UserFeedback.Validation;
+
+public class ServerCandidateSelection extends MUCandidateSelection<MUExperiment> {
+	
+	MUExperiment experiment;
+	private SimilarityMatrix classesMatrix;
+	private SimilarityMatrix propertiesMatrix;
+	private final double weight_um=0.5;
+	private final int overlapping=3;
+	
+	List<Mapping> allRanked=new ArrayList<Mapping>();
+	
+	public ServerCandidateSelection(){
+		super();
+	}
+	
+	@Override
+	public void rank(MUExperiment exp, String id) {
+		this.experiment=exp;
+		inizialization();
+		
+		uncertainMappingRetrieval();
+		//almostCertainMappingRetrieval();
+		disagreementRanking();
+		
+//		Mapping m;
+//		List<Mapping> mList=new ArrayList<Mapping>();
+		int users=experiment.usersGroup.size();
+		
+		HashSet<Integer> mpCheck=new HashSet<Integer>();
+		if (experiment.getIterationNumber()>0)
+			while(mpCheck.size()<overlapping)
+				mpCheck.add((int) (Math.random()*users));
+		
+		done();
+	}
+
+	@Override
+	public List<Mapping> getRankedMappings(alignType typeOfRanking, String id) {
+		// TODO Auto-generated method stub
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/multiUserFeedback/storage/FeedbackAgregation.java

@@ -1,0 +1,59 @@
+package am.extension.multiUserFeedback.storage;
+
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+
+import javax.swing.SwingUtilities;
+import javax.swing.event.EventListenerList;
+
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+import am.extension.userfeedback.UserFeedback.Validation;
+import am.extension.userfeedback.experiments.UFLExperiment;
+import am.extension.userfeedback.ui.UFLControlGUI;
+
+public abstract class FeedbackAgregation <T extends UFLExperiment>{
+	SimilarityMatrix classes;
+	SimilarityMatrix properties;
+	Mapping candidateMapping;
+	Validation userFeedback;
+	EventListenerList listeners;  // list of listeners for this class
+	
+	public FeedbackAgregation() {
+		listeners = new EventListenerList();
+	}
+	public abstract void addFeedback(T exp);
+	
+	public abstract double[][] getTrainingSet(alignType type, String quantity);
+	
+	public void addActionListener( ActionListener l ) {
+		listeners.add(ActionListener.class, l);
+	}
+	
+	
+	protected void fireEvent( ActionEvent e ) {
+		final ActionEvent evt = e;
+		SwingUtilities.invokeLater(new Runnable() {
+			@Override
+			public void run() {
+				ActionListener[] actionListeners = listeners.getListeners(ActionListener.class);
+				
+				for( int i = actionListeners.length-1; i >= 0; i-- ) {
+					actionListeners[i].actionPerformed(evt);
+				}
+			}
+		});
+		
+	}
+	
+	public Mapping getCandidateMapping() {
+		return candidateMapping;
+	}
+	
+	protected void done() {
+		ActionEvent e = new ActionEvent(this, 0, UFLControlGUI.ActionCommands.FEEDBACK_AGREGATION_DONE.name() );
+		fireEvent(e);
+	}
+	
+}

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/multiUserFeedback/storage/ServerFeedbackAggregation.java

@@ -1,0 +1,270 @@
+package am.extension.multiUserFeedback.storage;
+
+
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.Collections;
+import java.util.Comparator;
+import java.util.LinkedList;
+import java.util.List;
+
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.Alignment;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+import am.app.mappingEngine.similarityMatrix.SparseMatrix;
+import am.app.ontology.Node;
+import am.extension.multiUserFeedback.experiment.MUExperiment;
+import am.extension.userfeedback.UserFeedback.Validation;
+import am.extension.userfeedback.experiments.UFLExperimentParameters.Parameter;
+
+public class ServerFeedbackAggregation extends FeedbackAgregation<MUExperiment>{
+	
+	private MUExperiment experiment;
+
+	private final double cm_upper_threshold=0.89d;
+	private final double cm_lower_threshold=0.1d;
+	
+	//Boolean flag=false;
+	
+	@Override
+	public void addFeedback(MUExperiment exp) {
+		this.experiment=exp;
+		candidateMapping = exp.selectedMapping;
+		
+		int mappingRow = candidateMapping.getSourceKey();
+		int mappingCol = candidateMapping.getTargetKey();
+		
+		userFeedback = experiment.userFeedback.getUserFeedback();
+
+		// update the validation matrices
+		SparseMatrix validationMatrix = exp.getFeedbackMatrix(candidateMapping.getAlignmentType(), userFeedback);
+		int count = (int) validationMatrix.getSimilarity(mappingRow, mappingCol);
+		count++;
+
+		validationMatrix.setSimilarity(mappingRow, mappingCol, (double)count);
+
+		exp.setFeedBackMatrix(validationMatrix, candidateMapping.getAlignmentType(), userFeedback);
+		
+		// update the forbidden positions
+		updateForbiddenPositions(candidateMapping, userFeedback);
+		
+		// print out the forbidden positions
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/userfeedback/MLutility/WekaUtility.java

@@ -1,0 +1,163 @@
+package am.extension.userfeedback.MLutility;
+
+
+import weka.classifiers.functions.LibSVM;
+import weka.classifiers.functions.LinearRegression;
+import weka.core.Attribute;
+import weka.core.FastVector;
+import weka.core.Instance;
+import weka.core.Instances;
+
+
+
+public class WekaUtility {
+	Instances trainingSet;
+	LinearRegression lr=new LinearRegression();
+	
+	
+	
+	public void setTrainingSet(double[][] ts)
+	{
+		trainingSet=createTrainingInstances(ts);
+		try {
+			lr.buildClassifier(trainingSet);
+		} catch (Exception e) {
+			// TODO Auto-generated catch block
+			e.printStackTrace();
+		}
+	}
+	
+
+	private Instance createDataInstances(double[] dtInstance){
+				
+		//initialize the attribute array
+		int attributeNum=dtInstance.length;
+		Attribute[] attributes = new Attribute[dtInstance.length+1]; 
+		for(int i = 0; i<attributeNum;i++){
+			attributes[i]= new Attribute("att"+i);
+		}
+		attributes[attributeNum]= new Attribute("theClass");
+		
+	
+		// Declare the feature vector
+		FastVector fvWekaAttributes = new FastVector(dtInstance.length+1);
+		for (int i = 0; i< dtInstance.length+1; i++){
+			fvWekaAttributes.addElement(attributes[i]);
+		}
+		
+		// Create an empty training set
+		Instances isTrainingSet = new Instances("Rel", fvWekaAttributes, dtInstance.length);        
+//		
+		isTrainingSet.setClassIndex(dtInstance.length-1);
+		
+
+		Instance instance = null;
+		
+		//for each ontology create an instance and add it to the trainingset
+		// Create the instance
+		instance = new Instance(dtInstance.length+1);
+		for (int i = 0; i<dtInstance.length; i++){
+			instance.setValue((Attribute)fvWekaAttributes.elementAt(i), dtInstance[i]);
+		}
+				
+			
+		// add the instance
+		//isTrainingSet=instance;
+
+		
+		return instance;
+
+		
+	}	
+	
+	private Instances createTrainingInstances(double[][] ts){
+		//initialize the attribute array
+		int attributeNum=ts[0].length-1;
+		int labelIndex=ts[0].length-1;
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/userfeedback/UFLRegistry.java

@@ -1,0 +1,163 @@
+package am.extension.userfeedback;
+
+import am.extension.multiUserFeedback.storage.FeedbackAgregation;
+import am.extension.userfeedback.evaluation.CandidateSelectionEvaluation;
+import am.extension.userfeedback.evaluation.PropagationEvaluation;
+import am.extension.userfeedback.experiments.UFLExperiment;
+import am.extension.userfeedback.inizialization.FeedbackLoopInizialization;
+import am.extension.userfeedback.propagation.FeedbackPropagation;
+import am.extension.userfeedback.selection.CandidateSelection;
+
+
+/**
+ * This class is just a wrapper class for several registry enums.
+ * 
+ * @author cosmin
+ *
+ */
+public class UFLRegistry {
+
+	/* Different experimental setups (Ontologies + Reference alignment) */
+	public enum ExperimentRegistry {
+		ServerExperiment ( am.extension.multiUserFeedback.experiment.MUExperiment.class ),
+		ClientExperiment ( am.extension.userfeedback.experiments.MLFExperiment.class),
+		SingleUser( am.extension.userfeedback.experiments.SUExperiment.class),
+		Manual ( am.extension.userfeedback.common.ManualExperimentSetup.class );
+		/* *********************** DO NOT EDIT BELOW THIS LINE **************************** */
+		Class<? extends UFLExperiment> clazz;
+
+		ExperimentRegistry( Class<? extends UFLExperiment> cs ) { clazz = cs; }
+		public Class<? extends UFLExperiment> getEntryClass() { return clazz; }
+	}
+	
+	public enum InitialMatcherRegistry {
+		SemanticStructuralCombination( am.extension.userfeedback.clustering.disagreement.SestCombinationMatchers.class ),
+		LargeOrthoCombination ( am.extension.userfeedback.clustering.disagreement.LargeOntologyOrthoMatchers.class ),
+		OrthoCombination ( am.extension.userfeedback.clustering.disagreement.OrthoCombinationMatchers.class );
+			
+		/* *********************** DO NOT EDIT BELOW THIS LINE **************************** */
+		Class<? extends InitialMatchers> clazz;
+		
+		InitialMatcherRegistry( Class<? extends InitialMatchers> cs ) { clazz = cs; }
+		public Class<? extends InitialMatchers> getEntryClass() { return clazz; }
+	}
+	
+	public enum LoopInizializationRegistry {
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/userfeedback/clustering/disagreement/DisagreementRanking.java

@@ -1,0 +1,113 @@
+package am.extension.userfeedback.clustering.disagreement;
+
+import java.util.ArrayList;
+import java.util.Collections;
+import java.util.List;
+
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MappingSimilarityComparator;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+import am.app.ontology.Ontology;
+import am.evaluation.disagreement.variance.VarianceDisagreement;
+import am.evaluation.disagreement.variance.VarianceDisagreementParameters;
+import am.extension.userfeedback.experiments.UFLExperiment;
+import am.extension.userfeedback.selection.CandidateSelection;
+
+public class DisagreementRanking<T extends UFLExperiment> extends CandidateSelection<T> {
+
+	private List<Mapping> rankedClassMappings;
+	private List<Mapping> rankedPropertyMappings;
+	private List<Mapping> allRanked;
+	
+	private UFLExperiment experiment;
+	
+	@Override public List<Mapping> getRankedMappings(alignType t) { 
+		if( t == alignType.aligningClasses ) { return rankedClassMappings; }
+		if( t == alignType.aligningProperties ) { return rankedPropertyMappings; }
+		return null;
+	}
+	
+	@Override
+	public List<Mapping> getRankedMappings() {
+		return allRanked;
+	}
+	
+	@Override
+	public void rank(UFLExperiment ex) {
+		this.experiment = ex;
+
+		// get the matchers from the execution semantics
+		List<MatchingTask> matchers = ex.initialMatcher.getComponentMatchers();
+		
+		rank(matchers);
+	}
+	
+	public void rank(List<MatchingTask> matchers) {
+				
+		if( allRanked == null ) {
+			initializeRankedList(matchers);
+		}
+		
+		for( int i = 0; i < allRanked.size(); i++ ){
+			if( experiment.correctMappings == null && experiment.incorrectMappings == null )
+			{
+				selectedMapping = allRanked.get(i);
+				break;
+			}
+			
+			Mapping m = allRanked.get(i);
+			if( experiment.correctMappings != null && (experiment.correctMappings.contains(m.getEntity1(),Ontology.SOURCE) != null ||
+				experiment.correctMappings.contains(m.getEntity2(),Ontology.TARGET) != null) ) {
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/userfeedback/clustering/disagreement/LargeOntologyOrthoMatchers.java

@@ -1,0 +1,326 @@
+package am.extension.userfeedback.clustering.disagreement;
+
+import java.lang.reflect.InvocationTargetException;
+import java.util.ArrayList;
+import java.util.List;
+
+import org.apache.log4j.Logger;
+
+import am.app.Core;
+import am.app.lexicon.LexiconBuilderParameters;
+import am.app.mappingEngine.AbstractMatcher;
+import am.app.mappingEngine.Alignment;
+import am.app.mappingEngine.DefaultSelectionParameters;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MatchingProgressListener;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.SelectionAlgorithm;
+import am.app.mappingEngine.oneToOneSelection.MwbmSelection;
+import am.app.mappingEngine.utility.OAEI_Track;
+import am.app.ontology.Ontology;
+import am.app.ontology.profiling.manual.ManualOntologyProfiler;
+import am.extension.batchmode.matchingTask.SimpleMatchingTaskRunner;
+import am.extension.userfeedback.InitialMatchers;
+import am.extension.userfeedback.experiments.UFLExperiment;
+import am.matcher.Combination.CombinationMatcher;
+import am.matcher.Combination.CombinationParameters;
+import am.matcher.LexicalSynonymMatcher.LexicalSynonymMatcher;
+import am.matcher.LexicalSynonymMatcher.LexicalSynonymMatcherParameters;
+import am.matcher.asm.AdvancedSimilarityMatcher;
+import am.matcher.asm.AdvancedSimilarityParameters;
+import am.matcher.bsm.BaseSimilarityMatcher;
+import am.matcher.bsm.BaseSimilarityParameters;
+import am.matcher.multiWords.MultiWordsMatcher;
+import am.matcher.multiWords.MultiWordsParameters;
+import am.matcher.parametricStringMatcher.ParametricStringMatcher;
+import am.matcher.parametricStringMatcher.ParametricStringParameters;
+import am.ui.UIUtility;
+
+public class LargeOntologyOrthoMatchers extends InitialMatchers {
+private static final Logger LOG = Logger.getLogger(OrthoCombinationMatchers.class);
+
+	private BaseSimilarityParameters    param_bsm;  // the parameters that will be used for the BSM
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/userfeedback/clustering/disagreement/MaxInformationRanking.java

@@ -1,0 +1,522 @@
+package am.extension.userfeedback.clustering.disagreement;
+
+import java.io.BufferedWriter;
+import java.io.File;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.List;
+
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+import am.app.ontology.Node;
+import am.app.ontology.Ontology;
+import am.extension.userfeedback.experiments.SUExperiment;
+import am.extension.userfeedback.selection.CandidateSelection;
+
+public class MaxInformationRanking extends CandidateSelection<SUExperiment> {
+	
+	private List<Mapping> rankedClassMappings;
+	private List<Mapping> rankedPropertyMappings;
+	private List<Mapping> allRanked;
+	private SUExperiment experiment;
+	//weight for the Uncertain Mappings discovered in the system
+	private final double weight_um=0.5;
+	//weight for the suspected Missing Mapping in the system
+	private final double weight_mm=0.3;
+	private boolean flag=true;
+	
+	@Override public List<Mapping> getRankedMappings(alignType t) 
+	{ 
+		if( t == alignType.aligningClasses ) 
+		{ 
+			return rankedClassMappings; 
+		}
+		if( t == alignType.aligningProperties ) 
+		{ 
+			return rankedPropertyMappings; 
+		}
+
+		return null;
+	}
+	
+	public Mapping getCandidateMapping_1_1() 
+	{
+
+		for( int i = 0; i < allRanked.size(); i++ ){
+			if( experiment.correctMappings == null && experiment.incorrectMappings == null )
+				return allRanked.get(i);
+			
+			Mapping m = allRanked.get(i);
+			if( experiment.correctMappings != null && (experiment.correctMappings.contains(m.getEntity1(),Ontology.SOURCE) != null ||
+				experiment.correctMappings.contains(m.getEntity2(),Ontology.TARGET) != null) ) 
+			{
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/userfeedback/clustering/disagreement/MultiStrategyRanking.java

@@ -1,0 +1,330 @@
+package am.extension.userfeedback.clustering.disagreement;
+
+import java.util.ArrayList;
+import java.util.Collections;
+import java.util.List;
+
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.Alignment;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MappingSimilarityComparator;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+import am.evaluation.disagreement.variance.VarianceDisagreement;
+import am.evaluation.disagreement.variance.VarianceDisagreementParameters;
+import am.extension.multiUserFeedback.experiment.MUExperiment;
+import am.extension.userfeedback.selection.CandidateSelection;
+
+public class MultiStrategyRanking extends CandidateSelection<MUExperiment>{
+
+	private SimilarityMatrix classesMatrix;
+	private SimilarityMatrix propertiesMatrix;
+	private final double weight_um=0.5;
+	private final double weight_mm=0.3;
+	private MUExperiment experiment;
+	
+	@Override
+	public void rank(MUExperiment exp) {
+		this.experiment=exp;
+		//Inizialization
+		inizialization();
+		//one time ranking methods
+		if(exp.getIterationNumber()==1)
+		{
+			uncertainMappingRetrieval();
+		}
+		//every time ranking methods
+		almostCertainMappingRetrieval();
+		disagreementRanking();
+		
+		// select the candidate mapping
+		Mapping[] ranked=new Mapping[3];
+		if (experiment.disRanked!=null)
+			ranked[0]=notEvaluated(experiment.disRanked);
+		else
+			ranked[0]=new Mapping(0);
+		if (experiment.uncertainRanking!=null)
+			ranked[1]=notEvaluated(experiment.uncertainRanking);
+		else
+			ranked[1]=new Mapping(0);
+		if (experiment.almostRanking!=null)
+			ranked[2]=notEvaluated(experiment.almostRanking);
+		else
+			ranked[2]=new Mapping(0);
+		
+		Mapping cMapping=new Mapping(0.0);
+		for(int i=0;i<ranked.length;i++)
+		{
+			if (ranked[i].getSimilarity()>cMapping.getSimilarity())
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/userfeedback/clustering/disagreement/OrthoCombinationMatchers.java

@@ -1,0 +1,324 @@
+package am.extension.userfeedback.clustering.disagreement;
+
+import java.lang.reflect.InvocationTargetException;
+import java.util.ArrayList;
+import java.util.List;
+
+import org.apache.log4j.Logger;
+
+import am.app.Core;
+import am.app.lexicon.LexiconBuilderParameters;
+import am.app.mappingEngine.AbstractMatcher;
+import am.app.mappingEngine.Alignment;
+import am.app.mappingEngine.DefaultSelectionParameters;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MatchingProgressListener;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.SelectionAlgorithm;
+import am.app.mappingEngine.oneToOneSelection.MwbmSelection;
+import am.app.mappingEngine.utility.OAEI_Track;
+import am.app.ontology.Ontology;
+import am.app.ontology.profiling.manual.ManualOntologyProfiler;
+import am.extension.batchmode.matchingTask.FluentMatchingTaskRunner;
+import am.extension.batchmode.matchingTask.SimpleMatchingTaskRunner;
+import am.extension.userfeedback.InitialMatchers;
+import am.extension.userfeedback.experiments.UFLExperiment;
+import am.matcher.Combination.CombinationMatcher;
+import am.matcher.Combination.CombinationParameters;
+import am.matcher.LexicalSynonymMatcher.LexicalSynonymMatcher;
+import am.matcher.LexicalSynonymMatcher.LexicalSynonymMatcherParameters;
+import am.matcher.asm.AdvancedSimilarityMatcher;
+import am.matcher.asm.AdvancedSimilarityParameters;
+import am.matcher.bsm.BaseSimilarityMatcher;
+import am.matcher.bsm.BaseSimilarityParameters;
+import am.matcher.multiWords.MultiWordsMatcher;
+import am.matcher.multiWords.MultiWordsParameters;
+import am.matcher.parametricStringMatcher.ParametricStringMatcher;
+import am.matcher.parametricStringMatcher.ParametricStringParameters;
+import am.ui.UIUtility;
+
+/**
+ * The orthogonal combination matcher.  Used as the first step in the new
+ * User Feedback Loop.
+ * 
+ * @author Cosmin Stroe - Jan 29th, 2011.
+ *
+ */
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/userfeedback/experiments/UFLExperiment.java

@@ -1,0 +1,209 @@
+package am.extension.userfeedback.experiments;
+
+import java.io.BufferedWriter;
+import java.util.HashMap;
+import java.util.Map;
+
+import org.apache.log4j.LogManager;
+import org.apache.log4j.Logger;
+
+import am.app.mappingEngine.Alignment;
+import am.app.mappingEngine.Mapping;
+import am.app.ontology.Ontology;
+import am.evaluation.alignment.AlignmentMetrics;
+import am.evaluation.alignment.DeltaFromReference;
+import am.extension.multiUserFeedback.storage.FeedbackAgregation;
+import am.extension.multiUserFeedback.validation.ProbabilisticErrorAutomaticValidation;
+import am.extension.userfeedback.InitialMatchers;
+import am.extension.userfeedback.SaveFeedback;
+import am.extension.userfeedback.UFLStatistics;
+import am.extension.userfeedback.UserFeedback;
+import am.extension.userfeedback.UserFeedback.Validation;
+import am.extension.userfeedback.common.ExperimentData;
+import am.extension.userfeedback.common.ExperimentIteration;
+import am.extension.userfeedback.evaluation.CandidateSelectionEvaluation;
+import am.extension.userfeedback.evaluation.PropagationEvaluation;
+import am.extension.userfeedback.experiments.UFLExperimentParameters.Parameter;
+import am.extension.userfeedback.inizialization.FeedbackLoopInizialization;
+import am.extension.userfeedback.logic.api.UFLControlLogic;
+import am.extension.userfeedback.propagation.FeedbackPropagation;
+import am.extension.userfeedback.selection.CandidateSelection;
+import am.extension.userfeedback.ui.UFLProgressDisplay;
+
+public abstract class UFLExperiment {
+
+	private static final Logger LOG = LogManager.getLogger(UFLExperiment.class);
+	
+	public final UFLExperimentSetup							setup;
+	
+	public InitialMatchers 								initialMatcher;
+	public FeedbackLoopInizialization<UFLExperiment>        dataInizialization;
+	public CandidateSelection<UFLExperiment> 				candidateSelection;
+	public CandidateSelectionEvaluation 					csEvaluation;
+	public UserFeedback										userFeedback;
+	public FeedbackPropagation<UFLExperiment>				feedbackPropagation;
+	public PropagationEvaluation<UFLExperiment>				propagationEvaluation;
+	public UFLProgressDisplay								gui;
+	public SaveFeedback< UFLExperiment>						saveFeedback;
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/userfeedback/logic/PersistentControlLogic.java

@@ -1,0 +1,207 @@
+package am.extension.userfeedback.logic;
+
+import am.extension.multiUserFeedback.storage.FeedbackAgregation;
+import am.extension.userfeedback.InitialMatchers;
+import am.extension.userfeedback.SaveFeedback;
+import am.extension.userfeedback.UFLRegistry.UFLStatisticRegistry;
+import am.extension.userfeedback.UFLStatistics;
+import am.extension.userfeedback.UserFeedback;
+import am.extension.userfeedback.evaluation.CandidateSelectionEvaluation;
+import am.extension.userfeedback.evaluation.PropagationEvaluation;
+import am.extension.userfeedback.experiments.UFLExperiment;
+import am.extension.userfeedback.inizialization.FeedbackLoopInizialization;
+import am.extension.userfeedback.logic.api.AbstractUFLControlLogic;
+import am.extension.userfeedback.propagation.FeedbackPropagation;
+import am.extension.userfeedback.selection.CandidateSelection;
+
+public abstract class PersistentControlLogic<T extends UFLExperiment> extends AbstractUFLControlLogic<T> {
+	
+	protected void runInitialMatchers() {
+		// Run the initial matchers in a separate thread.
+		try {
+			if( experiment.initialMatcher == null ) {
+	
+				Class<? extends InitialMatchers> c = experiment.setup.im.getEntryClass();
+				experiment.info("Instantiating InitialMatchers: " + c.getName());
+				experiment.initialMatcher = c.newInstance();
+				experiment.initialMatcher.addActionListener(this);
+			}
+			startThread(new Runnable(){
+				@Override public void run() {
+					experiment.initialMatcher.run(experiment);	
+				}
+			});
+		} catch (InstantiationException | IllegalAccessException e) {
+			e.printStackTrace();
+		}
+	}
+	
+	protected void runInizialization() {
+		// Run the initial matchers in a separate thread.
+		try {
+			if( experiment.dataInizialization == null ) {
+				Class<? extends FeedbackLoopInizialization> c = experiment.setup.fli.getEntryClass();
+				experiment.info("Instantiating FeedbackLoopInitialization: " + c.getName());
+				experiment.dataInizialization = c.newInstance();
+				experiment.dataInizialization.addActionListener(this);
+			}
+			startThread(new Runnable(){ 
+				@Override public void run() {
+					experiment.dataInizialization.initialize(experiment);	
+				}
+			});
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/AgreementMaker-UserFeedback/src/main/java/am/extension/userfeedback/utility/UFLutility.java

@@ -1,0 +1,378 @@
+package am.extension.userfeedback.utility;
+
+import java.io.BufferedWriter;
+import java.io.File;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.io.Writer;
+import java.math.BigDecimal;
+import java.util.ArrayList;
+import java.util.List;
+
+import org.apache.log4j.LogManager;
+import org.apache.log4j.Logger;
+
+import am.app.Core;
+import am.app.mappingEngine.AbstractMatcher;
+import am.app.mappingEngine.AbstractMatcher.alignType;
+import am.app.mappingEngine.Alignment;
+import am.app.mappingEngine.DefaultSelectionParameters;
+import am.app.mappingEngine.Mapping;
+import am.app.mappingEngine.MatcherResult;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.oneToOneSelection.MwbmSelection;
+import am.app.mappingEngine.similarityMatrix.SimilarityMatrix;
+import am.app.ontology.Node;
+import am.app.ontology.Ontology;
+import am.extension.userfeedback.experiments.UFLExperiment;
+
+public class UFLutility {
+	
+	public static final Logger LOG = LogManager.getLogger(UFLutility.class);
+	
+	static public double[] getSignatureVector(Mapping mp, List<MatchingTask> inputMatchers)
+	{
+		int size=inputMatchers.size();
+		Node sourceNode=mp.getEntity1();
+		Node targetNode=mp.getEntity2();
+		MatchingTask a;
+		double[] ssv=new double[size];
+		for (int i=0;i<size;i++)
+		{
+			a = inputMatchers.get(i);
+			ssv[i] = a.selectionResult.getAlignment().getSimilarity(sourceNode, targetNode);
+				
+		}
+		return ssv;
+	}
+	
+	//check if the signature vector is valid. A valid signature vector must have at least one non zero element.
+	static public boolean validSsv(double[] ssv)
+	{
+		double obj=0.0d;
+		for(int i=0;i<ssv.length;i++)
+		{
+			if (!(ssv[i] == obj))
+				return true;
+		}
+		return false;
+	}
+	
+	static public Alignment<Mapping> combineResults(AbstractMatcher am, UFLExperiment experiment)
+	{
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/Matcher-OAEI/src/main/java/am/matcher/oaei/oaei2011/OAEI2011Matcher.java

@@ -1,0 +1,1209 @@
+/**
+ * 
+ */
+package am.matcher.oaei.oaei2011;
+
+import java.io.BufferedReader;
+import java.io.File;
+import java.io.FileReader;
+import java.util.ArrayList;
+import java.util.HashMap;
+import java.util.List;
+import java.util.Map;
+
+import am.Utility;
+import am.app.Core;
+import am.app.lexicon.LexiconBuilderParameters;
+import am.app.mappingEngine.AbstractMatcher;
+import am.app.mappingEngine.AbstractMatcherParametersPanel;
+import am.app.mappingEngine.DefaultMatcherParameters;
+import am.app.mappingEngine.DefaultSelectionParameters;
+import am.app.mappingEngine.MatcherFactory;
+import am.app.mappingEngine.MatchingProgressListener;
+import am.app.mappingEngine.MatchingTask;
+import am.app.mappingEngine.StringUtil.NormalizerParameter;
+import am.app.mappingEngine.StringUtil.StringMetrics;
+import am.app.mappingEngine.oneToOneSelection.MwbmSelection;
+import am.app.mappingEngine.qualityEvaluation.QualityMetricRegistry;
+import am.app.mappingEngine.utility.OAEI_Track;
+import am.app.ontology.Node;
+import am.app.ontology.NodeHierarchy;
+import am.app.ontology.hierarchy.AlternateHierarchy;
+import am.app.ontology.profiling.classification.OntologyClassifier;
+import am.app.ontology.profiling.classification.OntologyClassifier.OAEI2011Configuration;
+import am.app.ontology.profiling.manual.ManualOntologyProfiler;
+import am.matcher.Combination.CombinationMatcher;
+import am.matcher.Combination.CombinationParameters;
+import am.matcher.FilterMatcher.FilterMatcher;
+import am.matcher.IterativeInstanceStructuralMatcher.IterativeInstanceStructuralMatcher;
+import am.matcher.IterativeInstanceStructuralMatcher.IterativeInstanceStructuralParameters;
+import am.matcher.LexicalSynonymMatcher.LexicalSynonymMatcher;
+import am.matcher.LexicalSynonymMatcher.LexicalSynonymMatcherParameters;
+import am.matcher.LexicalSynonymMatcher.LexicalSynonymMatcherWeighted;
+import am.matcher.asm.AdvancedSimilarityMatcher;
+import am.matcher.asm.AdvancedSimilarityParameters;
[…]

### 2016-01-05 agreementmaker/AgreementMaker-OSGi/Matcher-OAEI/src/main/java/am/matcher/oaei/oaei2011/OAEI2011MatcherParameters.java

@@ -1,0 +1,27 @@
+package am.matcher.oaei.oaei2011;
+
+import am.app.mappingEngine.DefaultMatcherParameters;
+import am.app.ontology.profiling.classification.OntologyClassifier.OAEI2011Configuration;
+
+/**
+ * This year's matching algorithm uses a completely automatic configuration. 
+ *
+ */
+public class OAEI2011MatcherParameters extends DefaultMatcherParameters {
+
+	private static final long serialVersionUID = 5708419970641391711L;
+	
+	public boolean automaticConfiguration = true;
+	public OAEI2011Configuration selectedConfiguration = OAEI2011Configuration.GENERAL_PURPOSE;
+	
+	public boolean showIntermediateMatchers = false;
+	public boolean parallelExecution = false;
+		
+	public OAEI2011MatcherParameters() { 
+		super(); 
+	}
+
+    public OAEI2011MatcherParameters(DefaultMatcherParameters params) {
+        super(params);
+    }
+}

### 2016-01-09 Paper/Draft.tex
Added Semantic Web, Current merging strategies, word2vec, AgreementMaker to first draft

@@
  \subsection{Short Context}
+ On the Semantic Web, ontologies are used to define and share knowledge.
  \subsection{Problem}
+ When knowledge bases are combined, their ontologies need to be merged.
  \subsection{Research questions}
+
  \subsection{Hypotheses}
+
  \subsection{Justification}
- Consider moving this up
+ Reliable, error proof ontology matching will be key for the distributed Semantic Web.
 
  \section{Context}
+ In this section I will discuss all concepts that are required to understand the study.
  \subsection{The Semantic Web}
+ The Semantic Web, or Web 3.0, is a concept of a Web that enhances the User Experience in ways that the current Web can not provide.
+Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and barely any interconnectivity.
+For example, Facebook is a hub for sharing content with people you consider friends, but if you want to share that content with more people you will have to go to another hub, like imgur or Pinterest.
+The Semantic Web, on the other hand, sees web pages as sources of \textit{information} that can be combined whenever the user needs it.
+This allows not only humans to browse the internet, but also Artificial Intelligences, which will use this information to aid their users.
+
+For example, if a user wants to see a movie this weekend, he orders his AI, or \textit{softbot}, to find him a suitable time and movie to see.
+The softbot then accesses the Internet Movie Database to see which movies currently play and which of those are similar to what the user liked in the past.
+He will then access the pages of the local movie theaters to see when those movies play.
+Lastly, he will contact the softbots of the friends of the user to ask if they will also come to see that movie.
+After a short exchange the optimal time, place and participant set are decided, and the softbot tells the user what the results are.
+When the user accepts, the appointment is automatically added to his agenda.
+
+All of this is possible, if the softbot can access all of the information reliably.
+In the current Web, this is not possible, as all information is written in an ambiguous, unstructured format called human language.
+To allow softbots to access the same information that we can, the Semantic Web proposes to add a layer to the internet where all information is saved in a unified format that is unambiguous, robot-interpretable and can be used to store any type of knowledge.
+
  \subsubsection{Goal}
+ The goal of the Semantic Web is very pragmatic: help people in everyday activities by leveraging all information available on the internet.
+The fact that it is pragmatic goes a long way of making it a reality: if even one application comes into existence that uses online information in a structured way and thus makes everyday tasks a little easier, the goal is accomplished.
+Of course, then the goal resets and we should make more applications leveraging more information for more tasks.
  \subsubsection{Current state}
@@
  \subsection{Current merging strategies}
+ Many different merging strategies have already been developed.
+All strategies follow the same two-step approach.
+The two steps are independent and as such different methods can be used interchangeably.
+The first step is to generate an initial correspondence set, where correspondences between nodes are found based on just their labels and meta-data.
+The second step is to use this initial set and the structure of the ontology to find more correspondences.
+These steps are called the terminological and the structural steps.
+Some strategies also use extra steps like the extensional and semantic steps, which use vector space models and inference, respectively.
+https://hal.inria.fr/hal-00917910/document
+
+ Popular terminological strategies are WordNet comparison and edit distance.
+The former uses the popular WordNet hierarchy as a distance measure between to concepts, e.g.
+the number of edges between the concepts and their least general common superconcept.
+http://disi.unitn.it/~p2p/RelatedWork/Matching/Lin_WordNet_OM.pdf
+ Edit distance is a purely string-based similarity measure.
+The similarity is a (weighted) count of edits required to transform one word into another, where common edits are insertion, deletion and replacement.
+Similar methods include substring matching and n-gram matching, which compare parts of the strings to find similarities.
+http://disi.unitn.it/~p2p/RelatedWork/Matching/6614ijdms01.pdf
  \subsection{Other related research}
+ \subsubsection{Word sense representation}
+ Skip-gram models have been widely used to represent words as vectors.
+This is useful as it is easy to calculate the distance between two vectors, which is a useful property for ontology matching.
+This vector distance has been shown to be correlated with the semantic distance between words.
+ Recently, an effective and efficient skip-gram model has been developed.
+It is called word2vec, and uses a number of extensions over previous methods that enable it to efficiently learn an effective representation.
+
+ Word2vec learns this representation by trying to predict a context matrix.
+First a one-hot encoding is made for the vocabulary.
+Then the model learns to predict a context matrix of C one-hot vectors based on the given one-hot input vector.
+The model is a neural network with one hidden layer and multiple output layers.
+Since the words are one-hot encoded the input to the hidden layer is equal to the row of the weight matrix that corresponds to the word.
+This row is the vector representation of the word.
+
+ % Continue with better w2v
  \subsection{Used technology}
@@
  \subsubsection{AgreementMaker}
+ AgreementMaker is an ontology matching system which obtained the highest F-measure in 6 of the 7 ontology matching tracks of OAEI 2015 http://disi.unitn.it/~pavel/om2015/papers/oaei15_paper1.pdf.
+The system has also been updated the most recent at the time of writing.
+
+ The system uses an extensible framework which allows its users to add new modules to the system.
+This is very useful for research as it allows the researcher to compare different modules by swapping in just those modules in the framework.
+The module-swapping technique will also be used in this work, but more of that will be discussed in $Evaluation methods$.
+ http://disi.unitn.it/~p2p/RelatedWork/Matching/vldb2009-revised.pdf
  \subsubsection{MapReduce}

### 2016-02-16 skipgram/train-mssg.sh
Added skipgram model to be adapted

@@ -1,0 +1,16 @@
+#!/bin/sh
+
+if [ ! -e text8 ]; then
+  wget https://dl.dropboxusercontent.com/u/39534006/text8.zip
+  unzip text8.zip
+fi
+
+if [ ! -e CP.hack ]; then
+    echo "Run make_cp.sh script first"
+    exit    
+fi
+
+classpath=`cat CP.hack`
+wordvec_app="java -Xmx100g -cp ${classpath} WordVec"
+
+${wordvec_app}  --model=MSSG-MaxOut --train=text8 --output=vectors-MSSG.gz --sense=2 --learn-top-v=4000 --size=300 --window=5 --min-count=15  --threads=23  --negative=1 --sample=0.001 --binary=1 --ignore-stopwords=1 --encoding=ISO-8859-15 --save-vocab=text8.vocab.gz --rate=0.025 --delta=0.1                    

### 2016-02-16 Paper/Draft.tex
Added Semantic Web, AgreementMaker and 2/6 core sentences

@@
  \subsubsection{Current state}
+
  \subsubsection{Technologies}
@@
 the number of edges between the concepts and their least general common superconcept.
-http://disi.unitn.it/~p2p/RelatedWork/Matching/Lin_WordNet_OM.pdf
+% http://disi.unitn.it/~p2p/RelatedWork/Matching/Lin_WordNet_OM.pdf
  Edit distance is a purely string-based similarity measure.
@@
 Similar methods include substring matching and n-gram matching, which compare parts of the strings to find similarities.
-http://disi.unitn.it/~p2p/RelatedWork/Matching/6614ijdms01.pdf
+%http://disi.unitn.it/~p2p/RelatedWork/Matching/6614ijdms01.pdf
  \subsection{Other related research}
@@
  \subsubsection{AgreementMaker}
- AgreementMaker is an ontology matching system which obtained the highest F-measure in 6 of the 7 ontology matching tracks of OAEI 2015 http://disi.unitn.it/~pavel/om2015/papers/oaei15_paper1.pdf.
+ AgreementMaker is an ontology matching system which obtained the highest F-measure in 6 of the 7 ontology matching tracks of OAEI 2015 %http://disi.unitn.it/~pavel/om2015/papers/oaei15_paper1.pdf.
 The system has also been updated the most recent at the time of writing.
@@
 The module-swapping technique will also be used in this work, but more of that will be discussed in $Evaluation methods$.
- http://disi.unitn.it/~p2p/RelatedWork/Matching/vldb2009-revised.pdf
+ %http://disi.unitn.it/~p2p/RelatedWork/Matching/vldb2009-revised.pdf
  \subsubsection{MapReduce}

### 2016-02-24 Paper/Draft.tex
Added section explaining the different possible methods

@@
  \usepackage[titletoc]{appendix}
- \title{Ontology Matching with Word2Vec}
+ \title{Ontology Matching with word2vec}
  \author{Harmen Prins}
@@
  \subsubsection{Role}
- \subsection{Current merging strategies}
- Many different merging strategies have already been developed.
+ \subsection{Current alignment strategies}
+ Many different alignment strategies have already been developed.
 All strategies follow the same two-step approach.
@@
 %http://disi.unitn.it/~p2p/RelatedWork/Matching/6614ijdms01.pdf
+ \subsection{Problems with ontology alignment}
  \subsection{Other related research}
@@
 This is useful as it is easy to calculate the distance between two vectors, which is a useful property for ontology matching.
-This vector distance has been shown to be correlated with the semantic distance between words.
+This vector distance has been shown to be related to the semantic similarity between words.
+This semantic similarity is very useful for ontology alignment, as parts of one ontology have to be aligned with parts of another ontology depending on their semantic relation.
+
  Recently, an effective and efficient skip-gram model has been developed.
 It is called word2vec, and uses a number of extensions over previous methods that enable it to efficiently learn an effective representation.
-
   Word2vec learns this representation by trying to predict a context matrix.
@@
  % Continue with better w2v
+ Word2vec has been expanded in a number of different ways.
+For example, word order can be preserved, leading to a similarity measure that is closer to syntax, as syntax defines which words go where in a sentence.
+This research shows that the input does not have to be a bag-of-words representation, which will be useful later on.
+% Reference
+ Another interesting development is the multi-sense word2vec, which has multiple vector representations per word, depending on the number of different definitions a word has.
+For example, the word bank represents both the monetary institute and the riverside, which would both have a different representation in this extension.
+It can differentiate between two different meanings based on the context.
+This will help with resolving ambiguity, a very important factor in ontology alignment.
  \subsection{Used technology}
@@
  %http://disi.unitn.it/~p2p/RelatedWork/Matching/vldb2009-revised.pdf
- \subsubsection{MapReduce}
+ \section{Method}
+ In this section, I will describe the method that I developed.
+Firstly, I will describe the general idea.
+In the second section, I will give a theoretical justification for why this method should work and how it works conceptually.
+After that I will describe the different ways that the input graphs can be used to train the word2vec model and create the alignment.
+ \subsection{Idea}
+ As explained earlier, word2vec is a model that learns two things: implicitly it learns the semantic vector representation of words, and explicitly it learns to predict words from their context or vice versa.
+I will use both of these pieces of information in our alignment algorithm.
+ The semantic representation will be used for finding nodes in the two ontology graphs that are similar, i.e.
+close in the vector space.
+This step is relatively straightforward if proper vector representations are found.
+However, this may be hard due to a number of problems which I have listed below.
 
- \section{Method}
+ \begin{itemize}
+  \item The problem I am trying to solve is the problem of differently labelled nodes referring to the same concept.
+For example \emph{writer} and \emph{author} will not be matched by a string matcher, but should be matched.
+The two concepts may also have different labels in their context even though their contexts refer to the same concepts.
+  \item The size of the training corpus should be large enough for proper representation to be learned for every concept.
+It should also be relevant to the labels that are in the ontologies.
+This is a problem since the ontologies may be relatively small, so they need to be extended while keeping relevance.
+  \item Some labels may be ambiguous, for example homonyms, which are concepts that have the same label but represent a different context.
+ \end{itemize}
+
+ To solve these problems I will adapt word2vec to graphs and extend it with multi-sense embeddings. Also hot-starting is considered as an improvement.
+
+ \subsection{Theory}
+ \subsection{Possibilities} % Rename please
+  \subsubsection{Training corpus}
+  Word embedding models need to be trained on a large corpus.
+These corpora need to cover the concepts that are contained in the ontology, but also need to be large enough to build good embeddings.
+Since the ontologies themselves do not necessarily contain enough examples to embed the concepts properly, I need to use ontologies that are likely to contain the concepts I want to align.
+  As a benchmark, I will use the WordNet and NELL ontologies.
+To check if adding the ontologies that are to be aligned helps, I will also train a model on an ontology consisting of WordNet, NELL and the two alignment candidates.
+  \subsubsection{Node vectorisation}
+  The most basic node2vec model converts a node to a vector purely based on its own label.
+This method has one advantage over simple string matching: if no node is found in the other ontology that matches exactly, we can still find a node that is similar since it is close in the vector space.
+Therefore, this method should already be an improvement over the most basic string matching algorithms.
+It may even be competitive with more advanced string matchers (that look at substrings of labels).
+For example, \emph{ear lobe} and \emph{ear} will be matched by a substring matcher, but are also semantically similar since they will often be mentioned in the same context.
+  \subsubsection{Combine with neighbours}
+  To improve the model, we can add context information from the neighbours of a node.
+The most basic context adaptation would be to create a vector as the average of the context vectors.
+The resulting vector should be combined with the node vector of the node that is being investigated.
+This can be done by averaging or weighted averaging where the context is weighed more if there are more neighbours, though not necessarily linearly.
+These possibilities were also investigated.
+  \subsubsection{Select from senses}
+  Another way to take into account the influence of neighbouring nodes is to train a multi-sense node embedding model as described in {appropriate section}, and selecting from the different node senses based on which is closest to the context average.
+  \subsubsection{Adding edge labels}
+  To add more information to the model, edge labels can also be added to the context of a node.
+This method effectively doubles the training data and context size when creating the context average.
+This should make the model more robust, although edge labels may be duplicate (one has many unique family members) and less informative in general, so a lower weight may be appropriate.
+Another problem with this method is that the relation between a neighbour node and its corresponding edge is lost, since they are just treated as independent contexts.
+  \subsubsection{Select from senses}
+  This method is exactly the same as the selecting from node senses with just the neighbour nodes except that you now also take into account the edge labels.
+  \subsubsection{Combining edges with nodes}
+  As can be read in {appropriate section}, 
+  \subsubsection{Hot start}
+ \subsection{Discarded possibilities} % Rename
+  \subsubsection{Training on text}
+  \subsubsection{Just words}
+  \subsubsection{Just edges}
+  \subsubsection{Context matrix representation}
+ \subsection{Implementation}
+
+ \section{Evaluation}
  \subsection{Evaluation methods}
+
  \subsection{Data}

### 2016-02-26 Paper/Draft.tex
Added Combining edges with nodes, hot start

@@
  \usepackage[titletoc]{appendix}
+ \usepackage{comments}
  \title{Ontology Matching with word2vec}
@@
   \subsubsection{Combining edges with nodes}
-  As can be read in {appropriate section}, 
+  As can be read in {appropriate section}, it is possible to drop the bag-of-words assumption that the context is sequence invariant.
+\begin{comment}maybe ref too\end{comment} This means we can for example have the context be (previous word, next word) and those words will be treated differently.
+Similarly we can separate the edge and node labels and treat them differently.
+This ensures that the model will find any relationship between the edge and the node if it exists and will take this into account.
+For example, the system might use just the information 'isMarriedTo' to infer that someone is a human, but may infer that 'isMarriedTo' in combination with a man usually refers to a woman.
+\begin{comment} Ja doe maar een ander voorbeeld ivm gelijkheid e.d.\end{comment}
   \subsubsection{Hot start}
+  It is hard to classify the algorithm in terms of the normal ontology alignment methods.
+It is not purely string matching, since it takes into account information from the context.
+However, it is also not structural, as it can work without a seed alignment and uses information other than the structure as well.
+It is not logical \begin{comment} Goeie woord?\end{comment} since it does not use inference.
+Nor is it terminological, which looks at dictionaries or other ontologies to find matches.
+However, it does use other ontologies (or text corpi\begin{comment}Check spelling\end{comment}) implicitly, so if it must be grouped it would be terminological.
+\begin{comment}Moet voorafgaand stukje op een andere plek?\end{comment}
+  The algorithm can find matches based purely on the given node and edge labels.
+However the algorithm might benefit from a hot start.
+Such a seed alignment might allow the algorithm to train with certain words that are known synonyms as if they were the same word, thus increasing the number of training samples per word (on known relevant words) and decreasing sparsity.
+This may help the model, improving performance.
+However, since some information from other algorithms is now used, it would not be fair to compare the results to the cold start algorithm results.
+For example, it may just add the results from the generic string matcher to its own results, improving performance, without learning any new relationships.
+A new testing method had to be designed for this algorithm.
+This method would have to compare it to the string matchers, to see if it improved over their results, rather than compare it to the cold start algorithm.
+However, if we compare the cold and hot algorithms with the generic string matchers, we may be able to compare them indirectly.
+\begin{comment}Dit moet weg als het bs blijkt te zijn\end{comment}
  \subsection{Discarded possibilities} % Rename
   \subsubsection{Training on text}
+  Rather than training on ontologies, it would be possible to train the model on text.
+Since there is more text available than ontologies when counting the number of training samples, it would make sense to use a purely text-trained model.
+However, this method has downsides which made me decide not to use it.
+Namely, the context of a word in a text corpus is very different from a node in an ontology.
+A word is surrounded by the words directly around it, or the sentence it is in, or the paragraph or entire document.
+However all these contexts are just words, usually represented as a bag of words to ensure enough data for the model.
+In an ontology, the context is a combination of a node with an edge, which have a very different relation than merely co-occurring.
+The relation may be inferred from one sentence, or many different documents.
+\begin{comment}Herschrijf dit aub want het is niet goed\end{comment}
   \subsubsection{Just words}

### 2016-02-29 Paper/Draft.tex
Added Evaluation and Data

@@
  \usepackage[titletoc]{appendix}
- \usepackage{comments}
  \title{Ontology Matching with word2vec}
@@
   As can be read in {appropriate section}, it is possible to drop the bag-of-words assumption that the context is sequence invariant. 
-\begin{comment}maybe ref too\end{comment} This means we can for example have the context be (previous word, next word) and those words will be treated differently.
+  % maybe ref too\endcomment
+  This means we can for example have the context be (previous word, next word) and those words will be treated differently.
 Similarly we can separate the edge and node labels and treat them differently.
@@
 For example, the system might use just the information 'isMarriedTo' to infer that someone is a human, but may infer that 'isMarriedTo' in combination with a man usually refers to a woman.
-\begin{comment} Ja doe maar een ander voorbeeld ivm gelijkheid e.d.\end{comment}
+  %  Ja doe maar een ander voorbeeld ivm gelijkheid e.d.\endcomment
   \subsubsection{Hot start}
@@
 However, it is also not structural, as it can work without a seed alignment and uses information other than the structure as well.
-It is not logical \begin{comment} Goeie woord?\end{comment} since it does not use inference.
-Nor is it terminological, which looks at dictionaries or other ontologies to find matches.
-However, it does use other ontologies (or text corpi\begin{comment}Check spelling\end{comment}) implicitly, so if it must be grouped it would be terminological.
-\begin{comment}Moet voorafgaand stukje op een andere plek?\end{comment}
+It is not logical
+  %  Goeie woord?\endcomment
+  since it does not use inference. Nor is it terminological, which looks at dictionaries or other ontologies to find matches. However, it does use other ontologies (or text corpi
+  % Check spelling\endcomment
+  ) implicitly, so if it must be grouped it would be terminological.
+  % Moet voorafgaand stukje op een andere plek?\endcomment
   The algorithm can find matches based purely on the given node and edge labels.
@@
 However, if we compare the cold and hot algorithms with the generic string matchers, we may be able to compare them indirectly.
-\begin{comment}Dit moet weg als het bs blijkt te zijn\end{comment}
+  % Dit moet weg als het bs blijkt te zijn\endcomment
  \subsection{Discarded possibilities} % Rename
@@
 The relation may be inferred from one sentence, or many different documents.
-\begin{comment}Herschrijf dit aub want het is niet goed\end{comment}
-  \subsubsection{Just words}
+  % Herschrijf dit aub want het is niet goed\endcomment
+  \subsubsection{Just context nodes}
+
   \subsubsection{Just edges}
+
   \subsubsection{Context matrix representation}
+
  \subsection{Implementation}
@@
  \section{Evaluation}
+ The goal of the research is to find an ontology alignment algorithm $A$ and proof that it performs better than current techniques.
+However, as current techniques may combine many different algorithms and sources of information, maybe such a comparison is not fair, nor is a comparison with individual algorithms as they may be optimised for being combined.
+So, instead we may want to see if performance is improved when adding $A$ to an ensemble of algorithms $E=(A_1,..,A_n)$.
  \subsection{Evaluation methods}
+ The evaluation should be done using a performance measure $P(Al,T)$ that takes the alignment an algorithm produces given an ontology and the ground truth.
+If both the alignment and truth are considered sets of alignments, i.e.
+$Al=\{a_1,..,a_n\}$ and $T=\{a'_1,..,a'_m\}$, then the True Positives $TP=\{a|a\in Al, a\in T\}$, False Positives $FP=\{a|a\in Al, a\notin T\}$ and False Negatives $FN=\{a|a\in T, a\notin Al\}$ determine the performance of the alignment.
+The True Negatives do not matter, as there are extremely many, and the goal of ontology matching is to find True Positives.
+Therefore the Jaccard similarity should be used as a performance measure.
 
+ The Jaccard similarity is calculated as follows
+ \[
+ J = \frac{TP}{TP + FP + FN}
+ \]
+ i.e. the fraction of the true positives over the sum of the true positives and mistakes.
+
+ The Jaccard similarity is a number between 0 and 1, with a higher number being better.
+Therefore if we compare two alignments, the one which is most similar to the truth, i.e.
+has a higher Jaccard similarity, is the better one.
+
+ However, if we want to find out if an algorithm improves an ensemble, we calculate the improvement as follows:
+ \[
+ I = J_{E\cup \{A\}} - J_E
+ \]
+ where $J_E$ is the Jaccard coefficient of an ensemble $E$.
+ To see if an algorithm is useful to an ensemble, the improvement score $I$ has to be \emph{significantly} higher than zero.
+To check if a score is significant, a statistical significance test will have to be carried out.
+The test works as follows: generate $N$ solutions randomly and score them.
+Then score the method you want to investigate.
+If the score is in the top p\%, it is significant, otherwise it is not.
+In this case the solutions are $E\cup \{R\}$, where $R$ is an algorithm that generates random alignments.
  \subsection{Data}
-
+ The data used comes from a list of data sets that the OAEI provides. % Zoek paper, misschien http://www.sciencedirect.com/science/article/pii/S1570826813000188
+ %Hoeveel preprocessing moest ik doen
+ Every data set contains two ontologies that need to be aligned and a ground truth alignment.
+The goal is straightforward: find the alignment given only the ontologies and whatever outside resources are needed.
  \section{Algorithm}

### 2016-03-01 skipgram/browse-mssg.sh
Removed skipgram so it can be moved into factorie

@@ -1,13 +1,0 @@
-#!/bin/sh
-## scipt for computing the vectors  and checking the accuracy with google's questions-words analogy task
-
-if [ ! -e CP.hack ]; then
-    echo "Run make_cp.sh script first"
-    exit 
-fi
-
-
-classpath=`cat CP.hack`
-nearest_neighbour_app="java -Xmx100g -cp ${classpath} MultiSenseEmbeddingBrowse"
-
-${nearest_neighbour_app} --embedding vectors-MSSG.gz --num-neighbour 20

### 2016-03-01 skipgram/demo-mssg.sh

@@ -1,5 +1,0 @@
-#!/bin/sh 
-
-./make_cp.sh     ## compile and make class-path
-./train-mssg.sh  ## train the embeddings 
-./browse-mssg.sh ## browse the nearest-neighbours

### 2016-03-01 skipgram/make_cp.sh

@@ -1,9 +1,0 @@
-#!/bin/sh
-
-mvn compile -X \
-  | grep 'classpathElements = ' \
-  | sed 's#^.* classpathElements = \[\(.*\)\]$#\1#g' \
-  | sed 's#, #:#g' \
-  &> CP.hack
-export MY_CP_PREPROCESS=`cat CP.hack`
-

### 2016-03-01 skipgram/src/CBOWEmbeddingModel.scala

@@ -1,73 +1,0 @@
-// package cc.factorie.app.nlp.embeddings 
-import cc.factorie.util.DoubleAccumulator
-import cc.factorie.la.{DenseTensor1, WeightsMapAccumulator}
-import cc.factorie.optimize.Example
-import scala.collection.mutable
-
-class CBOWNegSamplingEmbeddingModel(override val opts: EmbeddingOpts) extends WordEmbeddingModel(opts) {
-  val negative = opts.negative.value
-  val window = opts.window.value
-  val rng = new util.Random(5) // fix the seed. so that results can replicated on different machines
-  val sample = opts.sample.value.toDouble
-  override def process(doc: String): Int = {
-    // given a document, below line splits by space and converts each word to Int (by vocab.getId) and filters out words not in vocab
-    var sen = doc.stripLineEnd.split(' ').map(word => vocab.getId(word.toLowerCase)).filter(id => id != -1)
-    val wordCount = sen.size
-    
-    // subsampling -> speed increase 
-    if (sample > 0)
-      sen = sen.filter(id => subSample(id) != -1)
-      
-    val senLength = sen.size
-    for (senPosition <- 0 until senLength) {
-      val currWord = sen(senPosition)
-      val b = rng.nextInt(window)
-      val contexts = new mutable.ArrayBuffer[Int]
-      // make the contexts
-      for (a <- b until window * 2 + 1 - b) if (a != window) {
-        val c = senPosition - window + a
-        if (c >= 0 && c < senLength)
-          contexts += sen(c)
-      }
-      // make the examples
-      trainer.processExample(new CBOWNegSamplingExample(this, currWord, contexts, 1))
-      (0 until negative).foreach(neg => trainer.processExample(new CBOWNegSamplingExample(this, currWord, List(vocab.getRandWordId), -1)))
-    }
-    return wordCount
-  }
-  // subsampling 
-  def subSample(word: Int): Int = {
-    val ran = vocab.getSubSampleProb(word) // pre-computed to avoid sqrt call every time. Improvement of 10 secs on 100MB data ~ 15 MINs on 10GB
-    //val cnt = vocab.getCount(word)
-    //val ran = (math.sqrt(cnt / (sample * train_words)) + 1) * (sample * train_words) / cnt
-    val real_ran = rng.nextInt(0xFFFF) / 0xFFFF.toDouble
-    if (ran < real_ran) { return -1 }
-    else return word
-  }
-}
[…]

### 2016-03-01 skipgram/src/Distance.scala

@@ -1,93 +1,0 @@
-// package cc.factorie.app.nlp.embeddings
-import scala.io.Source
-import cc.factorie.la.DenseTensor1
-import scala.collection.mutable.PriorityQueue
-
-object EmbeddingDistance {
-
-  var threshold = 0
-  var vocab = Array[String]()
-  var weights = Array[DenseTensor1]()
-  var D = 0
-  var V = 0
-  var top = 30
-  def main(args: Array[String]) {
-
-    if (args.size != 1) {
-      println("Input vectors file missing. USAGE : distance vectors.txt")
-      return
-    }
-    val inputFile = args(0)
-    load(inputFile)
-    play()
-  }
-
-  def nearestNeighbours(inputFile: String, numNeighbours: Int = 30): Unit = {
-    top = numNeighbours
-    load(inputFile)
-    play()
-  }
-  def load(embeddingsFile: String): Unit = {
-    var lineItr = Source.fromFile(embeddingsFile).getLines
-    // first line is (# words, dimension)
-    val details = lineItr.next.stripLineEnd.split(' ').map(_.toInt)
-    V = if (threshold > 0 && details(0) > threshold) threshold else details(0)
-    D = details(1)
-    println("# words : %d , # size : %d".format(V, D))
-    vocab = new Array[String](V)
-    weights = new Array[DenseTensor1](V)
-    for (v <- 0 until V) {
-      val line = lineItr.next.stripLineEnd.split(' ')
-      vocab(v) = line(0).toLowerCase
-      weights(v) = new DenseTensor1(D, 0) // allocate the memory
-      for (d <- 0 until D) weights(v)(d) = line(d + 1).toDouble
-      weights(v) /= weights(v).twoNorm
-    }
-    println("loaded vocab and their embeddings")
-  }
-  def play(): Unit = {
-
-    while (true) {
-      print("Enter word (EXIT to break) : ")
-      var words = readLine.stripLineEnd.toLowerCase.split(' ').map(word => getID(word)).filter(id => id != -1)
-      if (words.size == 0) {
-        println("words not in vocab")
-      } else {
-        val embedding_in = new DenseTensor1(D, 0)
-        words.foreach(word => embedding_in.+=(weights(word)))
-        embedding_in./=(words.size)
-        var pq = new PriorityQueue[(String, Double)]()(dis)
-        for (i <- 0 until vocab.size) if (words.size != 1 || !words(0).equals(vocab(i))) {
[…]

### 2016-03-01 skipgram/src/EmbeddingOpts.scala

@@ -1,56 +1,0 @@
-//package cc.factorie.app.nlp.embeddings
-import cc.factorie.util.CmdOptions
-
-class EmbeddingOpts extends CmdOptions {
-
-  //
-  // Model
-  //
-  val model                   = new CmdOption("model", "MSSG-KMeans", "STRING", "use <string> name of the model")
-  //
-  // Algorithm related
-  //
-  val dimension               = new CmdOption("size", 200, "INT", "use <int> size of word vectors")
-  val window                  = new CmdOption("window", 5, "INT", "use <int> skip length between words")
-  val threads                 = new CmdOption("threads", 12, "INT", "use <int> threads")
-  val negative                = new CmdOption("negative", 1, "INT", "use <int> number of negative examples")
-  val minCount                = new CmdOption("min-count", 5, "INT", "This will discard words that appear less than <int> times; default is 5")
-  val ignoreStopWords         = new CmdOption("ignore-stopwords", 0, "INT", "use <int> to include or discard stopwords. Use 1 for discarding stopwords")
-  val cbow                    = new CmdOption("cbow", 2, "INT", "user cbow=1 for cbow and cbow=0 for skip-gram")
-  val sample                  = new CmdOption("sample", 0.001, "DOUBLE", "use <double> subsampling")
-  //
-  // Multiple Embeddings Option 
-  //
-  val sense                   = new CmdOption("sense", 5, "INT", "use <int> senses")
-  val bootVectors             = new CmdOption("boot-vectors", "", "STRING", "use <string> vector file")
-  val updateGlobal            = new CmdOption("update-global", 1, "INT", "use 0 to not to update global vectors. works only with bootstrapping")
-  //
-  // Clustering (DP means)
-  //
-  val learnOnlyTop            = new CmdOption("learn-top-v", 4000, "INT", "use <double>")
-  val createClusterLambda     = new CmdOption("create-cluster-lambda", 0.0, "DOUBLE", "use <int> to determine when to create the cluster") 
-  val loadMultiSenseVocabFile = new CmdOption("load-multi-vocab", "", "STRING", "feed 6000 vocab that socher used to learn multiple embeddings")
-  val debeugClusterInfo       = new CmdOption("debug-cluster-info", "", "STRING", "use <debug> info")  
-  //
-  // Optimization related (Don't change if you do not understand how vectors are initialized)
-  //
[…]

### 2016-03-01 skipgram/src/HogWildTrainer.scala

@@ -1,22 +1,0 @@
-
-import cc.factorie.optimize.{ GradientOptimizer, Trainer, Example }
-import cc.factorie.la.SmartGradientAccumulator
-import cc.factorie.util.{ LocalDoubleAccumulator, Threading }
-import cc.factorie.model.WeightsSet
-
-class HogWildTrainer(val weightsSet: WeightsSet, val optimizer: GradientOptimizer, val nThreads: Int = Runtime.getRuntime.availableProcessors(), val maxIterations: Int = 3)
-  extends Trainer {
-
-  var iteration = 0
-  def processExample(e: Example): Unit = {
-    val gradientAccumulator = new SmartGradientAccumulator
-    val value = new LocalDoubleAccumulator()
-    e.accumulateValueAndGradient(value, gradientAccumulator)
-    optimizer.step(weightsSet, gradientAccumulator.getMap, value.value)
-  }
-  def processExamples(examples: Iterable[Example]): Unit = {
-    Threading.parForeach(examples.toSeq, nThreads)(processExample(_))
-  }
-  def isConverged = iteration >= maxIterations
-  
-}

### 2016-03-01 skipgram/src/MultiSenseBrowseEmbedding.scala

@@ -1,248 +1,0 @@
-// package cc.factorie.app.nlp.embeddings
-import scala.io.Source
-import cc.factorie.la.DenseTensor1
-import scala.collection.mutable.PriorityQueue
-import java.util.zip.GZIPInputStream
-import java.io.FileInputStream
-import cc.factorie.util.CmdOptions
-
-
-class BrowseOptions extends CmdOptions {
-   val embedding = new CmdOption("embedding", "", "STRING", "use <string> for filename") 
-   val top       = new CmdOption("num-neighbour", 20, "INT", "use <int> to specify the k in knn")
-}
-
-object MultiSenseEmbeddingBrowse {
-
-  var threshold = 0
-  var vocab         = Array[String]()
-  var weights       = Array[Array[DenseTensor1]]()
-  var ncluster      = Array[Int]()
-  var nclusterCount = Array[Array[Int]]()
-  var D = 0
-  var V = 0
-  var top = 25
-  var S = 0
-  var maxoutMethod = 0
-  def main(args: Array[String]) {
-    val opts  = new BrowseOptions()
-    opts.parse(args)
-    val embeddingFile       = opts.embedding.value
-    top                     = opts.top.value
-    load(embeddingFile)
-    //if (args(3).toInt == 1) 
-    //   displayKNN()          // given the context words, hard pick the sense and show the K-NN
-    //else 
-       play()                // given the word, show the K-NN of all the words
-  }
-
-  def load(embeddingsFile: String): Unit = {
-    var lineItr = embeddingsFile.endsWith(".gz") match {
-      case false => Source.fromFile(embeddingsFile).getLines
-      case true => io.Source.fromInputStream(new GZIPInputStream(new FileInputStream(embeddingsFile)), "iso-8859-1").getLines
-    }
-    // first line is (# words, dimension)
-    val details = lineItr.next.stripLineEnd.split(' ').map(_.toInt)
-    V = if (threshold > 0 && details(0) > threshold) threshold else details(0)
-    D = details(1)
-    S = details(2)
-    maxoutMethod = details(3)
-    println("# words : %d , # size : %d".format(V, D))
-    vocab = new Array[String](V)
-    weights = Array.ofDim[DenseTensor1](V, S+1)
-    ncluster = Array.ofDim[Int](V)
-    nclusterCount = Array.ofDim[Int](V, S)
-    for (v <- 0 until V) {
-      val line = lineItr.next.stripLineEnd.split(' ')
-      vocab(v) = line(0).toLowerCase
[…]

### 2016-03-01 skipgram/src/MultiSenseSkipGramEmbeddingModel.scala

@@ -1,190 +1,0 @@
-import cc.factorie.util.DoubleAccumulator
-import cc.factorie.la.{DenseTensor1, WeightsMapAccumulator}
-import cc.factorie.optimize.Example
-import scala.collection.mutable
-
-class MultiSenseSkipGramEmbeddingModel(override val opts: EmbeddingOpts) extends MultiSenseWordEmbeddingModel(opts) {
-  val negative = opts.negative.value
-  val window = opts.window.value
-  val rng = new util.Random
-  val sample = opts.sample.value.toDouble
-  
-  override def process(doc: String): Int = {
-    // given a document, below line splits by space and converts each word to Int (by vocab.getId) and filters out words not in vocab
-    // id of a word is its freq-rank in the corpus
-    var sen = doc.stripLineEnd.split(' ').map(word => vocab.getId(word.toLowerCase())).filter(id => id != -1)
-    val wordCount = sen.size
-
-    // 
-    // subsampling the words : refer to Google's word2vec NIPS paper to understand this
-    //
-    if (sample > 0)
-      sen = sen.filter(id => subSample(id) != -1)
-
-    val senLength = sen.size
-    for (senPosition <- 0 until senLength) {
-      val currWord = sen(senPosition)
-      
-      //
-      // dynamic window-size as in word2vec. 
-      //
-      val b =  rng.nextInt(window)
-      
-      //
-      // make the contexts
-      //
-      val contexts = new mutable.ArrayBuffer[Int]
-      for (a <- b until window * 2 + 1 - b) if (a != window) {
-        val c = senPosition - window + a
-        if (c >= 0 && c < senLength)
-          contexts += sen(c)
-      }
-      
-      // predict the sense of the word given the contexts. P(word-sense | word, contexts)
-      var rightSense = 0
-      if (kmeans == 1)
-         rightSense  = cbow_predict_kmeans(currWord, contexts)
-      else if (dpmeans == 1)
-          rightSense = cbow_predict_dpmeans(currWord, contexts)
-      else
-          rightSense = cbow_predict(currWord, contexts)
-      
-      // make the examples. trainer is HogWild!
-      contexts.foreach(context => {
-        // postive example
-        trainer.processExample(new MSCBOWSkipGramNegSamplingExample(this, currWord, rightSense, context, 1))
-        // for each POS example, make negative NEG examples. 
[…]

### 2016-03-01 skipgram/src/MultiSenseWordEmbeddingModel.scala

@@ -1,239 +1,0 @@
-import cc.factorie.model.{Parameters, Weights}
-import cc.factorie.optimize.{Trainer, AdaGradRDA}
-import cc.factorie.la.DenseTensor1
-import cc.factorie.util.Threading
-import java.io.{File, PrintWriter}
-import java.util.zip.GZIPInputStream
-import java.io.FileInputStream
-import java.io.OutputStreamWriter
-import java.util.zip.GZIPOutputStream
-import java.io.BufferedOutputStream
-import java.io.FileOutputStream
-
-abstract class MultiSenseWordEmbeddingModel(val opts: EmbeddingOpts) extends Parameters {
-
-  // Algorithm related
-  val D                             = opts.dimension.value           // default value is 200
-  val S                             = opts.sense.value               // default value is 5
-  var V                             = 0                              // vocab size. Will computed in buildVocab() section 
-  protected val minCount            = opts.minCount.value            // default value is 5
-  protected val ignoreStopWords     = opts.ignoreStopWords.value     // default value is 0
-  protected val vocabHashSize       = opts.vocabHashSize.value       // default value is 20 M
-  protected val maxVocabSize        = opts.vocabSize.value           // default value is 1M
-  protected val samplingTableSize   = opts.samplingTableSize.value   // default value is 100 M
-  val updateGlobal                  = if (opts.bootVectors.value.size == 0) 1 else opts.updateGlobal.value.toInt
-  // Optimization Related
-  protected val threads             = opts.threads.value             // default value is 12
-  protected val adaGradDelta        = opts.delta.value               // default value is 0.1
-  protected val adaGradRate         = opts.rate.value                // default value is 0.025 
-  // IO Related
-  val corpus                        = opts.corpus.value              //
-  val storeInBinary                 = opts.binary.value              // default is true
-  val loadVocabFilename             = opts.loadVocabFile.value
-  val saveVocabFilename             = opts.saveVocabFile.value
-  protected val outputFile          = opts.output.value
-  private val encoding              = opts.encoding.value            // default is UTF-8
-  // Sense/Cluster related
[…]

### 2016-03-01 skipgram/src/SkipGramEmbeddingModel.scala

@@ -1,75 +1,0 @@
-//package cc.factorie.app.nlp.embeddings
-import cc.factorie.optimize.Example
-import cc.factorie.la.{DenseTensor1,WeightsMapAccumulator}
-import cc.factorie.util.DoubleAccumulator
-
-class SkipGramNegSamplingEmbeddingModel(override val opts: EmbeddingOpts) extends WordEmbeddingModel(opts) {
-  val negative = opts.negative.value
-  val window = opts.window.value
-  val rng = new util.Random(5) // https://github.com/iesl/Word2Vec.git
-  val sample = opts.sample.value.toDouble
-  override def process(doc: String): Int = {
-    // given a document, below line splits by space and converts each word to Int (by vocab.getId) and filters out words not in vocab
-    var sen = doc.stripLineEnd.split(' ').map(word => vocab.getId(word.toLowerCase)).filter(id => id != -1)
-    val wordCount = sen.size
-
-    // subsampling -> speed increase 
-    if (sample > 0)
-      sen = sen.filter(id => subSample(id) != -1)
-
-    val senLength = sen.size
-    for (senPosition <- 0 until senLength) {
-      val currWord = sen(senPosition)
-      val b = rng.nextInt(window)
-      // make the contexts
-      val contexts = new collection.mutable.ArrayBuffer[Int]
-      for (a <- b until window * 2 + 1 - b) if (a != window) {
-        val c = senPosition - window + a
-        if (c >= 0 && c < senLength)
-          contexts += sen(c)
-      }
-      // make the examples
-      contexts.foreach(context => {
-        trainer.processExample(new SkipGramNegSamplingExample(this, currWord, context, 1))
-        (0 until negative).foreach(neg => trainer.processExample(new SkipGramNegSamplingExample(this, currWord, vocab.getRandWordId, -1)))
-      })
-    }
-    return wordCount
-  }
-
-  def subSample(word: Int): Int = {
-    val ran = vocab.getSubSampleProb(word) // pre-computed to avoid sqrt call every time. Improvement of 10 secs on 100MB data ~ 15 MINs on 10GB
-    //val cnt = vocab.getCount(word)
-    //val ran = (math.sqrt(cnt / (sample * train_words)) + 1) * (sample * train_words) / cnt
-    val real_ran = rng.nextInt(0xFFFF) / 0xFFFF.toDouble
-    if (ran < real_ran) { return -1 }
-    else return word
-  }
-}
-
[…]

### 2016-03-01 skipgram/src/VocabBuilder.scala

@@ -1,227 +1,0 @@
-//package cc.factorie.app.nlp.embeddings
-import cc.factorie.util.Threading
-import cc.factorie.app._
-import scala.collection.mutable.ArrayBuffer
-import scala.math
-import scala.util.{Sorting, Random}
-import java.util.zip.{GZIPInputStream, GZIPOutputStream}
-import java.io.{OutputStreamWriter, BufferedOutputStream, FileInputStream, FileOutputStream}
-
-
-class VocabBuilder(vocab_hash_size: Int = 20e6.toInt, sampling_table_size: Int = 1e8.toInt, load_factor: Double = 0.7) {
-
-  // Highly Optimized hash table using linear probing 
-  private var vocab_max_size = 1000
-  private var vocab_size = 0
-  private var min_reduce = 1
-  private val power: Double = 0.75
-
-  // assign internal params 
-  private val rng = new Random(5) // fix the seed
-  private var train_words = 0
-  private var prev_vocab_size = 0
-
-  // allocate data structures
-  private var vocab_hash = new Array[Int](vocab_hash_size) // vocab_hash stores pointer to the vocab array 
-  private var vocab = new Array[vocab_word](vocab_max_size) //  vocab array holds the (word, cnt) pairs. In future, huffman encoding will be added. 
-  private var sampling_table = new Array[Int](sampling_table_size)
-  private var sub_sampling_table = new Array[Double](vocab_size)
-
-  (0 until vocab_hash_size).foreach(i => vocab_hash(i) = -1)
-  (0 until vocab_max_size).foreach(i => vocab(i) = null)
-
-  def size(): Int = vocab_size
-  def trainWords(): Long = {
-    // compute only if the vocab has changed .
-    if (prev_vocab_size != vocab_size) {
-      train_words = 0
-      vocab.foreach(word => train_words += word.cn)
-      prev_vocab_size = vocab_size
-    }
-    train_words
-  }
-
-  def addWordToVocab(key: String): Unit = {
-    val id = getId(key)
-    if (id == -1) {
-      vocab(vocab_size) = new vocab_word(1, key)
-      vocab_size += 1
-      // resize vocab array 
-      if (vocab_size + 2 >= vocab_max_size) {
-        vocab_max_size += 1000
-        var vocab1 = new Array[vocab_word](vocab_max_size)
-        (0 until vocab_size).foreach(i => vocab1(i) = vocab(i))
[…]

### 2016-03-01 skipgram/src/WordEmbeddingModel.scala

@@ -1,130 +1,0 @@
-//package cc.factorie.app.nlp.embeddings
-import cc.factorie.model.{Parameters, Weights}
-import cc.factorie.optimize.{Trainer, AdaGradRDA}
-import cc.factorie.la.DenseTensor1
-import cc.factorie.util.Threading
-import java.io.{File, PrintWriter, OutputStreamWriter, FileOutputStream, FileInputStream, BufferedOutputStream}
-import java.util.zip.{GZIPOutputStream, GZIPInputStream}
-
-
-abstract class WordEmbeddingModel(val opts: EmbeddingOpts) extends Parameters {
-
-  // Algo related
-  val D = opts.dimension.value // default value is 200
-  var V: Int = 0 // vocab size. Will computed in buildVocab() section 
-  protected val threads = opts.threads.value //  default value is 12
-  protected val adaGradDelta = opts.delta.value // default value is 0.1
-  protected val adaGradRate = opts.rate.value //  default value is 0.025 
-  protected val minCount = opts.minCount.value // default value is 5
-  protected val ignoreStopWords = opts.ignoreStopWords.value // default value is 0
-  protected val vocabHashSize = opts.vocabHashSize.value // default value is 20 M. load factor is 0.7. So, Vocab size = 0.7 * 20M = 14M vocab supported which is sufficient enough for large amounts of data
-  protected val samplingTableSize = opts.samplingTableSize.value // default value is 100 M
-  protected val maxVocabSize = opts.vocabSize.value
-  
-  // IO Related
-  val corpus = opts.corpus.value // corpus input filename. Code takes cares of .gz extension 
-  protected val outputFilename = opts.output.value // embeddings output filename
-  private val storeInBinary = opts.binary.value // binary=1 will make both vocab file (optional) and embeddings in .gz file
-  private val loadVocabFilename = opts.loadVocabFile.value // load the vocab file. Very useful for large corpus should you run multiple times 
-  private val saveVocabFilename = opts.saveVocabFile.value // save the vocab into a file. Next time for the same corpus, load it . Saves lot of time on large corpus
-  private val encoding = opts.encoding.value // Default is ISO-8859-15. Note: Blake server follows iso-5589-1 (david's GoogleEmbeddingcode has this. shouldn;t be ISO-8859-15) or  iso-5589-15 encoding (I see this) ??
-  
-  // data structures
-  protected var vocab: VocabBuilder = null 
[…]

### 2016-03-01 skipgram/src/WordEmbeddingUtils.scala

@@ -1,134 +1,0 @@
-//package cc.factorie.app.nlp.embeddings
-import cc.factorie.la._
-import scala.util.Random
-import java.io.{FileReader, RandomAccessFile}
-import java.io.InputStreamReader
-import java.nio.charset.Charset
-import java.io.BufferedReader
-import java.io.FileInputStream
-import java.util.zip.GZIPInputStream
-import java.io.DataInputStream
-import java.io.BufferedInputStream
-import java.io.File
-
-class FastWordReader(file: String, encoding: String = "ISO-8859-15") extends Iterator[String] {
-  private var in = file.endsWith(".gz") match {
-    case false => new BufferedReader(new InputStreamReader(new FileInputStream(file), encoding))
-    case true => new BufferedReader(new InputStreamReader(new GZIPInputStream(new FileInputStream(file)), encoding))
-  }
-  private var sb: StringBuilder = null
-  moveToNext()
-
-  private def moveToNext(): Unit = {
-    sb = new StringBuilder()
-    var c = in.read // read char
-    // go inside only if c is bad char
-    while (c != -1 && (c == '\n' || c == '\t' || c == ' ' || c == '\r')) c = in.read
-
-    // go inside only if c is good char
-    while (c != -1 && c != '\n' && c != '\t' && c != ' ' && c != '\r') {
-      sb.+=(c.toChar) // add the good char
-      c = in.read() //  read next char
-    }
-  }
-
-  def hasNext(): Boolean = sb.length() > 0
-  def next(): String = { moveToNext; sb.toString }
-
-}
-
-class FastLineReader(file: String, skipBytes: Long = 0, encoding: String = "ISO-8859-15") extends Iterator[String] {
-  //private var in = new FileReader(file)
-  private var sb: StringBuilder = null
-  private var line: String = null
-  private var in = file.endsWith(".gz") match {
-    case false => new BufferedReader(new InputStreamReader(new FileInputStream(file), encoding))
-    case true => new BufferedReader(new InputStreamReader(new GZIPInputStream(new FileInputStream(file)), encoding))
-  }
-  //println("Default charset of this JVM : " + in.getEncoding() + ", so using " + in.getEncoding() +  " to read the input file")
-  in.skip(skipBytes)
-  moveToNext()
-
-  private def moveToNext(): Unit = {
-    sb = new StringBuilder()
[…]

### 2016-03-01 skipgram/src/WordVec.scala

@@ -1,31 +1,0 @@
-// package cc.factorie.app.nlp.embeddings
-import java.nio.charset.Charset
-
-object WordVec {
-  def main(args: Array[String]) {
-    val opts = new EmbeddingOpts
-    opts.parse(args)
-    println("Default Charset of this JVM =" + Charset.defaultCharset());
-    println("User Provided Charset for this project=" + opts.encoding.value)
-    
-    val is_valid_model = opts.model.value.equals("MSSG-KMeans") || opts.model.value.equals("MSSG-MaxOut") || opts.model.value.equals("NP-MSSG")
-    if (is_valid_model) { 
-      println("Leanring Multiple Embeddings using " + opts.model.value)
-      val wordEmbedding = new MultiSenseSkipGramEmbeddingModel(opts)
-      val st1 = System.currentTimeMillis()
-      wordEmbedding.buildVocab()
-      val st = System.currentTimeMillis()
-      println("time taken to build vocab : " + (st - st1) / 1000.0)
-      wordEmbedding.learnEmbeddings()
-      val en = System.currentTimeMillis() - st
-      println("time taken to learn embedding : " + en / 1000.0)
-      wordEmbedding.store()
-    }
-    else {
-      println("InValid Model-" + opts.model.value)
-      println("Model Options are - MSSG-KMeans, MSSG-MaxOut, NP-MSSG")
-      return 
-    }
-    
-  }
-}

### 2016-03-01 skipgram/src/preprocess.scala

@@ -1,35 +1,0 @@
-import cc.factorie.app.nlp.segment.DeterministicTokenizer
-import cc.factorie.app.nlp.segment.DeterministicSentenceSegmenter
-import cc.factorie.app.nlp.Document
-import java.io.PrintWriter
-import java.nio.charset.Charset
-
-object preprocess {
-  def main(args : Array[String]) {
-      println("Default Charset=" + Charset.defaultCharset());
-    	println("file.encoding=" + System.getProperty("file.encoding"));
-    	
-      val inputFile = args(0)
-      val outFile = args(1)
-      val out = new PrintWriter(outFile, "ISO-8859-15")
-      val tokenizer = new DeterministicTokenizer
-      val sen_tokenizer = new DeterministicSentenceSegmenter
-      for (line <- io.Source.fromFile(inputFile, "ISO-8859-15").getLines) {
-            
-            val doc = new Document(line)
-            tokenizer.process(doc)
-            sen_tokenizer.process(doc)
-            if (doc.tokens.size > 10) {
-              for (token <- doc.tokens)
-                out.print(token.string + " ")
-               out.print("\n")
-               out.flush()
-            }
-            else {
-              println(doc.tokens.toArray)
-            }
-            
-      }
-      out.close()
-  }
-}

### 2016-03-01 skipgram/train-mssg.sh

@@ -1,16 +1,0 @@
-#!/bin/sh
-
-if [ ! -e text8 ]; then
-  wget https://dl.dropboxusercontent.com/u/39534006/text8.zip
-  unzip text8.zip
-fi
-
-if [ ! -e CP.hack ]; then
-    echo "Run make_cp.sh script first"
-    exit    
-fi
-
-classpath=`cat CP.hack`
-wordvec_app="java -Xmx100g -cp ${classpath} WordVec"
-
-${wordvec_app}  --model=MSSG-MaxOut --train=text8 --output=vectors-MSSG.gz --sense=2 --learn-top-v=4000 --size=300 --window=5 --min-count=15  --threads=23  --negative=1 --sample=0.001 --binary=1 --ignore-stopwords=1 --encoding=ISO-8859-15 --save-vocab=text8.vocab.gz --rate=0.025 --delta=0.1                    

### 2016-03-06 factorie/src/main/scala/cc/factorie/app/nlp/embeddings/CBOWEmbeddingModel.scala
Imported factorie and multisense without preprocess.scala to prevent unnecessary errors

@@ -1,4 +1,4 @@
-// package cc.factorie.app.nlp.embeddings 
+package cc.factorie.app.nlp.embeddings
 import cc.factorie.util.DoubleAccumulator
 import cc.factorie.la.{DenseTensor1, WeightsMapAccumulator}
 import cc.factorie.optimize.Example

### 2016-03-06 factorie/src/main/scala/cc/factorie/app/nlp/embeddings/Distance.scala

@@ -1,4 +1,4 @@
-// package cc.factorie.app.nlp.embeddings
+package cc.factorie.app.nlp.embeddings
 import scala.io.Source
 import cc.factorie.la.DenseTensor1
 import scala.collection.mutable.PriorityQueue

### 2016-03-06 factorie/src/main/scala/cc/factorie/app/nlp/embeddings/EmbeddingOpts.scala

@@ -1,4 +1,4 @@
-//package cc.factorie.app.nlp.embeddings
+package cc.factorie.app.nlp.embeddings
 import cc.factorie.util.CmdOptions
 
 class EmbeddingOpts extends CmdOptions {
@@ -52,5 +52,6 @@ class EmbeddingOpts extends CmdOptions {
   val vocabHashSize           = new CmdOption("vocab-hash-size", 14.3e6.toInt, "INT", "Vocabulary hash size")
   val samplingTableSize       = new CmdOption("sampling-table-size", 1e8.toInt, "INT", "Sampling Table size")
 
-  
+  val includeEdgeLabels       = new CmdOption("include-edge-labels", false, "BOOLEAN", "Should edges be taken into account when generating vocabulary?")
+
 }

### 2016-03-06 factorie/src/main/scala/cc/factorie/app/nlp/embeddings/HogWildTrainer.scala

@@ -1,4 +1,4 @@
-
+package cc.factorie.app.nlp.embeddings
 import cc.factorie.optimize.{ GradientOptimizer, Trainer, Example }
 import cc.factorie.la.SmartGradientAccumulator
 import cc.factorie.util.{ LocalDoubleAccumulator, Threading }

### 2016-03-06 factorie/src/main/scala/cc/factorie/app/nlp/embeddings/MultiSenseSkipGramEmbeddingModel.scala

@@ -1,3 +1,4 @@
+package cc.factorie.app.nlp.embeddings
 import cc.factorie.util.DoubleAccumulator
 import cc.factorie.la.{DenseTensor1, WeightsMapAccumulator}
 import cc.factorie.optimize.Example

### 2016-03-06 factorie/src/main/scala/cc/factorie/app/nlp/embeddings/SkipGramEmbeddingModel.scala

@@ -1,4 +1,4 @@
-//package cc.factorie.app.nlp.embeddings
+package cc.factorie.app.nlp.embeddings
 import cc.factorie.optimize.Example
 import cc.factorie.la.{DenseTensor1,WeightsMapAccumulator}
 import cc.factorie.util.DoubleAccumulator

### 2016-03-06 factorie/src/main/scala/cc/factorie/app/nlp/embeddings/VocabBuilder.scala

@@ -1,4 +1,4 @@
-//package cc.factorie.app.nlp.embeddings
+package cc.factorie.app.nlp.embeddings
 import cc.factorie.util.Threading
 import cc.factorie.app._
 import scala.collection.mutable.ArrayBuffer

### 2016-03-06 factorie/src/main/scala/cc/factorie/app/nlp/embeddings/WordEmbeddingModel.scala

@@ -1,4 +1,4 @@
-//package cc.factorie.app.nlp.embeddings
+package cc.factorie.app.nlp.embeddings
 import cc.factorie.model.{Parameters, Weights}
 import cc.factorie.optimize.{Trainer, AdaGradRDA}
 import cc.factorie.la.DenseTensor1

### 2016-03-06 factorie/src/main/scala/cc/factorie/app/nlp/embeddings/WordEmbeddingUtils.scala

@@ -1,4 +1,4 @@
-//package cc.factorie.app.nlp.embeddings
+package cc.factorie.app.nlp.embeddings
 import cc.factorie.la._
 import scala.util.Random
 import java.io.{FileReader, RandomAccessFile}

### 2016-03-06 factorie/src/main/scala/cc/factorie/app/nlp/embeddings/NodeEmbeddingModel.scala
Added NodeEmbeddingModel file

@@ -57,7 +57,7 @@ abstract class NodeEmbeddingModel(val opts: EmbeddingOpts) extends Parameters {
     }
     else vocab.loadVocab(loadVocabFilename, encoding)
 
-    vocab.sortVocab(minCount, if(ignoreStopWords) 1 else 0, maxVocabSize) // removes words whose count is less than minCount and sorts by frequency
+    vocab.sortVocab(minCount, ignoreStopWords, maxVocabSize) // removes words whose count is less than minCount and sorts by frequency
     vocab.buildSamplingTable() // for getting random word from vocab in O(1) otherwise would O(log |V|)
     vocab.buildSubSamplingTable(opts.sample.value) // precompute subsampling table
     V = vocab.size()

### 2016-03-06 factorie/src/main/scala/cc/factorie/app/nlp/embeddings/NodeEmbeddingModel.scala
Changed vocabulary creation to assume triples

@@ -9,7 +9,7 @@ import java.util.zip.{GZIPOutputStream, GZIPInputStream}
 
 
 abstract class NodeEmbeddingModel(val opts: EmbeddingOpts) extends Parameters {
-  implicit def bool2int(b:Boolean) = if (b) 1 else 0 // Converts booleans to ints when needed
+  implicit def bool2int(b:Boolean): Int = if (b) 1 else 0 // Converts booleans to ints when needed
   // Algo related
   val D = opts.dimension.value // default value is 200
   var V: Int = 0 // vocab size. Will computed in buildVocab() section
@@ -43,16 +43,19 @@ abstract class NodeEmbeddingModel(val opts: EmbeddingOpts) extends Parameters {
   def buildVocab(): Unit = {
     vocab = new VocabBuilder(vocabHashSize, samplingTableSize, 0.7) // 0.7 is the load factor
     println("Building Vocab")
-    if (loadVocabFilename.size == 0) {
+    if (loadVocabFilename.isEmpty) {
       val corpusLineItr = corpus.endsWith(".gz") match {
         case true => io.Source.fromInputStream(new GZIPInputStream(new FileInputStream(corpus)), encoding).getLines
         case false => io.Source.fromInputStream(new FileInputStream(corpus), encoding).getLines
       }
       while (corpusLineItr.hasNext) {
         val line = corpusLineItr.next
-        if (opts.includeEdgeLabels.value)
-          line.stripLineEnd.split(' ').foreach(word => vocab.addWordToVocab(word.toLowerCase())) // addWordToVocab() will incr by count. TODO : make this also parallel ? but it is an one time process, next time use load-vocab option
-
+        if (opts.includeEdgeLabels.value){
+          println("Edge labels no implemented yet")
+          System.exit(1)
+        }
+        var words = line.stripLineEnd.split(' ')
+        Array(0,2).foreach(i => vocab.addWordToVocab(words(i).toLowerCase)) // Only first and third labels are nodes/conceps
       }
     }
     else vocab.loadVocab(loadVocabFilename, encoding)
@@ -64,7 +67,7 @@ abstract class NodeEmbeddingModel(val opts: EmbeddingOpts) extends Parameters {
     train_nodes = vocab.trainWords()
     println("Corpus Stat - Vocab Size :" + V + " Total words (effective) in corpus : " + train_nodes)
     // save the vocab if the user provides the filename save-vocab
-    if (saveVocabFilename.size != 0) {
[…]

### 2016-03-06 factorie/src/main/scala/cc/factorie/app/nlp/embeddings/NodeEmbeddingModel.scala
Finished generic NodeEmbeddingModel

@@ -114,7 +114,7 @@ abstract class NodeEmbeddingModel(val opts: EmbeddingOpts) extends Parameters {
 
 
   protected def workerThread(id: Int, fileLen: Long, printAfterNDoc: Long = 100): Unit = {
-    val skipBytes: Long = fileLen / threads * id // fileLen now pre-computed before pasing to all threads. skip bytes. skipped bytes is done by other workers
+    val skipBytes: Long = fileLen / threads * id // fileLen now pre-computed before passing to all threads. skip bytes. skipped bytes is done by other workers
     val lineItr = new FastLineReader(corpus, skipBytes, encoding)
     var word_count: Long = 0
     var work = true
@@ -126,7 +126,7 @@ abstract class NodeEmbeddingModel(val opts: EmbeddingOpts) extends Parameters {
       if (id == 1 && ndoc % printAfterNDoc == 0) {  // print the process after processing 100 docs in 1st thread. It approx reflects the total progress
         println("Progress : " + word_count / total_words_per_thread.toDouble * 100 + " %")
       }
-      if (word_count > total_words_per_thread) work = false // Once, word_count reaches this limit, ask worker to end
+      work = word_count <= total_words_per_thread // Once, word_count reaches this limit, ask worker to end
     }
     // println("thread :" + id + " word count : " + word_count)
   }

### 2016-03-07 Paper/Draft.tex
Small changes to the draft
Restored part of the lost draft

@@
  \section{Introduction}
+ % Voorbeeld van semantisch web
 
@@
  On the Semantic Web, ontologies are used to define and share knowledge.
+The term ontology will be properly defined later on, but for now it suffices to know that an ontology is a set of rules that determine what relations are allowed and required.
+On the semantic web, ontologies are the foundation for communication between agents.
+
+ However, on the Semantic Web it is infeasible to use one single ontology, since the number of concepts it would have to contain is incredibly large.
+The larger an ontology the longer it takes to perform inference and searches on it, and thus to longer it takes to use it for communication.
+Therefore the semantic web will have separate ontologies for every domain.
+The downside of this approach is that when communication requires rules on multiple domains, which it often does, multiple ontologies need to be aligned or merged.
  \subsection{Problem}
- When knowledge bases are combined, their ontologies need to be merged.
+ We have seen that when information from multiple domains need to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged.
+Those ontologies contain rules about concepts and concept classes in the shape of triplets, with two concepts and a relation.
+For example, the rule{\tt Professors are humans} contains the concepts \emph{Professor} and \emph{human} and relationship \emph{being}.
+
+ If we want to merge two ontologies, we need to find the concepts from the different ontologies that are related by an 'is-same-as' or other rule.
+
+ However, since the ontologies are made for different domains, the same concept can be represented by different labels in the two ontologies.
+This problem is called the synonymy problem, as synonyms are two words that refer to the same concepts.
+
+ The opposite problem is called the homonymy problem, in which two concepts are represented by the same label.
+Since they have the same label, naive algorithms might align the concepts as being the same, when they are not.
+
+ Then there is the problem of ambiguity, which encompasses many other problems.
+It encompasses the fact that some concepts are used wrongly by humans, but also the fact that some concepts are extremely similar, and may occur in the same context, but are still slightly different.
+
+ Lastly, there is the problem of 
  \subsection{Research questions}
@@
 For example, the system might use just the information 'isMarriedTo' to infer that someone is a human, but may infer that 'isMarriedTo' in combination with a man usually refers to a woman.
-  %  Ja doe maar een ander voorbeeld ivm gelijkheid e.d.\endcomment
+  %  Ja doe maar een ander voorbeeld ivm gelijkheid e.d.
   \subsubsection{Hot start}
@@
 It is not logical
-  %  Goeie woord?\endcomment
+  %  Goeie woord?
   since it does not use inference. Nor is it terminological, which looks at dictionaries or other ontologies to find matches. However, it does use other ontologies (or text corpi
-  % Check spelling\endcomment
+  % Check spelling
   ) implicitly, so if it must be grouped it would be terminological.
-  % Moet voorafgaand stukje op een andere plek?\endcomment
+  % Moet voorafgaand stukje op een andere plek?
   The algorithm can find matches based purely on the given node and edge labels.
@@
 However, if we compare the cold and hot algorithms with the generic string matchers, we may be able to compare them indirectly.
-  % Dit moet weg als het bs blijkt te zijn\endcomment
+  % Dit moet weg als het bs blijkt te zijn
  \subsection{Discarded possibilities} % Rename
@@
 The relation may be inferred from one sentence, or many different documents.
-  % Herschrijf dit aub want het is niet goed\endcomment
+  % Herschrijf dit aub want het is niet goed
   \subsubsection{Just context nodes}

### 2016-03-07 Paper/Draft.tex
Restructured so that context if before problem

@@
 
- \section{Problem}
  \subsection{Short Context}
@@
 The downside of this approach is that when communication requires rules on multiple domains, which it often does, multiple ontologies need to be aligned or merged.
- \subsection{Problem}
- We have seen that when information from multiple domains need to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged.
-Those ontologies contain rules about concepts and concept classes in the shape of triplets, with two concepts and a relation.
-For example, the rule{\tt Professors are humans} contains the concepts \emph{Professor} and \emph{human} and relationship \emph{being}.
-
- If we want to merge two ontologies, we need to find the concepts from the different ontologies that are related by an 'is-same-as' or other rule.
-
- However, since the ontologies are made for different domains, the same concept can be represented by different labels in the two ontologies.
-This problem is called the synonymy problem, as synonyms are two words that refer to the same concepts.
-
- The opposite problem is called the homonymy problem, in which two concepts are represented by the same label.
-Since they have the same label, naive algorithms might align the concepts as being the same, when they are not.
-
- Then there is the problem of ambiguity, which encompasses many other problems.
-It encompasses the fact that some concepts are used wrongly by humans, but also the fact that some concepts are extremely similar, and may occur in the same context, but are still slightly different.
-
- Lastly, there is the problem of 
- \subsection{Research questions}
-
- \subsection{Hypotheses}
-
- \subsection{Justification}
- Reliable, error proof ontology matching will be key for the distributed Semantic Web.
 
@@
  %http://disi.unitn.it/~p2p/RelatedWork/Matching/vldb2009-revised.pdf
+
+ \section{Problem}
+
+ \subsection{Problem}
+ We have seen that when information from multiple domains need to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged.
+Those ontologies contain rules about concepts and concept classes in the shape of triplets, with two concepts and a relation.
+For example, the rule{\tt Professors are humans} contains the concepts \emph{Professor} and \emph{human} and relationship \emph{being}.
+
+ If we want to merge two ontologies, we need to find the concepts from the different ontologies that are related by an 'is-same-as' or other rule.
+
+ However, since the ontologies are made for different domains, the same concept can be represented by different labels in the two ontologies.
+This problem is called the synonymy problem, as synonyms are two words that refer to the same concepts.
+
+ The opposite problem is called the homonymy problem, in which two concepts are represented by the same label.
+Since they have the same label, naive algorithms might align the concepts as being the same, when they are not.
+
+ Then there is the problem of ambiguity, which encompasses many other problems.
+It encompasses the fact that some concepts are used wrongly by humans, but also the fact that some concepts are extremely similar, and may occur in the same context, but are still slightly different.
+
+ Lastly, there is the problem of different types of alignment relations.
+For example, one concept can be a \emph{part of} another concept, or an example of one.
+These different relations all require a different approach and come with their own sets of problems.
+
+ In summary, ontology aligning is required for multi-domain communication but poses a number of problems that make it difficult for concepts, the building blocks of ontologies, to be matched.
+ \subsection{Research questions}
+
+ \subsection{Hypotheses}
+
+ \subsection{Justification}
+ Reliable, error proof ontology matching will be key for the distributed Semantic Web.
+
  \section{Method}

### 2016-03-11 Paper/Draft.tex
Added a few comments
Wrote introduction

@@
  \maketitle
+ \newpage
 
@@
  \section{Introduction}
- % Voorbeeld van semantisch web
+ % Voorbeeld van semantisch web?
+ It is a Friday afternoon and you realise you want to watch a movie with some friends. So, what do you do? To achieve this goal you must take 4 steps.
+
+ Firstly, you must open up an internet Movie Database, search for movies that you like that are also playing this weekend.
+To do this you must either manually go through the list of movies playing this weekend or movies the Database recommends for you and check if any movies on that list match your full criteria.
+
+ Once you have found one or more movies that match your search criteria, you have to select a time at which you can see the candidate movies, so you check for every movie every available time slot at every cinema near you.
+The number of time slots is equal to the number of movies you chose in the previous step, times the number of cinemas near you times the number of times every movie is shown at one cinema.
+
+ The next step is to filter the number of time slots based on your agenda, so you cross-reference the available movie times with the times you are available during the weekend.
+
+ Then onto the last step, getting friends to go with you.
+In this step you do not want to burden your friends to much by having them pick both the movie and the time, so you will have to decide which movie to watch or when, even though you do not know if your friends will like this movie or are available at that time.
+Once you contact your friends, most of them do not respond as they are not online at that time or they do not feel like filling in a poll about availability or movie choices.
+
+ What would happen if this process was automated?
+The first step, finding movies that match two criteria would be considered trivial with modern technology.
+One finds the two lists of movies that are recommended for you and movies that are playing this weekend and intersect them.
+A ranking can be added based on how expensive the tickets are, how certain it is that you may like the movie, and other factors.
+
+ The second step, cross-referencing the list of movies with cinema play times, would already be harder.
+Most of the time the cinema play times are written in a human-readable format, something that is often hard to incorporate for a computer.
+Either the play times have to be made in a computer-readable format or a computer has to interpret them and convert them into computer-readable.
+However, errors might occur because the local cinema labelled a sequel as "Movie II" whereas the list we have has it labelled as "Movie 2".
+
+ Checking an agenda to find an appropriate time would be easy if the times from the cinemas can be transformed to the same format as your agenda.
+If we are automating the process, we may be able to add more features, like changing standing appointments (of course incurring a penalty to the score of that time spot) and such.
+
+ The last step, contacting friends can be done in one click.
+Let us call the program that automated the first three steps a \emph{softbot} and assume they are universal, i.e.
+everyone has one.
+Rather than bothering your friends with scheduling, your softbot can contact those of your friends and find the movie and time slot that optimize a cost function, taking into account which friends you like the most, which movie everybody likes the most and at which time the fewest dinners with wives need to be moved.
+Once this best time is chosen, everyone gets an invite to see the movie and once it is known who will go, a car pooling route is calculated and you can sit back an enjoy your Friday afternoon with no planning or scheduling required.
+
+ The most amazing thing about this story, is that it is already possible with the current technology.
+The algorithms to convert for example cinema website text to computer-readable format exist.
+Many open databases already contain a lot of structured data that can be used to reason about data.
+
+ Three things are required before this web of computers who communicate and understand, this Semantic Web, will come into existence. The first thing is ???. 
+ Secondly, it needs to be adopted by humans.
+They must see the value of these personal assistants that can schedule things for you, that take into account your personal context when searching the web, that understand questions and can ask you for more information that can improve the search.
+People have to realise that the current search engines are not good enough, and that having to read through many papers to find the one nugget of information or the one connection that you are looking for is not acceptable or necessary.
+ Lastly, the different knowledge bases and unstructured texts need to be aligned.
+This means that softbots should be able to reason about facts that are contained in different domains and documents.
+This last problem is the one that I will work on in this thesis.
+Once we can combine the information from different databases and unstructured text, the Semantic Web is technically possible and only needs to be socially accepted before it will become the norm.
 
@@
 When the user accepts, the appointment is automatically added to his agenda.
+% Mogelijk verplaatsen naar introduction
 

### 2016-03-11 Paper/Draft.tex
2 comments

@@
 
- Three things are required before this web of computers who communicate and understand, this Semantic Web, will come into existence. The first thing is ???. 
- Secondly, it needs to be adopted by humans.
+ Two things are required before this web of computers who communicate and understand, this Semantic Web, will come into existence. 
+ Firstly, the Semantic Web needs to be adopted by humans.
 They must see the value of these personal assistants that can schedule things for you, that take into account your personal context when searching the web, that understand questions and can ask you for more information that can improve the search.
@@
 
+ % This should actually be quite long since the whole context section is probably going to be ~10 pages, so 1 page is still fairly short.
+With a context too short a lot of information gets lost and it comes across as cluttered.
+
 \section{Context}
+% Give an overview of the section
  In this section I will discuss all concepts that are required to understand the study.

### 2016-03-11 factorie/src/main/scala/cc/factorie/app/nlp/embeddings/EmbeddingOpts.scala
SkipGramNodeEmbedding debugged

@@ -14,7 +14,7 @@ class EmbeddingOpts extends CmdOptions {
   val window                  = new CmdOption("window", 5, "INT", "use <int> skip length between words")
   val threads                 = new CmdOption("threads", 12, "INT", "use <int> threads")
   val negative                = new CmdOption("negative", 1, "INT", "use <int> number of negative examples")
-  val minCount                = new CmdOption("min-count", 5, "INT", "This will discard words that appear less than <int> times; default is 5")
+  val minCount                = new CmdOption("min-count", 3, "INT", "This will discard words that appear less than <int> times; default is 5")
   val ignoreStopWords         = new CmdOption("ignore-stopwords", 0, "INT", "use <int> to include or discard stopwords. Use 1 for discarding stopwords")
   val cbow                    = new CmdOption("cbow", 2, "INT", "user cbow=1 for cbow and cbow=0 for skip-gram")
   val sample                  = new CmdOption("sample", 0.001, "DOUBLE", "use <double> subsampling")

### 2016-03-11 factorie/src/main/scala/cc/factorie/app/nlp/embeddings/SkipGramNodeEmbedding.scala

@@ -8,26 +8,29 @@ class SkipGramNodeEmbedding(override val opts: EmbeddingOpts) extends NodeEmbedd
   val sample = opts.sample.value.toDouble
   override def process(doc: String): Int = {
     val words = doc.split(' ')
-    val concepts = Array(words(0), words(2)).map(concept => vocab.getId(concept.toLowerCase)).filter(id => id != -1)
+    val concepts = Array(words(0), words(2)).map(concept => vocab.getId(concept.toLowerCase))
     val conceptCount = 2
 
     for (i <- 0 until 2) {
-      val context = new collection.mutable.ArrayBuffer[Int]
-      context += concepts(1-i) // Add the other concept
-      if (bidirectional)
-        println("Bidirectionality not implemented yet") //TODO: implement bidirectionality
-      else if (addInvertedEdges)
-        println("Inverted edges not implemented yet") //TODO: implement inverted edges
-      else if (i==1) // Otherwise parents are not in context so no training required
-        break
+      if (concepts(i) != -1) {
+        var context = new collection.mutable.ArrayBuffer[Int]
+        context += concepts(1 - i) // Add the other concept
+        if (bidirectional)
+          println("Bidirectionality not implemented yet") //TODO: implement bidirectionality
+        else if (addInvertedEdges)
+          println("Inverted edges not implemented yet") //TODO: implement inverted edges
+        else if (i == 1) // Otherwise parents are not in context so no training required
+          break
 
-      if (combineContext)
-        println("Combined context not implemented yet") //TODO: implement context combining
-      else
-        context.foreach(context => {
-          trainer.processExample(new SkipGramNegSamplingExample(this, concepts(i), context, 1))
-          (0 until negative).foreach(neg => trainer.processExample(new SkipGramNegSamplingExample(this, concepts(i), vocab.getRandWordId, -1)))
-        })
+        context = context.filter(v => v != -1)
+        if (combineContext)
+          println("Combined context not implemented yet") //TODO: implement context combining
+        else
+          context.foreach(context => {
+            trainer.processExample(new SkipGramNegSamplingExample(this, concepts(i), context, 1))
+            (0 until negative).foreach(neg => trainer.processExample(new SkipGramNegSamplingExample(this, concepts(i), vocab.getRandWordId, -1)))
+          })
+      }
     }
     return conceptCount
   }

### 2016-03-14 Paper/Draft.tex
Added to the Goal subsection

@@
  \section*{Summary}
-
+ %TODO explain why one large ontology won't work
  \tableofcontents
@@
 Of course, then the goal resets and we should make more applications leveraging more information for more tasks.
+
+ Ultimately, the goal is to leverage all information that is available to an entity on the internet to improve the lives of humans.
+This information is not limited to the information that is online \emph{now}, but can include sensor data from the Internet of Things, data from robots, facts deduced or statistically inferred from existing data and so on.
+All this information can be used to accommodate the wants and needs of humans, when asked for it but also before the users are even aware of their needs.
+The personal agent should be able to predict the users need and provide the tools that can satisfy the need.
+
+ To provide these tools to the user, an agent uses many different sources.
+For example, if the need of a researcher is knowledge on a certain topic, the agent must chart relevant topics, map relations between different domains and connect these new ideas to topics the researcher already knows about.
+In fact, the largest part of the job an agent has to carry out on the Semantic Web is finding relationships between pieces of information on the Web.
+Based on this observation, we can state that Ontology and Knowledge Base Alignment is the cornerstone  of the Semantic Web, since without this vital system the Web is merely a collection of separate pieces of information.
+Only when those pieces are aligned can we talk of knowledge, of semantics.
+
+ To summarize, the goal of the Semantic Web is to connect all online information to help humans.
+Only when all information can be connected will it be possible to aid humans in their needs.
+But humans will only accept the Semantic Web if it is useful to them, so the Semantic Web must show its applications and usefulness before it will be used in daily life.
  \subsubsection{Current state}
-
  \subsubsection{Technologies}

### 2016-03-15 Paper/Draft.tex
Saved a few comments
Added skeleton for Current State

@@
  \section*{Summary}
- %TODO explain why one large ontology won't work
+ %TODO somewhere else: explain why one large ontology won't work
+ %TODO Definitions
+ %TODO Word index
  \tableofcontents
+ \newpage
 
@@
  However, on the Semantic Web it is infeasible to use one single ontology, since the number of concepts it would have to contain is incredibly large.
-The larger an ontology the longer it takes to perform inference and searches on it, and thus to longer it takes to use it for communication.
+The larger an ontology the longer it takes to perform inference and searches on it, and thus the longer it takes to use it for communication.
 Therefore the semantic web will have separate ontologies for every domain.
@@
 With a context too short a lot of information gets lost and it comes across as cluttered.
+
+ \subsection{Overview}
+ This thesis is structured as follows.
 
@@
  \subsubsection{Current state}
+ The Semantic Web is currently divided into two groups: the people who need high accuracy and the people who need high recall.
+The first group consist of scientists that work on specific fields that require exact knowledge, whereas the second group are data scientists that want big amounts of data available.
+
+ The group that requires high recall use hand-crafted knowledge bases, created by experts, containing only facts that are accurate, verified and relevant.
+This method of creating a knowledge base does not scale very well and usually consists of fewer than ten thousand facts.
+Because of this, the knowledge bases are restricted to small domains, including parts of medicine and cultural heritage.
+%TODO CITE en vind meer
+
+ The group that requires a high recall, i.e.
+requires a huge amount of data, automated methods are required.
+These methods work fast, parsing thousands of websites a minute, but are inclined to make mistakes.
+Often, these methods use crowd-sourcing to improve accuracy, using experts or the general public to suggest or check facts.
+%TODO CITE
+
+ Beside these knowledge bases, many other pieces of the Semantic Web are already in use. For example, the W3C %TODO OWL/RDF stats,
+
+ Large ontologies already exist, with the largest, DBPedia, boasting almost two billion triples and the three hundred combined Large Open Data databases contain over thirty billion.
+%http://semantic-web-journal.net/system/files/swj499.pdf and http://lod-cloud.net/state/
+
+ Leading scientists suggest that more research should be focused on
+
+ Applications include
+ %TODO vind meer en https://googleblog.blogspot.nl/2012/05/introducing-knowledge-graph-things-not.html
+
+ Overall it is clear that % Samenvatten/enumerate, gevolg voor deze thesis (dus ik moet... mijn bijdrage is belangrijk...)
  \subsubsection{Technologies}
@@
 %http://disi.unitn.it/~p2p/RelatedWork/Matching/6614ijdms01.pdf
- \subsection{Problems with ontology alignment}
+ \subsection{Problems in ontology alignment}
  \subsection{Other related research}
@@
 The goal is straightforward: find the alignment given only the ontologies and whatever outside resources are needed.
+
+ \subsubsection{Parts of OWL ignored}
+
  \section{Algorithm}

### 2016-03-16 Paper/Draft.tex
Few comments and typo's

@@
  \section{Introduction}
- % Voorbeeld van semantisch web?
  It is a Friday afternoon and you realise you want to watch a movie with some friends. So, what do you do? To achieve this goal you must take 4 steps.
@@
  \subsection{Overview}
- This thesis is structured as follows.
+ This thesis is structured as follows...
 
@@
  Leading scientists suggest that more research should be focused on
+
+ %https://www.researchgate.net/profile/Hai_Dong/publication/260329617_Semantic_Web_Service_matchmakers_State_of_the_art_and_challenges/links/0a85e531190b602215000000.pdf
 

### 2016-04-10 Paper/Draft.tex
Added Ontologes

@@
  On the Semantic Web, ontologies are used to define and share knowledge.
-The term ontology will be properly defined later on, but for now it suffices to know that an ontology is a set of rules that determine what relations are allowed and required.
+The term ontology will be properly defined later on, but for now it suffices to know that an ontology is a set of rules that determine what relations are allowed and required in a given domain of discourse.
 On the semantic web, ontologies are the foundation for communication between agents.
@@
  \subsection{Ontologies}
+ Earlier, ontologies were referred to as 'a set of rules that determine what relations are allowed and required.' Now, the term will be defined more extensively, the standard format will be describe and the uses of ontologies will be discussed.
+
+ An ontology describes concepts as their relationships to other concepts.
+The concepts that are described determine the domain the ontology covers, and the relationships determine the rules the ontology imposes on the domain.
+For example, a hierarchy is an ontology that describes concepts that are subclasses of other concepts.
+Therefore the relationships are 'part-of' relationships: birds are part-of the animals concept class.
+ Concepts can be instantiated, which is done in a Knowledge Base (KB).
+KBs and Ontologies are often confused, and are indeed very similar in structure.
+The Knowledge Base in our example can contain actually existing birds or fictional birds, and refers to the Ontology concept of bird to embed the instantiations with meaning.
  \subsubsection{OWL}
+
  \subsubsection{Role}
+
+ \subsubsection{Aristotle and Plato} 
  \subsection{Current alignment strategies}

### 2016-04-10 Paper/Draft.tex
Added SPARQL, Role, Aristole vs Plato

@@
  \subsection{Ontologies}
- Earlier, ontologies were referred to as 'a set of rules that determine what relations are allowed and required.' Now, the term will be defined more extensively, the standard format will be describe and the uses of ontologies will be discussed.
+ Earlier, ontologies were referred to as 'a set of rules that determine what relations are allowed and required.' Now, the term will be defined more extensively, the standard format will be described and the uses of ontologies will be discussed.
 
@@
  \subsubsection{OWL}
+ OWL is a family of languages and syntaxes that can be used to create an ontology.
+The different languages are designed around requirements of possible relationships and concept definitions, and thus may differ a lot between them.
+The W3C has defined three variants which are the bases for all other adaptations.
+The variants trade off levels of expressiveness versus computability.
+ \subsubsection{SPARQL}
+ SPARQL is the query language for knowledge bases and ontologies. It allows a user to select nodes whose context match the query, similar to how rows are selected in SQL based on the row contents.
+ \subsubsection{Role}
+ The reason ontologies are used in databases consists of multiple parts.
+Firstly, it allows querying languages to optimize the search process.
+Secondly, it allows expansion of information on a node.
+Thirdly, it allows for consistency checking a Knowledge Base.
+Lastly, it allows merging of knowledge bases.
 
- \subsubsection{Role}
+ Search can be optimized by taking into account constraints the ontology provides.
+For example, no professor is a student, therefore no professor can be connected to a course with 'follows' predicate.
+This allows a search algorithm to skip all professors when looking for people that might follow a certain course.
 
+ Expanding the available information of a certain node can be done by taking into account \textit{positive} constraints of a concept.
+For example, since all birds have beaks, it would be inefficient to store this fact for every instance of bird in the knowledge base.
+However, if this is a constraint given in the ontology, it can be accessed for all instantiations of the bird concept with less space required.
+Superclassing enables ontologies to store these types of information even more efficiently, allowing for enormous amounts of information to be extracted for every node without the need to store it all explicitly for that node.
+
+ One important aspect of data bases is consistency.
+Manipulations on a data base such as a knowledge base must not result in a knowledge base that does not adhere to the data base constraints.
+In a knowledge base, these constraints are defined in the ontology.
+
+ When two knowledge bases need to be merged, aligned or matched, instantiations that refer to the same thing need to be merged.
+For example, if two person databases both contain references to the same person, all information on that person needs to be linked to the same object, such that information of that person from both knowledge bases can be combined.
+Merging the ontologies of the two knowledge bases vastly improves the alignment between the two knowledge bases.
+However, ontology and knowledge base merging is not a trivial problem and actually the problem that this thesis addresses.
+Therefore it will be explained more in-depth later on.
  \subsubsection{Aristotle and Plato}
+ All ontologies lie on a spectrum of formality.
+On the one end of the spectrum are the Platonic ontologies, which should only contain concepts that are perfectly defined and constraints which are completely binding.
+The name refers to the Platonic philosophy that all concepts are existing entities and can thus be perfectly captured in a definition.
+
+ On the other end of the spectrum are the Aristotelian ontologies, which do not necessarily contain perfectly defined concepts, but rather concepts as we observe them.
+Aristotle disagreed with Plato's theory that concepts are existing things, and thus these ontologies are named after him.
+
+ Aristotelian ontologies have the advantage of being easier to create.
+One could use statistical methods given a sample of all possible observations or crowd sourcing to create concepts and constraints.
+This would enable enormous ontologies and knowledge bases with the amount of data currently available and cheap mental labour with services like Amazon's Mechanical Turk.
+
+ The advantage of a Platonic ontology would be the fact that every query would result in a fact, since the ontology itself is perfect.
+The disadvantage is that creating such an ontology is much more costly than an Aristotelian ontology, since every concept and constraint needs to be correct in all cases.
+
+ Another way to represent this spectrum is the precision-recall trade-off.
+A Platonic ontology has maximum precision but its recall is limited since it can only represent very little if creation budget is limited, or paradoxes exist.
+The Aristotelian ontology on the other hand, can theoretically reach perfect recall given enough storage size and observations for its statistical methods.
+Again, in reality this is limited by a budget.
+All ontologies fall between these two extremes.
+Often, a combination of statistical methods with expert confirmation is used.
+
+ Platonic ontologies are often used in areas where precision is important, like medicine, where lives depend on the information contained in the ontology and its knowledge base.
+Aristotelian ontologies are more common on the Semantic Web, where massive amounts of data need to be represented and queried.
  \subsection{Current alignment strategies}

### 2016-04-10 Paper/Draft.tex
Added current state & Current alignment strategies

@@
 This method of creating a knowledge base does not scale very well and usually consists of fewer than ten thousand facts.
-Because of this, the knowledge bases are restricted to small domains, including parts of medicine and cultural heritage.
-%TODO CITE en vind meer
+Because of this, the knowledge bases are restricted to small domains, including some parts of medicine and cultural heritage.
+\cite{byrne, le2002}
 
@@
 Often, these methods use crowd-sourcing to improve accuracy, using experts or the general public to suggest or check facts.
-%TODO CITE
+\cite{zhou2007}
 
- Beside these knowledge bases, many other pieces of the Semantic Web are already in use. For example, the W3C %TODO OWL/RDF stats,
+ Beside these knowledge bases, many other pieces of the Semantic Web are already in use. For example, the W3C \cite{rdf, owl}
+ %TODO: stats?
 
  Large ontologies already exist, with the largest, DBPedia, boasting almost two billion triples and the three hundred combined Large Open Data databases contain over thirty billion.
-%http://semantic-web-journal.net/system/files/swj499.pdf and http://lod-cloud.net/state/
+\cite{dbpedia, lod} The LOD is simply one huge alignment of hundreds of knowledge bases...
+%Doorschrijven
 
- Leading scientists suggest that more research should be focused on
+% Leading scientists suggest that more research should be focused on creating
 
- %https://www.researchgate.net/profile/Hai_Dong/publication/260329617_Semantic_Web_Service_matchmakers_State_of_the_art_and_challenges/links/0a85e531190b602215000000.pdf
+ Applications include improved web searching, question answering, product comparison, context merging, data integration, decision support, translation, all the way up to the intelligent softbot mentioned earlier.
 
- Applications include
- %TODO vind meer en https://googleblog.blogspot.nl/2012/05/introducing-knowledge-graph-things-not.html
+ % Elke behandelen
 
@@
  \subsubsection{Technologies}
+
  \subsection{Ontologies}
@@
 the number of edges between the concepts and their least general common superconcept.
-% http://disi.unitn.it/~p2p/RelatedWork/Matching/Lin_WordNet_OM.pdf
+\cite{lin2008}
  Edit distance is a purely string-based similarity measure.
 The similarity is a (weighted) count of edits required to transform one word into another, where common edits are insertion, deletion and replacement.
-Similar methods include substring matching and n-gram matching, which compare parts of the strings to find similarities.
-%http://disi.unitn.it/~p2p/RelatedWork/Matching/6614ijdms01.pdf
+Similar methods include substring matching and n-gram matching, which compare parts of the strings to find similarities.\cite{singh2014, levenshtein}
  \subsection{Problems in ontology alignment}

### 2016-04-10 Paper/Draft.tex
Added problems

@@
 
-% Leading scientists suggest that more research should be focused on creating
-
  Applications include improved web searching, question answering, product comparison, context merging, data integration, decision support, translation, all the way up to the intelligent softbot mentioned earlier.
+%http://www.cs.vu.nl/~guus/papers/Schreiber06a.pdf https://hal.inria.fr/hal-00917910/document
 
@@
 Aristotelian ontologies are more common on the Semantic Web, where massive amounts of data need to be represented and queried.
- \subsection{Current alignment strategies}
+ \subsection{Current alignment strategies} \label{strategies}
  Many different alignment strategies have already been developed.
@@
  \subsection{Problems in ontology alignment}
+ There are a number of different problems ... % Opsommen en samenvatten
+
+ How should the wildly differing demands the applications place on the ontology matching systems be satisfied by a single of a few systems?
+When merging ontologies on one end of the Aristotle-Plato spectrum, often a completely different approach is required than an ontology on the other side.
+Sometimes the matching needs to be very fast, for example when the ontologies are used in a search query which the user expects to be done in milliseconds.
+
+ Online matching would allow for updates in a knowledge base to be represented in the alignments of that knowledge base.
+This would be required on any ontology that tracks changing knowledge, like stores, movie theatres and social media, for example.
+
+ Based on the previous two points, we can state that it would also be useful to have different benchmarks to test those different types of challenges and matching systems.
+This would allow for better comparison of methods and better tracking of the improvements in the field.
+
+ Since the Linked Open Data keeps growing, it, and other resources, should be used in matching.
+This is already done to some degree, as discussed in the WordNet matching strategy section \ref{strategies}.
+The challenge is to all available ontologies and other sources rather than just WordNet.
+
+ Matchers should be able to explain the results it produces, i.e.
+making those results more interpretable.
+This would allow a number of other improvements to occur.
+Firstly, it would allow users of a system to have more confidence in the results and make better decisions based on the source of the result.
+Secondly, it would allow people manually aiding the alignment to check if the matcher did a good job, and thus improve the interaction between the system and the domain expert.
+Thirdly, it would allow researchers to improve the matching system because they are able to detect the source of errors.
+
+ When these problems are solved, ontology matching has matured enough to be used in Semantic Web applications. Then it is merely the challenge to have the public adopt these technologies.
+
  \subsection{Other related research}
@@
  \section{Evaluation}
+ %https://hal.inria.fr/hal-00917910/document
  The goal of the research is to find an ontology alignment algorithm $A$ and proof that it performs better than current techniques.

### 2016-04-10 agreementmaker/AgreementMaker-OSGi/AgreementMaker-Matchers/src/main/java/am/matcher/WordSenseMatcher/EvaluateMain.java
Added main to test Matcher

@@ -1,0 +1,177 @@
+package am.matcher.WordSenseMatcher;
+
+import am.Utility;
+import am.app.mappingEngine.*;
+import am.app.mappingEngine.referenceAlignment.ReferenceAlignmentMatcher;
+import am.app.mappingEngine.referenceAlignment.ReferenceAlignmentParameters;
+import am.app.mappingEngine.referenceAlignment.ReferenceEvaluator;
+import am.app.ontology.Ontology;
+import am.app.ontology.ontologyParser.OntoTreeBuilder;
+import am.app.ontology.ontologyParser.OntologyDefinition;
+
+import java.util.ArrayList;
+
+public class EvaluateMain {
+
+    private static WordSenseMatcher mm;
+
+    public static void main(String[] args) throws Exception {
+
+        String ONTOLOGY_BASE_PATH ="conference_dataset/"; // Use your base path
+        String[] confs = {"cmt","conference","confOf","edas","ekaw","iasted","sigkdd"};
+        //String[] confs = {"edas","sigkdd"};
+
+
+        mm = new WordSenseMatcher();
+        System.setProperty("wordnet.database.dir","wordnet-3.0/dict");
+        double precision=0.0d;
+        double recall=0.0d;
+        double fmeasure=0.0d;
+        int size=21;
+
+        //stop=new StopWords();
+        for(int i = 0; i < confs.length-1; i++)
+        {
+            for(int j = i+1; j < confs.length; j++)
+            {
+                Ontology source = OntoTreeBuilder.loadOWLOntology(ONTOLOGY_BASE_PATH + "/"+confs[i]+".owl");
+                Ontology target = OntoTreeBuilder.loadOWLOntology(ONTOLOGY_BASE_PATH + "/"+confs[j]+".owl");
+
+                OntologyDefinition def1=new OntologyDefinition(true, source.getURI(), null, null);
+                OntologyDefinition def2=new OntologyDefinition(true, target.getURI(), null, null);
+
+                def1.largeOntologyMode=false;
+                source.setDefinition(def1);
+                def2.largeOntologyMode=false;
+                target.setDefinition(def2);
+                mm.setSourceOntology(source);
+                mm.setTargetOntology(target);
+
+                DefaultMatcherParameters param = new DefaultMatcherParameters();
+
+                //Set your parameters
+                param.threshold = 0.0;
+                param.maxSourceAlign = 1;
+                param.maxTargetAlign = 1;
[…]

### 2016-04-11 Paper/Draft.tex
Added problems in ontology alignment and some references

@@
 This is useful as it is easy to calculate the distance between two vectors, which is a useful property for ontology matching.
-This vector distance has been shown to be related to the semantic similarity between words.
-This semantic similarity is very useful for ontology alignment, as parts of one ontology have to be aligned with parts of another ontology depending on their semantic relation.
+This vector distance has been shown to be related to the semantic similarity between words, which is very useful for ontology alignment, as parts of one ontology have to be aligned with parts of another ontology depending on their semantic relation.
 
- Recently, an effective and efficient skip-gram model has been developed.
-It is called word2vec, and uses a number of extensions over previous methods that enable it to efficiently learn an effective representation.
-  Word2vec learns this representation by trying to predict a context matrix.
-First a one-hot encoding is made for the vocabulary.
-Then the model learns to predict a context matrix of C one-hot vectors based on the given one-hot input vector.
-The model is a neural network with one hidden layer and multiple output layers.
-Since the words are one-hot encoded the input to the hidden layer is equal to the row of the weight matrix that corresponds to the word.
+ Recently, an effective and efficient skip-gram model has been developed, called word2vec, which uses a number of extensions over previous methods that enable it to efficiently learn an effective representation.
+ Word2vec learns this representation by trying to predict the context of a word.
+First the vocabulary is one-hot encoded.
+Then the model learns to predict a context vector that minimizes the distance to the context one-hot encoded vectors.
+The model is a neural network with one hidden layer.
+Since the input is one-hot encoded, every word in the vocabulary is represented by one row in the weight matrix between the input layer and hidden layer.
 This row is the vector representation of the word.
 
- % Continue with better w2v
  Word2vec has been expanded in a number of different ways.
 For example, word order can be preserved, leading to a similarity measure that is closer to syntax, as syntax defines which words go where in a sentence.
-This research shows that the input does not have to be a bag-of-words representation, which will be useful later on.
-% Reference
- Another interesting development is the multi-sense word2vec, which has multiple vector representations per word, depending on the number of different definitions a word has.
+This preservation was done by having multiple output layers, one for every word in the context.
+The research shows that the input does not have to be a bag-of-words representation, which will be useful later on.
+\cite{ling2015}
+ Another interesting development is the multi-sense word2vec, which allows for multiple vector representations per word, depending on the number of different definitions a word has.
 For example, the word bank represents both the monetary institute and the riverside, which would both have a different representation in this extension.
 It can differentiate between two different meanings based on the context.
-This will help with resolving ambiguity, a very important factor in ontology alignment.
+This will help with resolving ambiguity, a very important factor in ontology alignment.\cite{multisense}
  \subsection{Used technology}
- \subsubsection{Ontology constructor}
  \subsubsection{AgreementMaker}
- AgreementMaker is an ontology matching system which obtained the highest F-measure in 6 of the 7 ontology matching tracks of OAEI 2015 %http://disi.unitn.it/~pavel/om2015/papers/oaei15_paper1.pdf.
-The system has also been updated the most recent at the time of writing.
+ AgreementMaker is an ontology matching system which obtained the highest F-measure in 6 of the 7 ontology matching tracks of OAEI 2015.
+\cite{OAEI2015} The system has also been updated the most recent at the time of writing\cite{agreementmaker}.
 
@@
 This is very useful for research as it allows the researcher to compare different modules by swapping in just those modules in the framework.
-The module-swapping technique will also be used in this work, but more of that will be discussed in $Evaluation methods$.
- %http://disi.unitn.it/~p2p/RelatedWork/Matching/vldb2009-revised.pdf
-
+The module-swapping technique will also be used in this work, but more of that will be discussed in \ref{Evaluation methods}.
  \section{Problem}
@@
  To solve these problems I will adapt word2vec to graphs and extend it with multi-sense embeddings. Also hot-starting is considered as an improvement.
-
- \subsection{Theory}
  \subsection{Possibilities} % Rename please
@@
 So, instead we may want to see if performance is improved when adding $A$ to an ensemble of algorithms $E=(A_1,..,A_n)$.
- \subsection{Evaluation methods}
+ \subsection{Evaluation methods} \label{Evaluation methods}
  The evaluation should be done using a performance measure $P(Al,T)$ that takes the alignment an algorithm produces given an ontology and the ground truth.
@@
  \subsection{Theory}
+
  \subsection{Product}
@@
  \section*{References}
-
+ \bibliographystyle{plain}
+ \bibliography{bibliography}{}
  \end{document}

### 2016-04-11 Paper/Draft.tex
Added Idea

@@
 In this case the solutions are $E\cup \{R\}$, where $R$ is an algorithm that generates random alignments.
+
+ It is in principle possible to weigh False Positives and False Negatives differently, but this is not done in practice.
+To make the results of this study easily comparable to others, equal weights will be used.
  \subsection{Data}
@@
 
+ A reference alignment can be made by experts or be created by bipartitioning an existing ontology. %expand this.
  \subsubsection{Parts of OWL ignored}
@@
  \subsection{Idea}
+ The goal of any ontology matcher is to find an alignment between two ontologies that is as similar as possible to the true alignment.
+Such an alignment consists of node pairs where the two nodes in each pair come from the two different ontologies.
+Sometimes a label is added to each pair, indicating the relationship the two nodes have.
+For example, 'part-of', 'similar-to', and such.
+However, we only consider equality relationships and thus the label can be omitted.
+
+ Then the question becomes: \textit{how do we measure similarity of concepts between ontologies?} As shown in \ref{strategies}, attempts have been made to model similarity of nodes as the string similarity of their labels.
+Also, WordNet is used to find similar nodes.
+The string similarity assumes that similar labels refer to similar concepts.
+While this is true to a certain degree, homonyms, synonyms, and other phenomena make this assumption very weak.
+WordNet-based similarity measures are better since WordNet links concepts semantically, and thus similar concepts will be close in WordNet.
+The major problem with WordNet is that it is constructed by hand, and thus does not scale very well to new domains.
+
+ The idea behind the algorithm introduced in this study is to find an alternative to WordNet that is at least as good in modelling semantic distance but scales to new domains.
+It should be trainable on this new domain through existing ontologies and texts in an unsupervised way so that it does not require the interference of experts.
+This will allow it to overcome the weakness of WordNet.
+This is only relevant, though, if the performance is equal to WordNet-based matchers.
+
+ Word2vec is an unsupervised method that maps words to a vector space that has been shown to contain semantic properties %cite.
+ It can be trained on large corpora quickly and the resulting vectors can easily be used to measure the distance between words.
+All these properties make it an excellent candidate for a concept distance measure to use for ontology matching.
+As an added benefit, it can also take into account the context of a concept, which may be able to improve its performance over a matcher that only uses the label of a concept.
  \subsection{Theory}

### 2016-04-11 Paper/Draft.tex
Renamed possibilities to considered implementations

@@
  To solve these problems I will adapt word2vec to graphs and extend it with multi-sense embeddings. Also hot-starting is considered as an improvement.
- \subsection{Possibilities} % Rename please
+ \subsection{Considered implementations}
+ In this section, I will discuss the different implementations that were made of the algorithm.
+All implementations use the same basic algorithm in different ways by taking into account the context in different ways.
+All of these implementations were tested and the results can be found in \ref{results}.
+Some implementations are extensions of other implementations, but all implementations are mentioned for completeness and to enable explanation of the source of improvements.
   \subsubsection{Training corpus}
@@
  Every data set contains two ontologies that need to be aligned and a ground truth alignment.
-The goal is straightforward: find the alignment given only the ontologies and whatever outside resources are needed.
+The goal is straightforward: find the alignment given only the ontologies and whichever outside resources are needed.
 
@@
 
- \section{Results}
+ \section{Results} \label{results}
 

### 2016-04-11 Paper/Draft.tex
Added research questions and hypotheses

@@
  \subsection{Problem}
- We have seen that when information from multiple domains need to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged.
+ We have seen that when information from multiple domains needs to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged.
 Those ontologies contain rules about concepts and concept classes in the shape of triplets, with two concepts and a relation.
@@
  \subsection{Research questions}
+ Can distributed representations of concepts be used to find relationships between concepts in ontologies better than existing terminological matchers?
+
+ Can distributed representations use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers?
+
+ Can distributed representations perform well in a domain it was not designed for?
 
  \subsection{Hypotheses}
+ Since multiple implementations of the algorithm are considered, every hypothesis that follows is considered for every implementation.
+
+ \textit{The distributed representations of concepts matcher can find relationships between concepts in ontologies better than existing terminological matchers.}
+
+ \textit{The distributed representations matcher can use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers.}
+
+ \textit{The distributed representations matcher can perform well in a domain it was not designed for.}
+
+ The following hypotheses are true if for at least one implementation the corresponding hypothesis is true.
+
+ \textit{A distributed representations of concepts matcher can find relationships between concepts in ontologies better than existing terminological matchers.}
+
+ \textit{A distributed representations matcher can use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers.}
+
+ \textit{A distributed representations matcher can perform well in a domain it was not designed for.}
 

### 2016-04-11 Paper/Draft.tex
Added Justification, Context

@@
  In this section I will discuss all concepts that are required to understand the study.
+Firstly, the Semantic Web, the key technology that depends very strongly on ontology matching, will be discussed.
+Then the concept of the Ontology itself will be addressed.
+Lastly, current alignment strategies, their problems and other research and technologies will be discussed.
  \subsection{The Semantic Web}
@@
  We have seen that when information from multiple domains needs to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged.
+% Waar?
   Those ontologies contain rules about concepts and concept classes in the shape of triplets, with two concepts and a relation.
@@
  \subsection{Justification}
- Reliable, error proof ontology matching will be key for the distributed Semantic Web.
+ On the Semantic Web, many relatively small knowledge bases will be combined temporarily so that it is possible to reason over the combined knowledge of those knowledge bases.
+To combine these knowledge bases, their ontologies first need to be aligned.
+This is an act that will happen very often on the Semantic Web, since every interaction with the Semantic Web will usually require information from multiple domains.
+Large domains may be stored over multiple devices, which can be viewed as different knowledge bases which also need to be aligned.
+Therefore, it is save to say that efficient ontology matching will be very valuable.
 
+ Since most of the Semantic Web will consist of Aristotelian ontologies, some of the information it contains can be unreliable and even wrong.
+Therefore, ontology matching that is capable of handling this uncertain data is required.
+
+ Calculating the distance between vectors can be done very efficiently, therefore ontology matching with distributed concept representations fits that efficiency criteria.
+Since these representations can use the context of a concept, they are also most robust than methods that do not take the context into account.
+
+ Since distributed representation algorithms can be trained unsupervised on new domains, they can be applied to those new domains without effort from humans, unlike current matching algorithms.
+This is also an improvement for the semantic web.
+
+ However, ontology matching is also used outside of the semantic web.
+It is already in use for companies that want to merge knowledge from other companies, for example.
+If the proposed matching algorithm is better than the current algorithms, or at least improves the performance when used in ensemble with the current algorithms, it will be useful in any situation, not just on the Semantic Web.
  \section{Method}

### 2016-04-12 Paper/Draft.tex
Added Short context, method and some newpages

@@
  \begin{document}
+ \pagenumbering{gobble}
  \maketitle
  \newpage
+
+ \pagenumbering{roman}
+ \section*{Acknowledgements}
+ \section*{Abstract}
 
@@
 
+ \pagenumbering{arabic}
  \section{Introduction}
@@
 
+ A lot of research has been done on creating ontologies, ranging from what an ontology structure should look like to how ontologies should be generated unsupervised.
+Some research has focused on ontology merging, with promising but slowing results.
+
+ Recently, a model that embeds words in a vector space that appears to contains semantics has become popular.
+Since it is unsupervised and can be used to calculate a semantic distance between words, it may very well be applicable to ontology matching.
+The model will be explained much more in-depth in \ref{w2v}.
+
  % This should actually be quite long since the whole context section is probably going to be ~10 pages, so 1 page is still fairly short.
@@
 
+\newpage
 \section{Context}
@@
  \subsection{Other related research}
- \subsubsection{Word sense representation}
+ \subsubsection{Word sense representation} \label{w2v}
  Skip-gram models have been widely used to represent words as vectors.
@@
  \subsection{Used technology}
- \subsubsection{AgreementMaker}
+ \subsubsection{AgreementMaker} \label{agreementmaker}
  AgreementMaker is an ontology matching system which obtained the highest F-measure in 6 of the 7 ontology matching tracks of OAEI 2015.
@@
 The module-swapping technique will also be used in this work, but more of that will be discussed in \ref{Evaluation methods}.
+
+ \subsubsection{Factorie} \label{factorie}
+
+ \newpage
  \section{Problem}
@@
   Those ontologies contain rules about concepts and concept classes in the shape of triplets, with two concepts and a relation.
-For example, the rule{\tt Professors are humans} contains the concepts \emph{Professor} and \emph{human} and relationship \emph{being}.
+For example, the rule {\tt Professors are humans} contains the concepts \emph{Professor} and \emph{human} and relationship \emph{being}.
 
@@
  \subsection{Research questions}
- Can distributed representations of concepts be used to find relationships between concepts in ontologies better than existing terminological matchers?
+ Can distributed representations of concepts be used to find relationships between concepts in ontologies better than existing terminological matchers?\\\\
 
- Can distributed representations use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers?
+ Can distributed representations use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers?\\\\
 
@@
  \subsection{Hypotheses}
- Since multiple implementations of the algorithm are considered, every hypothesis that follows is considered for every implementation.
+ Since multiple implementations of the algorithm are considered, every hypothesis that follows is considered for every implementation.\\\\
 
+ \begin{center}
  \textit{The distributed representations of concepts matcher can find relationships between concepts in ontologies better than existing terminological matchers.}
-
+ \end{center}
+ \begin{center} 
  \textit{The distributed representations matcher can use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers.}
-
+ \end{center}
+ \begin{center}
  \textit{The distributed representations matcher can perform well in a domain it was not designed for.}
+ \end{center}
 
@@
 
+ \begin{center}  
  \textit{A distributed representations of concepts matcher can find relationships between concepts in ontologies better than existing terminological matchers.}
-
+ \end{center} 
+ \begin{center}
  \textit{A distributed representations matcher can use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers.}
-
+ \end{center}
+ \begin{center}
  \textit{A distributed representations matcher can perform well in a domain it was not designed for.}
+ \end{center}
 
@@
 If the proposed matching algorithm is better than the current algorithms, or at least improves the performance when used in ensemble with the current algorithms, it will be useful in any situation, not just on the Semantic Web.
+
+ \newpage
  \section{Method}
@@
 In the second section, I will give a theoretical justification for why this method should work and how it works conceptually.
-After that I will describe the different ways that the input graphs can be used to train the word2vec model and create the alignment.
+After that I will describe the different ways that the input graphs can be used to train the word2vec model and create the alignment, some of which I have discarded on theoretical grounds as I will explain in the relevant section.
+Lastly, I will talk about the implementation process.
  \subsection{Idea}
@@
   % Dit moet weg als het bs blijkt te zijn
- \subsection{Discarded possibilities} % Rename
+ \subsection{Discarded implementations}
   \subsubsection{Training on text}
@@
  \subsection{Implementation}
+ The two foundations the algorithm has been build and tested on are Factorie, described in \ref{factorie}, and AgreementMaker, described in \ref{agreementmaker}, respectively.
+Earlier work on a forked branch of factorie was done by \cite{multisensecode} to implement multi-sense word2vec.
 
+ \newpage
  \section{Evaluation}
@@
 
+ \newpage
  \section{Algorithm}
@@
 
- Word2vec is an unsupervised method that maps words to a vector space that has been shown to contain semantic properties %cite.
+ Word2vec is an unsupervised method that maps words to a vector space that has been shown to contain semantic properties. %cite
  It can be trained on large corpora quickly and the resulting vectors can easily be used to measure the distance between words.
@@
 
+ \newpage
  \section{Results} \label{results}
 
+ \newpage
  \section{Conclusions}
@@
 
+ \newpage
  \section{Discussion}
@@
 
+ \newpage
+ \bibliographystyle{plain}
+ \bibliography{bibliography}{}
+
+ \newpage
  \begin{appendices}
+  \pagenumbering{Roman}
   \section{Appendix 1}
@@
 
- \section*{References}
- \bibliographystyle{plain}
- \bibliography{bibliography}{}
  \end{document}

### 2016-04-12 Paper/Draft.tex
Added Factorie

@@
  Recently, an effective and efficient skip-gram model has been developed, called word2vec, which uses a number of extensions over previous methods that enable it to efficiently learn an effective representation.
+/cite{w2v}
  Word2vec learns this representation by trying to predict the context of a word.
@@
  \subsubsection{AgreementMaker} \label{agreementmaker}
- AgreementMaker is an ontology matching system which obtained the highest F-measure in 6 of the 7 ontology matching tracks of OAEI 2015.
+ AgreementMaker is an ontology matching system that obtained the highest F-measure in 6 of the 7 ontology matching tracks of OAEI 2015.
 \cite{OAEI2015} The system has also been updated the most recent at the time of writing\cite{agreementmaker}.
@@
  \subsubsection{Factorie} \label{factorie}
+ "FACTORIE [is a] a toolkit for probabilistic modeling based on imperatively-defined factor graphs" \cite{git-factorie}.
+As a toolkit it contains many different parts that can be used together.
+One example is the NLP package in the toolkit, which provides many algorithms to process text.
+One of those algorithms is the distributed representation of words algorithm by \cite{w2v}.
+
+ Factorie is written in scala, a relatively new language that interfaces with java.
+See \ref{scala}.
+This allows for interoperability between factorie and AgreementMaker.
+Any algorithm that is implemented in factorie or on top of factorie can therefore be used as a matching algorithm in AgreementMaker.
+
+ Factorie provides a number of utilities for writing an algorithm in the shape of abstract classes with existing functionality, namely IO, parallelisation, quick parsing and command line argument parsing.
+It also provides example implementations and programs.
+
+ The automated IO allows for quick reading in of the data set and secure saving of the trained model.
+The file reading is quicker than a naive CSV parser would allow for, and thus enabled quicker training of the models.
+This meant less time is used and more time can be used for experimenting and improving the algorithm.
+Saving the different models allows for model comparison after all models have been trained, which means new investigations can be performed after conclusions have been drawn from earlier investigations, without having to retrain all models.
+This also allows multiple models to be trained during a period where the experimenter is absent, after which he can still manually investigate the models.
+
+ Parallelisation can massively improve training speed.
+It allows an algorithm to update its model for multiple learning instances at the same time, thus reducing the time needed by the number of instances it can process simultaneously.
+The number of parallel processes differs per device but modern personal computers already boast 8 parallel processors.
+
+ When model training is extremely fast, which is the case for parallelised neural network training, parsing the data from string format to vectors in a proper data structure can become a bottleneck.
+Recently, factorie added JFlex to parse its data.
+This improved its parsing by \%5000, removing the bottleneck.
+
+ Since I investigate many different implementations of the same algorithm, it should be easy to switch between these implementations at run-time without much effort.
+Command line parsing allows for this to happen, and thus improves experimentation ease.
 

### 2016-05-08 Paper/Draft.tex
Someone forgot to commit some time ago.

@@
  \section{Introduction}
- It is a Friday afternoon and you realise you want to watch a movie with some friends. So, what do you do? To achieve this goal you must take 4 steps.
+ It is a Friday afternoon and you realise you want to watch a movie with some friends this weekend. So, what do you do? To achieve this goal you must take four steps.
 
@@
  Then onto the last step, getting friends to go with you.
-In this step you do not want to burden your friends to much by having them pick both the movie and the time, so you will have to decide which movie to watch or when, even though you do not know if your friends will like this movie or are available at that time.
+In this step you do not want to burden your friends too much by having them pick both the movie and the time, so you will have to decide which movie to watch or when, even though you do not know if your friends will like this movie or are available at that time.
 Once you contact your friends, most of them do not respond as they are not online at that time or they do not feel like filling in a poll about availability or movie choices.
 
- What would happen if this process was automated?
+ Most of the time people will limit their options to avoid these steps, considering only a few movies, cinemas, time slots and friends.
+But this is not necessary.
+What would happen if the above process was automated?
 The first step, finding movies that match two criteria would be considered trivial with modern technology.
@@
  The second step, cross-referencing the list of movies with cinema play times, would already be harder.
-Most of the time the cinema play times are written in a human-readable format, something that is often hard to incorporate for a computer.
-Either the play times have to be made in a computer-readable format or a computer has to interpret them and convert them into computer-readable.
-However, errors might occur because the local cinema labelled a sequel as "Movie II" whereas the list we have has it labelled as "Movie 2".
+Most of the time the cinema play times are written in a human-readable format, something that is often hard to interpret for a computer.
+Either the play times have to be written in or transformed into a computer-readable format manually or a computer has to interpret the format and convert it into a computer-readable one.
+However, errors might occur because the local cinema labelled a sequel as "Movie II" whereas the list we have has it labelled as "Movie 2", for example.
 
@@
 everyone has one.
-Rather than bothering your friends with scheduling, your softbot can contact those of your friends and find the movie and time slot that optimize a cost function, taking into account which friends you like the most, which movie everybody likes the most and at which time the fewest dinners with wives need to be moved.
-Once this best time is chosen, everyone gets an invite to see the movie and once it is known who will go, a car pooling route is calculated and you can sit back an enjoy your Friday afternoon with no planning or scheduling required.
+Rather than bothering your friends with scheduling, your softbot can contact the softbots of your friends and find the movie and time slot that optimize a cost function, taking into account which friends you like the most, which movie everybody likes the most and at which time the fewest dinners with wives need to be moved.
+Once this best time slot is chosen, everyone gets an invite to see the movie and once it is known who will go, a car pooling route is calculated and you can sit back an enjoy your Friday afternoon with no planning or scheduling required.
 
  The most amazing thing about this story, is that it is already possible with the current technology.
-The algorithms to convert for example cinema website text to computer-readable format exist.
+The algorithms to convert for example cinema website text to a computer-readable format exist.
 Many open databases already contain a lot of structured data that can be used to reason about data.
+And algorithms to combine these piece of information to make decisions already exist and work.
 
- Two things are required before this web of computers who communicate and understand, this Semantic Web, will come into existence. 
+ Two things are required before this web of computers that communicate and understand, this Semantic Web, will come into existence. 
  Firstly, the Semantic Web needs to be adopted by humans.
@@
 People have to realise that the current search engines are not good enough, and that having to read through many papers to find the one nugget of information or the one connection that you are looking for is not acceptable or necessary.
- Lastly, the different knowledge bases and unstructured texts need to be aligned.
-This means that softbots should be able to reason about facts that are contained in different domains and documents.
+ But also, the different knowledge bases and unstructured texts need to be \emph{aligned}.
+Aligning means that softbots should be able to combine information that is contained in different domains, documents and databases.
 This last problem is the one that I will work on in this thesis.
-Once we can combine the information from different databases and unstructured text, the Semantic Web is technically possible and only needs to be socially accepted before it will become the norm.
+Once this problem has been solved, the Semantic Web is technically possible and only needs to be socially accepted before it will become the norm.
 
  \subsection{Short Context}
- On the Semantic Web, ontologies are used to define and share knowledge.
+ In this section, I will give a short summary of the context for the problem.
+This will enable the reader to put the problem in perspective as well as understand the reasoning behind the solution to the problem.
+Everything that is mentioned in this section will be explained more in-depth further on.
+
+ On the Semantic Web, Ontologies are used to define and share knowledge.
 The term ontology will be properly defined later on, but for now it suffices to know that an ontology is a set of rules that determine what relations are allowed and required in a given domain of discourse.
-On the semantic web, ontologies are the foundation for communication between agents.
+Without ontologies, agents on the Semantic Web would be unable to communicate, as all concepts are defined in an Ontology.
 
- However, on the Semantic Web it is infeasible to use one single ontology, since the number of concepts it would have to contain is incredibly large.
-The larger an ontology the longer it takes to perform inference and searches on it, and thus the longer it takes to use it for communication.
-Therefore the semantic web will have separate ontologies for every domain.
-The downside of this approach is that when communication requires rules on multiple domains, which it often does, multiple ontologies need to be aligned or merged.
+ However, using one single ontology is infeasible.
+This is due to the fact that inference and search time scales with Ontology size, and the number of concepts that are needed on the Semantic Web is enormous.
+Every single concept that is present in the billions of Terabytes of text, images and sounds that are on the web needs to be represented, for every professional domain and science, in every language.
+And all these concepts are related.
+Searching through this Ontology just to find one concept would be incredibly costly.
+And since every interaction on the Semantic Web requires lookups in an Ontology or corresponding Knowledge Base, these lookups need to be fast.
 
- A lot of research has been done on creating ontologies, ranging from what an ontology structure should look like to how ontologies should be generated unsupervised.
+ The solution to this problem is to split this Ontology into many smaller Ontologies. However, as often is the case in Computer Science, this creates two new, albeit smaller, problems.
+
+ The first problem is the problem of splitting the Ontology.
+How do we find the distribution of all concepts over the different Ontologies to maximize their usefulness.
+Usefulness in this case should take into account co-occurrence of concepts.
+Naturally, connected concepts should be more likely to occur in the same Ontology as concepts that are not connected, since it is likely that agents that want to know about a concept also want to know things about its neighbours.
+
+ The second problem, the one I address in this thesis, is the problem of conversations that cover multiple domains.
+These conversations will occur more often if there are more Ontologies, but they can always occur if the number of Ontologies is larger than one.
+When a conversation requires information from multiple domains, the Ontologies corresponding to those domains need to be merged.
+This means connecting the related concepts from the different Ontologies.
 Some research has focused on ontology merging, with promising but slowing results.
+
+ The problem of Ontologies on the Semantic Web is to find those Ontologies that are as small as possible to improve search speed, but need to be merged as little as possible, to ensure as little time is used to merge the Ontologies before they can be searched.
+If it is possible to quickly and reliably merge Ontologies, Ontologies can be made small and communication on the Semantic Web can be done quickly.
 
@@
 Since it is unsupervised and can be used to calculate a semantic distance between words, it may very well be applicable to ontology matching.
-The model will be explained much more in-depth in \ref{w2v}.
-
- % This should actually be quite long since the whole context section is probably going to be ~10 pages, so 1 page is still fairly short.
-With a context too short a lot of information gets lost and it comes across as cluttered.
 
@@
 \section{Context}
-% Give an overview of the section
  In this section I will discuss all concepts that are required to understand the study.
-Firstly, the Semantic Web, the key technology that depends very strongly on ontology matching, will be discussed.
+Firstly, the Semantic Web, the key technology that depends very strongly on Ontology matching, will be discussed.
 Then the concept of the Ontology itself will be addressed.
@@
  \subsection{The Semantic Web}
- The Semantic Web, or Web 3.0, is a concept of a Web that enhances the User Experience in ways that the current Web can not provide.
-Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and barely any interconnectivity.
+ The Semantic Web, also called Web 3.0, is a concept of a Web that enhances the User Experience in ways that the current Web can not provide.
+Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and limited interconnectivity.
 For example, Facebook is a hub for sharing content with people you consider friends, but if you want to share that content with more people you will have to go to another hub, like imgur or Pinterest.
-The Semantic Web, on the other hand, sees web pages as sources of \textit{information} that can be combined whenever the user needs it.
-This allows not only humans to browse the internet, but also Artificial Intelligences, which will use this information to aid their users.
+It is possible to link to content from other hubs using URLs, but this moves the user to another hub, rather than connecting the content present in the hubs.
+The Semantic Web, on the other hand, contains sources of \textit{information} that can be combined whenever the user needs it.
+To stick with the social media example, a person can create a piece of content, say a picture of a tree, en shares it with his friends.
+One of his friends then can share this piece of content with a group of people that likes nature pictures.
+However, everyone can access all references someone makes.
+So if a person from the nature group notices the tree is ill and comments on this, the original poster can see this comment and act accordingly.
+On the current web the friend who shared the picture with the group has to be contacted directly by the commenter and then has to relay the message manually.
 
-For example, if a user wants to see a movie this weekend, he orders his AI, or \textit{softbot}, to find him a suitable time and movie to see.
-The softbot then accesses the Internet Movie Database to see which movies currently play and which of those are similar to what the user liked in the past.
-He will then access the pages of the local movie theaters to see when those movies play.
-Lastly, he will contact the softbots of the friends of the user to ask if they will also come to see that movie.
-After a short exchange the optimal time, place and participant set are decided, and the softbot tells the user what the results are.
-When the user accepts, the appointment is automatically added to his agenda.
-% Mogelijk verplaatsen naar introduction
+ The linking of every piece of content to another allows not only humans to browse the internet, but also virtual agents, which can use this information to aid their users in ways that are simply impossible nowadays.
+If someone wants to find information on a certain topic, the agent can collect all documents that are relevant to that topic, summarize each document in a way that is relevant to the search request and provide sources for every fact it finds.
+It would even be possible to have a question answering session on that specific topic, where the agent finds the answer to every question posed in the material that is linked to the topic.
 
-All of this is possible, if the softbot can access all of the information reliably.
+ Another possibility is the scenario from the introduction \ref{intro}, where a user wanted to see a movie, and ordered his softbot, to find him a suitable time and movie to see.
+This was shown to reduce a lot of planning and allow for much more favourable decisions since many more variables can be taken into account.
+
+ All of this is possible if the softbots can access all of the information reliably.
 In the current Web, this is not possible, as all information is written in an ambiguous, unstructured format called human language.
@@
 The fact that it is pragmatic goes a long way of making it a reality: if even one application comes into existence that uses online information in a structured way and thus makes everyday tasks a little easier, the goal is accomplished.
-Of course, then the goal resets and we should make more applications leveraging more information for more tasks.
+Of course, then the goal is stretched and we should make more applications leveraging more information for more tasks.
 
@@
 This information is not limited to the information that is online \emph{now}, but can include sensor data from the Internet of Things, data from robots, facts deduced or statistically inferred from existing data and so on.
-All this information can be used to accommodate the wants and needs of humans, when asked for it but also before the users are even aware of their needs.
+All this information can be used to accommodate the wants and needs of humans, when asked for it \textit{and} before the users are aware of their needs.
 The personal agent should be able to predict the users need and provide the tools that can satisfy the need.
@@
  To provide these tools to the user, an agent uses many different sources.
-For example, if the need of a researcher is knowledge on a certain topic, the agent must chart relevant topics, map relations between different domains and connect these new ideas to topics the researcher already knows about.
+For example, if the need of a researcher is knowledge on a certain topic, the agent must chart relevant topics, map relations between different domains and connect these new ideas to topics that the researcher is already familiar with.
 In fact, the largest part of the job an agent has to carry out on the Semantic Web is finding relationships between pieces of information on the Web.
@@
  \subsubsection{Current state}
+ Currently, people are not aware of the Semantic Web.
+Either websites and applications do not use any semantic information, or it is used on the back-end, hidden with other complex programs that users will not understand.
+So what is the Semantic Web used for nowadays, if at all?
+In this section, I will list a number of general ways people use Semantic Web technologies as well as specific applications.
+Note that these are Semantic Web technologies, i.e.
+technologies that came into existence through Semantic Web research and can eventually be used in the Semantic Web, but currently are not used for the Semantic Web since it does not exist yet.
+
  The Semantic Web is currently divided into two groups: the people who need high accuracy and the people who need high recall.
 The first group consist of scientists that work on specific fields that require exact knowledge, whereas the second group are data scientists that want big amounts of data available.
+In the past it was not possible to extract information from texts and other sources automatically, so
 
@@
 The Knowledge Base in our example can contain actually existing birds or fictional birds, and refers to the Ontology concept of bird to embed the instantiations with meaning.
+
  \subsubsection{OWL}
@@
  \subsubsection{Role}
+ %Beschrijf de drie manieren om top-down ontologien te maken. Geen intra-ontologiale verwijzingen, verwijzingen of overlap (maar dan nog steeds verwijzingen). Beschrijf bottom-up ontologie maken.
+
  The reason ontologies are used in databases consists of multiple parts.
@@
  Popular terminological strategies are WordNet comparison and edit distance.
-The former uses the popular WordNet hierarchy as a distance measure between to concepts, e.g.
+The former uses the popular WordNet hierarchy as a distance measure between two concepts, e.g.
 the number of edges between the concepts and their least general common superconcept.
@@
  \subsection{Research questions}
- Can distributed representations of concepts be used to find relationships between concepts in ontologies better than existing terminological matchers?\\\\
+ The main question that I will answer with this work is the following research question:
 
- Can distributed representations use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers?\\\\
+ \begin{center}
+ \textit{
+ Can distributed representations of concepts be used to find relationships between concepts in ontologies better than existing terminological matchers?
+ }
+ \end{center}
+ % Alternatively, do my matcher add anything? i.e. does adding it to an ensemble of existing matchers increase performance?
 
+ I will also investigate the following two related but different questions:
+
+ \begin{center}
+ \textit{
+ Can distributed representations use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers?
+ }
+ \end{center}
+
+ \begin{center}
+ \textit{
  Can distributed representations perform well in a domain it was not designed for?
+ }
+ \end{center}
 
  \subsection{Hypotheses}
- Since multiple implementations of the algorithm are considered, every hypothesis that follows is considered for every implementation.\\\\
+ Since multiple implementations of the algorithm are considered, every hypothesis that follows is considered for every implementation.
 
  \begin{center}
- \textit{The distributed representations of concepts matcher can find relationships between concepts in ontologies better than existing terminological matchers.}
+ \textit{This specific matcher that uses a distributed representation of concepts can find relationships between concepts in ontologies better than existing terminological matchers.}
  \end{center}
+
+ To prove this hypothesis, I must proof the following points:
+ \begin{itemize}
+ \item The algorithm uses distributed representations of concepts.
+ \item The algorithm finds relationships between concepts in ontologies.
+ \item The algorithm has been compared to the currently best matchers.
+ \item The algorithm performs better.
+ \end{itemize}
+
+ The first three points will be shown in \ref{proofs}, whereas the last point is shown in \ref{conclusions}.
+
  \begin{center} 

### 2016-05-08 Paper/Draft.tex
Added Jena

@@
  \documentclass{article}
+
  \usepackage[utf8]{inputenc}
  \usepackage[titletoc]{appendix}
+ \usepackage{listings}
+
  \title{Ontology Matching with word2vec}
@@
 
+ \subsubsection{Jena}
+ Jena is the most used library for storing, manipulating, querying and reasoning on ontologies.
+It has an interface that allows for easy access to an ontology.
+For example, if one would like to obtain a list of all neighbours of a certain node, one can simply use the following Jena command:
+ \lstset{language=Java}
+ \begin{lstlisting}
+  ontology.listStatements(givenNode, null, null)
+ \end{lstlisting}
+
+ It automatically gives all statements that have the given node as subject. In terms of graphs this is equal to obtaining all edges that go out of the given node.
+
+ In Jena it is possible to obtain the label of any node, if it has it, by calling:
+
+ \begin{lstlisting}
+  label = node.isBlank() ? 
+  		  node.getBlankNodeLabel() : 
+  		  node.getLiteral()
+ \end{lstlisting}
+
+ The ternary is to distinguish between blank and non-blank nodes. Blank nodes are a feature of ontologies and thus need to be taken into account.
+
+ \subsubsection{Never-ending Language Learner}
+ The Never-Ending Language Learner, or NELL, also known as the Read the Web Project, has created a big ontology of facts extracted from the web.
+
+ \subsubsection{WordNet}
+ WordNet is a manually constructed database of semantic relations between words.
+ % https://wordnet.princeton.edu/wordnet/publications/poznan.springer.pdf
+
  \newpage

### 2016-05-14 Paper/Draft.tex
Corrections up to p.9

@@
  \pagenumbering{arabic}
- \section{Introduction}
+ \section{Introduction} \label{intro}
  It is a Friday afternoon and you realise you want to watch a movie with some friends this weekend. So, what do you do? To achieve this goal you must take four steps.
@@
 The term ontology will be properly defined later on, but for now it suffices to know that an ontology is a set of rules that determine what relations are allowed and required in a given domain of discourse.
-Without ontologies, agents on the Semantic Web would be unable to communicate, as all concepts are defined in an Ontology.
+As a consequence, if two agents want to communicate in a given domain, they need to agree on the rules of that domain, or in other words, share the ontology of that domain.
 
- However, using one single ontology is infeasible.
+ However, it is unlikely that a conversation only covers one domain.
+To solve this, there are two potential solutions.
+Either you ensure that all possible combinations of domains are covered by an ontology, which means one ontology that covers all domains is required, or, alternatively, ontologies are combined on-the-fly.
+
+ The first option, using one single ontology, is infeasible.
 This is due to the fact that inference and search time scales with Ontology size, and the number of concepts that are needed on the Semantic Web is enormous.
@@
 Searching through this Ontology just to find one concept would be incredibly costly.
-And since every interaction on the Semantic Web requires lookups in an Ontology or corresponding Knowledge Base, these lookups need to be fast.
+And since every interaction on the Semantic Web requires lookups in an Ontology, these lookups need to be fast.
 
- The solution to this problem is to split this Ontology into many smaller Ontologies. However, as often is the case in Computer Science, this creates two new, albeit smaller, problems.
+ The second option, the one I address in this thesis, is the problem of combining ontologies from multiple domains.
+Combining in this sense means connecting the related concepts from the different Ontologies.
+Some research has focused on Ontology Merging, with promising results.
+However, recently research has been slowing to the point where there is little improvement.
 
- The first problem is the problem of splitting the Ontology.
-How do we find the distribution of all concepts over the different Ontologies to maximize their usefulness.
-Usefulness in this case should take into account co-occurrence of concepts.
-Naturally, connected concepts should be more likely to occur in the same Ontology as concepts that are not connected, since it is likely that agents that want to know about a concept also want to know things about its neighbours.
+ One big problem in Ontology merging is the fact that in different domains, words can have different meanings.
+Common examples are synonyms like author and writer, homonyms like bank (for money or by a river) and ambiguity.
+Ambiguity means that similar words mean slightly different things, or a word might have multiple related meanings.
+There are a few ways to deal with these forms of ambiguity already in use, however they are not sufficient.
 
- The second problem, the one I address in this thesis, is the problem of conversations that cover multiple domains.
-These conversations will occur more often if there are more Ontologies, but they can always occur if the number of Ontologies is larger than one.
-When a conversation requires information from multiple domains, the Ontologies corresponding to those domains need to be merged.
-This means connecting the related concepts from the different Ontologies.
-Some research has focused on ontology merging, with promising but slowing results.
-
- The problem of Ontologies on the Semantic Web is to find those Ontologies that are as small as possible to improve search speed, but need to be merged as little as possible, to ensure as little time is used to merge the Ontologies before they can be searched.
-If it is possible to quickly and reliably merge Ontologies, Ontologies can be made small and communication on the Semantic Web can be done quickly.
-
- Recently, a model that embeds words in a vector space that appears to contains semantics has become popular.
-Since it is unsupervised and can be used to calculate a semantic distance between words, it may very well be applicable to ontology matching.
+ A recently developed model for word embedding may be used to deal with ambiguity.
+It maps words to a vector space that has semantic properties, and thus can be used to calculate the relatedness of two words.
+There are a number of extensions that can deal with homonyms as well as data structured other than the continuous bag of words representation that the initial model was developed for.
+These facts show that it may be possible to make an embedding model for Ontologies and use the word relatedness to combine Ontologies.
 
@@
  The Semantic Web, also called Web 3.0, is a concept of a Web that enhances the User Experience in ways that the current Web can not provide.
-Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and limited interconnectivity.
-For example, Facebook is a hub for sharing content with people you consider friends, but if you want to share that content with more people you will have to go to another hub, like imgur or Pinterest.
-It is possible to link to content from other hubs using URLs, but this moves the user to another hub, rather than connecting the content present in the hubs.
+Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and limited interconnectivity.\footnote{For example, Facebook is a hub for sharing content with people you consider friends, but if you want to share that content with more people you will have to go to another hub, like imgur or Pinterest.} It is possible to link to content from other hubs using URLs, but this moves the user to another hub, rather than connecting the content present in the hubs.
 The Semantic Web, on the other hand, contains sources of \textit{information} that can be combined whenever the user needs it.
-To stick with the social media example, a person can create a piece of content, say a picture of a tree, en shares it with his friends.
+To stick with the social media example, a person can create a piece of content, say a picture of a tree, and share it with his friends.
 One of his friends then can share this piece of content with a group of people that likes nature pictures.
@@
  All of this is possible if the softbots can access all of the information reliably.
-In the current Web, this is not possible, as all information is written in an ambiguous, unstructured format called human language.
+In the current Web, this is not possible, as all information is written in an ambiguous, unstructured format called natural language.
 To allow softbots to access the same information that we can, the Semantic Web proposes to add a layer to the internet where all information is saved in a unified format that is unambiguous, robot-interpretable and can be used to store any type of knowledge.
@@
 But humans will only accept the Semantic Web if it is useful to them, so the Semantic Web must show its applications and usefulness before it will be used in daily life.
- \subsubsection{Current state}
+ \subsubsection{Current state} %TODO This bit can use some work
+ %TODO Cite Peter Mika (see Arjen notes 1)
  Currently, people are not aware of the Semantic Web.
@@
 
- The Semantic Web is currently divided into two groups: the people who need high accuracy and the people who need high recall.
-The first group consist of scientists that work on specific fields that require exact knowledge, whereas the second group are data scientists that want big amounts of data available.
-In the past it was not possible to extract information from texts and other sources automatically, so
+ Semantic Web systems are currently divided into two groups: the systems that need high accuracy and the ones that need high recall.
+The first group are deployed in domains that require exact knowledge, whereas the second group are systems that must make available a big amount of data.
+In the past it was not possible to extract information from texts and other sources automatically, so all systems were hand-crafted and thus highly accurate but very small.
+This also impacted research, which did not focus on scaling ontologies until recently.
 
@@
 This method of creating a knowledge base does not scale very well and usually consists of fewer than ten thousand facts.
-Because of this, the knowledge bases are restricted to small domains, including some parts of medicine and cultural heritage.
-\cite{byrne, le2002}
+Because of this, the knowledge bases are restricted to small domains, including some parts of medicine and cultural heritage\cite{byrne, le2002}.
 
- The group that requires a high recall, i.e.
-requires a huge amount of data, automated methods are required.
+ For the group that requires a high recall, or in other words a big amount of data, automated methods are required.
 These methods work fast, parsing thousands of websites a minute, but are inclined to make mistakes.
-Often, these methods use crowd-sourcing to improve accuracy, using experts or the general public to suggest or check facts.
-\cite{zhou2007}
+Often, these methods use crowd-sourcing to improve accuracy, using experts or the general public to suggest or check facts\cite{zhou2007}.
 
@@
 
- Large ontologies already exist, with the largest, DBPedia, boasting almost two billion triples and the three hundred combined Large Open Data databases contain over thirty billion.
-\cite{dbpedia, lod} The LOD is simply one huge alignment of hundreds of knowledge bases...
+ Large ontologies already exist, with the largest, Freebase, boasting almost two billion triples and the three hundred combined Large Open Data databases contain over thirty billion\cite{dbpedia, lod}.
+The LOD is simply one huge alignment of hundreds of knowledge bases...
 %Doorschrijven
@@
  \subsection{Ontologies}
- Earlier, ontologies were referred to as 'a set of rules that determine what relations are allowed and required.' Now, the term will be defined more extensively, the standard format will be described and the uses of ontologies will be discussed.
+ Earlier, ontologies were referred to as `a set of rules that determine what relations are allowed and required.' Now, the term will be defined more extensively, the standard format will be described and the uses of ontologies will be discussed.
 
@@
 For example, a hierarchy is an ontology that describes concepts that are subclasses of other concepts.
-Therefore the relationships are 'part-of' relationships: birds are part-of the animals concept class.
+Therefore the relationships are 'is-a' relationships: a bird \emph{is an} animal.
  Concepts can be instantiated, which is done in a Knowledge Base (KB).
@@
 The variants trade off levels of expressiveness versus computability.
+%TODO consider SKOS
  \subsubsection{SPARQL}
  SPARQL is the query language for knowledge bases and ontologies. It allows a user to select nodes whose context match the query, similar to how rows are selected in SQL based on the row contents.
- \subsubsection{Role}
- %Beschrijf de drie manieren om top-down ontologien te maken. Geen intra-ontologiale verwijzingen, verwijzingen of overlap (maar dan nog steeds verwijzingen). Beschrijf bottom-up ontologie maken.
-
- The reason ontologies are used in databases consists of multiple parts.
+ \subsubsection{Uses of Ontologies}
+ %Beschrijf bottom-up ontologie maken.
+ There are three main reasons Ontologies are used.
 Firstly, it allows querying languages to optimize the search process.
@@
 Therefore it will be explained more in-depth later on.
+%TODO add \ref
  \subsubsection{Aristotle and Plato}
@@
 Aristotle disagreed with Plato's theory that concepts are existing things, and thus these ontologies are named after him.
+%TODO cite
 
@@
 The disadvantage is that creating such an ontology is much more costly than an Aristotelian ontology, since every concept and constraint needs to be correct in all cases.
+%TODO cite Lakoff
 
@@
 Some strategies also use extra steps like the extensional and semantic steps, which use vector space models and inference, respectively.
-https://hal.inria.fr/hal-00917910/document
+%TODO cite https://hal.inria.fr/hal-00917910/document
 
@@
 The former uses the popular WordNet hierarchy as a distance measure between two concepts, e.g.
-the number of edges between the concepts and their least general common superconcept.
-\cite{lin2008}
+the number of edges between the concepts and their least general common superconcept\cite{lin2008}.
  Edit distance is a purely string-based similarity measure.
 The similarity is a (weighted) count of edits required to transform one word into another, where common edits are insertion, deletion and replacement.
-Similar methods include substring matching and n-gram matching, which compare parts of the strings to find similarities.\cite{singh2014, levenshtein}
+Similar methods include substring matching and n-gram matching, which compare parts of the strings to find similarities\cite{singh2014, levenshtein}.
  \subsection{Problems in ontology alignment}
@@
 
- Recently, an effective and efficient skip-gram model has been developed, called word2vec, which uses a number of extensions over previous methods that enable it to efficiently learn an effective representation.
-/cite{w2v}
+ Recently, an effective and efficient skip-gram model has been developed, called word2vec, which uses a number of extensions over previous methods that enable it to efficiently learn an effective representation/cite{w2v}.
  Word2vec learns this representation by trying to predict the context of a word.
@@
 This preservation was done by having multiple output layers, one for every word in the context.
-The research shows that the input does not have to be a bag-of-words representation, which will be useful later on.
-\cite{ling2015}
+The research shows that the input does not have to be a bag-of-words representation, which will be useful later on\cite{ling2015}.
  Another interesting development is the multi-sense word2vec, which allows for multiple vector representations per word, depending on the number of different definitions a word has.
@@
 It can differentiate between two different meanings based on the context.
-This will help with resolving ambiguity, a very important factor in ontology alignment.\cite{multisense}
+This will help with resolving ambiguity, a very important factor in ontology alignment\cite{multisense}.
  \subsection{Used technology}
  \subsubsection{AgreementMaker} \label{agreementmaker}
- AgreementMaker is an ontology matching system that obtained the highest F-measure in 6 of the 7 ontology matching tracks of OAEI 2015.
-\cite{OAEI2015} The system has also been updated the most recent at the time of writing\cite{agreementmaker}.
+ AgreementMaker is an ontology matching system that obtained the highest F-measure in 6 of the 7 ontology matching tracks of OAEI 2015 \cite{OAEI2015}.
+The system has also been updated the most recent at the time of writing\cite{agreementmaker}.
 

### 2016-05-15 Paper/Draft.tex
Feedback up to page 16

@@
 
- \subsection{Other related research}
- \subsubsection{Word sense representation} \label{w2v}
+ \subsection{Word sense representation} \label{w2v}
  Skip-gram models have been widely used to represent words as vectors.
@@
 
- Recently, an effective and efficient skip-gram model has been developed, called word2vec, which uses a number of extensions over previous methods that enable it to efficiently learn an effective representation/cite{w2v}.
- Word2vec learns this representation by trying to predict the context of a word.
+ Recently, an effective and efficient skip-gram model has been developed, called \textf{word2vec}, which uses a number of extensions over previous methods that enable it to efficiently learn an effective representation\cite{w2v}.
+ \textf{Word2vec} learns this representation by trying to predict the context of a word.
 First the vocabulary is one-hot encoded.
@@
 
- Word2vec has been expanded in a number of different ways.
+ \textf{Word2vec} has been expanded in a number of different ways.
 For example, word order can be preserved, leading to a similarity measure that is closer to syntax, as syntax defines which words go where in a sentence.
@@
 The research shows that the input does not have to be a bag-of-words representation, which will be useful later on\cite{ling2015}.
- Another interesting development is the multi-sense word2vec, which allows for multiple vector representations per word, depending on the number of different definitions a word has.
+ Another interesting development is the multi-sense \textf{Word2vec}, which allows for multiple vector representations per word, depending on the number of different definitions a word has.
 For example, the word bank represents both the monetary institute and the riverside, which would both have a different representation in this extension.
@@
  \subsection{Used technology}
- \subsubsection{AgreementMaker} \label{agreementmaker}
- AgreementMaker is an ontology matching system that obtained the highest F-measure in 6 of the 7 ontology matching tracks of OAEI 2015 \cite{OAEI2015}.
-The system has also been updated the most recent at the time of writing\cite{agreementmaker}.
-
- The system uses an extensible framework which allows its users to add new modules to the system.
-This is very useful for research as it allows the researcher to compare different modules by swapping in just those modules in the framework.
-The module-swapping technique will also be used in this work, but more of that will be discussed in \ref{Evaluation methods}.
-
- \subsubsection{Factorie} \label{factorie}
+ %TODO Guide user from problem to research question. See Arjen's notes 1. 
+ \subsubsection{Factorie} \label{factorie} %TODO rewrite
  "FACTORIE [is a] a toolkit for probabilistic modeling based on imperatively-defined factor graphs" \cite{git-factorie}.
@@
   Those ontologies contain rules about concepts and concept classes in the shape of triplets, with two concepts and a relation.
-For example, the rule {\tt Professors are humans} contains the concepts \emph{Professor} and \emph{human} and relationship \emph{being}.
+For example, the rule {\tt Professors are humans} contains the concepts \emph{Professor} and \emph{human} and an \emph{is-a}-relationship.
 
@@
 These different relations all require a different approach and come with their own sets of problems.
+%Meronymy?
 
@@
  \textit{
- Can distributed representations perform well in a domain it was not designed for?
+ Can distributed representations perform well in a domain it was not trained for?
  }
@@
  \subsection{Hypotheses} 
- Since multiple implementations of the algorithm are considered, every hypothesis that follows is considered for every implementation.
-
  \begin{center}
@@
  \begin{center}
- \textit{The distributed representations matcher can perform well in a domain it was not designed for.}
+ \textit{The distributed representations matcher can perform well in a domain it was not trained for.}
  \end{center}
 
- The following hypotheses are true if for at least one implementation the corresponding hypothesis is true.
-
- \begin{center}  
- \textit{A distributed representations of concepts matcher can find relationships between concepts in ontologies better than existing terminological matchers.}
- \end{center} 
- \begin{center}
- \textit{A distributed representations matcher can use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers.}
- \end{center}
- \begin{center}
- \textit{A distributed representations matcher can perform well in a domain it was not designed for.}
- \end{center}
+ These hypotheses are true for distributed representations matcher if they are true for one distributed representation matcher.
+Therefore to test the hypotheses, I must test them for every distinct implementation of the matcher.
 
@@
 
- Since distributed representation algorithms can be trained unsupervised on new domains, they can be applied to those new domains without effort from humans, unlike current matching algorithms.
+ Since distributed representation algorithms can be trained unsupervised on new domains, they can be applied to those new domains without effort from humans, as opposed to for example the string edit distance.
 This is also an improvement for the semantic web.
@@
 It is already in use for companies that want to merge knowledge from other companies, for example.
-If the proposed matching algorithm is better than the current algorithms, or at least improves the performance when used in ensemble with the current algorithms, it will be useful in any situation, not just on the Semantic Web.
+If the proposed matching algorithm is better than the current algorithms, or at least improves the performance when used in ensemble with the current algorithms, it will be useful in these situations, not just on the Semantic Web.
 
@@
  \section{Method}
- In this section, I will describe the method that I developed.
+ This Section will describe the method that I developed.
 Firstly, I will describe the general idea.
 In the second section, I will give a theoretical justification for why this method should work and how it works conceptually.
-After that I will describe the different ways that the input graphs can be used to train the word2vec model and create the alignment, some of which I have discarded on theoretical grounds as I will explain in the relevant section.
+After that I will describe the different ways that the input graphs can be used to train the \textf{Word2vec} model and create the alignment, some of which I have discarded on theoretical grounds as I will explain in the relevant section.
 Lastly, I will talk about the implementation process.
  \subsection{Idea}
- As explained earlier, word2vec is a model that learns two things: implicitly it learns the semantic vector representation of words, and explicitly it learns to predict words from their context or vice versa.
+ As explained earlier, \textf{word2vec} is a model that learns two things: implicitly it learns the semantic vector representation of words, and explicitly it learns to predict words from their context or vice versa.
 I will use both of these pieces of information in our alignment algorithm.
@@
 
- To solve these problems I will adapt word2vec to graphs and extend it with multi-sense embeddings. Also hot-starting is considered as an improvement.
+ To solve these problems I will adapt \textf{Word2vec} to graphs and extend it with multi-sense embeddings.
+Also hot-starting is considered as an improvement.
+%TODO this paragraph needs to be explained
  \subsection{Considered implementations}
@@
 All implementations use the same basic algorithm in different ways by taking into account the context in different ways.
-All of these implementations were tested and the results can be found in \ref{results}.
-Some implementations are extensions of other implementations, but all implementations are mentioned for completeness and to enable explanation of the source of improvements.
+All of these implementations were tested and the results can be found in Section \ref{results}.
+Some implementations extend others, but all implementations are covered to ensure completeness.
+This way, all improvements are recorded precisely.
   \subsubsection{Training corpus}
@@
  The two foundations the algorithm has been build and tested on are Factorie, described in \ref{factorie}, and AgreementMaker, described in \ref{agreementmaker}, respectively.
-Earlier work on a forked branch of factorie was done by \cite{multisensecode} to implement multi-sense word2vec.
+Earlier work on a forked branch of factorie was done by \cite{multisensecode} to implement multi-sense \textf{Word2vec}.
 
@@
 
- Word2vec is an unsupervised method that maps words to a vector space that has been shown to contain semantic properties. %cite
+ \textf{Word2vec} is an unsupervised method that maps words to a vector space that has been shown to contain semantic properties. %cite
  It can be trained on large corpora quickly and the resulting vectors can easily be used to measure the distance between words.

### 2016-06-16 node_embedding/src/DeepWalkNodeEmbedding.scala
DeepWalk implemented. Result of first tests: ~.7 dice (accuracy 80%, recall 60%).

@@ -1,0 +1,183 @@
+import cc.factorie.app.nlp.embeddings.{SkipGramNegSamplingEmbeddingModel, SkipGramNegSamplingExample}
+import com.hp.hpl.jena.rdf.model.{RDFNode, Resource, Statement}
+
+import scala.util.Random
+import scala.collection.JavaConverters._
+import scala.collection.immutable.List
+import scala.collection.mutable
+import scala.collection.mutable.ArrayBuffer
+
+/**
+  * Created by harmen on 16-6-16.
+  */
+class DeepWalkNodeEmbedding extends NodeEmbeddingModel {
+
+  var it = 0
+
+  val URIs = Array("http://mouse.owl#",
+                   "http://human.owl#")
+  val LABEL_URI = "http://www.w3.org/2000/01/rdf-schema#label"
+
+  def getNeighbours(curNode: String, curOnt: Int) : Array[String] = {
+    val onto = ontology.getOntologies(curOnt).asInstanceOf[RDFOntology]
+    val edges = onto.getEdges
+    var nbs = new mutable.ArrayBuffer[String]()
+    for (edge <- edges) {
+      if (edge.split(" ")(0) == curNode)
+        nbs += edge.split(" ")(2)
+      else if (edge.split(" ")(2) == curNode)
+        nbs += edge.split(" ")(0)
+    }
+    nbs.toArray
+  }
+
+  def getWeights(neighbors: Seq[String]): Seq[Double] = {
+    Seq.fill(neighbors.length)(1.0)
+  }
+
+  def getSample(weights: Seq[Double]): Int = {
+    var cm = 0.0
+    val cms_ = new ArrayBuffer[Double]()
+    for ((w, i) <- weights zipWithIndex) {
+      cm += w
+      cms_ += cm
+    }
+    val cms = cms_.toArray
+    val v = rng.nextDouble()*weights.sum
+    for ((w, i) <- cms zipWithIndex) {
+      if (w >= v)
+        return i
+    }
+    0
+  }
+
+  def other(curOnt: Int): Int = {
+    1 - curOnt
+  }
+
+  def maybeSwitch(curOnt: Int): Int = {
+    // TODO don't hardcode chance
+    val p = 0.9
+    if (rng.nextDouble() > p)
+      return other(curOnt)
+    else
+      return curOnt
+  }
+
+  def check_finished(): Boolean = {
+    it+=1
+    return it < 1000
+  }
+
[…]

### 2016-06-16 node_embedding/src/Evaluator.scala

@@ -10,7 +10,7 @@ import scala.util.Try
 object Evaluator {
 
   val opts = WordSenseOpts
-  val model = new SkipGramNodeEmbedding()
+  val model = new DeepWalkNodeEmbedding() //SkipGramNodeEmbedding()
 
   def compare(alignment: Alignment, truth: Alignment): Double = {
     val alignmentset = alignment.alignments.asScala.toSet[(String, String, Double)].map { case (s: String, o: String, v: Double) => (s, o) }

### 2016-06-16 node_embedding/src/MultiVocabBuilder.scala

@@ -35,10 +35,13 @@ class MultiVocabBuilder(n: Int = 2) extends VocabBuilder {
 
   override def getId(word: String): Int = {
     var w = -1
+    var sum = 0
     for (v <- vocabs) {
       w = v.getId(word)
       if (w != -1)
-        return w
+        return sum + w
+      else
+        sum += v.size()
     }
     w
   }
@@ -72,11 +75,20 @@ class MultiVocabBuilder(n: Int = 2) extends VocabBuilder {
   }
 
   override def buildSubSamplingTable(s: Double) : Unit = {
-    throw new NotImplementedException("Author did not require this method.")
+    for (v <- vocabs)
+      v.buildSubSamplingTable(s)
   }
 
   override def getSubSampleProb(id: Int): Double = {
-    throw new NotImplementedException("Author did not require this method.")
+    var cur_N = 0
+    for (v <- vocabs) {
+      if (id - cur_N < v.size) {
+        return v.getSubSampleProb(id - cur_N) * (v.size() / size())
+      } else {
+        cur_N += v.size
+      }
+    }
+    0
   }
 
   override def size(): Int = {

### 2016-06-16 node_embedding/src/NodeEmbeddingModel.scala

@@ -1,4 +1,4 @@
-import cc.factorie.app.nlp.embeddings.{LiteHogwildTrainer => HogWildTrainer}
+import cc.factorie.app.nlp.embeddings.{EmbeddingOpts, TensorUtils, WordEmbeddingModel, LiteHogwildTrainer => HogWildTrainer}
 import cc.factorie.model.Weights
 import cc.factorie.optimize.AdaGradRDA
 import cc.factorie.la.DenseTensor1
@@ -6,12 +6,11 @@ import java.io._
 import java.util.zip.{GZIPInputStream, GZIPOutputStream}
 
 import scala.collection.JavaConverters._
-import cc.factorie.app.nlp.embeddings.{TensorUtils,WordEmbeddingModel}
-
 import scala.collection.mutable
 import scala.util.Try
 
-abstract class NodeEmbeddingModel() extends WordEmbeddingModel(WordSenseOpts) {
+
+abstract class NodeEmbeddingModel extends WordEmbeddingModel(WordSenseOpts) {
   //implicit def bool2int(b:Boolean): Int = if (b) 1 else 0 // Converts booleans to ints when needed
   //implicit def int2bool(i:Int): Boolean = if(i==0) false else true // Convert ints to booleans when needed
   // Algo related
@@ -37,6 +36,7 @@ abstract class NodeEmbeddingModel() extends WordEmbeddingModel(WordSenseOpts) {
   def getRootSynonym(w: String): String = {
     getRootSynonym(w, loadSynonyms())
   }
+
   def getRootSynonym(w: String, synonyms: mutable.HashMap[String, String]): String = {
     var w_ = Try(synonyms(w)).getOrElse(w)
     while(synonyms.contains(w_) && w_ != w)

### 2016-06-16 node_embedding/src/SkipGramNodeEmbedding.scala

@@ -8,7 +8,7 @@ import smile.neighbor.KDTree
 import scala.collection.mutable.ArrayBuffer
 import scala.util.control.Breaks._
 
-class SkipGramNodeEmbedding() extends NodeEmbeddingModel(){
+class SkipGramNodeEmbedding() extends NodeEmbeddingModel {
 
 
   val negative = WordSenseOpts.negative.value

### 2016-06-16 node_embedding/src/WordSenseOpts.scala

@@ -26,7 +26,7 @@ object WordSenseOpts extends EmbeddingOpts{
   corpusses.setValue("Data/anatomy/mouse.owl;Data/anatomy/human.owl")
   output.setValue("Data/output.csv")
   saveVocabFile.setValue("Data/vocab.csv")
-  loadVocabFile.setValue("Data/vocab.csv")
-  inputFilename.setValue("Data/output.csv")
+  //loadVocabFile.setValue("Data/vocab.csv")
+  //inputFilename.setValue("Data/output.csv")
 }
 

### 2016-06-17 Paper/Draft.tex
Few more changes based on feedback

@@
  \subsection{Word sense representation} \label{w2v}
+ \subsubsection{Skip-gram models}
  Skip-gram models have been widely used to represent words as vectors.
@@
 
- Recently, an effective and efficient skip-gram model has been developed, called \textf{word2vec}, which uses a number of extensions over previous methods that enable it to efficiently learn an effective representation\cite{w2v}.
+ \subsubsection{The state of the art} 
+ Recently, an effective and efficient skip-gram model has been developed, called \textf{Word2vec}, which uses a number of extensions over previous methods that enable it to efficiently learn an effective representation\cite{w2v}.
  \textf{Word2vec} learns this representation by trying to predict the context of a word.
@@
 
+ \subsubsection{Extensions}
  \textf{Word2vec} has been expanded in a number of different ways.
@@
 This will help with resolving ambiguity, a very important factor in ontology alignment\cite{multisense}.
+
  \subsection{Used technology}
@@
  \subsubsection{Factorie} \label{factorie} %TODO rewrite
- "FACTORIE [is a] a toolkit for probabilistic modeling based on imperatively-defined factor graphs" \cite{git-factorie}.
-As a toolkit it contains many different parts that can be used together.
-One example is the NLP package in the toolkit, which provides many algorithms to process text.
-One of those algorithms is the distributed representation of words algorithm by \cite{w2v}.
+ Factorie is a toolkit that contains a number of tools which includes word-embedding models \cite{git-factorie}. \cite{w2v}.
 

### 2016-06-17 Paper/Draft.tex
Wrote blank nodes to Jena

@@
 Firstly, the Semantic Web, the key technology that depends very strongly on Ontology matching, will be discussed.
-Then the concept of the Ontology itself will be addressed.
-Lastly, current alignment strategies, their problems and other research and technologies will be discussed.
+Secondly, the concept of the Ontology itself will be addressed.
+Thirdly, current alignment strategies and their their problems are discussed.
+Lastly, other related research and technologies will be discussed.
+Later sections will refer back to the concepts discussed in this section.
  \subsection{The Semantic Web}
- The Semantic Web, also called Web 3.0, is a concept of a Web that enhances the User Experience in ways that the current Web can not provide.
+ The first concept is the Semantic Web, also called Web 3.0, a vision of a Web that enhances the User Experience in ways that the current Web can not provide.
 Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and limited interconnectivity.\footnote{For example, Facebook is a hub for sharing content with people you consider friends, but if you want to share that content with more people you will have to go to another hub, like imgur or Pinterest.} It is possible to link to content from other hubs using URLs, but this moves the user to another hub, rather than connecting the content present in the hubs.
@@
  \subsection{Problems in ontology alignment}
- There are a number of different problems ... % Opsommen en samenvatten
+ There are a number of different problems ... %TODO Opsommen en samenvatten
 
@@
 
- The ternary is to distinguish between blank and non-blank nodes. Blank nodes are a feature of ontologies and thus need to be taken into account.
+ The ternary is to distinguish between blank and non-blank nodes.
+Blank nodes are a feature of ontologies and thus need to be taken into account.
+Blank nodes can be used to represent concepts with multiple representations, for example a label, a description and a known synonym.
+More advanced algorithms can take into account all these representations.
+Another use of a blank node is representing a complex relationship that cannot be represented by an object-predicate-subject triple.
+For example, if the relationship has a certain confidence or more than two concepts are involved.
 

### 2016-06-17 Paper/Draft.tex
Final feedback and moved Idea to appropriate section

@@
 To allow softbots to access the same information that we can, the Semantic Web proposes to add a layer to the internet where all information is saved in a unified format that is unambiguous, robot-interpretable and can be used to store any type of knowledge.
+
+ The Semantic Web has a current state, the technologies that have been developed, which will be discussed later. But more importantly it is an idea
 
@@
  \begin{center} 
- \textit{The distributed representations matcher can use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers.}
+ \textit{The distributed representations matcher can use the context of a concept to find relationships between concepts in ontologies better than existing terminological and structural matchers.}
  \end{center}
@@
 Lastly, I will talk about the implementation process.
- \subsection{Idea}
- As explained earlier, \textf{word2vec} is a model that learns two things: implicitly it learns the semantic vector representation of words, and explicitly it learns to predict words from their context or vice versa.
-I will use both of these pieces of information in our alignment algorithm.
- The semantic representation will be used for finding nodes in the two ontology graphs that are similar, i.e.
-close in the vector space.
+
+ \section{Idea}
+The goal of any ontology matcher is to find an alignment between two ontologies that is as similar as possible to the true alignment.
+Such an alignment consists of node pairs where the two nodes in each pair come from the two different ontologies.
+Sometimes a label is added to each pair, indicating the relationship the two nodes have.
+For example, 'part-of', 'similar-to', and such.
+However, we only consider equality relationships and thus the label can be omitted.
+
+ Then the question becomes: \textit{how do we measure similarity of concepts between ontologies?} As shown in \ref{strategies}, attempts have been made to model similarity of nodes as the string similarity of their labels.
+Also, WordNet is used to find similar nodes.
+The string similarity assumes that similar labels refer to similar concepts.
+While this is true to a certain degree, homonyms, synonyms, and other phenomena make this assumption very weak.
+WordNet-based similarity measures are better since WordNet links concepts semantically, and thus similar concepts will be close in WordNet.
+The major problem with WordNet is that it is constructed by hand, and thus does not scale very well to new domains.
+
+ The idea behind the algorithm introduced in this study is to find an alternative to WordNet that is at least as good in modelling semantic distance but scales to new domains.
+It should be trainable on this new domain through existing ontologies and texts in an unsupervised way so that it does not require the interference of experts.
+This will allow it to overcome the weakness of WordNet.
+This is only relevant, though, if the performance is equal to WordNet-based matchers.
+
+ \textf{Word2vec} is an unsupervised method that implicitly maps words to a vector space that has been shown to contain semantic properties.
+Explicitly, it predicts words from the context of that word.
+%cite
+ It can be trained on large corpora quickly and the resulting vectors can easily be used to measure the distance between words.
+All these properties make it an excellent candidate for a concept distance measure to use for ontology matching.
+As an added benefit, it can also take into account the context of a concept, which may be able to improve its performance over a matcher that only uses the label of a concept.
+
+ \subsection{Challenges}
+ The semantic representation will be used for finding nodes in the two ontology graphs that are similar, i.e.\ close in the vector space.
 This step is relatively straightforward if proper vector representations are found.
@@
 
- To solve these problems I will adapt \textf{Word2vec} to graphs and extend it with multi-sense embeddings.
-Also hot-starting is considered as an improvement.
+ To solve these problems I will adapt \textf{Word2vec} to graphs to create an algorithm that converts nodes to vectors, in other words \textf{Node2vec}.
+It can be extended with multi-sense embeddings, different ways of considering the neighbourhood and hot-starting.
 %TODO this paragraph needs to be explained
@@
 This way, all improvements are recorded precisely.
-  \subsubsection{Training corpus}
-  Word embedding models need to be trained on a large corpus.
-These corpora need to cover the concepts that are contained in the ontology, but also need to be large enough to build good embeddings.
-Since the ontologies themselves do not necessarily contain enough examples to embed the concepts properly, I need to use ontologies that are likely to contain the concepts I want to align.
-  As a benchmark, I will use the WordNet and NELL ontologies.
-To check if adding the ontologies that are to be aligned helps, I will also train a model on an ontology consisting of WordNet, NELL and the two alignment candidates.
   \subsubsection{Node vectorisation}
-  The most basic node2vec model converts a node to a vector purely based on its own label.
+  The most basic \textf{Node2vec} model converts a node to a vector purely based on its own label.
 This method has one advantage over simple string matching: if no node is found in the other ontology that matches exactly, we can still find a node that is similar since it is close in the vector space.
@@
 This should make the model more robust, although edge labels may be duplicate (one has many unique family members) and less informative in general, so a lower weight may be appropriate.
-Another problem with this method is that the relation between a neighbour node and its corresponding edge is lost, since they are just treated as independent contexts.
+A different possible problem with this method is that the relation between a neighbour node and its corresponding edge may be lost, since they are just treated as independent contexts.
   \subsubsection{Select from senses}
@@
   \subsubsection{Hot start}
-  It is hard to classify the algorithm in terms of the normal ontology alignment methods.
+  It is hard to classify the proposed algorithm in terms of the conventional ontology alignment method classes.
 It is not purely string matching, since it takes into account information from the context.
@@
   %  Goeie woord?
-  since it does not use inference. Nor is it terminological, which looks at dictionaries or other ontologies to find matches. However, it does use other ontologies (or text corpi
-  % Check spelling
-  ) implicitly, so if it must be grouped it would be terminological.
+  since it does not use inference.
+Nor is it terminological, which looks at dictionaries or other ontologies to find matches.
+However, it does use other ontologies (or text corpora) implicitly, so if it must be grouped it would be terminological.
   % Moet voorafgaand stukje op een andere plek?
@@
 However, if we compare the cold and hot algorithms with the generic string matchers, we may be able to compare them indirectly.
-  % Dit moet weg als het bs blijkt te zijn
- \subsection{Discarded implementations}
+ \subsubsection{Training corpus}
+  Word embedding models need to be trained on a large corpus.
+These corpora need to cover the concepts that are contained in the ontology, but also need to be large enough to build good embeddings.
+Since the ontologies themselves do not necessarily contain enough examples to embed the concepts properly, I need to use ontologies that are likely to contain the concepts I want to align.
+  As a benchmark, I will use the WordNet and NELL ontologies.
+To check if adding the ontologies that are to be aligned helps, I will also train a model on an ontology consisting of WordNet, NELL and the two alignment candidates.
+ \subsubsection{DeepWalk}
+  An alternative way of increasing the number of examples that the algorithm considers is using DeepWalk.
+DeepWalk generates sentences by randomly walking through the ontology and processes those sentences using a normal embedding model.
+This has the advantage of having a wider neighbourhood, as the neighbours of neighbours are also used as context, or even further neighbours depending on the scope of the algorithm.
+It also allows for weighting of edges to change the sampling rate of the random walk, which can be used to prioritize important nodes or highlight informative neighbours.
+ \subsection{Discarded implementations} %TODO consider adding to future
   \subsubsection{Training on text}
@@
  %https://hal.inria.fr/hal-00917910/document
- The goal of the research is to find an ontology alignment algorithm $A$ and proof that it performs better than current techniques.
+ The goal of the research is to find an ontology alignment algorithm $A$ and prove that it performs better than current techniques.
 However, as current techniques may combine many different algorithms and sources of information, maybe such a comparison is not fair, nor is a comparison with individual algorithms as they may be optimised for being combined.
@@
 The True Negatives do not matter, as there are extremely many, and the goal of ontology matching is to find True Positives.
-Therefore the Jaccard similarity should be used as a performance measure.
+If we only care about True Positives, the Jaccard similarity is a prime candidate for the performance measure.
 
@@
  To see if an algorithm is useful to an ensemble, the improvement score $I$ has to be \emph{significantly} higher than zero.
-To check if a score is significant, a statistical significance test will have to be carried out.
-The test works as follows: generate $N$ solutions randomly and score them.
+To check if a score is significant, a statistical significance test will have to be carried out, which works as follows: generate $N$ solutions randomly and score them.
 Then score the method you want to investigate.
@@
 In this case the solutions are $E\cup \{R\}$, where $R$ is an algorithm that generates random alignments.
+%TODO ref for stats test
 
@@
  \subsubsection{Parts of OWL ignored}
-
- \newpage
- \section{Algorithm}
- \subsection{Idea}
- The goal of any ontology matcher is to find an alignment between two ontologies that is as similar as possible to the true alignment.
-Such an alignment consists of node pairs where the two nodes in each pair come from the two different ontologies.
-Sometimes a label is added to each pair, indicating the relationship the two nodes have.
-For example, 'part-of', 'similar-to', and such.
-However, we only consider equality relationships and thus the label can be omitted.
-
- Then the question becomes: \textit{how do we measure similarity of concepts between ontologies?} As shown in \ref{strategies}, attempts have been made to model similarity of nodes as the string similarity of their labels.
-Also, WordNet is used to find similar nodes.
-The string similarity assumes that similar labels refer to similar concepts.
-While this is true to a certain degree, homonyms, synonyms, and other phenomena make this assumption very weak.
-WordNet-based similarity measures are better since WordNet links concepts semantically, and thus similar concepts will be close in WordNet.
-The major problem with WordNet is that it is constructed by hand, and thus does not scale very well to new domains.
-
- The idea behind the algorithm introduced in this study is to find an alternative to WordNet that is at least as good in modelling semantic distance but scales to new domains.
-It should be trainable on this new domain through existing ontologies and texts in an unsupervised way so that it does not require the interference of experts.
-This will allow it to overcome the weakness of WordNet.
-This is only relevant, though, if the performance is equal to WordNet-based matchers.
-
- \textf{Word2vec} is an unsupervised method that maps words to a vector space that has been shown to contain semantic properties. %cite
- It can be trained on large corpora quickly and the resulting vectors can easily be used to measure the distance between words.
-All these properties make it an excellent candidate for a concept distance measure to use for ontology matching.
-As an added benefit, it can also take into account the context of a concept, which may be able to improve its performance over a matcher that only uses the label of a concept.
- \subsection{Theory}
-
- \subsection{Product}
 

### 2016-06-17 Paper/Draft.tex
Added example to OWL

@@
  \subsubsection{The state of the art} 
- Recently, an effective and efficient skip-gram model has been developed, called \textf{Word2vec}, which uses a number of extensions over previous methods that enable it to efficiently learn an effective representation\cite{w2v}.
- \textf{Word2vec} learns this representation by trying to predict the context of a word.
+ Recently, an effective and efficient skip-gram model has been developed, called \textbf{Word2vec}, which uses a number of extensions over previous methods that enable it to efficiently learn an effective representation\cite{w2v}.
+ \textbf{Word2vec} learns this representation by trying to predict the context of a word.
 First the vocabulary is one-hot encoded.
@@
  \subsubsection{Extensions}
- \textf{Word2vec} has been expanded in a number of different ways.
+ \textbf{Word2vec} has been expanded in a number of different ways.
 For example, word order can be preserved, leading to a similarity measure that is closer to syntax, as syntax defines which words go where in a sentence.
@@
 The research shows that the input does not have to be a bag-of-words representation, which will be useful later on\cite{ling2015}.
- Another interesting development is the multi-sense \textf{Word2vec}, which allows for multiple vector representations per word, depending on the number of different definitions a word has.
+ Another interesting development is the multi-sense \textbf{Word2vec}, which allows for multiple vector representations per word, depending on the number of different definitions a word has.
 For example, the word bank represents both the monetary institute and the riverside, which would both have a different representation in this extension.
@@
 In the second section, I will give a theoretical justification for why this method should work and how it works conceptually.
-After that I will describe the different ways that the input graphs can be used to train the \textf{Word2vec} model and create the alignment, some of which I have discarded on theoretical grounds as I will explain in the relevant section.
+After that I will describe the different ways that the input graphs can be used to train the \textbf{Word2vec} model and create the alignment, some of which I have discarded on theoretical grounds as I will explain in the relevant section.
 Lastly, I will talk about the implementation process.
@@
 
- \textf{Word2vec} is an unsupervised method that implicitly maps words to a vector space that has been shown to contain semantic properties.
+ \textbf{Word2vec} is an unsupervised method that implicitly maps words to a vector space that has been shown to contain semantic properties.
 Explicitly, it predicts words from the context of that word.
@@
 
- To solve these problems I will adapt \textf{Word2vec} to graphs to create an algorithm that converts nodes to vectors, in other words \textf{Node2vec}.
+ To solve these problems I will adapt \textbf{Word2vec} to graphs to create an algorithm that converts nodes to vectors, in other words \textbf{Node2vec}.
 It can be extended with multi-sense embeddings, different ways of considering the neighbourhood and hot-starting.
@@
   \subsubsection{Node vectorisation}
-  The most basic \textf{Node2vec} model converts a node to a vector purely based on its own label.
+  The most basic \textbf{Node2vec} model converts a node to a vector purely based on its own label.
 This method has one advantage over simple string matching: if no node is found in the other ontology that matches exactly, we can still find a node that is similar since it is close in the vector space.
@@
  The two foundations the algorithm has been build and tested on are Factorie, described in \ref{factorie}, and AgreementMaker, described in \ref{agreementmaker}, respectively.
-Earlier work on a forked branch of factorie was done by \cite{multisensecode} to implement multi-sense \textf{Word2vec}.
+Earlier work on a forked branch of factorie was done by \cite{multisensecode} to implement multi-sense \textbf{Word2vec}.
 

### 2016-06-17 Paper/Draft.tex
Added examples to current alignment strategies

@@
 
+ \subsubsection{Example}
+ An example of an ontology or a knowledge base of mice and men would be the following:
+ A mouse consists of the following body parts:
+ \begin{itemize}
+ \item Head
+ \item Torso
+ \item Whiskers
+ \item Tail
+ \item Front paws
+ \item Hind paws
+ \end{itemize}
+
+ They are connected as follows: IMAGE
+
+ Humans consist of:
+ \begin{itemize}
+ \item Head
+ \item Torso
+ \item Moustache
+ \item Arms
+ \item Legs
+ \end{itemize}
+
+ Humans and mice are connected as follows: MATCHING IMAGE
+
  \subsubsection{OWL}
@@
 %TODO consider SKOS
+
+ A relationship in OWL is written as follows:
+
+ \lstset{language=XML}
+ \begin{lstlisting}
+ <owl:Class rdf:about="http://mouse.owl#Whiskers">
+   <rdfs:connectedTo rdf:resource="http://mouse.owl#Head"/>
+ </owl:Class>
+ \end{lstlisting}
+
  \subsubsection{SPARQL}
- SPARQL is the query language for knowledge bases and ontologies. It allows a user to select nodes whose context match the query, similar to how rows are selected in SQL based on the row contents.
+ SPARQL is the query language for knowledge bases and ontologies. It allows a user to select nodes whose context match the query, similar to how SQL selects rows whose content match the query.
  \subsubsection{Uses of Ontologies}
@@
 the number of edges between the concepts and their least general common superconcept\cite{lin2008}.
+ For example, the distance between moustache and whiskers is 3, since their least general common superconcept is hair the distance between moustache and hair is 2 (with facial hair between them) and the distance between whisker and hair is 1 (direct).
  Edit distance is a purely string-based similarity measure.
@@
 Similar methods include substring matching and n-gram matching, which compare parts of the strings to find similarities\cite{singh2014, levenshtein}.
+ For example, arm and front paw have an edit distance of 8, since they have 1 character in sequence in common (either the a or the r) and thus 8 characters that are different.
  \subsection{Problems in ontology alignment}
@@
 
+ \lstset{language=Java}
  \begin{lstlisting}

### 2016-06-17 Paper/Draft.tex
Added full running example to paper

@@
 
- \subsubsection{Example}
+ \subsubsection{Example} \label{example}
  An example of an ontology or a knowledge base of mice and men would be the following:
@@
 
- How should the wildly differing demands the applications place on the ontology matching systems be satisfied by a single of a few systems?
+ How should the wildly differing demands the applications place on the ontology matching systems be satisfied by a single or just a few systems?
 When merging ontologies on one end of the Aristotle-Plato spectrum, often a completely different approach is required than an ontology on the other side.
@@
 This way, all improvements are recorded precisely.
+ The explanations refer back to the example in Section \ref{example}
   \subsubsection{Node vectorisation}
@@
 It may even be competitive with more advanced string matchers (that look at substrings of labels).
-For example, \emph{ear lobe} and \emph{ear} will be matched by a substring matcher, but are also semantically similar since they will often be mentioned in the same context.
+For example, \emph{whisker} and \emph{moustache} will be matched by a substring matcher, but are also semantically similar since they will often be mentioned in the same context.
   \subsubsection{Combine with neighbours}
@@
 These possibilities were also investigated.
+  For example, since the \emph{front paws} and \emph{arms} are both attached to the \emph{torso}, their context vectors will be similar as well.
   \subsubsection{Select from senses}
   Another way to take into account the influence of neighbouring nodes is to train a multi-sense node embedding model as described in {appropriate section}, and selecting from the different node senses based on which is closest to the context average.
+%TODO appropriate section
   \subsubsection{Adding edge labels}
@@
 A different possible problem with this method is that the relation between a neighbour node and its corresponding edge may be lost, since they are just treated as independent contexts.
+  In the case of the mouse Ontology, the \emph{head} is above the \emph{torso} so \emph{isAbove} will be added to the context of \emph{head}.
+The same goes for the \emph{human head}, which will make them more similar.
   \subsubsection{Select from senses}
@@
   As can be read in {appropriate section}, it is possible to drop the bag-of-words assumption that the context is sequence invariant.
-  % maybe ref too\endcomment
+  %TODO appropriate section
+  %TODO maybe ref too\endcomment
   This means we can for example have the context be (previous word, next word) and those words will be treated differently.
@@
 This ensures that the model will find any relationship between the edge and the node if it exists and will take this into account.
-For example, the system might use just the information 'isMarriedTo' to infer that someone is a human, but may infer that 'isMarriedTo' in combination with a man usually refers to a woman.
-  %  Ja doe maar een ander voorbeeld ivm gelijkheid e.d.
+For example, \emph{isBelow} and \emph{torso} will combine into a vector that is similar to \emph{tail} whereas \emph{isAbove} and \emph{torso} combine into a vector that is similar to \emph{head} since the edge and node labels are combined in the model, rather than considered separately.
   \subsubsection{Hot start}
@@
 However, it is also not structural, as it can work without a seed alignment and uses information other than the structure as well.
-It is not logical
-  %  Goeie woord?
-  since it does not use inference.
+It is not semantic (or logical) since it does not use inference.
 Nor is it terminological, which looks at dictionaries or other ontologies to find matches.
-However, it does use other ontologies (or text corpora) implicitly, so if it must be grouped it would be terminological.
+However, it can use dictionaries and other ontologies to improve performance.
   % Moet voorafgaand stukje op een andere plek?
@@
 However, if we compare the cold and hot algorithms with the generic string matchers, we may be able to compare them indirectly.
+  An example of a hot start is that \emph{mouse torso} is already matched with \emph{human torso}.
+Then it is likely that their neighbours are also related.
+Since the \emph{front paws} and \emph{arms} are next to the \emph{torso}, they are more likely to be matched now.
+In the case of \textbf{Node2vec} they are more likely to be matched, since their neighbourhoods are the same (the only neighbour of both \emph{arms} and \emph{paws} is \emph{connectedTo torso}).
  \subsubsection{Training corpus}
@@
 Since the ontologies themselves do not necessarily contain enough examples to embed the concepts properly, I need to use ontologies that are likely to contain the concepts I want to align.
+In the case of the mice and men ontologies, anatomical or medical ontologies can be useful, since they may list more anatomical relationships or common relationships (for example \emph{whisker} and \emph{moustache} are related to \emph{hair}).
   As a benchmark, I will use the WordNet and NELL ontologies.
@@
  \subsection{Implementation}
- The two foundations the algorithm has been build and tested on are Factorie, described in \ref{factorie}, and AgreementMaker, described in \ref{agreementmaker}, respectively.
+ The foundation the algorithm has been build and tested on is Factorie, described in \ref{factorie}.
 Earlier work on a forked branch of factorie was done by \cite{multisensecode} to implement multi-sense \textbf{Word2vec}.

### 2016-06-21 Paper/Draft.tex
Added results and interpretation

@@
  \usepackage{listings}
+ \usepackage{amsmath}
+ \usepackage{graphicx}
+ \usepackage{float}
+ \usepackage{caption}
 
@@
  \subsection{Overview}
- This thesis is structured as follows...
+ This thesis is structured as follows: firstly, I will describe the context of the problem, which includes the Semantic Web, Ontologies, Ontology matching and other relevant research.
+Secondly, I will outline the problem and research questions.
+Thirdly, I will describe the method I used to develop the solution, which includes the idea, challenges and considered implementations.
+The fourth section after this describes methods I used to evaluate the solution, with the fifth section showing the results, the sixth section the conclusions and the last and seventh section the discussion.
 
@@
 
- The linking of every piece of content to another allows not only humans to browse the internet, but also virtual agents, which can use this information to aid their users in ways that are simply impossible nowadays.
+ Linking every piece of content to another allows not only humans to browse the internet, but also virtual agents, which can use this information to aid their users in ways that are simply impossible nowadays.
 If someone wants to find information on a certain topic, the agent can collect all documents that are relevant to that topic, summarize each document in a way that is relevant to the search request and provide sources for every fact it finds.
@@
 
- The Semantic Web has a current state, the technologies that have been developed, which will be discussed later. But more importantly it is an idea
+ The Semantic Web has a current state, the technologies that have been developed, which will be discussed later. But more importantly the Semantic Web is a
 
@@
 KBs and Ontologies are often confused, and are indeed very similar in structure.
-The Knowledge Base in our example can contain actually existing birds or fictional birds, and refers to the Ontology concept of bird to embed the instantiations with meaning.
+The Knowledge Base in our example can contain actually existing birds or fictional birds, and refers to the Ontology concept of bird to embed the instantiations with meaning\cite{ontologyGuru}.
 
@@
 
- \subsubsection{SPARQL}
- SPARQL is the query language for knowledge bases and ontologies. It allows a user to select nodes whose context match the query, similar to how SQL selects rows whose content match the query.
  \subsubsection{Uses of Ontologies}
@@
 However, ontology and knowledge base merging is not a trivial problem and actually the problem that this thesis addresses.
-Therefore it will be explained more in-depth later on.
-%TODO add \ref
+Therefore it will be explained more in-depth later on\cite{09ontology}.
  \subsubsection{Aristotle and Plato}
@@
  On the other end of the spectrum are the Aristotelian ontologies, which do not necessarily contain perfectly defined concepts, but rather concepts as we observe them.
-Aristotle disagreed with Plato's theory that concepts are existing things, and thus these ontologies are named after him.
-%TODO cite
+Aristotle disagreed with Plato's theory that concepts are existing things, and thus these ontologies are named after him\cite{aristotleplato}.
 
@@
 The disadvantage is that creating such an ontology is much more costly than an Aristotelian ontology, since every concept and constraint needs to be correct in all cases.
-%TODO cite Lakoff
 
@@
 Aristotelian ontologies are more common on the Semantic Web, where massive amounts of data need to be represented and queried.
+
  \subsection{Current alignment strategies} \label{strategies}
@@
 These steps are called the terminological and the structural steps.
-Some strategies also use extra steps like the extensional and semantic steps, which use vector space models and inference, respectively.
-%TODO cite https://hal.inria.fr/hal-00917910/document
+Some strategies also use extra steps like the extensional and semantic steps, which use vector space models and inference, respectively\cite{matchingchallenges}.
 
@@
 
- \subsection{Word sense representation} \label{w2v}
+ \subsection{Word representation} \label{w2v}
+ An important area of research in Natural Language Process is the representation of words.
+The most obvious representation is the collection of characters humans are used to.
+However, this is not useful for computers as these characters do not say anything about the meaning of the words, nor is it a representation that computers can quickly do calculations on.
+
+ Many different representations have been proposed.
+The main purpose of word representations in NLP is to represent the meaning of the word.
+One way to represent a word is the term frequency.
+This representation counts the number of occurrences of a word per document in a set of documents.
+The resulting vector of occurrence counts is then used to represent the words.
+Since the documents have a subject, there is some meaning embedded in the vector representation.
+However, the representation is very sparse and the semantics or meaning of the word are not captured very well.
+Also, the method requires many discrete documents to train on, which are not available in Ontology matching.
+
+ The rest of this subsection will describe the latest word representation model which has very interesting results in NLP.
+It will cover the history and the most recent advances that are relevant to this study.
+
  \subsubsection{Skip-gram models}
- Skip-gram models have been widely used to represent words as vectors.
-This is useful as it is easy to calculate the distance between two vectors, which is a useful property for ontology matching.
-This vector distance has been shown to be related to the semantic similarity between words, which is very useful for ontology alignment, as parts of one ontology have to be aligned with parts of another ontology depending on their semantic relation.
+ Skip-gram models have been in use for some time.
+Like the document frequency representation, it represents words as vectors.
+However, the vectors are much more dense and can be trained on sentences rather than documents.
+The vector distance of skip-gram models has been shown to be related to the semantic similarity between words.
+This semantic similarity property is very useful for ontology alignment, as parts of one ontology have to be aligned with parts of another ontology depending on their semantic relation.
+
+ Skip-gram models work by teaching a 3-layer neural network to predict the context of a word.
+In NLP the context is a number of words before and after the word.
+Firstly, all words a represented by 1-hot encoding, which is a vector with all zeroes and a single one on the index of the word.
+This vector has length $V$ equal to the number of words in the corpus.
+This vector represents the first layer, the input layer of the neural network.
+The second layer, the hidden layer is obtained by multiplying the first weight matrix with the first layer.
+Since the first layer is one-hot encoded, this is equal to the row of the matrix corresponding to the index of the word.
+This representation will later be used as the representation of the word.
+
+ Then the representation is multiplied with another matrix to create the third layer, the output layer.
+The word representations and second matrix are optimized in such a way that the output layer is as close as possible to the one-hot encodings of the context.
+
+ As a consequence words that occur in similar contexts will be represented similarly.
+This again causes contexts that contain similarly represented words to also become more similar.
+This positive feedback loop causes co-occurring words to be represented more and more similarly.
+On convergence, words with similar meanings are represented similarly.
 
@@
  Recently, an effective and efficient skip-gram model has been developed, called \textbf{Word2vec}, which uses a number of extensions over previous methods that enable it to efficiently learn an effective representation\cite{w2v}.
- \textbf{Word2vec} learns this representation by trying to predict the context of a word.
-First the vocabulary is one-hot encoded.
-Then the model learns to predict a context vector that minimizes the distance to the context one-hot encoded vectors.
-The model is a neural network with one hidden layer.
-Since the input is one-hot encoded, every word in the vocabulary is represented by one row in the weight matrix between the input layer and hidden layer.
-This row is the vector representation of the word.
+One example of such an extension is negative sampling, which is a step that teaches the network that randomly selected words should have non-similar representations.
 
- \subsubsection{Extensions}
+ These extensions enable \textbf{Word2vec} to be trained on large corpora and represent words in a way that is very useful in NLP.
+It is used as a language model in part-of-speech tagging and machine translation.
+
+ Interestingly, the representations have been shown to contain semantic information too.
+A common example is the following formula: $vec("\text{queen}") = vec("king") - vec("man") + vec("woman")$.
+This means that gender is encoded in the vectors and other types of meaning may also be encoded.
+
+ After the authors showed the usefulness of \textbf{Word2vec}, many researchers developed new uses for the algorithm.
+Some extensions that are relevant to this study will be discussed.
+Firstly, I will describe a model that represents syntax as opposed to semantics.
+Secondly, I will describe a model that is capable of representing multiple meanings per words.
+
+ \subsubsection{Word order}
  \textbf{Word2vec} has been expanded in a number of different ways.
-For example, word order can be preserved, leading to a similarity measure that is closer to syntax, as syntax defines which words go where in a sentence.
-This preservation was done by having multiple output layers, one for every word in the context.
-The research shows that the input does not have to be a bag-of-words representation, which will be useful later on\cite{ling2015}.
+For example, word order can be preserved, leading to a similarity measure that is closer to syntax, as syntax defines positional properties of words within a sentence\cite{ling2015}.
+To enable this alternative representation, the model had to be changed structurally.
+Rather than a single output layer generated by a single matrix, one layer per word in the context was used.
+As such, the model learns to predict the context words based on their position relative to the source word.
+More important than the fact that these models can be used for syntax is the fact that the research shows that the input does not have to be a continuous bag-of-words representation.
+This sparked the idea that it may also be possible to have a graph as the input to the network.
+This assumption is the basis of this study and will be tested thoroughly.
+
+ \subsubsection{Multi-sense}
  Another interesting development is the multi-sense \textbf{Word2vec}, which allows for multiple vector representations per word, depending on the number of different definitions a word has.
@@
 It can differentiate between two different meanings based on the context.
-This will help with resolving ambiguity, a very important factor in ontology alignment\cite{multisense}.
+The importance of allowing for multiple meanings is that between multiple ontologies, the same word can have different meanings and as such should not be matched.
+On the other hand, a concept in a single ontology can have multiple meanings and should therefore be matched with more than one concept from another ontology\cite{multisense}.
+This idea sparked the second reason why I started investigating semantic word representations for Ontology matching, since current methods do not allow for disambiguation.
+
+ For example, string matchers only look at the phrases representing the concepts, and as such do not care about semantics.
+Structural matchers use the context, but do not use the meaning of the concept since they only look at the location of the concept within the graph.
+Lastly, lexical matchers do use synonyms and antonyms to see which different words could refer to the same concept, but if two concepts can be represented by one word.
+As such, initially the multi-sense representation seemed like a very strong candidate for improving matching results.
 
@@
  \section{Method}
- This Section will describe the method that I developed.
-Firstly, I will describe the general idea.
-In the second section, I will give a theoretical justification for why this method should work and how it works conceptually.
-After that I will describe the different ways that the input graphs can be used to train the \textbf{Word2vec} model and create the alignment, some of which I have discarded on theoretical grounds as I will explain in the relevant section.
-Lastly, I will talk about the implementation process.
 
- \section{Idea}
+ \subsection{Idea}
 The goal of any ontology matcher is to find an alignment between two ontologies that is as similar as possible to the true alignment.
@@
 It can be extended with multi-sense embeddings, different ways of considering the neighbourhood and hot-starting.
-%TODO this paragraph needs to be explained
+
  \subsection{Considered implementations}
@@
 It also allows for weighting of edges to change the sampling rate of the random walk, which can be used to prioritize important nodes or highlight informative neighbours.
- \subsection{Discarded implementations} %TODO consider adding to future
-  \subsubsection{Training on text}
-  Rather than training on ontologies, it would be possible to train the model on text.
-Since there is more text available than ontologies when counting the number of training samples, it would make sense to use a purely text-trained model.
-However, this method has downsides which made me decide not to use it.
-Namely, the context of a word in a text corpus is very different from a node in an ontology.
-A word is surrounded by the words directly around it, or the sentence it is in, or the paragraph or entire document.
-However all these contexts are just words, usually represented as a bag of words to ensure enough data for the model.
-In an ontology, the context is a combination of a node with an edge, which have a very different relation than merely co-occurring.
-The relation may be inferred from one sentence, or many different documents.
-  % Herschrijf dit aub want het is niet goed
-  \subsubsection{Just context nodes}
-
-  \subsubsection{Just edges}
-
-  \subsubsection{Context matrix representation}
 
@@
  A reference alignment can be made by experts or be created by bipartitioning an existing ontology. %expand this.
- \subsubsection{Parts of OWL ignored}
+ %\subsubsection{Parts of OWL ignored}
 
@@
  \section{Results} \label{results}
+
+ In this section I will show the objective results of the study.
+Firstly, I will show the precision-recall trade-off curve of all algorithms.
+Then I will go into detail of the results of the most promising algorithm.
+
+ \subsection{Precision versus recall}
+  \subsubsection{Mice and men data}
+  \begin{figure}[H]
+   \centering
+   \includegraphics[width=\textwidth]{plots/untrained_ROC}
+   \caption{The precision and recall trade-off for the results of the untrained Node2vec. $AP = 0.04194$}
+   \label{ROC_trained}
+  \end{figure}
+
+  \begin{figure}[H]
+   \centering
+   \includegraphics[width=\textwidth]{plots/Generic_ROC}
+   \caption{The precision and recall trade-off for the results of the Word2vec algorithm. $AP: 0.04636$}
+   \label{ROC_trained}
+  \end{figure}
+
+  \begin{figure}[H]
+   \centering
+   \includegraphics[width=\textwidth]{plots/trained_ROC}
+   \caption{The precision and recall trade-off for the results of the bidirectional Node2vec. $AP = 0.04198$}
+   \label{ROC_trained}
+  \end{figure}
+
+  \begin{figure}[H]
+   \centering
+   \includegraphics[width=\textwidth]{plots/Alternative_ROC}
+   \caption{The precision and recall trade-off for the results of the alternative DeepWalk algorithm. $AP = 0.04193$}
+   \label{ROC_trained}
+  \end{figure}
+   \subsubsection{Medical data}
+   TBD
+
+ \newpage
+ \section{Interpretation}
+  The system underperforms on the provided data. This can have one or more of the following four causes:
+  \begin{itemize}
+  \item The data breaks the considered algorithms.
+  \item There are bugs in the developed system unrelated to the algorithms.
+  \item The considered context extraction does not work.
+  \item The considered algorithms are not suited for Ontology matching.
+  \end{itemize}
+
+  \subsection{The data}
+  If the data set is the cause of the underperformance, logically switching to another data set will improve performance over the baseline.
+Possible reasons the data set causes underperformance include a too small data set or a data set having a structure that does not work with the algorithm.
+
+  The algorithm has been run on multiple data sets with no significant difference in performance, therefore the data is not the cause of the underperformance.
+  \subsection{The system}
+  If any of the steps in the software system contains an error, the whole system may fail.
+This could cause all algorithms to learn badly or the results to be misinterpreted.
+The system consists of a data loader, preprocessor, context extractor, the algorithm, the matcher and multiple visualizers.
+
+  All other steps I have replaced by another piece of software that does the preprocessing, context extraction and the algorithm.
+The results are titled "alternative DeepWalk" in the results Section.
+Since that software has been used in other projects and is written by someone else, it can be concluded that it works.
+Since the results are the same as with my system, it can be concluded that the corresponding parts of my system work.
+
+  The preprocessing works, as described in Section \ref{preprocessing}.
+The matcher is a simple KD-tree that finds the nearest neighbours of every node in the opposing Ontology.
+This is unlikely to contain errors.
+
+  Since the visualizers work in parallel, errors in them would not cascade to the others, so they are all faulty or none of them are.
+
+  As such, it is safe to conclude that the system has been thoroughly tested and is not faulty.
+  \subsection{Context extraction}
+  The context extraction works, as described in Section \ref{sentences}.
+  \subsection{The algorithm}
+  Since we have excluded all other possibilities, we can conclude that the remaining possibility, that the set of algorithms do not work well on Ontology data.
 
@@
  \subsection{Future research}
+ \subsection{Discarded implementations} %TODO consider adding to future
+
+  \subsubsection{Just context nodes} % In future?
+
+  \subsubsection{Just edges}
+
+  \subsubsection{Context matrix representation}
 

### 2016-06-22 Paper/Draft.tex
Shuffled sections around

@@
  %TODO Word index
+ %TODO List of tables
+ %TODO List of figures
  \tableofcontents
@@
 
+%TODO \section{Motivation}
+
  \pagenumbering{arabic}
- \section{Introduction} \label{intro}
+ \section{Introduction}
  It is a Friday afternoon and you realise you want to watch a movie with some friends this weekend. So, what do you do? To achieve this goal you must take four steps.
@@
 Many open databases already contain a lot of structured data that can be used to reason about data.
-And algorithms to combine these piece of information to make decisions already exist and work.
+And algorithms to combine these pieces of information to make decisions already exist and work.
 
@@
 
- \subsection{Short Context}
+ \subsection{Motivation} %TODO aanleiding?
+ In \cite{mccallumweblecture}, McCallum talks about Universal schema.
+This system learns embeddings of entities and relations found in text and Knowledge Bases.
+These embeddings are then used to predict new relations for the knowledge bases.
+The system find embeddings such that the embeddings of entities and relations that co-occur are highly similar.
+If some entities and relations have similar embeddings but are not known to co-occur, they are flagged as being similar.
+Similarly, if two entities or two relations have similar embeddings, they are likely referring to the same thing.
+This can be used to infer even more similarities by collaborative filtering.
+The technique had very promising results in Knowledge Base completion tasks.
+
+ The embeddings are optimized by a model called the skip-gram word embedding model.
+It is a neural network model that learns to predict the context of a word (in this case the context of an entity is the relations it is co-occurs with and vice versa).
+McCallum talked about a new extension to the algorithm that allowed for homonyms and as such can deal with more ambiguous data\cite{mccallumweblecture}.
+
+ If these embeddings can be used to predict new inter-knowledge base relations, it should also be possible to predict new intra-knowledge base relations.
+If these relations can be predicted, it is possible to use multiple knowledge bases together.
+Predicting these relations is called alignment.
+
+ Currently, knowledge base and ontology alignment techniques do not make use of embeddings.
+Since embedding models have good performance on intra-knowledge base relation prediction, they should also work on ontology alignment.
+
+ \subsection{Context}
  In this section, I will give a short summary of the context for the problem.
@@
 
- \subsection{Overview}
+ \subsection{Justification} %relocate?
+ On the Semantic Web, many relatively small knowledge bases will be combined temporarily so that it is possible to reason over the combined knowledge of those knowledge bases.
+To combine these knowledge bases, their ontologies first need to be aligned.
+This is an act that will happen very often on the Semantic Web, since every interaction with the Semantic Web will usually require information from multiple domains.
+Large domains may be stored over multiple devices, which can be viewed as different knowledge bases which also need to be aligned.
+Therefore, it is save to say that efficient ontology matching will be very valuable.
+
+ Since most of the knowledge on the Semantic Web is automatically gathered, it may be unreliable and even wrong.
+Therefore, ontology matching that is capable of handling this uncertain knowledge is required.
+Word Embeddings and especially multi-sense Word Embeddings should be able to handle a high amount of uncertainty.
+
+ Calculating the distance between vectors can be done very efficiently, therefore ontology matching with distributed concept representations fits that efficiency criteria.
+Since these representations can use the context of a concept, they are also most robust than methods that do not take the context into account.
+
+ Since distributed representation algorithms can be trained unsupervised on new domains, they can be applied to those new domains without effort from humans, as opposed to for example the string edit distance.
+This is also an improvement for the semantic web.
+
+ Also, ontology matching is already used outside of the semantic web.
+It is currently in use for companies that want to merge knowledge from other companies, for example.
+If the proposed matching algorithm is better than the current algorithms, or at least improves the performance when used in ensemble with the current algorithms, it will be useful immediately in these situations, not just in the future, on the Semantic Web.
+
+ \subsection{Problem}
+ We have seen that when information from multiple domains needs to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged.
+% Waar?
+  Those ontologies contain rules about concepts and concept classes in the shape of triplets, with two concepts and a relation.
+For example, the rule {\tt Professors are humans} contains the concepts \emph{Professor} and \emph{human} and an \emph{is-a}-relationship.
+
+ If we want to merge two ontologies, we need to find the concepts from the different ontologies that are related by an 'is-same-as' or other rule.
+
+ However, since the ontologies are made for different domains, the same concept can be represented by different labels in the two ontologies.
+This problem is called the synonymy problem, as synonyms are two words that refer to the same concepts.
+
+ The opposite problem is called the homonymy problem, in which two concepts are represented by the same label.
+Since they have the same label, naive algorithms might align the concepts as being the same, when they are not.
+
+ Then there is the problem of ambiguity, which encompasses many other problems.
+It encompasses the fact that some concepts are used wrongly by humans, but also the fact that some concepts are extremely similar, and may occur in the same context, but are still slightly different.
+
+ Lastly, there is the problem of different types of alignment relations.
+For example, one concept can be a \emph{part of} another concept, or an example of one.
+These different relations all require a different approach and come with their own sets of problems.
+%Meronymy?
+
+ In summary, ontology aligning is required for multi-domain communication but poses a number of problems that make it difficult for concepts, the building blocks of ontologies, to be matched.
+
+ \subsection{Overview} %TODO rewrite
  This thesis is structured as follows: firstly, I will describe the context of the problem, which includes the Semantic Web, Ontologies, Ontology matching and other relevant research.
@@
 
+ \subsection{Research questions}
+ The main question that I will answer with this work is the following research question:
+
+ \begin{center}
+ \textit{
+ Can distributed representations of concepts be used to find relationships between concepts in ontologies better than existing terminological matchers?
+ }
+ \end{center}
+ % Alternatively, do my matcher add anything? i.e. does adding it to an ensemble of existing matchers increase performance?
+
+ I will also investigate the following two related but different questions:
+
+ \begin{center}
+ \textit{
+ Can distributed representations use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers?
+ }
+ \end{center}
+
+ \begin{center}
+ \textit{
+ Can distributed representations perform well in a domain it was not trained for?
+ }
+ \end{center}
+
+ \subsection{Hypothesis}
+ \begin{center}
+ \textit{This specific matcher that uses a distributed representation of concepts can find relationships between concepts in ontologies better than the best existing matchers.}
+ \end{center}
+
+ To prove this hypothesis, I must proof the following points:
+ \begin{itemize}
+ \item The algorithm uses distributed representations of concepts.
+ \item The algorithm finds relationships between concepts in ontologies.
+ \item The algorithm has been compared to the currently best matchers.
+ \item The algorithm performs better.
+ \end{itemize}
+
+ The first three points will be shown in Section \ref{proofs}, whereas the last point is evaluated in Section \ref{conclusions}.
+
+ This hypothesis are true for distributed representations matcher if they are true for one distributed representation matcher.
+Therefore to test the hypotheses, I must test them for every distinct implementation of the matcher.
+
 \newpage
-\section{Context}
+\section{Theory}
  In this section I will discuss all concepts that are required to understand the study.
@@
   The first concept is the Semantic Web, also called Web 3.0, a vision of a Web that enhances the User Experience in ways that the current Web can not provide. 
+ \subsubsection{The current Web}
 Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and limited interconnectivity.\footnote{For example, Facebook is a hub for sharing content with people you consider friends, but if you want to share that content with more people you will have to go to another hub, like imgur or Pinterest.} It is possible to link to content from other hubs using URLs, but this moves the user to another hub, rather than connecting the content present in the hubs.
@@
  \subsubsection{Uses of Ontologies}
- %Beschrijf bottom-up ontologie maken.
  There are three main reasons Ontologies are used.
@@
 These steps are called the terminological and the structural steps.
-Some strategies also use extra steps like the extensional and semantic steps, which use vector space models and inference, respectively\cite{matchingchallenges}.
+Some strategies also use extra steps like the extensional and semantic steps, which use vector space models and inference, respectively\cite{future}.
 
@@
  Factorie is written in scala, a relatively new language that interfaces with java.
-See \ref{scala}.
+See \cite{scala}.
 This allows for interoperability between factorie and AgreementMaker.
@@
  \newpage
- \section{Problem}
-
- \subsection{Problem}
- We have seen that when information from multiple domains needs to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged.
-% Waar?
-  Those ontologies contain rules about concepts and concept classes in the shape of triplets, with two concepts and a relation.
-For example, the rule {\tt Professors are humans} contains the concepts \emph{Professor} and \emph{human} and an \emph{is-a}-relationship.
-
- If we want to merge two ontologies, we need to find the concepts from the different ontologies that are related by an 'is-same-as' or other rule.
-
- However, since the ontologies are made for different domains, the same concept can be represented by different labels in the two ontologies.
-This problem is called the synonymy problem, as synonyms are two words that refer to the same concepts.
-
- The opposite problem is called the homonymy problem, in which two concepts are represented by the same label.
-Since they have the same label, naive algorithms might align the concepts as being the same, when they are not.
-
- Then there is the problem of ambiguity, which encompasses many other problems.
-It encompasses the fact that some concepts are used wrongly by humans, but also the fact that some concepts are extremely similar, and may occur in the same context, but are still slightly different.
-
- Lastly, there is the problem of different types of alignment relations.
-For example, one concept can be a \emph{part of} another concept, or an example of one.
-These different relations all require a different approach and come with their own sets of problems.
-%Meronymy?
-
- In summary, ontology aligning is required for multi-domain communication but poses a number of problems that make it difficult for concepts, the building blocks of ontologies, to be matched.
- \subsection{Research questions}
- The main question that I will answer with this work is the following research question:
-
- \begin{center}
- \textit{
- Can distributed representations of concepts be used to find relationships between concepts in ontologies better than existing terminological matchers?
- }
- \end{center}
- % Alternatively, do my matcher add anything? i.e. does adding it to an ensemble of existing matchers increase performance?
-
- I will also investigate the following two related but different questions:
-
- \begin{center}
- \textit{
- Can distributed representations use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers?
- }
- \end{center}
-
- \begin{center}
- \textit{
- Can distributed representations perform well in a domain it was not trained for?
- }
- \end{center}
-
- \subsection{Hypotheses} 
- \begin{center}
- \textit{This specific matcher that uses a distributed representation of concepts can find relationships between concepts in ontologies better than existing terminological matchers.}
- \end{center}
-
- To prove this hypothesis, I must proof the following points:
- \begin{itemize}
- \item The algorithm uses distributed representations of concepts.
- \item The algorithm finds relationships between concepts in ontologies.
- \item The algorithm has been compared to the currently best matchers.
- \item The algorithm performs better.
- \end{itemize}
-
- The first three points will be shown in \ref{proofs}, whereas the last point is shown in \ref{conclusions}.
-
- \begin{center} 
- \textit{The distributed representations matcher can use the context of a concept to find relationships between concepts in ontologies better than existing terminological and structural matchers.}
- \end{center}
- \begin{center}
- \textit{The distributed representations matcher can perform well in a domain it was not trained for.}
- \end{center}
-
- These hypotheses are true for distributed representations matcher if they are true for one distributed representation matcher.
-Therefore to test the hypotheses, I must test them for every distinct implementation of the matcher.
-
- \subsection{Justification}
- On the Semantic Web, many relatively small knowledge bases will be combined temporarily so that it is possible to reason over the combined knowledge of those knowledge bases.
-To combine these knowledge bases, their ontologies first need to be aligned.
-This is an act that will happen very often on the Semantic Web, since every interaction with the Semantic Web will usually require information from multiple domains.
-Large domains may be stored over multiple devices, which can be viewed as different knowledge bases which also need to be aligned.
-Therefore, it is save to say that efficient ontology matching will be very valuable.
-
- Since most of the Semantic Web will consist of Aristotelian ontologies, some of the information it contains can be unreliable and even wrong.
-Therefore, ontology matching that is capable of handling this uncertain data is required.
-
- Calculating the distance between vectors can be done very efficiently, therefore ontology matching with distributed concept representations fits that efficiency criteria.
-Since these representations can use the context of a concept, they are also most robust than methods that do not take the context into account.
-
- Since distributed representation algorithms can be trained unsupervised on new domains, they can be applied to those new domains without effort from humans, as opposed to for example the string edit distance.
-This is also an improvement for the semantic web.
-
- However, ontology matching is also used outside of the semantic web.
-It is already in use for companies that want to merge knowledge from other companies, for example.
-If the proposed matching algorithm is better than the current algorithms, or at least improves the performance when used in ensemble with the current algorithms, it will be useful in these situations, not just on the Semantic Web.
-
- \newpage
- \section{Method}
+ \section{Method} %Controleer overgang
+ %hier iets opschrijven?
 
@@
  \newpage
- \section{Evaluation}
+ \subsection{Evaluation}
  %https://hal.inria.fr/hal-00917910/document
@@
 So, instead we may want to see if performance is improved when adding $A$ to an ensemble of algorithms $E=(A_1,..,A_n)$.
- \subsection{Evaluation methods} \label{Evaluation methods}
+ \subsubsection{Evaluation methods} \label{Evaluation methods}
  The evaluation should be done using a performance measure $P(Al,T)$ that takes the alignment an algorithm produces given an ontology and the ground truth.
@@
 To make the results of this study easily comparable to others, equal weights will be used.
- \subsection{Data}
+ \subsubsection{Data}
  The data used comes from a list of data sets that the OAEI provides. % Zoek paper, misschien http://www.sciencedirect.com/science/article/pii/S1570826813000188
@@
    \caption{The precision and recall trade-off for the results of the untrained Node2vec. $AP = 0.04194$}
-   \label{ROC_trained}
+   \label{ROC_untrained}
   \end{figure}
@@
    \caption{The precision and recall trade-off for the results of the Word2vec algorithm. $AP: 0.04636$}
-   \label{ROC_trained}
+   \label{ROC_generic}
   \end{figure}
@@
    \caption{The precision and recall trade-off for the results of the alternative DeepWalk algorithm. $AP = 0.04193$}
-   \label{ROC_trained}
+   \label{ROC_alternative}
   \end{figure}
@@
 
+  \subsection{F-score}
+  \begin{tabular}{l|l}
+  \textbf{Matcher} & \textbf{$F_1$-score}\\
+  \hline
+  Alternative & 0.4244\\
+  Bidirectional & 0.4245\\
+  Untrained & 0.4245\\
+  Generic & 0.4245\\
+  \textbf{AML} & \textbf{0.94}\\ %http://disi.unitn.it/~pavel/om2015/papers/om2015_proceedings.pdf#page=125
+  \end{tabular}
+  \subsection{Jaccard}
+  TBD
+  \subsection{Examples to illustrate the differences}
+  TBD
+
  \newpage
- \section{Interpretation}
+ \subsection{Interpretation}
+ \subsubsection{Unexpected results}
+ \subsubsection{Expected results}
+
+ \newpage
+ \section{Conclusion and discussion}
+ %\subsection{Recap research questions} % Maak 'figure' van
+ %\subsection{Recap hypotheses}
+ \subsection{Conclusions}
+ From the results and interpretation we can conclude that distributed word representations can currently \textbf{not} find relationships between concepts in ontologies better than existing matchers.
+
+ \subsection{Discussion}
   The system underperforms on the provided data. This can have one or more of the following four causes:
@@
 
-  \subsection{The data}
+  \subsubsection{The data}
   If the data set is the cause of the underperformance, logically switching to another data set will improve performance over the baseline.
@@
   The algorithm has been run on multiple data sets with no significant difference in performance, therefore the data is not the cause of the underperformance.
-  \subsection{The system}
+  \subsubsection{The system}
   If any of the steps in the software system contains an error, the whole system may fail.
@@
   As such, it is safe to conclude that the system has been thoroughly tested and is not faulty.
-  \subsection{Context extraction}
-  The context extraction works, as described in Section \ref{sentences}.
-  \subsection{The algorithm}
+  \subsubsection{Context extraction}
+  The context extraction for DeepWalk works, as described in Section \ref{sentences}.
+
+  The context extraction of the pre-trained Word2vec consists of splitting up every label into multiple words which can be looked up.
+For example "Adrenal vein" can be split up into "Adrenal" and "vein".
+  The pre-trained model does not use any other form of context integration.
+
+  For the Node2vec algorithms, the context extraction is more advanced.
+All edges are extracted from the Ontology using Jena.
+Then, for every node the context is decided as every node it has an edge with.
+In the case of the bidirectional algorithm, both outgoing and ingoing edges count as being connected, whereas in the monodirectional algorithm only outgoing edges count as the connectedness.
+For the algorithms that also use the edge labels for context, double the context size is expected.
+
+  The number of edges is known as it has been provided by the designers of the Ontologies\cite{mice_ontology}, so we can compare the number of edges found with the actual number of edges.
+If these match, the context extraction works.
+  \begin{table}
+  \begin{tabular}{l|ll}
+  & \multicolumn{2}{c}{\#edges}\\
+  Algorithm & expected & actual\\
+  \hline
+  \textbf{Truth}\cite{mice_ontology} & \multicolumn{2}{c}{\textbf{1000000}} \\
+  Monodirectional & & \\
+  Bidirectional & & \\
+  Bidirectional \& edges & & \\  
+  \end{tabular}
+  \end{table}
+  Since the expected number of edges and actual number of edges match, we can conclude that the context extraction works.
+
+  \subsubsection{The algorithm}
   Since we have excluded all other possibilities, we can conclude that the remaining possibility, that the set of algorithms do not work well on Ontology data.
+ \subsection{Future research}
+ \subsection{Discarded implementations}
 
- \newpage
- \section{Conclusions}
- \subsection{Recap research questions}
- \subsection{Recap hypotheses}
- \subsection{Conclusion per hypothesis}
- \subsection{Overview of results}
- \subsection{Final conclusion}
-
- \newpage
- \section{Discussion}
- \subsection{Interpretation}
- \subsection{Unexpected results}
- \subsection{Expected results}
- \subsection{Future research}
- \subsection{Discarded implementations} %TODO consider adding to future
-
-  \subsubsection{Just context nodes} % In future?
+  \subsubsection{Just context nodes}
 
@@
   \subsubsection{Context matrix representation}
+
+ \section{List of figures and tables}
+
+ \newpage
+ \subsection{Figures}
+ \subsection{Tables}
+
+ \section{Bibliography} %Fix
 
@@
  \newpage
+ \section{Appendices}
  \begin{appendices}

### 2016-06-22 node_embedding/src/Alignment.scala
Hacked a lot to test many different models.

@@ -14,14 +14,23 @@ class Alignment {
   }
 
   def set_threshold(new_t: Double, mustbehigher: Boolean = false) = {
-    t = new_t
-    alignments.retainAll(alignments.filter(tup => (tup._3 >= t) == mustbehigher))
+    if (new_t < 1.0) {
+      t = new_t
+      alignments.retainAll(alignments.filter(tup => (tup._3 >= t) == mustbehigher))
+    } else {
+      val t_ : Int = new_t.toInt
+      if (t_ < alignments.size) {
+        val alignments_ = MinMaxPriorityQueue.orderedBy(ordering).maximumSize(t_).create[(String, String, Double)]()
+        alignments_.addAll(this.alignments.take(t_)) //.dropRight(alignments.size() - t_)
+        alignments = alignments_
+      }
+    }
   }
 
   val ordering = new Ordering[(String, String, Double)] {
     override def compare(x: (String, String, Double), y: (String, String, Double)): Int = x._3.compare(y._3)
   }
-  val alignments = MinMaxPriorityQueue.orderedBy(ordering).maximumSize(20000).create[(String, String, Double)]()
+  var alignments = MinMaxPriorityQueue.orderedBy(ordering).maximumSize(100000).create[(String, String, Double)]()
   //TODO: unhardcode maximum size
 
 

### 2016-06-22 node_embedding/src/DeepWalkNodeEmbedding.scala

@@ -3,7 +3,7 @@ import com.hp.hpl.jena.rdf.model.{RDFNode, Resource, Statement}
 
 import scala.util.Random
 import scala.collection.JavaConverters._
-import scala.collection.immutable.List
+import scala.collection.immutable.{HashMap, List}
 import scala.collection.mutable
 import scala.collection.mutable.ArrayBuffer
 
@@ -12,23 +12,31 @@ import scala.collection.mutable.ArrayBuffer
   */
 class DeepWalkNodeEmbedding extends NodeEmbeddingModel {
 
-  var it = 0
-
   val URIs = Array("http://mouse.owl#",
                    "http://human.owl#")
   val LABEL_URI = "http://www.w3.org/2000/01/rdf-schema#label"
+  val neighbours = buildNeighbours()
+
+  def buildNeighbours(): Array[Map[String, Array[String]]] = {
+    val neighbours = new Array[Map[String, Array[String]]](2)
+
+    for (curOnt <- 0 to 1) {
+      val curNeighbours = new mutable.HashMap[String, Array[String]]()
+      val onto = ontology.getOntologies(curOnt).asInstanceOf[RDFOntology]
+      val edges = onto.getEdges
+      for (edge <- edges) {
+        val nbs: Array[String] = curNeighbours.getOrElse(edge.split(" ")(0), Array())
+        curNeighbours.put(edge.split(" ")(0), nbs :+ edge.split(" ")(2))
+        val nbs_ = curNeighbours.getOrElse(edge.split(" ")(2), Array())
+        curNeighbours.put(edge.split(" ")(2), nbs_ :+ edge.split(" ")(0))
+      }
+      neighbours(curOnt) = collection.immutable.HashMap[String, Array[String]](curNeighbours.toList: _*)
+    }
+    neighbours
+  }
 
   def getNeighbours(curNode: String, curOnt: Int) : Array[String] = {
-    val onto = ontology.getOntologies(curOnt).asInstanceOf[RDFOntology]
-    val edges = onto.getEdges
-    var nbs = new mutable.ArrayBuffer[String]()
-    for (edge <- edges) {
-      if (edge.split(" ")(0) == curNode)
-        nbs += edge.split(" ")(2)
-      else if (edge.split(" ")(2) == curNode)
-        nbs += edge.split(" ")(0)
-    }
-    nbs.toArray
+    neighbours(curOnt).getOrElse(curNode, new Array[String](0))
   }
 
[…]

### 2016-06-22 node_embedding/src/Evaluator.scala

@@ -1,3 +1,6 @@
+import java.io.{File, FileReader}
+
+import breeze.io.TextWriter.FileWriter
 import com.hp.hpl.jena.rdf.model.{RDFNode, Resource, Statement}
 import smile.neighbor.KDTree
 import smile.plot.PlotCanvas
@@ -5,6 +8,7 @@ import smile.plot.PlotCanvas
 import scala.collection.JavaConverters._
 import math.sqrt
 import scala.collection.mutable
+import scala.collection.mutable.ArrayBuffer
 import scala.util.Try
 
 object Evaluator {
@@ -12,25 +16,32 @@ object Evaluator {
   val opts = WordSenseOpts
   val model = new DeepWalkNodeEmbedding() //SkipGramNodeEmbedding()
 
-  def compare(alignment: Alignment, truth: Alignment): Double = {
+  def get_compare_stats(alignment: Alignment, truth: Alignment, calc: (String, String) => Double = this.calc): (Int, Int, Int) = {
     val alignmentset = alignment.alignments.asScala.toSet[(String, String, Double)].map { case (s: String, o: String, v: Double) => (s, o) }
     val truthset = truth.alignments.asScala.toSet[(String, String, Double)].map { case (s: String, o: String, v: Any) => (s, o) }
+    val truthset_ = truthset.filterNot(t => calc(t._1, t._2) >= 100000)
     val N = alignmentset.size
-    val M = truthset.size
-
-    printf("N: %d, M: %d%n", N, M)
+    val M = truthset_.size
 
     val alignmentset_ = alignmentset.map(_.swap)
-    val count: Float = ((alignmentset union alignmentset_) intersect truthset).size
+    val count: Int = ((alignmentset union alignmentset_) intersect truthset_).size
+    (N, M, count)
+  }
+
+  def compare(alignment: Alignment, truth: Alignment): Double = {
+    val stats = get_compare_stats(alignment, truth)
+    val N = stats._1
+    val M = stats._2
+    val count = stats._3.toFloat
     println("Accuracy %f".format(count / N))
     println("Recall %f".format(count / M))
-    2f * count / (N + M)
+    2f * count/ (N + M)
   }
 
   def show_alignment(alignment: Alignment, other: Alignment) = {
     val a = alignment.alignments.asScala.toSet[(String, String, Double)]
     val a_ = other.alignments.asScala.toSet[(String, String, Double)]
[…]

### 2016-06-22 node_embedding/src/NodeEmbeddingModel.scala

@@ -21,17 +21,17 @@ abstract class NodeEmbeddingModel extends WordEmbeddingModel(WordSenseOpts) {
   protected val nIts = WordSenseOpts.nIts.value
 
   // IO Related
-  private val storeInBinary = opts.binary.value // binary=1 will make both vocab file (optional) and embeddings in .gz file
-  private val loadVocabFilename = opts.loadVocabFile.value // load the vocab file. Very useful for large corpus should you run multiple times
-  private val saveVocabFilename = opts.saveVocabFile.value // save the vocab into a file. Next time for the same corpus, load it . Saves lot of time on large corpus
-  private val encoding = opts.encoding.value // Default is ISO-8859-15. Note: Blake server follows iso-5589-1 (david's GoogleEmbeddingcode has this. shouldn;t be ISO-8859-15) or  iso-5589-15 encoding (I see this) ??
-  private val includeEdgeLabels = WordSenseOpts.includeEdgeLabels.value
+  protected val storeInBinary = opts.binary.value // binary=1 will make both vocab file (optional) and embeddings in .gz file
+  protected val loadVocabFilename = opts.loadVocabFile.value // load the vocab file. Very useful for large corpus should you run multiple times
+  protected val saveVocabFilename = opts.saveVocabFile.value // save the vocab into a file. Next time for the same corpus, load it . Saves lot of time on large corpus
+  protected val encoding = opts.encoding.value // Default is ISO-8859-15. Note: Blake server follows iso-5589-1 (david's GoogleEmbeddingcode has this. shouldn;t be ISO-8859-15) or  iso-5589-15 encoding (I see this) ??
+  protected val includeEdgeLabels = WordSenseOpts.includeEdgeLabels.value
   protected val corpusses = WordSenseOpts.corpusses.value
   protected var current_corpus = ""
 
   /**override**/ this.vocab = new MultiSynonymVocabBuilder()
   protected val ontology : SharedOntology = new SharedOntology(corpusses)
-  private var train_nodes: Long = 0
+  protected var train_nodes: Long = 0
 
   def getRootSynonym(w: String): String = {
     getRootSynonym(w, loadSynonyms())
@@ -44,7 +44,7 @@ abstract class NodeEmbeddingModel extends WordEmbeddingModel(WordSenseOpts) {
     w_
   }
 
[…]

### 2016-06-22 node_embedding/src/Normal_W2V.scala

@@ -1,0 +1,199 @@
+import java.io.{BufferedInputStream, BufferedReader, FileInputStream, InputStreamReader}
+import java.util.zip.GZIPInputStream
+
+import Evaluator.KDTree
+import cc.factorie.DenseTensor1
+import cc.factorie.app.nlp.embeddings.{TensorUtils, VocabBuilder}
+import cc.factorie.model.Weights
+import com.hp.hpl.jena.rdf.model.RDFNode
+
+import math.sqrt
+import scala.util.Try
+
+/**
+  * Created by harmen on 20-6-16.
+  */
+object Normal_W2V {
+
+  WordSenseOpts.inputFilename.setValue("Data/pretrained/glove.6B.50d.txt")
+  WordSenseOpts.binary.setValue(true)
+  val model = new NormalEmbeddingModel()
+
+  def main(args: Array[String]): Unit = {
+    model.buildVocab()
+    model.loadEmbeddings()
+    val alignment = align()
+
+    //Visualizer.hist_alignment(alignment)
+    //alignment.set_threshold(0.075)
+    val truth = Evaluator.loadTruth()
+    Visualizer.compare_hist(alignment, truth, calc)
+    val dice = Evaluator.compare(alignment, truth)
+    val synonyms = Evaluator.loadTruth(WordSenseOpts.synonyms.value)
+    val dice_ = Evaluator.compare(synonyms, truth)
+    printf("The result of what you have been working for for months: %s%n", dice)
+    printf("For reference, just the synonyms scores: %s%n", dice_)
+    //show_alignment(alignment, truth)
+    Evaluator.plot_roc(alignment, truth, this.calc)
+  }
+
+  def align(): Alignment = {
+    val o1 = model.getOntologies(0)
+    val o2 = model.getOntologies(1)
+    println("Building trees for aligning")
+    val synonyms = model.loadSynonyms()
+
+    val nodes1 = o1.getNodes.map(model.getRootSynonym(_, synonyms)).toSet[String].toArray[String] // Don't grab all synonyms too
+    val vectors1 : Array[Array[Double]] = nodes1.map(n => model.getVector(n))
+    val nv1 = vectors1.zip(nodes1).filterNot{case (v,_) => v(0).isNaN}.unzip
+
+    val nodes2 = o2.getNodes.map(model.getRootSynonym(_, synonyms)).toSet[String].toArray[String]
+    val vectors2 : Array[Array[Double]] = nodes2.map(n => model.getVector(n))
[…]

### 2016-06-22 node_embedding/src/Ontology.scala

@@ -9,9 +9,9 @@ import scala.collection.immutable.HashMap
 
 abstract class Ontology {
   val LABEL_URI = "http://www.w3.org/2000/01/rdf-schema#label"
-  val EDGE_URIS = Array("http://www.geneontology.org/formats/oboInOwl#hasRelatedSynonym",
-                        "http://www.w3.org/2000/01/rdf-schema#subClassOf",
-                        "http://www.geneontology.org/formats/oboInOwl#hasDefinition")
+  val EDGE_URIS = Array(//"http://www.geneontology.org/formats/oboInOwl#hasRelatedSynonym",
+                        "http://www.w3.org/2000/01/rdf-schema#subClassOf"
+  )// "http://www.geneontology.org/formats/oboInOwl#hasDefinition")
   val REF_URIS = Array("http://knowledgeweb.semanticweb.org/heterogeneity/alignmententity1",
                        "http://knowledgeweb.semanticweb.org/heterogeneity/alignmententity2",
                        "http://knowledgeweb.semanticweb.org/heterogeneity/alignmentmeasure")
@@ -62,21 +62,29 @@ class RDFOntology (filename: String, reference: Boolean = false) extends Ontolog
   val model : Model = FileManager.get.loadModel(filename)
 
   def getNodes: Iterator[String] = {
-    getEdges.map(_.split(" ")).flatMap[String](a => Array(a(0),a(2))).toSet.toIterator
+    val nodes = getEdges.map(_.split(" ")).flatMap[String](a => Array(a(0),a(2)))
+    if(this.reference)
+      return nodes
+    else
+      return nodes.filterNot(_.contains("blank:")).toSet.toIterator
   }
 
   def getEdges: Iterator[String] = {
     val stmtit = reference match {
       case false =>
-        model.listStatements(null, model.getProperty(EDGE_URIS(0)), null) andThen
-        model.listStatements(null, model.getProperty(EDGE_URIS(1)), null) andThen
-        model.listStatements(null, model.getProperty(EDGE_URIS(2)), null)
+ //       model.listStatements(null, model.getProperty(EDGE_URIS(0)), null) andThen
+ //       model.listStatements(null, model.getProperty(EDGE_URIS(1)), null) andThen
+        model.listStatements(null, model.getProperty(EDGE_URIS(0)), null)
       case true =>
         model.listStatements(null, model.getProperty(REF_URIS(0)), null) andThen
[…]

### 2016-06-22 node_embedding/src/SkipGramNodeEmbedding.scala

@@ -115,8 +115,6 @@ class SkipGramNodeEmbedding() extends NodeEmbeddingModel {
     vocab.getId("INV" + str)
   }
 
-  def getOntologies : Array[Ontology] = ontology.ontologies
-
 }
 
 case class SkipGramKHotSamplingExample(model: SkipGramNodeEmbedding, word: Int, context: Seq[Int], label: Int) extends Example {

### 2016-06-22 node_embedding/src/Visualizer.scala

@@ -25,7 +25,7 @@ object Visualizer {
     f.saveas("alignment_hist.pdf")
   }
 
-  def compare_hist(alignment: Alignment, truth: Alignment) = {
+  def compare_hist(alignment: Alignment, truth: Alignment, calc: (String, String) => Double = Evaluator.calc) = {
     val keys = alignment.alignments.asScala.toArray.map{case (a,b,c) => (a,b)}
     val values: Array[Double] = alignment.alignments.asScala.toArray.map(_._3).sorted
 
@@ -33,7 +33,7 @@ object Visualizer {
     val vec = DenseVector(values)
 
     val keys_ = truth.alignments.asScala.toArray.map{case (a,b,c) => (a,b)}
-    val values_ : Array[Double] = keys_.map(t => Evaluator.calc(t._1, t._2))
+    val values_ : Array[Double] = keys_.map(t => calc(t._1, t._2)).filterNot(t => t >= 100000)
     val vec_ = DenseVector(values_)
 
     val f = plot.Figure()
@@ -46,4 +46,15 @@ object Visualizer {
     f.saveas("comparative_hist.pdf")
   }
 
+  def scatter(xs: Seq[Double], ys: Seq[Double], connected: Boolean=true): Unit = {
+    val f = plot.Figure()
+    val p = f.subplot(0)
+    p += plot.plot(xs, ys)
+    p.ylabel = "precision"
+    p.xlabel = "recall"
+    p.xlim(0, 1)
+    p.ylim(0, 1)
+    p.title = "Precision-recall curve"
+    f.saveas("ROC.pdf")
+  }
 }

### 2016-06-22 node_embedding/src/WordSenseOpts.scala

@@ -11,8 +11,11 @@ object WordSenseOpts extends EmbeddingOpts{
   val combineContext    = new CmdOption("combined-context", false, "BOOLEAN", "Give edge and neighbour to trainer together")
   val synonyms          = new CmdOption("synonym-file", "Data/anatomy/VectorMatcherResults.rdf", "String", "File containing synonyms")
   val nIts              = new CmdOption("n-its", 5, "INTEGER", "Number of times w2v should go over the corpus")
-  nIts.setValue(10)
-  threads.setValue(1)
+  val continue          = new CmdOption("continue", true, "BOOLEAN", "")
+  nIts.setValue(0)//1000000)
+  threads.setValue(4)
+  continue.setValue(false)
+  dimension.setValue(50)
 
   // IO
   val inputFilename     = new CmdOption("embeddingsfile", "", "String", "Loads embeddings from this file if not empty")
@@ -24,9 +27,15 @@ object WordSenseOpts extends EmbeddingOpts{
   // Hard-coding data files
   //corpusses.setValue("Data/anatomy/mouse.owl;Data/anatomy/human.owl;Data/NELL_clean.csv")
   corpusses.setValue("Data/anatomy/mouse.owl;Data/anatomy/human.owl")
+  //corpusses.setValue("Data/medical/oaei2013_SNOMED_small_overlapping_nci.owl;Data/medical/oaei2013_NCI_small_overlapping_snomed.owl")
+  //truthfile.setValue("Data/medical/oaei2013_SNOMED2NCI_repaired_UMLS_mappings.rdf")
   output.setValue("Data/output.csv")
-  saveVocabFile.setValue("Data/vocab.csv")
+  //saveVocabFile.setValue("Data/vocab.csv")
   //loadVocabFile.setValue("Data/vocab.csv")
   //inputFilename.setValue("Data/output.csv")
+  //inputFilename.setValue("Data/forthelongesttime.csv")
+  //inputFilename.setValue("edgemappings.csv")
+  //inputFilename.setValue("Data/pretrained/glove.6B.50d.txt")
+  continue.setValue(continue.value && !inputFilename.value.isEmpty) // Can't continue on nothing
 }
 

### 2016-06-24 node_embedding/src/Evaluator.scala
Committing before I move Jena to OWLAPI

@@ -14,7 +14,7 @@ import scala.util.Try
 object Evaluator {
 
   val opts = WordSenseOpts
-  val model = new DeepWalkNodeEmbedding() //SkipGramNodeEmbedding()
+  val model = new SkipGramNodeEmbedding()
 
   def get_compare_stats(alignment: Alignment, truth: Alignment, calc: (String, String) => Double = this.calc): (Int, Int, Int) = {
     val alignmentset = alignment.alignments.asScala.toSet[(String, String, Double)].map { case (s: String, o: String, v: Double) => (s, o) }
@@ -41,9 +41,10 @@ object Evaluator {
   def show_alignment(alignment: Alignment, other: Alignment) = {
     val a = alignment.alignments.asScala.toSet[(String, String, Double)]
     val a_ = other.alignments.asScala.toSet[(String, String, Double)]
+    val b = a.flatMap(t => Array(t._1, t._2))
+    val b_ = a_.flatMap(t => Array(t._1, t._2))
     val minus = a_ -- a//a -- a_
     val minus_ = minus.filter(t => t._1 != t._2)
-    //val b = minus.flatMap(t => Array(t._1, t._2))
     //val c = b.map(model.getVocab.getId(_))
     println(minus_)
   }
@@ -79,7 +80,7 @@ object Evaluator {
         case 'e' => (trip._1, trip._2, subj_)
       }
       if (trip._1 != null && trip._2 != null && trip._3 != null)
-        truthalignment.add(trip._1, trip._2, trip._3.toDouble)
+        truthalignment.add(trip._1.toLowerCase, trip._2.toLowerCase, trip._3.toDouble)
       else
         edgemap.put(obj, trip)
     }
@@ -146,12 +147,15 @@ object Evaluator {
     } else {
       println("Starting")
 
+      /*
       val file = io.Source.fromFile("edgemappings.csv")
       val hm = new mutable.HashMap[String, String]()
       for (line <- file.getLines()) {
         hm.put(line.split(" ").head, line.split(" ").last)
       }
+      */
 
+      loadTruth()
       model.buildVocab()
       model.learnEmbeddings()
 
@@ -161,15 +165,15 @@ object Evaluator {
   }
 
     def dotherest(alignment: Alignment) {
-      //Visualizer.hist_alignment(alignment)
-      alignment.set_threshold(0.0075)
+      Visualizer.hist_alignment(alignment)
+      //alignment.set_threshold(0.0075)
       val truth = loadTruth()
[…]

### 2016-06-24 node_embedding/src/NodeEmbeddingModel.scala

@@ -103,7 +103,8 @@ abstract class NodeEmbeddingModel extends WordEmbeddingModel(WordSenseOpts) {
   // Component-1
   def buildVocab(all: Boolean): Unit = {
     vocab = new MultiSynonymVocabBuilder(2) //TODO: unhardcode 2
-    val synonyms = loadSynonyms()
+    //val synonyms = loadSynonyms()
+    val synonyms = new mutable.HashMap[String, String]()
     if (loadVocabFilename.isEmpty) {
       for ((one_corpus, i) <- corpusses.split(";").zipWithIndex) {
         buildVocab(one_corpus, synonyms, i)
@@ -181,7 +182,11 @@ abstract class NodeEmbeddingModel extends WordEmbeddingModel(WordSenseOpts) {
     val threadIds = (0 until threads).map(i => i)
     //val fileLen = new File(current_corpus).length
     val fileLen = ontology.getEdges.size
-    threadIds.par.foreach(workerThread(_, fileLen, 300))
+    for (it <- 0 to nIts) {
+      println("Iteration: " + it)
+      threadIds.par.foreach(workerThread(_, fileLen, 300))
+      store()
+    }
     println("Done learning embeddings.")
     if (!WordSenseOpts.embeddingOutFile.value.isEmpty && (WordSenseOpts.inputFilename.value.isEmpty || WordSenseOpts.continue.value))
       store()
@@ -231,7 +236,7 @@ abstract class NodeEmbeddingModel extends WordEmbeddingModel(WordSenseOpts) {
       word_count += process(edgeItr.next) // Design choice : should word count be computed here and just expose process(doc : String): Unit ?.
       ndoc += 1
       if (id == 0 && ndoc % printAfterNDoc == 0) {  // print the process after processing 100 docs in 1st thread. It approx reflects the total progress
-        printf("Progress: %f.3%% @%d%n", ndoc / fileLen.toDouble * 100, ndoc)
+        printf("Progress: %f%% @%d%n", ndoc / fileLen.toDouble * 100, ndoc)
       }
       //work = word_count <= total_words_per_thread // Once, word_count reaches this limit, ask worker to end
     }

### 2016-06-24 node_embedding/src/Ontology.scala

@@ -66,7 +66,7 @@ class RDFOntology (filename: String, reference: Boolean = false) extends Ontolog
     if(this.reference)
       return nodes
     else
-      return nodes.filterNot(_.contains("blank:")).toSet.toIterator
+      return nodes.toSet.toIterator//.filterNot(_.contains("blank:")).toSet.toIterator
   }
 
   def getEdges: Iterator[String] = {

### 2016-06-24 node_embedding/src/Visualizer.scala

@@ -32,7 +32,7 @@ object Visualizer {
     val alignmentMap = (keys zip values).toMap
     val vec = DenseVector(values)
 
-    val keys_ = truth.alignments.asScala.toArray.map{case (a,b,c) => (a,b)}
+    val keys_ = truth.alignments.asScala.toArray.map{case (a,b,c) => (a.toLowerCase,b.toLowerCase)}
     val values_ : Array[Double] = keys_.map(t => calc(t._1, t._2)).filterNot(t => t >= 100000)
     val vec_ = DenseVector(values_)
 

### 2016-06-24 node_embedding/src/WordSenseOpts.scala

@@ -2,7 +2,6 @@ import cc.factorie.app.nlp.embeddings.EmbeddingOpts
 
 object WordSenseOpts extends EmbeddingOpts{
 
-
   minCount.setValue(0) // For some reason many nodes have no neighbours. Looking into that.
   // Model
   val includeEdgeLabels = new CmdOption("include-edge-labels", true, "BOOLEAN", "Should edges be taken into account when generating vocabulary?")
@@ -15,7 +14,7 @@ object WordSenseOpts extends EmbeddingOpts{
   nIts.setValue(0)//1000000)
   threads.setValue(4)
   continue.setValue(false)
-  dimension.setValue(50)
+  dimension.setValue(5)
 
   // IO
   val inputFilename     = new CmdOption("embeddingsfile", "", "String", "Loads embeddings from this file if not empty")
@@ -30,7 +29,7 @@ object WordSenseOpts extends EmbeddingOpts{
   //corpusses.setValue("Data/medical/oaei2013_SNOMED_small_overlapping_nci.owl;Data/medical/oaei2013_NCI_small_overlapping_snomed.owl")
   //truthfile.setValue("Data/medical/oaei2013_SNOMED2NCI_repaired_UMLS_mappings.rdf")
   output.setValue("Data/output.csv")
-  //saveVocabFile.setValue("Data/vocab.csv")
+  saveVocabFile.setValue("Data/vocab.csv")
   //loadVocabFile.setValue("Data/vocab.csv")
   //inputFilename.setValue("Data/output.csv")
   //inputFilename.setValue("Data/forthelongesttime.csv")

### 2016-06-24 Paper/Draft.tex
Perfected Introduction and Background

@@
  \section*{Summary}
- %TODO somewhere else: explain why one large ontology won't work
  %TODO Definitions
  %TODO Word index
- %TODO List of tables
- %TODO List of figures
  \tableofcontents
@@
  \subsection{Motivation} %TODO aanleiding?
- In \cite{mccallumweblecture}, McCallum talks about Universal schema.
+ At ICTIR 2015, McCallum ...
+kkeynot...
+titel \cite{mccallumweblecture}, McCallum talks about Universal schema.
 This system learns embeddings of entities and relations found in text and Knowledge Bases.
@@
 It is a neural network model that learns to predict the context of a word (in this case the context of an entity is the relations it is co-occurs with and vice versa).
-McCallum talked about a new extension to the algorithm that allowed for homonyms and as such can deal with more ambiguous data\cite{mccallumweblecture}.
+McCallum discussed a new extension to the algorithm that allowed for homonyms and as such can deal with more ambiguous data\cite{mccallumweblecture}.
 
@@
 Since embedding models have good performance on intra-knowledge base relation prediction, they should also work on ontology alignment.
+
+ \subsection{Justification}
+ On the Semantic Web, many relatively small knowledge bases will be combined temporarily so that it is possible to reason over the combined knowledge of those knowledge bases.
+To combine these knowledge bases, their ontologies first need to be aligned.
+This is an act that will happen very often on the Semantic Web, since every interaction with the Semantic Web will usually require information from multiple domains.
+Large domains may be stored over multiple devices, which can be viewed as different knowledge bases which also need to be aligned.
+Therefore, it is save to say that efficient ontology matching will be very valuable.
+
+ Since most of the knowledge on the Semantic Web is automatically gathered, it may be unreliable and even wrong.
+Therefore, ontology matching that is capable of handling this uncertain knowledge is required.
+Word Embeddings and especially multi-sense Word Embeddings should be able to handle a high amount of uncertainty.
+
+ Calculating the distance between vectors can be done very efficiently, therefore ontology matching with distributed concept representations fits that efficiency criteria.
+Since these representations can use the context of a concept, they are also most robust than methods that do not take the context into account.
+
+ Distributed representation algorithms can be trained unsupervised on new domains, so they can be applied to those new domains without effort from humans, as opposed to for example the string edit distance.
+This is also an improvement for the semantic web.
+
+ Also, ontology matching is already used in areas other than the semantic web.
+It is, for example, used by companies for merging knowledge from different knowledge bases when merging with other companies.
+If the proposed matching algorithm is better than the current algorithms, or at least improves the performance when used in ensemble with the current algorithms, it will be useful immediately in these situations, not just in the future, on the Semantic Web.
 
@@
 
- \subsection{Justification} %relocate?
- On the Semantic Web, many relatively small knowledge bases will be combined temporarily so that it is possible to reason over the combined knowledge of those knowledge bases.
-To combine these knowledge bases, their ontologies first need to be aligned.
-This is an act that will happen very often on the Semantic Web, since every interaction with the Semantic Web will usually require information from multiple domains.
-Large domains may be stored over multiple devices, which can be viewed as different knowledge bases which also need to be aligned.
-Therefore, it is save to say that efficient ontology matching will be very valuable.
-
- Since most of the knowledge on the Semantic Web is automatically gathered, it may be unreliable and even wrong.
-Therefore, ontology matching that is capable of handling this uncertain knowledge is required.
-Word Embeddings and especially multi-sense Word Embeddings should be able to handle a high amount of uncertainty.
-
- Calculating the distance between vectors can be done very efficiently, therefore ontology matching with distributed concept representations fits that efficiency criteria.
-Since these representations can use the context of a concept, they are also most robust than methods that do not take the context into account.
-
- Since distributed representation algorithms can be trained unsupervised on new domains, they can be applied to those new domains without effort from humans, as opposed to for example the string edit distance.
-This is also an improvement for the semantic web.
-
- Also, ontology matching is already used outside of the semantic web.
-It is currently in use for companies that want to merge knowledge from other companies, for example.
-If the proposed matching algorithm is better than the current algorithms, or at least improves the performance when used in ensemble with the current algorithms, it will be useful immediately in these situations, not just in the future, on the Semantic Web.
-
  \subsection{Problem}
@@
 
- \subsection{Overview} %TODO rewrite
- This thesis is structured as follows: firstly, I will describe the context of the problem, which includes the Semantic Web, Ontologies, Ontology matching and other relevant research.
-Secondly, I will outline the problem and research questions.
-Thirdly, I will describe the method I used to develop the solution, which includes the idea, challenges and considered implementations.
-The fourth section after this describes methods I used to evaluate the solution, with the fifth section showing the results, the sixth section the conclusions and the last and seventh section the discussion.
-
- \subsection{Research questions}
+ \subsection{Research questions} \label{researchquestions}
  The main question that I will answer with this work is the following research question:
@@
  \textit{
- Can distributed representations of concepts be used to find relationships between concepts in ontologies better than existing terminological matchers?
+ Can distributed representations of concepts be used to find relationships between concepts in ontologies better than existing matchers?
  }
@@
 
- I will also investigate the following two related but different questions:
-
- \begin{center}
- \textit{
- Can distributed representations use the context of a concept to find relationships between concepts in ontologies better than existing structural matchers?
- }
- \end{center}
+ I will also investigate the following related but different question:
 
@@
 
- \subsection{Hypothesis}
+ \subsection{Hypotheses} \label{hypotheses}
  \begin{center}
@@
 
- This hypothesis are true for distributed representations matcher if they are true for one distributed representation matcher.
-Therefore to test the hypotheses, I must test them for every distinct implementation of the matcher.
+ This hypothesis is true for distributed representations matching in general if it is true for one distributed representation matcher.
+Therefore to test the hypothesis, I must test it for every distinct implementation of the matcher.
+
+ \subsection{Overview} %TODO rewrite
+ This thesis is structured as follows: firstly, I will describe the context of the problem, which includes the Semantic Web, Ontologies, Ontology matching and other relevant research.
+Secondly, I will outline the problem and research questions.
+Thirdly, I will describe the method I used to develop the solution, which includes the idea, challenges and considered implementations.
+The fourth section after this describes methods I used to evaluate the solution, with the fifth section showing the results, the sixth section the conclusions and the last and seventh section the discussion.
 
 \newpage
-\section{Theory}
+\section{Background}
  In this section I will discuss all concepts that are required to understand the study.
@@
 
- Beside these knowledge bases, many other pieces of the Semantic Web are already in use. For example, the W3C \cite{rdf, owl}
- %TODO: stats?
+ On way the W3C is fighting ambiguity is to ensure very few different languages are used for ontologies and knowledge bases. The main languages W3C endorses are RDF, OWL and SKOS\cite{rdf, owl, skos}.
 
  Large ontologies already exist, with the largest, Freebase, boasting almost two billion triples and the three hundred combined Large Open Data databases contain over thirty billion\cite{dbpedia, lod}.
-The LOD is simply one huge alignment of hundreds of knowledge bases...
-%Doorschrijven
+The LOD is simply a single alignment over many different knowledge bases.
 
  Applications include improved web searching, question answering, product comparison, context merging, data integration, decision support, translation, all the way up to the intelligent softbot mentioned earlier.
-%http://www.cs.vu.nl/~guus/papers/Schreiber06a.pdf https://hal.inria.fr/hal-00917910/document
+\cite{schreiber, future}
 
- % Elke behandelen
-
- Overall it is clear that % Samenvatten/enumerate, gevolg voor deze thesis (dus ik moet... mijn bijdrage is belangrijk...)
+ The many uses of ontology matching show that it is important to research all avenues that might improve ontology matching, as it will have a direct result in many other fields.
  \subsubsection{Technologies}
+ %TODO Wil ik dit nog doen?
 
@@
 The variants trade off levels of expressiveness versus computability.
-%TODO consider SKOS
 
@@
  For example, arm and front paw have an edit distance of 8, since they have 1 character in sequence in common (either the a or the r) and thus 8 characters that are different.
- \subsection{Problems in ontology alignment}
- There are a number of different problems ... %TODO Opsommen en samenvatten
-
+ \subsubsection{Problems in ontology alignment}
  How should the wildly differing demands the applications place on the ontology matching systems be satisfied by a single or just a few systems?
@@
  \subsubsection{The state of the art}
- Recently, an effective and efficient skip-gram model has been developed, called \textbf{Word2vec}, which uses a number of extensions over previous methods that enable it to efficiently learn an effective representation\cite{w2v}.
+ Recently, an effective and efficient skip-gram model has been developed, called \emph{Word2vec}, which uses a number of extensions over previous methods that enable it to efficiently learn an effective representation\cite{w2v}.
 One example of such an extension is negative sampling, which is a step that teaches the network that randomly selected words should have non-similar representations.
 
- These extensions enable \textbf{Word2vec} to be trained on large corpora and represent words in a way that is very useful in NLP.
+ These extensions enable \emph{Word2vec} to be trained on large corpora and represent words in a way that is very useful in NLP.
 It is used as a language model in part-of-speech tagging and machine translation.
@@
 
- After the authors showed the usefulness of \textbf{Word2vec}, many researchers developed new uses for the algorithm.
+ After the authors showed the usefulness of \emph{Word2vec}, many researchers developed new uses for the algorithm.
 Some extensions that are relevant to this study will be discussed.
@@
 
- \subsubsection{Word order}
- \textbf{Word2vec} has been expanded in a number of different ways.
+ \subsubsection{Word order} \label{wordorder}
+ \emph{Word2vec} has been expanded in a number of different ways.
 For example, word order can be preserved, leading to a similarity measure that is closer to syntax, as syntax defines positional properties of words within a sentence\cite{ling2015}.
@@
 
- \subsubsection{Multi-sense}
- Another interesting development is the multi-sense \textbf{Word2vec}, which allows for multiple vector representations per word, depending on the number of different definitions a word has.
+ \subsubsection{Multi-sense} \label{multisense}
+ Another interesting development is the multi-sense \emph{Word2vec}, which allows for multiple vector representations per word, depending on the number of different definitions a word has.
 For example, the word bank represents both the monetary institute and the riverside, which would both have a different representation in this extension.
@@
  \subsection{Used technology}
- %TODO Guide user from problem to research question. See Arjen's notes 1. 
- \subsubsection{Factorie} \label{factorie} %TODO rewrite
+ \subsubsection{Factorie} \label{factorie}
  Factorie is a toolkit that contains a number of tools which includes word-embedding models \cite{git-factorie}. \cite{w2v}.
-
- Factorie is written in scala, a relatively new language that interfaces with java.
-See \cite{scala}.
-This allows for interoperability between factorie and AgreementMaker.
-Any algorithm that is implemented in factorie or on top of factorie can therefore be used as a matching algorithm in AgreementMaker.
 
@@
 It also provides example implementations and programs.
+Factorie is written in scala, a language that has been gaining popularity recently and interfaces with java.
+See \cite{scala}.
 
@@
 
- When model training is extremely fast, which is the case for parallelised neural network training, parsing the data from string format to vectors in a proper data structure can become a bottleneck.
-Recently, factorie added JFlex to parse its data.
-This improved its parsing by \%5000, removing the bottleneck.
-
  Since I investigate many different implementations of the same algorithm, it should be easy to switch between these implementations at run-time without much effort.
@@
  \subsubsection{Jena}
- Jena is the most used library for storing, manipulating, querying and reasoning on ontologies.
+ Jena is the most used library for storing, manipulating, querying and reasoning on ontologies\cite{jena}.
 It has an interface that allows for easy access to an ontology.
@@
 
- \subsubsection{Never-ending Language Learner}
- The Never-Ending Language Learner, or NELL, also known as the Read the Web Project, has created a big ontology of facts extracted from the web.
-
- \subsubsection{WordNet}
- WordNet is a manually constructed database of semantic relations between words.
- % https://wordnet.princeton.edu/wordnet/publications/poznan.springer.pdf
-
  \newpage
- \section{Method} %Controleer overgang
- %hier iets opschrijven?
+ \section{Method} 
+ This section contains the description of the matching system and experimental setup.
+It consists of four parts.
+Firstly, it describes the idea and challenges of implementing the system.
+Secondly, it describes the data used to test the system.
+The third part describes all different implementations of the system.
+The fourth and last part describes the evaluation criteria.
 
@@
 
- \textbf{Word2vec} is an unsupervised method that implicitly maps words to a vector space that has been shown to contain semantic properties.
+ \emph{Word2vec} is an unsupervised method that implicitly maps words to a vector space that has been shown to contain semantic properties.
 Explicitly, it predicts words from the context of that word.
@@
 
- To solve these problems I will adapt \textbf{Word2vec} to graphs to create an algorithm that converts nodes to vectors, in other words \textbf{Node2vec}.
+ To solve these problems I will adapt \emph{Word2vec} to graphs to create an algorithm that converts nodes to vectors, in other words \emph{Node2vec}.
 It can be extended with multi-sense embeddings, different ways of considering the neighbourhood and hot-starting.
+
+  \subsection{Data}
+ The data used comes from a list of data sets that the OAEI provides\cite{euzenat2013ontology}.
+ Every data set contains two ontologies that need to be aligned and a ground truth alignment.
+The goal is straightforward: find the alignment given only the ontologies and whichever outside resources are needed.
+
+ \subsubsection{Mice and men}
+ The first data set considered consists of two anatomical ontologies.
+The first ontology describes the anatomy of mice and the second ontology the anatomy of men.
+Since they are similar creatures, there are many correspondences between the anatomy.
+The ontologies contain X and Y nodes, and X and Y edges, respectively.
+There are Z correspondences between the two ontologies.
+
+ The ontology is structured as a hierarchical tree with the only label being \emph{subClassOf}.
+This poses a few problems for some of the implementations as they take into account the edge labels.
+Since there are no edge labels, these implementations will not be different from their edge-less counterparts.
+ \subsubsection{Medical}
+ The second data set is larger, boasting X and Y medical concepts with X and Y relations. There are Z correspondences between the two ontologies. This data set has N different edge labels.
 
@@
 This way, all improvements are recorded precisely.
- The explanations refer back to the example in Section \ref{example}
+ The explanations refer back to the example in Section \ref{example}.
   \subsubsection{Node vectorisation}
-  The most basic \textbf{Node2vec} model converts a node to a vector purely based on its own label.
+  The most basic \emph{Node2vec} model converts a node to a vector purely based on its own label.
 This method has one advantage over simple string matching: if no node is found in the other ontology that matches exactly, we can still find a node that is similar since it is close in the vector space.
@@
   \subsubsection{Select from senses}
-  Another way to take into account the influence of neighbouring nodes is to train a multi-sense node embedding model as described in {appropriate section}, and selecting from the different node senses based on which is closest to the context average.
-%TODO appropriate section
+  Another way to take into account the influence of neighbouring nodes is to train a multi-sense node embedding model as described in Section \ref{multisense}, and selecting from the different node senses based on which is closest to the context average.
   \subsubsection{Adding edge labels}
@@
   \subsubsection{Combining edges with nodes}
-  As can be read in {appropriate section}, it is possible to drop the bag-of-words assumption that the context is sequence invariant.
-  %TODO appropriate section
-  %TODO maybe ref too\endcomment
+  As can be read in Section \ref{wordorder}, it is possible to drop the bag-of-words assumption that the context is sequence invariant.
   This means we can for example have the context be (previous word, next word) and those words will be treated differently.
@@
 However, it can use dictionaries and other ontologies to improve performance.
-  % Moet voorafgaand stukje op een andere plek?
   The algorithm can find matches based purely on the given node and edge labels.
@@
 Since the \emph{front paws} and \emph{arms} are next to the \emph{torso}, they are more likely to be matched now.
-In the case of \textbf{Node2vec} they are more likely to be matched, since their neighbourhoods are the same (the only neighbour of both \emph{arms} and \emph{paws} is \emph{connectedTo torso}).
+In the case of \emph{Node2vec} they are more likely to be matched, since their neighbourhoods are the same (the only neighbour of both \emph{arms} and \emph{paws} is \emph{connectedTo torso}).
  \subsubsection{Training corpus}
@@
  The foundation the algorithm has been build and tested on is Factorie, described in \ref{factorie}.
-Earlier work on a forked branch of factorie was done by \cite{multisensecode} to implement multi-sense \textbf{Word2vec}.
+Earlier work on a forked branch of factorie was done by \cite{multisensecode} to implement multi-sense \emph{Word2vec}.
 
@@
  \subsection{Evaluation}
- %https://hal.inria.fr/hal-00917910/document
  The goal of the research is to find an ontology alignment algorithm $A$ and prove that it performs better than current techniques.
@@
 So, instead we may want to see if performance is improved when adding $A$ to an ensemble of algorithms $E=(A_1,..,A_n)$.
- \subsubsection{Evaluation methods} \label{Evaluation methods}
+ \subsubsection{Evaluation methods} \label{EvaluationMethods}
  The evaluation should be done using a performance measure $P(Al,T)$ that takes the alignment an algorithm produces given an ontology and the ground truth.
@@
 If the score is in the top p\%, it is significant, otherwise it is not.
-In this case the solutions are $E\cup \{R\}$, where $R$ is an algorithm that generates random alignments.
-%TODO ref for stats test
+In this case the solutions are $E\cup \{R\}$, where $R$ is an algorithm that generates random alignments\cite{fisher1925statistical}.
 
@@
 To make the results of this study easily comparable to others, equal weights will be used.
- \subsubsection{Data}
- The data used comes from a list of data sets that the OAEI provides. % Zoek paper, misschien http://www.sciencedirect.com/science/article/pii/S1570826813000188
- %Hoeveel preprocessing moest ik doen
- Every data set contains two ontologies that need to be aligned and a ground truth alignment.
-The goal is straightforward: find the alignment given only the ontologies and whichever outside resources are needed.
-
- A reference alignment can be made by experts or be created by bipartitioning an existing ontology. %expand this.
- %\subsubsection{Parts of OWL ignored}
 
@@
 
+ %TODO F measure noteren op pieken. Dan confidence vs F-measure bespreken in interpretation.
+ % Wat is de threshold van AML?
+ % Extra rij met baseline literal string matcher
  \subsection{Precision versus recall}
@@
   \subsection{F-score}
+  \begin{table}[H]
   \begin{tabular}{l|l}
@@
   \end{tabular}
+  \caption{The $F_1$-scores for the different matchers for the mice dataset}
+  \label{fscores}
+  \end{table}
   \subsection{Jaccard}
@@
  \section{Conclusion and discussion}
+ In this section I will consider the research questions and hypotheses as formulated in Sections \ref{researchquestions} and \ref{hypotheses}.
+In the second part of this section, I will discuss the implications of these results.
+In the third and last part of the section, I will describe a few avenues that might be interesting to explore further, including a number of implementations I did not consider and why.
+
  %\subsection{Recap research questions} % Maak 'figure' van
  %\subsection{Recap hypotheses}
- \subsection{Conclusions}
- From the results and interpretation we can conclude that distributed word representations can currently \textbf{not} find relationships between concepts in ontologies better than existing matchers.
+ \subsection{Conclusions} \label{conclusions}
+ The main research question from Section \ref{researchquestions} is
+ \begin{center}
+ \textit{
+ Can distributed representations of concepts be used to find relationships between concepts in ontologies better than existing matchers?
+ }
+ \end{center}
+
+ The results from all the different evaluation measures are in agreement.
+From those results we can conclude that the distributed word representations system is currently \textbf{not} able to find relationships between concepts in ontologies better than existing matchers.
 
  \subsection{Discussion}
-  The system underperforms on the provided data. This can have one or more of the following four causes:
+  The system underperforms on the provided data. This can have one or more of the following four potential causes:
   \begin{itemize}
@@
 
+  I will investigate all four of these causes to see which is the most likely.
+If potential cause one is the case, the study is invalid and should be repeated on one or more different data sets.
+If potential cause two is the actual cause or potential cause three is the actual cause, the study is invalid and the results should not be published until the system is fixed and the results do not change.
+If it is the case that none of these three potential causes is the actual cause, by elimination the fourth potential cause must be the actual cause.
+In that case the study is valid and it will be possible to draw the final conclusion.
+
   \subsubsection{The data}
   If the data set is the cause of the underperformance, logically switching to another data set will improve performance over the baseline.
-Possible reasons the data set causes underperformance include a too small data set or a data set having a structure that does not work with the algorithm.
+Possible reasons the data set causes underperformance include the data set being too small, labels that are not useful or the data set having a structure that does not work with the algorithm.
+For example, the pre-trained \emph{Word2vec} model is expected to work better on a data set that has commonly used words as labels.
+%Aanpassen als ik 3e dataset heb.
 
-  The algorithm has been run on multiple data sets with no significant difference in performance, therefore the data is not the cause of the underperformance.
+ The algorithm has been run on multiple data sets with no significant difference in performance.
+For example, compare the Average precision for the medical dataset with the anatomy dataset.
+The %TODO AP is between baseline en AML for both?
   \subsubsection{The system}
@@
 
-  The number of edges is known as it has been provided by the designers of the Ontologies\cite{mice_ontology}, so we can compare the number of edges found with the actual number of edges.
+  First, I obtained the number of edges from VOWLview\cite{vowlview}, an Ontology graphing program.
+This was necessary since the creators of the data did not share how many edges were in the database.
+With the actual number of edges, obtained, it is possible to compare them with the number of edges found.
 If these match, the context extraction works.
-  \begin{table}
-  \begin{tabular}{l|ll}
-  & \multicolumn{2}{c}{\#edges}\\
-  Algorithm & expected & actual\\
+  \begin{table}[H]
+  \begin{tabular}{l|ll|ll}
+  & \multicolumn{2}{c}{\#edges mice} & \multicolumn{2}{c|}{\#edges humans}\\
+  Algorithm & expected & actual & expected & actual\\
   \hline
-  \textbf{Truth}\cite{mice_ontology} & \multicolumn{2}{c}{\textbf{1000000}} \\
-  Monodirectional & & \\
-  Bidirectional & & \\
-  Bidirectional \& edges & & \\  
+  \textbf{Truth}\cite{mice_ontology} & \multicolumn{2}{c|}{\textbf{1810}} & \multicolumn{2}{c}{\textbf{3780}} \\
+  Monodirectional & & & &\\
+  Bidirectional & & & &\\
+  Bidirectional \& edges & & & &\\
   \end{tabular}
+  \caption{The number of edges compared to show that edge parsing was successful.}
+  \label{edgecounts}
   \end{table}
@@
   \subsubsection{The algorithm}
-  Since we have excluded all other possibilities, we can conclude that the remaining possibility, that the set of algorithms do not work well on Ontology data.
+  At the beginning of this section, I reasoned that there are four possible causes for the underperformance of the system.
+The first three being bad data, bad code and bad context extraction.
+I have shown that all three are very unlikely to be the cause of the underperformance.
+Since those three possibilities have been excluded, the most likely conclusion is last remaining possibility: the set of distributed embedding algorithms do not work well on Ontology data.
  \subsection{Future research}
+
  \subsection{Discarded implementations}
@@
 
- \section{List of figures and tables}
+ \section{Lists of figures and tables}
 
  \newpage
- \subsection{Figures}
- \subsection{Tables}
+ \listoffigures
+ \listoftables
 
@@
   \pagenumbering{Roman}
-  \section{Appendix 1}
-  \section{Appendix 2}
+  \section*{Appendix 1}
+  \section*{Appendix 2}
  \end{appendices}

### 2016-06-25 Paper/Draft.tex
Too many small details added to name

@@
  \usepackage{caption}
+ \usepackage[export]{adjustbox}
+ \usepackage{url}
+\usepackage{subcaption}
 
@@
  %TODO Word index
+ %TODO Fix hoofdletters (bv ontology, kb)
+ %TODO spelling (database dataset)
  \tableofcontents
@@
 
-%TODO \section{Motivation}
-
  \pagenumbering{arabic}
  \section{Introduction} \label{intro}
- It is a Friday afternoon and you realise you want to watch a movie with some friends this weekend. So, what do you do? To achieve this goal you must take four steps.
-
- Firstly, you must open up an internet Movie Database, search for movies that you like that are also playing this weekend.
-To do this you must either manually go through the list of movies playing this weekend or movies the Database recommends for you and check if any movies on that list match your full criteria.
-
- Once you have found one or more movies that match your search criteria, you have to select a time at which you can see the candidate movies, so you check for every movie every available time slot at every cinema near you.
+ It is a Friday afternoon and you realise you want to watch a movie with some friends this weekend.
+So, what do you do?
+To achieve this goal you must take three steps.
+These steps are also shown in Figure \ref{movies}.
+
+ Firstly, search for movies that you like that are also playing this weekend.
+To do this you must either manually go through the list of movies playing this weekend and check if any movies on that list match your preferences.
+
+ Once you have found one or more movies that you like, you have to select a time at which you can see the candidate movies, so you check for every movie every time slot at every cinema near you.
 The number of time slots is equal to the number of movies you chose in the previous step, times the number of cinemas near you times the number of times every movie is shown at one cinema.
-
- The next step is to filter the number of time slots based on your agenda, so you cross-reference the available movie times with the times you are available during the weekend.
-
- Then onto the last step, getting friends to go with you.
+You also have to filter the out time slots based on your availability, so you cross-reference the available movie showtimes with your agenda.
+
+ Then onto the third and final step, getting friends to go with you.
 In this step you do not want to burden your friends too much by having them pick both the movie and the time, so you will have to decide which movie to watch or when, even though you do not know if your friends will like this movie or are available at that time.
-Once you contact your friends, most of them do not respond as they are not online at that time or they do not feel like filling in a poll about availability or movie choices.
-
- Most of the time people will limit their options to avoid these steps, considering only a few movies, cinemas, time slots and friends.
-But this is not necessary.
+Once you contact your friends, most of them do not respond as they are not online at that time or they do not want to fill out an availability poll or movie choices.
+
+ Most of the time people will limit themselves to suboptimal options by avoiding these steps, considering only a few movies, cinemas, time slots and friends.
+But limitations like this are not necessary.
 What would happen if the above process was automated?
+
+ \begin{figure}
+ \centering
+ \includegraphics[width=0.9\textwidth]{plots/select_movies}
+ \caption{To find the best movie, the shown movies need to be filtered by the ones you like and the showtimes need to be filtered by the times you are available.
+All remaining showtimes need to be cross-references with the preferences of your friends.
+This is a lot of work and can be automated on the Semantic Web.}
+ \label{movies}
+ \end{figure}
+
 The first step, finding movies that match two criteria would be considered trivial with modern technology.
@@
 
- \subsection{Motivation} %TODO aanleiding?
- At ICTIR 2015, McCallum ...
-kkeynot...
-titel \cite{mccallumweblecture}, McCallum talks about Universal schema.
-This system learns embeddings of entities and relations found in text and Knowledge Bases.
-These embeddings are then used to predict new relations for the knowledge bases.
-The system find embeddings such that the embeddings of entities and relations that co-occur are highly similar.
+ \subsection{Motivation}
+ In this section I will explain how the study came into existence.
+
+ At the 14th International Semantic Web Conference McCallum presented his keynote on \emph{Representation and Reasoning with Universal Schema Embeddings}\cite{mccallumweblecture}.
+
+ \begin{figure}[H]
+ \begin{subfigure}{.475\textwidth}
+ \includegraphics[width=0.95\linewidth]{plots/McCallum_matrix}
+ \end{subfigure}
+ \begin{subfigure}{0.475\textwidth}
+ \includegraphics[width=0.95\linewidth]{plots/graaf1}
+ \end{subfigure}
+ \caption{The Universal Schema.
+Every row and every column is represented by an embedding (in purple).
+Green cells mean a row and column are in the context of the other.
+For example, the pair Bill and Microsoft are connected to \emph{chairman}.
+ The embeddings are then trained so that the context can be predicted. That means the embeddings of Bill \& Microsoft and \emph{chairman} will become more similar.}
+ \label{McCallum_matrix}
+ \end{figure}
+
+The Universal Schema uses two steps.
+Firstly, the system learns embeddings of entities and relations found in text and Knowledge Bases\cite{univeralschema}, see Figure \ref{McCallum_matrix}.
+Secondly, these embeddings are then used to predict new relations for the knowledge bases.
+The system finds embeddings such that the embeddings of entities and relations that co-occur are highly similar, see Figure \ref{McCallum_matrix}.
+
+ \begin{figure}[H]
+ \begin{subfigure}{0.475\textwidth}
+ \includegraphics[width=0.95\linewidth]{plots/McCallum_matrix2}
+ \end{subfigure}
+ \begin{subfigure}{0.475\textwidth}
+ \includegraphics[width=0.95\linewidth]{plots/graaf2}
+ \end{subfigure}
+ \caption{After the embeddings are learned, rows and columns with similar embeddings are connected (in light green).
+ For example, the embeddings of Melinda \& Seattle and \emph{lives in} may have become very similar. In that case, the system connects the pair with that relation.}
+ \label{McCallum_matrix2}
+ \end{figure}
+
  If some entities and relations have similar embeddings but are not known to co-occur, they are flagged as being similar.
-Similarly, if two entities or two relations have similar embeddings, they are likely referring to the same thing.
+Similarly, if two entities or two relations have similar embeddings, they are likely referring to the same or similar things.
 This can be used to infer even more similarities by collaborative filtering.
@@
 
- The embeddings are optimized by a model called the skip-gram word embedding model.
-It is a neural network model that learns to predict the context of a word (in this case the context of an entity is the relations it is co-occurs with and vice versa).
+ \begin{figure}[H]
+ \centering
+ \includegraphics[width=0.8\textwidth]{plots/Skip-Gram}
+ \label{Skip-Gram-img}
+ \caption{The embedding of a row (in pink) is optimized to be close to its context embeddings (in purple) but far away from other embeddings (in red).}
+ \end{figure}
+
+ The embeddings are optimized by a model called the skip-gram word embedding model\cite{w2v}, a neural network model that learns to predict the context of a word.
 McCallum discussed a new extension to the algorithm that allowed for homonyms and as such can deal with more ambiguous data\cite{mccallumweblecture}.
 
- If these embeddings can be used to predict new inter-knowledge base relations, it should also be possible to predict new intra-knowledge base relations.
-If these relations can be predicted, it is possible to use multiple knowledge bases together.
-Predicting these relations is called alignment.
+ McCallum plans on using these embeddings to predict new inter-knowledge base relations.
+However, from they keynote it is clear that this technique should work with multiple Knowledge Bases as the Universal Schema is applied to a set of Knowledge Bases including Freebase, knowledge extracted from text and the TAC Knowledge Bases Population Track Dataset.
+This means that intra-knowledge base relations can also be predicted using the Word Embedding Tensor Factorisation technique.
+ An example of an intra-knowledge base relation is shown in Figure \ref{merge_graph}.
+If these relations can be predicted, multiple knowledge bases can be aligned.
+Doing ontology alignment using these word embeddings is the goal of this work.
+
+ \begin{figure}[H]
+ \centering
+ \includegraphics[width=0.8\linewidth]{plots/graaf}
+ \caption{ Similar to how the embeddings are used to predict relations within an ontology, ontology matching can be done by predicting relations between two ontologies.
+For example, since Gates and Bill will have very similar sets of embeddings (as their contexts are very similar) the system will recognise they are the same entity.}
+ \label{merge_graph}
+ \end{figure}
 
@@
  \subsection{Justification} 
- On the Semantic Web, many relatively small knowledge bases will be combined temporarily so that it is possible to reason over the combined knowledge of those knowledge bases.
+ This study is important to the future of the World Wide Web.
+The next goal of the Web is the Semantic Web, where computers can interact with web pages as humans do.
+It is necessary to build the Semantic Web as soon as possible, as the amount of information on the Web is growing so fast it will be infeasible for humans to handle\cite{overload}.
+
+ The core of the Semantic Web are Knowledge Bases with the corresponding Ontologies.
+Ontology Matching is essential for the Semantic Web to work, as the information contained in the Knowledge Bases has to be combined.
+Since the Semantic Web will have many small knowledge bases, they will be combined at the moment information from them is required.
 To combine these knowledge bases, their ontologies first need to be aligned.
 This is an act that will happen very often on the Semantic Web, since every interaction with the Semantic Web will usually require information from multiple domains.
-Large domains may be stored over multiple devices, which can be viewed as different knowledge bases which also need to be aligned.
+Large domains may be stored on multiple devices, which can be viewed as different knowledge bases which also need to be aligned.
 Therefore, it is save to say that efficient ontology matching will be very valuable.
 
- Since most of the knowledge on the Semantic Web is automatically gathered, it may be unreliable and even wrong.
+ The most important goal of this study is to find an Ontology Matcher that is able to deal with ambiguous concepts.
+Since most of the knowledge on the Semantic Web is automatically gathered, it may be unreliable, ambiguous and even wrong.
 Therefore, ontology matching that is capable of handling this uncertain knowledge is required.
-Word Embeddings and especially multi-sense Word Embeddings should be able to handle a high amount of uncertainty.
-
+Word Embeddings and especially multi-sense Word Embeddings should be able to handle a high amount of ambiguity, since multi-sense Word Embeddings are made to differentiate between different meanings of the same word.
+
+ Normally, the raw text representation of words is used for matching, for example to calculate the string distance.
+However, Word Embeddings Models use a vector representation, which should be more efficient.
  Calculating the distance between vectors can be done very efficiently, therefore ontology matching with distributed concept representations fits that efficiency criteria.
-Since these representations can use the context of a concept, they are also most robust than methods that do not take the context into account.
-
- Distributed representation algorithms can be trained unsupervised on new domains, so they can be applied to those new domains without effort from humans, as opposed to for example the string edit distance.
+
+ I believe the algorithms proposed in this study will work on new data without the need for redesigning.
+This is because distributed representation algorithms can be trained unsupervised on new domains, so they can be applied to those new domains without effort from humans.
+As opposed to for example the string edit distance.
 This is also an improvement for the semantic web.
 
- Also, ontology matching is already used in areas other than the semantic web.
+ This study should be done now, as ontology matching is already used in areas other than the semantic web.
 It is, for example, used by companies for merging knowledge from different knowledge bases when merging with other companies.
@@
 
+ In summary, Ontologies are the core of the I hope it is clear that ontology matching is an important area of study and that this study will contribute to it.
+
  \subsection{Context}
- In this section, I will give a short summary of the context for the problem.
-This will enable the reader to put the problem in perspective as well as understand the reasoning behind the solution to the problem.
+ This section will enable the reader to put the problem in perspective as well as understand the reasoning behind the solution to the problem.
 Everything that is mentioned in this section will be explained more in-depth further on.
-
- On the Semantic Web, Ontologies are used to define and share knowledge.
+ Firstly, I will give a short summary of the context by explaining why the Semantic Web requires Ontology Matching.
+Then I will illustrate the problem of ambiguity.
+Lastly, I will describe the algorithm that this study is based on.
+
+ \subsubsection{Semantic Web}
+ On the Semantic Web, Ontologies are used to define knowledge\cite{fensel2001ontologies}.
  The term ontology will be properly defined later on, but for now it suffices to know that an ontology is a set of rules that determine what relations are allowed and required in a given domain of discourse.
@@
 
- The first option, using one single ontology, is infeasible.
-This is due to the fact that inference and search time scales with Ontology size, and the number of concepts that are needed on the Semantic Web is enormous.
-Every single concept that is present in the billions of Terabytes of text, images and sounds that are on the web needs to be represented, for every professional domain and science, in every language.
+ The first option, using one single ontology, is infeasible. This is due to the fact that inference and search time scales with Ontology size, %citaat
+ and the number of concepts that are needed on the Semantic Web is enormous.
+Every single concept that is present in the billions of terabytes of text, images and sounds that are on the web needs to be represented, for every professional domain and science, in every language.
 And all these concepts are related.
@@
 
- One big problem in Ontology merging is the fact that in different domains, words can have different meanings.
+ \subsubsection{Ontology Matching}
+ One big problem in Ontology matching is the fact that in different domains, words can have different meanings.
 Common examples are synonyms like author and writer, homonyms like bank (for money or by a river) and ambiguity.
 Ambiguity means that similar words mean slightly different things, or a word might have multiple related meanings.
-There are a few ways to deal with these forms of ambiguity already in use, however they are not sufficient.
+%cite
 
@@
 There are a number of extensions that can deal with homonyms as well as data structured other than the continuous bag of words representation that the initial model was developed for.
-These facts show that it may be possible to make an embedding model for Ontologies and use the word relatedness to combine Ontologies.
+These facts show that it may be possible to make an embedding model for Ontologies and use the word relatedness to combine Ontologies\cite{multisense}.
+
+  \subsubsection{Language}
+  Homonyms are two concepts that share a label, or in other words, a homonym is one word with multiple distinct meanings.
+As such, homonyms are inherently ambiguous, since the meaning is uncertain without context.
+This ambiguity is very hard for computers to deal with, as computers are used to dealing with absolute certainties.
 
@@
  We have seen that when information from multiple domains needs to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged.
-% Waar?
-  Those ontologies contain rules about concepts and concept classes in the shape of triplets, with two concepts and a relation.
-For example, the rule {\tt Professors are humans} contains the concepts \emph{Professor} and \emph{human} and an \emph{is-a}-relationship.
 
@@
 
- Lastly, there is the problem of different types of alignment relations.
-For example, one concept can be a \emph{part of} another concept, or an example of one.
-These different relations all require a different approach and come with their own sets of problems.
-%Meronymy?
-
- In summary, ontology aligning is required for multi-domain communication but poses a number of problems that make it difficult for concepts, the building blocks of ontologies, to be matched.
-
- \subsection{Research questions} \label{researchquestions}
+ The problem is:
+
+"" 
+  Matching ontologies and dealing with the ambiguity and homonymy contained in them.
+""
+
+  I will use distributed word representations to answer the above question, as McCallum suggested in his keynote.
+Distributed word representations, specifically multi-sense \emph{Word2vec}, should be used for this problem since multi-sense \emph{Word2vec} is specifically designed to combat homonymy while the neural networks in distributed word representations use the context to deal with ambiguity.
+  %TODO vraag Arjen of dit 'antwoord' in problem hoort
+
+ \subsection{Research question} \label{researchquestion}
  The main question that I will answer with this work is the following research question:
@@
  \end{center}
- % Alternatively, do my matcher add anything? i.e. does adding it to an ensemble of existing matchers increase performance?
-
- I will also investigate the following related but different question:
+ % Andere scriptie kijken wat hier nog moet?
+
+ \subsection{Hypothesis} \label{hypotheses}
+ % Waarom deze hypothesis? Sanna
+ % McCallum (hij is heel slim) zei het
+ % Waarom w2v? goeie resultaten recent
 
  \begin{center}
- \textit{
- Can distributed representations perform well in a domain it was not trained for?
- }
- \end{center}
-
- \subsection{Hypotheses} \label{hypotheses}
- \begin{center}
- \textit{This specific matcher that uses a distributed representation of concepts can find relationships between concepts in ontologies better than the best existing matchers.}
+ \textit{Matchers that use a distributed representation of concepts can find relationships between concepts in ontologies better than the best existing matchers.}
  \end{center}
@@
  \subsection{Overview} %TODO rewrite
- This thesis is structured as follows: firstly, I will describe the context of the problem, which includes the Semantic Web, Ontologies, Ontology matching and other relevant research.
-Secondly, I will outline the problem and research questions.
-Thirdly, I will describe the method I used to develop the solution, which includes the idea, challenges and considered implementations.
-The fourth section after this describes methods I used to evaluate the solution, with the fifth section showing the results, the sixth section the conclusions and the last and seventh section the discussion.
 
@@
  \subsubsection{Example} \label{example}
- An example of an ontology or a knowledge base of mice and men would be the following:
+ In this section I will give an example of a pair of anatomical ontologies with their alignment. This example will be used throughout this work.
+
+\begin{minipage}{0.3\textwidth}
  A mouse consists of the following body parts:
@@
  \end{itemize}
-
- They are connected as follows: IMAGE
-
+\end{minipage} \hfill
+\begin{minipage}{0.65\textwidth}
+ \begin{figure}[H]
+ \includegraphics[width=0.9\linewidth]{plots/muis1}
+ \label{mouse_example}
+ \caption{The different body parts of the mouse are connected as in this image.}
+ \end{figure}
+\end{minipage}
+
+\begin{minipage}{0.3\textwidth}
  Humans consist of:
@@
  \end{itemize}
-
- Humans and mice are connected as follows: MATCHING IMAGE
+\end{minipage} \hfill
+\begin{minipage}{0.7\textwidth}
+ \begin{figure}[H]
+ \includegraphics[width=0.7\linewidth]{plots/man}
+ \label{man_example}
+ \caption{The different body parts of the man are connected as in this image.}
+ \end{figure}
+\end{minipage}
+
+ \begin{figure}[H]
+ \includegraphics[width=0.7\linewidth]{plots/muisman}
+ \label{muis_man_example}
+ \caption{Humans and mice are connected as shown in this image.}
+ \end{figure}
 
@@
  \subsubsection{Multi-sense} \label{multisense}
+ %TODO Voorbeeld uit McCallum's slides kopieren en uitleggen
  Another interesting development is the multi-sense \emph{Word2vec}, which allows for multiple vector representations per word, depending on the number of different definitions a word has.
@@
  The data used comes from a list of data sets that the OAEI provides\cite{euzenat2013ontology}.
+% OAEI en kleine data common in OM.
+Vergelijkbaar met andere resultaten.
+Kleine datasets zijn logisch want: oude tak van sport.
+ % Ik heb gekeken naar DeepWalk (nieuwe tak van sport)(gebruikt ook NN) OOK kleine data.
  Every data set contains two ontologies that need to be aligned and a ground truth alignment.
 The goal is straightforward: find the alignment given only the ontologies and whichever outside resources are needed.
+
+ \subsubsection{Preprocessing} \label{preprocessing}
 
@@
  \section{Conclusion and discussion}
- In this section I will consider the research questions and hypotheses as formulated in Sections \ref{researchquestions} and \ref{hypotheses}.
+ In this section I will consider the research questions and hypotheses as formulated in Sections \ref{researchquestion} and \ref{hypotheses}.
 In the second part of this section, I will discuss the implications of these results.
@@
 
- %\subsection{Recap research questions} % Maak 'figure' van
+ %\subsection{Recap research question} % Maak 'figure' van
  %\subsection{Recap hypotheses}
  \subsection{Conclusions} \label{conclusions}
- The main research question from Section \ref{researchquestions} is
+ The main research question from Section \ref{researchquestion} is
  \begin{center}
@@
 The %TODO AP is between baseline en AML for both?
+
+ %Ik heb bewust gekozen voor kleine data zodat het te vergelijken was met andere matchers. Want iedereen in OM gebruikt kleine datasets.
+ %Deepwalk paper ook kleine data
+ %Misschien heb ik te weinig data gebruikt maar er is geen grote dataset met ground truth beschikbaar.
+ %Further research: grote dataset maken door LOD te pakken, 10% weg te gooien en kijken of je dat reconstruct. 
   \subsubsection{The system}
@@
 Since those three possibilities have been excluded, the most likely conclusion is last remaining possibility: the set of distributed embedding algorithms do not work well on Ontology data.
+
+  % Uit mijn onderzoek blijkt dat McCallum's algoritme niet werkt op SW.
+Als ik terugkijk naar zijn keynote, is dat wel logisch, want in zijn voorbeeld heeft hij een dataset gegeven waar de KBs toevallig dezelfde Named Entities hebben (perfect zijn).
+In de echte wereld is dit met de meeste data niet zo, helemaal in het SW omdat veel ambiguiteit door auatomatscih maken.
+
+ % Plaatje van mccallum matrix. Kijk, Steve heet Steven in alle drie de KBs. Dit is in het echt dus niet zo.
  \subsection{Future research}

### 2016-06-25 Paper/Draft.tex
Added paragraphs

@@
 These steps are also shown in Figure \ref{movies}.
-
+ \paragraph{}
  Firstly, search for movies that you like that are also playing this weekend.
@@
 You also have to filter the out time slots based on your availability, so you cross-reference the available movie showtimes with your agenda.
-
+ \paragraph{}
  Then onto the third and final step, getting friends to go with you.
@@
 Once you contact your friends, most of them do not respond as they are not online at that time or they do not want to fill out an availability poll or movie choices.
-
+ \paragraph{}
  Most of the time people will limit themselves to suboptimal options by avoiding these steps, considering only a few movies, cinemas, time slots and friends.
@@
 A ranking can be added based on how expensive the tickets are, how certain it is that you may like the movie, and other factors.
-
+ \paragraph{}
  The second step, cross-referencing the list of movies with cinema play times, would already be harder.
@@
 However, errors might occur because the local cinema labelled a sequel as "Movie II" whereas the list we have has it labelled as "Movie 2", for example.
-
+ \paragraph{}
  Checking an agenda to find an appropriate time would be easy if the times from the cinemas can be transformed to the same format as your agenda.
 If we are automating the process, we may be able to add more features, like changing standing appointments (of course incurring a penalty to the score of that time spot) and such.
-
+ \paragraph{}
  The last step, contacting friends can be done in one click.
@@
 Once this best time slot is chosen, everyone gets an invite to see the movie and once it is known who will go, a car pooling route is calculated and you can sit back an enjoy your Friday afternoon with no planning or scheduling required.
-
+ \paragraph{}
  The most amazing thing about this story, is that it is already possible with the current technology.
@@
 And algorithms to combine these pieces of information to make decisions already exist and work.
-
+ \paragraph{}
  Two things are required before this web of computers that communicate and understand, this Semantic Web, will come into existence.
@@
  In this section I will explain how the study came into existence.
-
+ \paragraph{}
  At the 14th International Semantic Web Conference McCallum presented his keynote on \emph{Representation and Reasoning with Universal Schema Embeddings}\cite{mccallumweblecture}.
@@
 McCallum discussed a new extension to the algorithm that allowed for homonyms and as such can deal with more ambiguous data\cite{mccallumweblecture}.
-
+ \paragraph{}
  McCallum plans on using these embeddings to predict new inter-knowledge base relations.
@@
 It is necessary to build the Semantic Web as soon as possible, as the amount of information on the Web is growing so fast it will be infeasible for humans to handle\cite{overload}.
-
+ \paragraph{}
  The core of the Semantic Web are Knowledge Bases with the corresponding Ontologies.
@@
 Therefore, it is save to say that efficient ontology matching will be very valuable.
-
+ \paragraph{}
  The most important goal of this study is to find an Ontology Matcher that is able to deal with ambiguous concepts.
@@
 Word Embeddings and especially multi-sense Word Embeddings should be able to handle a high amount of ambiguity, since multi-sense Word Embeddings are made to differentiate between different meanings of the same word.
-
+ \paragraph{}
  Normally, the raw text representation of words is used for matching, for example to calculate the string distance.
@@
  Calculating the distance between vectors can be done very efficiently, therefore ontology matching with distributed concept representations fits that efficiency criteria. 
-
+ \paragraph{}
  I believe the algorithms proposed in this study will work on new data without the need for redesigning.
@@
 This is also an improvement for the semantic web.
-
+ \paragraph{}
  This study should be done now, as ontology matching is already used in areas other than the semantic web.
@@
 If the proposed matching algorithm is better than the current algorithms, or at least improves the performance when used in ensemble with the current algorithms, it will be useful immediately in these situations, not just in the future, on the Semantic Web.
-
+ \paragraph{}
  In summary, Ontologies are the core of the I hope it is clear that ontology matching is an important area of study and that this study will contribute to it.
@@
 As a consequence, if two agents want to communicate in a given domain, they need to agree on the rules of that domain, or in other words, share the ontology of that domain.
-
+ \paragraph{}
  However, it is unlikely that a conversation only covers one domain.
@@
 Either you ensure that all possible combinations of domains are covered by an ontology, which means one ontology that covers all domains is required, or, alternatively, ontologies are combined on-the-fly.
-
+ \paragraph{}
  The first option, using one single ontology, is infeasible. This is due to the fact that inference and search time scales with Ontology size, %citaat
@@
 And since every interaction on the Semantic Web requires lookups in an Ontology, these lookups need to be fast.
-
+ \paragraph{}
  The second option, the one I address in this thesis, is the problem of combining ontologies from multiple domains.
@@
 %cite
-
+ \paragraph{}
  A recently developed model for word embedding may be used to deal with ambiguity.
@@
 These facts show that it may be possible to make an embedding model for Ontologies and use the word relatedness to combine Ontologies\cite{multisense}.
-
+  \paragraph{}
   \subsubsection{Language}
@@
  We have seen that when information from multiple domains needs to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged.
-
+ \paragraph{}
  If we want to merge two ontologies, we need to find the concepts from the different ontologies that are related by an 'is-same-as' or other rule.
-
+ \paragraph{}
  However, since the ontologies are made for different domains, the same concept can be represented by different labels in the two ontologies.
 This problem is called the synonymy problem, as synonyms are two words that refer to the same concepts.
-
+ \paragraph{}
  The opposite problem is called the homonymy problem, in which two concepts are represented by the same label.
 Since they have the same label, naive algorithms might align the concepts as being the same, when they are not.
-
+ \paragraph{}
  Then there is the problem of ambiguity, which encompasses many other problems.
 It encompasses the fact that some concepts are used wrongly by humans, but also the fact that some concepts are extremely similar, and may occur in the same context, but are still slightly different.
-
+ \paragraph{}
  The problem is:
@@
  The first three points will be shown in Section \ref{proofs}, whereas the last point is evaluated in Section \ref{conclusions}.
-
+ \paragraph{}
  This hypothesis is true for distributed representations matching in general if it is true for one distributed representation matcher.
@@
 On the current web the friend who shared the picture with the group has to be contacted directly by the commenter and then has to relay the message manually.
-
+ \paragraph{}
  Linking every piece of content to another allows not only humans to browse the internet, but also virtual agents, which can use this information to aid their users in ways that are simply impossible nowadays.
@@
 It would even be possible to have a question answering session on that specific topic, where the agent finds the answer to every question posed in the material that is linked to the topic.
-
+ \paragraph{}
  Another possibility is the scenario from the introduction \ref{intro}, where a user wanted to see a movie, and ordered his softbot, to find him a suitable time and movie to see.
 This was shown to reduce a lot of planning and allow for much more favourable decisions since many more variables can be taken into account.
-
+ \paragraph{}
  All of this is possible if the softbots can access all of the information reliably.
@@
 To allow softbots to access the same information that we can, the Semantic Web proposes to add a layer to the internet where all information is saved in a unified format that is unambiguous, robot-interpretable and can be used to store any type of knowledge.
-
+ \paragraph{}
  The Semantic Web has a current state, the technologies that have been developed, which will be discussed later. But more importantly the Semantic Web is a
@@
 Of course, then the goal is stretched and we should make more applications leveraging more information for more tasks.
-
+ \paragraph{}
  Ultimately, the goal is to leverage all information that is available to an entity on the internet to improve the lives of humans.
@@
 The personal agent should be able to predict the users need and provide the tools that can satisfy the need.
-
+ \paragraph{}
  To provide these tools to the user, an agent uses many different sources.
@@
 Only when those pieces are aligned can we talk of knowledge, of semantics.
-
+ \paragraph{}
  To summarize, the goal of the Semantic Web is to connect all online information to help humans.
@@
 technologies that came into existence through Semantic Web research and can eventually be used in the Semantic Web, but currently are not used for the Semantic Web since it does not exist yet.
-
+ \paragraph{}
  Semantic Web systems are currently divided into two groups: the systems that need high accuracy and the ones that need high recall.
@@
 This also impacted research, which did not focus on scaling ontologies until recently.
-
+ \paragraph{}
  The group that requires high recall use hand-crafted knowledge bases, created by experts, containing only facts that are accurate, verified and relevant.
@@
 Because of this, the knowledge bases are restricted to small domains, including some parts of medicine and cultural heritage\cite{byrne, le2002}.
-
+ \paragraph{}
  For the group that requires a high recall, or in other words a big amount of data, automated methods are required.
@@
 Often, these methods use crowd-sourcing to improve accuracy, using experts or the general public to suggest or check facts\cite{zhou2007}.
-
- On way the W3C is fighting ambiguity is to ensure very few different languages are used for ontologies and knowledge bases. The main languages W3C endorses are RDF, OWL and SKOS\cite{rdf, owl, skos}.
-
+ \paragraph{}
+ On way the W3C is fighting ambiguity is to ensure very few different languages are used for ontologies and knowledge bases.
+The main languages W3C endorses are RDF, OWL and SKOS\cite{rdf, owl, skos}.
+ \paragraph{}
  Large ontologies already exist, with the largest, Freebase, boasting almost two billion triples and the three hundred combined Large Open Data databases contain over thirty billion\cite{dbpedia, lod}.
 The LOD is simply a single alignment over many different knowledge bases.
-
+ \paragraph{}
  Applications include improved web searching, question answering, product comparison, context merging, data integration, decision support, translation, all the way up to the intelligent softbot mentioned earlier.
 \cite{schreiber, future}
-
+ \paragraph{}
  The many uses of ontology matching show that it is important to research all avenues that might improve ontology matching, as it will have a direct result in many other fields.
@@
  Earlier, ontologies were referred to as `a set of rules that determine what relations are allowed and required.' Now, the term will be defined more extensively, the standard format will be described and the uses of ontologies will be discussed.
-
+ \paragraph{}
  An ontology describes concepts as their relationships to other concepts.
@@
 The variants trade off levels of expressiveness versus computability.
-
+ \paragraph{}
  A relationship in OWL is written as follows:
@@
 Lastly, it allows merging of knowledge bases.
-
+ \paragraph{}
  Search can be optimized by taking into account constraints the ontology provides.
@@
 This allows a search algorithm to skip all professors when looking for people that might follow a certain course.
-
+ \paragraph{}
  Expanding the available information of a certain node can be done by taking into account \textit{positive} constraints of a concept.
@@
 Superclassing enables ontologies to store these types of information even more efficiently, allowing for enormous amounts of information to be extracted for every node without the need to store it all explicitly for that node.
-
+ \paragraph{}
  One important aspect of data bases is consistency.
@@
 In a knowledge base, these constraints are defined in the ontology.
-
+ \paragraph{}
  When two knowledge bases need to be merged, aligned or matched, instantiations that refer to the same thing need to be merged.
@@
 The name refers to the Platonic philosophy that all concepts are existing entities and can thus be perfectly captured in a definition.
-
+ \paragraph{}
  On the other end of the spectrum are the Aristotelian ontologies, which do not necessarily contain perfectly defined concepts, but rather concepts as we observe them.
 Aristotle disagreed with Plato's theory that concepts are existing things, and thus these ontologies are named after him\cite{aristotleplato}.
-
+ \paragraph{}
  Aristotelian ontologies have the advantage of being easier to create.
@@
 This would enable enormous ontologies and knowledge bases with the amount of data currently available and cheap mental labour with services like Amazon's Mechanical Turk.
-
+ \paragraph{}
  The advantage of a Platonic ontology would be the fact that every query would result in a fact, since the ontology itself is perfect.
 The disadvantage is that creating such an ontology is much more costly than an Aristotelian ontology, since every concept and constraint needs to be correct in all cases.
-
+ \paragraph{}
  Another way to represent this spectrum is the precision-recall trade-off.
@@
 Often, a combination of statistical methods with expert confirmation is used.
-
+ \paragraph{}
  Platonic ontologies are often used in areas where precision is important, like medicine, where lives depend on the information contained in the ontology and its knowledge base.
@@
 Some strategies also use extra steps like the extensional and semantic steps, which use vector space models and inference, respectively\cite{future}.
-
+ \paragraph{}
  Popular terminological strategies are WordNet comparison and edit distance.
@@
 Sometimes the matching needs to be very fast, for example when the ontologies are used in a search query which the user expects to be done in milliseconds.
-
+ \paragraph{}
  Online matching would allow for updates in a knowledge base to be represented in the alignments of that knowledge base.
 This would be required on any ontology that tracks changing knowledge, like stores, movie theatres and social media, for example.
-
+ \paragraph{}
  Based on the previous two points, we can state that it would also be useful to have different benchmarks to test those different types of challenges and matching systems.
 This would allow for better comparison of methods and better tracking of the improvements in the field.
-
+ \paragraph{}
  Since the Linked Open Data keeps growing, it, and other resources, should be used in matching.
@@
 The challenge is to all available ontologies and other sources rather than just WordNet.
-
+ \paragraph{}
  Matchers should be able to explain the results it produces, i.e.
@@
 Thirdly, it would allow researchers to improve the matching system because they are able to detect the source of errors.
-
+ \paragraph{}
  When these problems are solved, ontology matching has matured enough to be used in Semantic Web applications. Then it is merely the challenge to have the public adopt these technologies.
@@
 However, this is not useful for computers as these characters do not say anything about the meaning of the words, nor is it a representation that computers can quickly do calculations on.
-
+ \paragraph{}
  Many different representations have been proposed.
@@
 Also, the method requires many discrete documents to train on, which are not available in Ontology matching.
-
+ \paragraph{}
  The rest of this subsection will describe the latest word representation model which has very interesting results in NLP.
@@
 This semantic similarity property is very useful for ontology alignment, as parts of one ontology have to be aligned with parts of another ontology depending on their semantic relation.
-
+ \paragraph{}
  Skip-gram models work by teaching a 3-layer neural network to predict the context of a word.
@@
 This representation will later be used as the representation of the word.
-
+ \paragraph{}
  Then the representation is multiplied with another matrix to create the third layer, the output layer.
 The word representations and second matrix are optimized in such a way that the output layer is as close as possible to the one-hot encodings of the context.
-
+ \paragraph{}
  As a consequence words that occur in similar contexts will be represented similarly.
@@
 One example of such an extension is negative sampling, which is a step that teaches the network that randomly selected words should have non-similar representations.
-
+ \paragraph{}
  These extensions enable \emph{Word2vec} to be trained on large corpora and represent words in a way that is very useful in NLP.
 It is used as a language model in part-of-speech tagging and machine translation.
-
+ \paragraph{}
  Interestingly, the representations have been shown to contain semantic information too.
@@
 This means that gender is encoded in the vectors and other types of meaning may also be encoded.
-
+ \paragraph{}
  After the authors showed the usefulness of \emph{Word2vec}, many researchers developed new uses for the algorithm.
@@
 This idea sparked the second reason why I started investigating semantic word representations for Ontology matching, since current methods do not allow for disambiguation.
-
+ \paragraph{}
  For example, string matchers only look at the phrases representing the concepts, and as such do not care about semantics.
@@
  Factorie is a toolkit that contains a number of tools which includes word-embedding models \cite{git-factorie}. \cite{w2v}.
-
+ \paragraph{}
  Factorie provides a number of utilities for writing an algorithm in the shape of abstract classes with existing functionality, namely IO, parallelisation, quick parsing and command line argument parsing.
@@
 See \cite{scala}.
-
+ \paragraph{}
  The automated IO allows for quick reading in of the data set and secure saving of the trained model.
@@
 This also allows multiple models to be trained during a period where the experimenter is absent, after which he can still manually investigate the models.
-
+ \paragraph{}
  Parallelisation can massively improve training speed.
@@
 The number of parallel processes differs per device but modern personal computers already boast 8 parallel processors.
-
+ \paragraph{}
  Since I investigate many different implementations of the same algorithm, it should be easy to switch between these implementations at run-time without much effort.
@@
 For example, if one would like to obtain a list of all neighbours of a certain node, one can simply use the following Jena command:
+
  \lstset{language=Java}
@@
  It automatically gives all statements that have the given node as subject. In terms of graphs this is equal to obtaining all edges that go out of the given node.
-
+ \paragraph{}
  In Jena it is possible to obtain the label of any node, if it has it, by calling:
@@
 However, we only consider equality relationships and thus the label can be omitted.
-
+ \paragraph{}
  Then the question becomes: \textit{how do we measure similarity of concepts between ontologies?} As shown in \ref{strategies}, attempts have been made to model similarity of nodes as the string similarity of their labels.
@@
 The major problem with WordNet is that it is constructed by hand, and thus does not scale very well to new domains.
-
+ \paragraph{}
  The idea behind the algorithm introduced in this study is to find an alternative to WordNet that is at least as good in modelling semantic distance but scales to new domains.
@@
 This is only relevant, though, if the performance is equal to WordNet-based matchers.
-
+ \paragraph{}
  \emph{Word2vec} is an unsupervised method that implicitly maps words to a vector space that has been shown to contain semantic properties.
@@
 There are Z correspondences between the two ontologies.
-
+ \paragraph{}
  The ontology is structured as a hierarchical tree with the only label being \emph{subClassOf}.
@@
 If we only care about True Positives, the Jaccard similarity is a prime candidate for the performance measure.
-
+ \paragraph{}
  The Jaccard similarity is calculated as follows
@@
  i.e. the fraction of the true positives over the sum of the true positives and mistakes.
-
+ \paragraph{}
  The Jaccard similarity is a number between 0 and 1, with a higher number being better.
@@
 has a higher Jaccard similarity, is the better one.
-
+ \paragraph{}
  However, if we want to find out if an algorithm improves an ensemble, we calculate the improvement as follows:
@@
 In this case the solutions are $E\cup \{R\}$, where $R$ is an algorithm that generates random alignments\cite{fisher1925statistical}.
-
+ \paragraph{}
  It is in principle possible to weigh False Positives and False Negatives differently, but this is not done in practice.
@@
 %Aanpassen als ik 3e dataset heb.
-
+  \paragraph{}
  The algorithm has been run on multiple data sets with no significant difference in performance.
@@
 The system consists of a data loader, preprocessor, context extractor, the algorithm, the matcher and multiple visualizers.
-
+  \paragraph{}
   All other steps I have replaced by another piece of software that does the preprocessing, context extraction and the algorithm.
@@
 Since the results are the same as with my system, it can be concluded that the corresponding parts of my system work.
-
+  \paragraph{}
   The preprocessing works, as described in Section \ref{preprocessing}.
@@
 This is unlikely to contain errors.
-
+  \paragraph{}
   Since the visualizers work in parallel, errors in them would not cascade to the others, so they are all faulty or none of them are.
-
+  \paragraph{}
   As such, it is safe to conclude that the system has been thoroughly tested and is not faulty.
@@
   The context extraction for DeepWalk works, as described in Section \ref{sentences}.
-
+  \paragraph{}
   The context extraction of the pre-trained Word2vec consists of splitting up every label into multiple words which can be looked up.
@@
   The pre-trained model does not use any other form of context integration.
-
+  \paragraph{}
   For the Node2vec algorithms, the context extraction is more advanced.
@@
 For the algorithms that also use the edge labels for context, double the context size is expected.
-
+  \paragraph{}
   First, I obtained the number of edges from VOWLview\cite{vowlview}, an Ontology graphing program.

### 2016-06-25 Paper/Draft.tex
Fixed structured up to SW.Goal

@@
  \paragraph{}
- The first option, using one single ontology, is infeasible. This is due to the fact that inference and search time scales with Ontology size, %citaat
+ The first option, using one single ontology, is infeasible. This is due to the fact that inference and search time scales with Ontology size\cite{complexity},
  and the number of concepts that are needed on the Semantic Web is enormous.
@@
 Ambiguity means that similar words mean slightly different things, or a word might have multiple related meanings.
-%cite
  \paragraph{}
@@
  \subsection{Hypothesis} \label{hypotheses}
- % Waarom deze hypothesis? Sanna
- % McCallum (hij is heel slim) zei het
- % Waarom w2v? goeie resultaten recent
 
@@
  \subsection{The Semantic Web}
-  The first concept is the Semantic Web, also called Web 3.0, a vision of a Web that enhances the User Experience in ways that the current Web can not provide. 
- \subsubsection{The current Web}
-Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and limited interconnectivity.\footnote{For example, Facebook is a hub for sharing content with people you consider friends, but if you want to share that content with more people you will have to go to another hub, like imgur or Pinterest.} It is possible to link to content from other hubs using URLs, but this moves the user to another hub, rather than connecting the content present in the hubs.
-The Semantic Web, on the other hand, contains sources of \textit{information} that can be combined whenever the user needs it.
+  The first concept I will discuss is the Semantic Web, also called Web 3.0, a vision of a Web that enhances the User Experience in ways that the current Web can not provide.
+ \subsubsection{Progression of the Web}
+ The original Web connected authors to readers.
+It allowed authors to create content, mostly static websites.
+Readers, however, could not change anything, merely read the sites and click on links.
+In this iteration of the Web there was no interaction.
+%cite web1.0?
+ \paragraph{}
+ Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and interaction between users.
+However, there is only limited interconnectivity between those hubs\footnote{For example, Facebook is a hub for sharing content with people you consider friends, but if you want to share that content with more people you will have to go to another hub, like Imgur or Pinterest.}.
+%cite web2.0
+ It is possible to link to content from other hubs using URLs, but this moves the user to another hub, rather than connecting the content present in the hubs.
+ \paragraph{}
+ We are currently progressing towards Web 3.0, where not only users interact, but also virtual agents.
+The so-called Semantic Web contains sources of \textit{information} which can be combined whenever the user needs it.
+ If someone wants to find information on a certain topic, the virtual agent can collect all documents that are relevant to that topic, summarize each document in a way that is relevant to the search request and provide sources for every fact it finds.
+It would even be possible to have a question answering session on that specific topic, where the agent finds the answer to every question posed in the material that is linked to the topic.
+ \paragraph{}
+ Another possibility is the scenario from the introduction (Section \ref{intro}), where a user wanted to see a movie, and ordered his softbot, to find him a suitable time and movie to see.
+This was shown to reduce a lot of planning and allow for much more favourable decisions since many more variables can be taken into account.
+ \paragraph{}
+ All of this is possible if the softbots can access all of the information reliably.
+In the current Web, this is not possible, as all information is written in an ambiguous, unstructured format called natural language.
+To allow softbots to access the same information that we can, the Semantic Web proposes to add a layer to the internet where all information is saved in a unified format that is unambiguous, robot-interpretable and can be used to store any type of knowledge.
+ \paragraph{}
+  The Semantic Web also improves user interactivity by connecting sources of information.
 To stick with the social media example, a person can create a piece of content, say a picture of a tree, and share it with his friends.
@@
 On the current web the friend who shared the picture with the group has to be contacted directly by the commenter and then has to relay the message manually.
- \paragraph{}
- Linking every piece of content to another allows not only humans to browse the internet, but also virtual agents, which can use this information to aid their users in ways that are simply impossible nowadays.
-If someone wants to find information on a certain topic, the agent can collect all documents that are relevant to that topic, summarize each document in a way that is relevant to the search request and provide sources for every fact it finds.
-It would even be possible to have a question answering session on that specific topic, where the agent finds the answer to every question posed in the material that is linked to the topic.
- \paragraph{}
- Another possibility is the scenario from the introduction \ref{intro}, where a user wanted to see a movie, and ordered his softbot, to find him a suitable time and movie to see.
-This was shown to reduce a lot of planning and allow for much more favourable decisions since many more variables can be taken into account.
- \paragraph{}
- All of this is possible if the softbots can access all of the information reliably.
-In the current Web, this is not possible, as all information is written in an ambiguous, unstructured format called natural language.
-To allow softbots to access the same information that we can, the Semantic Web proposes to add a layer to the internet where all information is saved in a unified format that is unambiguous, robot-interpretable and can be used to store any type of knowledge.
- \paragraph{}
- The Semantic Web has a current state, the technologies that have been developed, which will be discussed later. But more importantly the Semantic Web is a
 
@@
 But humans will only accept the Semantic Web if it is useful to them, so the Semantic Web must show its applications and usefulness before it will be used in daily life.
+ \subsubsection{Workings} % Technisch uitleg. Veel voorbeelden, veel citaties. Hoe komt er info in. Hoe eruit. Hoe gaat een mens om met de SW (visie). Tags: grafen, ontologien,
+
  \subsubsection{Current state} %TODO This bit can use some work
- %TODO Cite Peter Mika (see Arjen notes 1)
  Currently, people are not aware of the Semantic Web.
@@
  \paragraph{}
- The group that requires high recall use hand-crafted knowledge bases, created by experts, containing only facts that are accurate, verified and relevant.
+ The group that requires high recall use hand-crafted knowledge bases, created by experts, containing only facts that are accurate, verified and relevant\cite{mika2015schema}.
 This method of creating a knowledge base does not scale very well and usually consists of fewer than ten thousand facts.

### 2016-06-26 Paper/Draft.tex
Explained Semantic Web Workings

@@
  %TODO spelling (database dataset)
+ %TODO volgorde bieb (APA?)
  \tableofcontents
@@
 These steps are also shown in Figure \ref{movies}.
- \paragraph{}
+
+ \begin{figure}[H]
+ \centering
+ \includegraphics[width=0.9\textwidth]{plots/select_movies}
+ \caption{To find the best movie, the shown movies need to be filtered by the ones you like and the showtimes need to be filtered by the times you are available.
+All remaining showtimes need to be cross-references with the preferences of your friends.}
+ \label{movies}
+ \end{figure}
+
  Firstly, search for movies that you like that are also playing this weekend.
@@
 You also have to filter the out time slots based on your availability, so you cross-reference the available movie showtimes with your agenda.
- \paragraph{}
+
  Then onto the third and final step, getting friends to go with you.
@@
 
- \begin{figure}
- \centering
- \includegraphics[width=0.9\textwidth]{plots/select_movies}
- \caption{To find the best movie, the shown movies need to be filtered by the ones you like and the showtimes need to be filtered by the times you are available.
-All remaining showtimes need to be cross-references with the preferences of your friends.
-This is a lot of work and can be automated on the Semantic Web.}
- \label{movies}
- \end{figure}
-
 The first step, finding movies that match two criteria would be considered trivial with modern technology.
@@
 A ranking can be added based on how expensive the tickets are, how certain it is that you may like the movie, and other factors.
- \paragraph{}
+
  The second step, cross-referencing the list of movies with cinema play times, would already be harder.
@@
 However, errors might occur because the local cinema labelled a sequel as "Movie II" whereas the list we have has it labelled as "Movie 2", for example.
- \paragraph{}
+
  Checking an agenda to find an appropriate time would be easy if the times from the cinemas can be transformed to the same format as your agenda.
 If we are automating the process, we may be able to add more features, like changing standing appointments (of course incurring a penalty to the score of that time spot) and such.
- \paragraph{}
+
  The last step, contacting friends can be done in one click.
@@
 Once this problem has been solved, the Semantic Web is technically possible and only needs to be socially accepted before it will become the norm.
-
+%cite microformats.org
+ %TODO per stap refereren naar plaatje
  \subsection{Motivation}
@@
  If some entities and relations have similar embeddings but are not known to co-occur, they are flagged as being similar.
-Similarly, if two entities or two relations have similar embeddings, they are likely referring to the same or similar things.
+Similarly, if two entities or two relations have similar embeddings, they are likely referring to the same or similar things, see Figure \ref{McCallum_matrix2}.
 This can be used to infer even more similarities by collaborative filtering.
@@
 
- The embeddings are optimized by a model called the skip-gram word embedding model\cite{w2v}, a neural network model that learns to predict the context of a word.
+ The embeddings are optimized by a model called the skip-gram word embedding model\cite{w2v}, a neural network model that learns to predict the context of a word, see Figure \ref{Skip-Gram-img}.
 McCallum discussed a new extension to the algorithm that allowed for homonyms and as such can deal with more ambiguous data\cite{mccallumweblecture}.
- \paragraph{}
- McCallum plans on using these embeddings to predict new inter-knowledge base relations.
-However, from they keynote it is clear that this technique should work with multiple Knowledge Bases as the Universal Schema is applied to a set of Knowledge Bases including Freebase, knowledge extracted from text and the TAC Knowledge Bases Population Track Dataset.
-This means that intra-knowledge base relations can also be predicted using the Word Embedding Tensor Factorisation technique.
- An example of an intra-knowledge base relation is shown in Figure \ref{merge_graph}.
-If these relations can be predicted, multiple knowledge bases can be aligned.
-Doing ontology alignment using these word embeddings is the goal of this work.
 
@@
 
+ McCallum plans on using these embeddings to predict new intra-knowledge base relations.
+However, from they keynote it is clear that this technique should work with multiple Knowledge Bases as the Universal Schema is applied to a set of Knowledge Bases including Freebase, knowledge extracted from text and the TAC Knowledge Bases Population Track Dataset.
+This means that inter-knowledge base relations can also be predicted using the Word Embedding Tensor Factorisation technique.
+
+ An example of an inter-knowledge base relation is shown in Figure \ref{merge_graph}.
+If these relations can be predicted, multiple knowledge bases can be aligned.
+Doing ontology alignment using these word embeddings is the goal of this work.
+ \paragraph{}
  Currently, knowledge base and ontology alignment techniques do not make use of embeddings.
-Since embedding models have good performance on intra-knowledge base relation prediction, they should also work on ontology alignment.
+Since embedding models have good performance on intra-knowledge base relation prediction, they should also work well on ontology alignment.
 
@@
 If the proposed matching algorithm is better than the current algorithms, or at least improves the performance when used in ensemble with the current algorithms, it will be useful immediately in these situations, not just in the future, on the Semantic Web.
- \paragraph{}
- In summary, Ontologies are the core of the I hope it is clear that ontology matching is an important area of study and that this study will contribute to it.
 
@@
 Lastly, I will describe the algorithm that this study is based on.
-
- \subsubsection{Semantic Web}
+ \paragraph{}
  On the Semantic Web, Ontologies are used to define knowledge\cite{fensel2001ontologies}.
@@
 However, recently research has been slowing to the point where there is little improvement.
-
- \subsubsection{Ontology Matching}
+ \paragraph{}
  One big problem in Ontology matching is the fact that in different domains, words can have different meanings.
@@
  \paragraph{}
-  \subsubsection{Language}
  Homonyms are two concepts that share a label, or in other words, a homonym is one word with multiple distinct meanings.
@@
  We have seen that when information from multiple domains needs to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged.
- \paragraph{}
  If we want to merge two ontologies, we need to find the concepts from the different ontologies that are related by an 'is-same-as' or other rule.
- \paragraph{}
  However, since the ontologies are made for different domains, the same concept can be represented by different labels in the two ontologies.
@@
   Matching ontologies and dealing with the ambiguity and homonymy contained in them.
-""
+"" %TODO mooier
 
@@
  \end{center}
- % Andere scriptie kijken wat hier nog moet?
 
@@
 In this iteration of the Web there was no interaction.
+See Figure \ref{web1}.
 %cite web1.0?
- \paragraph{}
- Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and interaction between users.
+
+ \begin{figure}[H]
+ \centering
+ \includegraphics[width=0.8\linewidth]{plots/pijl1}
+ \caption{The first iteration of the Web consisted of static content, written by authors and read by readers.}
+ \label{web1}
+ \end{figure}
+
+ Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and interaction between users, who can also add content, as in Figure \ref{web2}.
 However, there is only limited interconnectivity between those hubs\footnote{For example, Facebook is a hub for sharing content with people you consider friends, but if you want to share that content with more people you will have to go to another hub, like Imgur or Pinterest.}.
@@
  It is possible to link to content from other hubs using URLs, but this moves the user to another hub, rather than connecting the content present in the hubs.
- \paragraph{}
- We are currently progressing towards Web 3.0, where not only users interact, but also virtual agents.
+
+ \begin{figure}[H]
+ \centering
+ \includegraphics[width=0.8\linewidth]{plots/pijl2}
+ \caption{In the second iteration of the Web, readers have become users that can alter and add to the content found on the interactive hubs. This also allows users to interact with each other.}
+ \label{web2}
+ \end{figure}
+
+ We are currently progressing towards Web 3.0, where not only users interact, but also virtual agents, see Figure \ref{web3}.
 The so-called Semantic Web contains sources of \textit{information} which can be combined whenever the user needs it.
@@
 It would even be possible to have a question answering session on that specific topic, where the agent finds the answer to every question posed in the material that is linked to the topic.
- \paragraph{}
- Another possibility is the scenario from the introduction (Section \ref{intro}), where a user wanted to see a movie, and ordered his softbot, to find him a suitable time and movie to see.
+
+ \begin{figure}[H]
+ \centering
+ \includegraphics[width=0.8\linewidth]{plots/pijl3}
+ \caption{On the third iteration of the Web, virtual agents are also able to read and write content and interact with humans (through question answering as an example).
+Virtual agents may also work together.}
+ \label{web3}
+ \end{figure}
+
+ Another possibility on the Semantic Web is the scenario from the introduction (Section \ref{intro}), where a user wanted to see a movie, and ordered his softbot, to find him a suitable time and movie to see.
 This was shown to reduce a lot of planning and allow for much more favourable decisions since many more variables can be taken into account.
@@
 But humans will only accept the Semantic Web if it is useful to them, so the Semantic Web must show its applications and usefulness before it will be used in daily life.
- \subsubsection{Workings} % Technisch uitleg. Veel voorbeelden, veel citaties. Hoe komt er info in. Hoe eruit. Hoe gaat een mens om met de SW (visie). Tags: grafen, ontologien,
+ \subsubsection{Workings} % Technisch uitleg. Veel voorbeelden, veel citaties. Hoe komt er info in. Hoe eruit. Hoe gaat een mens om met de SW (visie). Tags: grafen, ontologien.
+ %Dit is belangrijk voor mij want... 
+ \begin{figure}[H]
+ \centering
+ \includegraphics[width=0.8\linewidth]{plots/SW}
+ \caption{An example of the Semantic Web represented as a graph of entities (in black) and relationships (in red). It contains many different kinds of entities, including countries and people.}
+ \label{semantic_web}
+ \end{figure}
+
+ The Semantic Web is one big graph of entities and relationships between those entities, containing information about, amongst others, people and countries as in Figure \ref{semantic_web}.
+
+ \begin{figure}[H]
+ \centering
+ \includegraphics[width=0.5\linewidth]{plots/kb}
+ \caption{New information to be added to the Semantic Web.}
+ \label{kb}
+ \end{figure}
+
+ If new information is added to the Semantic Web, a new concept or connection is added to this graph.
+In Figure \ref{kb} a whole set of related entities and their connections are shown.
+These entities are also connected to the rest of the Semantic Web graph so that it stays one connected web, as in Figure \ref{combine}.
+
+ \begin{figure}[H]
+ \centering
+ \makebox[\textwidth][c]{
+   \includegraphics[width=1.2\linewidth]{plots/combine}
+ }
+ \caption{The new information is connected to the rest of the Semantic Web by connecting the new entities with entities in the Semantic Web.}
+ \label{combine}
+ \end{figure}
+
+ \paragraph{}
+ This big graph covers many different domains, and every domain is covered by a part of the graph, a sub-graph.
+For example, all people are in the same sub-graph, as are countries and the recently added foods.
+Every such sub-graph is one Knowledge Base that covers that specific domain.
+See Figure \ref{kbs} for the Knowledge Bases in the example.
+
+ \begin{figure}[H]
+ \centering
+ \makebox[\textwidth][c]{
+   \includegraphics[width=1.2\linewidth]{plots/kb1}
+ }
+ \caption{The different sub-graphs in the Semantic Web graph. They are contained in different Knowledge Bases and connected by URIs.}
+ \label{kbs}
+ \end{figure}
+
+ To ensure that the Semantic Web is one big connected Web, the knowledge bases are connected by inter-knowledge base relations.
+The relations are made by referring to the URI of that entity.
+The URI consists of a link to the knowledge base and then the identifier of the entity.
+For example, the people are connected to their country of origin, so in the people Knowledge Base there is a reference from Obama to \emph{countries\#USA}.
+ \paragraph{}
+ In this paragraph I will explain the use of ontologies on the Semantic Web.
+Ontologies describe the rules by which the Knowledge Bases must play.
+For example, every food must have a country of origin, and those countries of origin need to be of the Country \emph{Class}.
+This rule enables search algorithms to limit search to the countries Knowledge Base, as it is the only Knowledge Base that contains countries\cite{whyontologies}.
+This is just one example of a constraint that improves the work of one system.
+There are many more reasons, for example adding the rule "all mothers are parents" allows inference systems to reason about richer information without having to explicitly write down every relationship.
+
+ \begin{figure}[H]
+ \centering
+ \makebox[\textwidth][c]{
+   \includegraphics[width=1.2\linewidth]{plots/vraag1}
+ }
+ \caption{}
+ \label{question_graph}
+ \end{figure}
+
+ There are many ways of interacting with the Semantic Web, but they all interact with the graph in some way.
+For example, a user can ask a question "What food does President Obama like?" Firstly, this question is converted into a format that can be used by a search system.
+Then, information from the ontologies is added so that the search can be performed more efficiently.
+Then the pattern is matched in the Semantic Web graph, listing all results.
+The results are then combined or filtered such that one answer pattern remains, and that pattern is converted to natural text.
+This process is depicted in Figure \ref{question_graph}.
+
+ \begin{figure}[H]
+ \centering
+ \makebox[\textwidth][c]{
+   \includegraphics[width=1.2\linewidth]{plots/vraag2}
+ }
+ \caption{}
+ \label{question_graph2}
+ \end{figure}
 
  \subsubsection{Current state} %TODO This bit can use some work
+ % Tip: google wie schreef Harry Potter
  Currently, people are not aware of the Semantic Web.

### 2016-06-26 Paper/Draft.tex
Added short captions

@@
  %TODO volgorde bieb (APA?)
+ %TODO \caption[DIT DOEN]{te lang}
  \tableofcontents
@@
  \includegraphics[width=0.9\textwidth]{plots/select_movies}
- \caption{To find the best movie, the shown movies need to be filtered by the ones you like and the showtimes need to be filtered by the times you are available.
+ \caption[Movie selection process]{To find the best movie, the shown movies need to be filtered by the ones you like and the showtimes need to be filtered by the times you are available.
 All remaining showtimes need to be cross-references with the preferences of your friends.}
@@
  \end{subfigure}
- \caption{The Universal Schema.
+ \caption[Universal Schema]{The Universal Schema.
 Every row and every column is represented by an embedding (in purple).
@@
  \end{subfigure}
- \caption{After the embeddings are learned, rows and columns with similar embeddings are connected (in light green).
+ \caption[Universal Schema predictions]{After the embeddings are learned, rows and columns with similar embeddings are connected (in light green).
  For example, the embeddings of Melinda \& Seattle and \emph{lives in} may have become very similar. In that case, the system connects the pair with that relation.}
@@
  \label{Skip-Gram-img}
- \caption{The embedding of a row (in pink) is optimized to be close to its context embeddings (in purple) but far away from other embeddings (in red).}
+ \caption[Skip-Gram Model]{The embedding of a row (in pink) is optimized to be close to its context embeddings (in purple) but far away from other embeddings (in red).}
  \end{figure}
@@
  \includegraphics[width=0.8\linewidth]{plots/graaf}
- \caption{ Similar to how the embeddings are used to predict relations within an ontology, ontology matching can be done by predicting relations between two ontologies.
+ \caption[Ontology Matching graph example]{Similar to how the embeddings are used to predict relations within an ontology, ontology matching can be done by predicting relations between two ontologies.
 For example, since Gates and Bill will have very similar sets of embeddings (as their contexts are very similar) the system will recognise they are the same entity.}
@@
 
- The first three points will be shown in Section \ref{proofs}, whereas the last point is evaluated in Section \ref{conclusions}.
  \paragraph{}
@@
  \includegraphics[width=0.8\linewidth]{plots/pijl1}
- \caption{The first iteration of the Web consisted of static content, written by authors and read by readers.}
+ \caption[Web 1.0]{The first iteration of the Web consisted of static content, written by authors and read by readers.}
  \label{web1}
@@
  \includegraphics[width=0.8\linewidth]{plots/pijl2}
- \caption{In the second iteration of the Web, readers have become users that can alter and add to the content found on the interactive hubs. This also allows users to interact with each other.}
+ \caption[Web 2.0]{In the second iteration of the Web, readers have become users that can alter and add to the content found on the interactive hubs.
+This also allows users to interact with each other.}
  \label{web2}
@@
  \includegraphics[width=0.8\linewidth]{plots/pijl3}
- \caption{On the third iteration of the Web, virtual agents are also able to read and write content and interact with humans (through question answering as an example).
+ \caption[Web 3.0]{On the third iteration of the Web, virtual agents are also able to read and write content and interact with humans (through question answering as an example).
 Virtual agents may also work together.}
@@
  \includegraphics[width=0.8\linewidth]{plots/SW}
- \caption{An example of the Semantic Web represented as a graph of entities (in black) and relationships (in red). It contains many different kinds of entities, including countries and people.}
+ \caption[Semantic Web graph]{An example of the Semantic Web represented as a graph of entities (in black) and relationships (in red).
+It contains many different kinds of entities, including countries and people.}
  \label{semantic_web}
@@
  \includegraphics[width=0.5\linewidth]{plots/kb}
- \caption{New information to be added to the Semantic Web.}
+ \caption[Knowledge Base graph]{New information to be added to the Semantic Web.}
  \label{kb}
@@
  }
- \caption{The new information is connected to the rest of the Semantic Web by connecting the new entities with entities in the Semantic Web.}
+ \caption[Linking the Knowledge Base]{The new information is connected to the rest of the Semantic Web by connecting the new entities with entities in the Semantic Web.}
  \label{combine}
@@
  }
- \caption{The different sub-graphs in the Semantic Web graph. They are contained in different Knowledge Bases and connected by URIs.}
+ \caption[Semantic Web Knowledge Base view]{The different sub-graphs in the Semantic Web graph. They are contained in different Knowledge Bases and connected by URIs.}
  \label{kbs}
@@
  }
- \caption{}
+ \caption[Graph question example]{The question posed in a) is converted to a query pattern b).
+Ontology information is added in c).
+The result is found after pattern matching in d) and then converted to a natural language answer in e).}
  \label{question_graph}
@@
  There are many ways of interacting with the Semantic Web, but they all interact with the graph in some way.
-For example, a user can ask a question "What food does President Obama like?" Firstly, this question is converted into a format that can be used by a search system.
+For example, a user can ask a question "What is Obama's favorite food?" Firstly, this question is converted into a format that can be used by a search system.
 Then, information from the ontologies is added so that the search can be performed more efficiently.
@@
  }
- \caption{}
+ \caption[Graph biography example]{Similarly to a question with a single answer, the question in a) is converted to the pattern in b).
+The answers that match b) are combined in c) and converted to natural language in d).}
  \label{question_graph2}
  \end{figure}
+
+ More complex question can be posed, although they do not need to be longer.
+If the question can be mapped to more parts of the Semantic Web, the answer will be longer.
+In this case all knowledge of Barack Obama is extracted, combined and converted into an answer.
 
@@
  \label{mouse_example}
- \caption{The different body parts of the mouse are connected as in this image.}
+ \caption[Mouse Ontology]{The different body parts of the mouse are connected as in this image.}
  \end{figure}
@@
  \label{man_example}
- \caption{The different body parts of the man are connected as in this image.}
+ \caption[Human Ontology]{The different body parts of the man are connected as in this image.}
  \end{figure}
@@
  \label{muis_man_example}
- \caption{Humans and mice are connected as shown in this image.}
+ \caption[Aligned Ontologies]{Humans and mice are connected as shown in this image.}
  \end{figure}
@@
   \subsection{Data}
+  % Uitleggen wat het verschil is en dus waarom handig in onderzoek (verschillen in grootte structuur en labels? zie conclusie)
  The data used comes from a list of data sets that the OAEI provides\cite{euzenat2013ontology}.
@@
 
+ % Hier de pipeline omschrijven zoals in discussie.system
+
  \newpage
@@
    \includegraphics[width=\textwidth]{plots/untrained_ROC}
-   \caption{The precision and recall trade-off for the results of the untrained Node2vec. $AP = 0.04194$}
+   \caption[Precision-recall curve untrained mice]{The precision and recall trade-off for the results of the untrained Node2vec. $AP = 0.04194$}
    \label{ROC_untrained}
@@
    \includegraphics[width=\textwidth]{plots/Generic_ROC}
-   \caption{The precision and recall trade-off for the results of the Word2vec algorithm. $AP: 0.04636$}
+   \caption[Precision-recall curve pre-trained mice]{The precision and recall trade-off for the results of the Word2vec algorithm. $AP: 0.04636$}
    \label{ROC_generic}
@@
    \includegraphics[width=\textwidth]{plots/trained_ROC}
-   \caption{The precision and recall trade-off for the results of the bidirectional Node2vec. $AP = 0.04198$}
+   \caption[Precision-recall curve trained mice model]{The precision and recall trade-off for the results of the bidirectional Node2vec. $AP = 0.04198$}
    \label{ROC_trained}
@@
    \includegraphics[width=\textwidth]{plots/Alternative_ROC}
-   \caption{The precision and recall trade-off for the results of the alternative DeepWalk algorithm. $AP = 0.04193$}
+   \caption[Precision-recall curve DeepWalk mice]{The precision and recall trade-off for the results of the alternative DeepWalk algorithm. $AP = 0.04193$}
    \label{ROC_alternative}
@@
   Generic & 0.4245\\
-  \textbf{AML} & \textbf{0.94}\\ %http://disi.unitn.it/~pavel/om2015/papers/om2015_proceedings.pdf#page=125
+  \textbf{AML} & \textbf{0.94}\\ %http://disi.unitn.it/~pavel/om2015/
+  %papers/om2015_proceedings.pdf#page=125
   \end{tabular}
-  \caption{The $F_1$-scores for the different matchers for the mice dataset}
+  \caption[$F_1$ mice]{The $F_1$-scores for the different matchers for the mice dataset}
   \label{fscores}
@@
  \section{Conclusion and discussion}
- In this section I will consider the research questions and hypotheses as formulated in Sections \ref{researchquestion} and \ref{hypotheses}.
-In the second part of this section, I will discuss the implications of these results.
+ In this section I will draw conclusions from the results, answer the research question and give a verdict on the hypothesis.
+In the second part of this section I will discuss these conclusions.
 In the third and last part of the section, I will describe a few avenues that might be interesting to explore further, including a number of implementations I did not consider and why.
@@
  \subsection{Conclusions} \label{conclusions}
- The main research question from Section \ref{researchquestion} is
+
+ The goal of this study was to answer the research question from Section \ref{researchquestion}:
  \begin{center}
@@
 
- The results from all the different evaluation measures are in agreement.
-From those results we can conclude that the distributed word representations system is currently \textbf{not} able to find relationships between concepts in ontologies better than existing matchers.
+ To answer this question I have examined the following points from Section \ref{hypotheses}:
+
+\paragraph{The algorithm uses distributed representations of concepts}
+\paragraph{The algorithm finds relationships between concepts in ontologies}
+\paragraph{The algorithm has been compared to the currently best matchers}
+\paragraph{The algorithm performs better}
+ I performed empirical research where I made the algorithm, applied it to different datasets and compared the results with existing methods.
+
+ Because the last point is not true, the answer is not in agreement with my hypothesis from Section \ref{hypotheses}:
+
+ \begin{center}
+ \textit{Matchers that use a distributed representation of concepts can find relationships between concepts in ontologies better than the best existing matchers.}
+ \end{center}
+
+The results from all the different evaluation measures are in agreement. From those results we can conclude the following:
+
+ \begin{center}
+ \textit{
+ The distributed word representations system is currently \textbf{not} able to find relationships between concepts in ontologies better than existing matchers.
+ }
+ \end{center}
 
@@
   The system underperforms on the provided data. This can have one or more of the following four potential causes:
-  \begin{itemize}
+  \begin{enumerate}
   \item The data breaks the considered algorithms.
@@
   \item The considered algorithms are not suited for Ontology matching.
-  \end{itemize}
+  \end{enumerate}
 
@@
 If potential cause one is the case, the study is invalid and should be repeated on one or more different data sets.
-If potential cause two is the actual cause or potential cause three is the actual cause, the study is invalid and the results should not be published until the system is fixed and the results do not change.
+If either potential cause two or three is the actual cause, the study is invalid and the results should not be published until the system is fixed and the results do not change.
 If it is the case that none of these three potential causes is the actual cause, by elimination the fourth potential cause must be the actual cause.
@@
   \subsubsection{The data}
-  If the data set is the cause of the underperformance, logically switching to another data set will improve performance over the baseline.
+  If the data set is the cause of the underperformance, switching to another data set will improve performance over the baseline.
 Possible reasons the data set causes underperformance include the data set being too small, labels that are not useful or the data set having a structure that does not work with the algorithm.
@@
   \paragraph{}
- The algorithm has been run on multiple data sets with no significant difference in performance.
+ The algorithm has been run on multiple data sets which are different.
+Despite that there is no significant difference in performance.
 For example, compare the Average precision for the medical dataset with the anatomy dataset.
 The %TODO AP is between baseline en AML for both?
+ So the data does not cause the underperformance of the system.
 
@@
   \subsubsection{The system}
-  If any of the steps in the software system contains an error, the whole system may fail.
+  % Sectie maken waar ik het systeem beschrijf
+  If any of the steps in the software system contains an error, the whole system would fail.
 This could cause all algorithms to learn badly or the results to be misinterpreted.
 The system consists of a data loader, preprocessor, context extractor, the algorithm, the matcher and multiple visualizers.
-  \paragraph{}
-  All other steps I have replaced by another piece of software that does the preprocessing, context extraction and the algorithm.
-The results are titled "alternative DeepWalk" in the results Section.
-Since that software has been used in other projects and is written by someone else, it can be concluded that it works.
-Since the results are the same as with my system, it can be concluded that the corresponding parts of my system work.
-  \paragraph{}
+If all of these systems work properly, the system is not the reason for the underperformance.
+
+  \begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{plots/programdiagram}
+  \label{program}
+  \caption[Program diagram]{The program is structured in sequence, except the visualisers which are structured in parallel.}
+  \end{figure}
+
+  \paragraph{Data loading}
+  \paragraph{Preprocessing}
   The preprocessing works, as described in Section \ref{preprocessing}.
@@
 This is unlikely to contain errors.
-  \paragraph{}
+  \paragraph{Matcher}
+  \paragraph{Statistics and visualisation}
   Since the visualizers work in parallel, errors in them would not cascade to the others, so they are all faulty or none of them are.
   \paragraph{}
-  As such, it is safe to conclude that the system has been thoroughly tested and is not faulty.
+  Since every part works, the system is not faulty. %TODO kan beter
+
+  Secondly, all steps have been replicated by another piece of software that does the data loading, preprocessing, context extraction and the algorithm.
+The results of that system are titled "alternative DeepWalk" in the results Section.
+As system has been used in other projects and is written by someone else, it can be concluded that it works.
+This is more proof that the system indeed works as intended.
+
   \subsubsection{Context extraction}
-  The context extraction for DeepWalk works, as described in Section \ref{sentences}.
-  \paragraph{}
-  The context extraction of the pre-trained Word2vec consists of splitting up every label into multiple words which can be looked up.
-For example "Adrenal vein" can be split up into "Adrenal" and "vein".
-  The pre-trained model does not use any other form of context integration.
+  There are different context extractors for some of the different algorithms.
+I will research every one: the sentence generator of DeepWalk, the context extractor for the graph-based models and the context extractor for the pre-trained model.
+If all three work well, the context extractors are not the cause of the underperformance.
+  \paragraph{}
+  The context extractor for DeepWalk works as generates sentences as described in Section \ref{sentences}.
+Since the sentences are generated properly and DeepWalk only requires sentences, the context extraction for DeepWalk works.
   \paragraph{}
@@
 For the algorithms that also use the edge labels for context, double the context size is expected.
+  \paragraph{}
+  The context extraction of the pre-trained Word2vec consists of splitting up every label into multiple words which can be looked up.
+For example "Adrenal vein" can be split up into "Adrenal" and "vein".
+  The pre-trained model does not use any other form of context integration.
   \paragraph{}
@@
   \end{tabular}
-  \caption{The number of edges compared to show that edge parsing was successful.}
+  \caption[Edge comparison]{The number of edges compared to show that edge parsing was successful.}
   \label{edgecounts}

### 2016-07-01 Paper/Draft.tex
Did some stuff yesterday but did not commit. Also, moved system check

@@
  \usepackage{subcaption}
-
- \title{Ontology Matching with word2vec}
+ \usepackage{multirow}
+
+ \title{Graphs of Mice and Men}
+ %subtitle{Matching ontologies with distributed word embeddings}
  \author{Harmen Prins}
@@
  \maketitle
+
+ \makebox[\textwidth][c]{
+ \includegraphics[width=1.35\textwidth]{plots/miceman}
+ }\footnote{Credit: Sanna Dinh}
  \newpage
@@
  %TODO volgorde bieb (APA?)
- %TODO \caption[DIT DOEN]{te lang}
+ %TODO Results interpretation: uitleg waarom hoger en lager
+ %TODO Plaatje VOWL
+ %TODO Verbeteringen discussieren
+ %TODO 
  \tableofcontents
  \newpage
+
+ %Vragen
+ % Hypothese waarom ik dat denk?
+ % extra hypothese
 
@@
 The Universal Schema uses two steps.
-Firstly, the system learns embeddings of entities and relations found in text and Knowledge Bases\cite{univeralschema}, see Figure \ref{McCallum_matrix}.
+Firstly, the system learns embeddings of entities and relations found in text and Knowledge Bases\cite{universalschema}, see Figure \ref{McCallum_matrix}.
 Secondly, these embeddings are then used to predict new relations for the knowledge bases.
@@
  \includegraphics[width=0.8\textwidth]{plots/Skip-Gram}
+ \caption[Skip-Gram Model]{The embedding of a row (in pink) is optimized to be close to its context embeddings (in purple) but far away from other embeddings (in red).}
  \label{Skip-Gram-img}
- \caption[Skip-Gram Model]{The embedding of a row (in pink) is optimized to be close to its context embeddings (in purple) but far away from other embeddings (in red).}
  \end{figure}
@@
  McCallum plans on using these embeddings to predict new intra-knowledge base relations.
-However, from they keynote it is clear that this technique should work with multiple Knowledge Bases as the Universal Schema is applied to a set of Knowledge Bases including Freebase, knowledge extracted from text and the TAC Knowledge Bases Population Track Dataset.
+However, from the keynote it is clear that this technique should work with multiple Knowledge Bases as the Universal Schema is applied to a set of Knowledge Bases including Freebase, knowledge extracted from text and the TAC Knowledge Bases Population Track Dataset.
 This means that inter-knowledge base relations can also be predicted using the Word Embedding Tensor Factorisation technique.
@@
 Secondly, it describes the data used to test the system.
-The third part describes all different implementations of the system.
+The third part describes the whole system, including all different implementations of the algorithm and a system check to ensure valid results.
 The fourth and last part describes the evaluation criteria.
@@
 
+ \subsection{System check}
+ To ensure the results are valid, I ran a system check. The check is designed to detect the following conditions.
+  \begin{enumerate}
+  \item The data breaks the considered algorithms.
+  \item There are bugs in the developed system unrelated to the algorithms.
+  \item The considered context extraction does not work.
+  \end{enumerate}
+
+  I will investigate all three to ensure they cannot be the cause of bad results and as a sanity check to prevent confirmation bias.
+  If potential cause one is the case, the study is invalid and should be repeated on one or more different data sets.
+If either potential cause two or three is the actual cause, the study is invalid and the results should not be published until the system is fixed and the results do not change.
+If it is the case that none of these three potential causes is the possible, the results are valid, the results reflect the performance of the algorithm and valid conclusions can be drawn from this study.
+
+  \subsubsection{The data}
+  If the data set is broken, switching to another data set will substantially change performance.
+Of course, different data sets are inherently unequal in their difficulty.
+Therefore I will check the performance relative to the baseline and the best known algorithm.
+If it performs similarly relative to those references, it can be concluded that the data works as intended.
+
+  Possible reasons for the data causing bad results include the data set being too small, labels that are not useful or the data set having a structure that does not work with the algorithm.
+For example, the pre-trained \emph{Word2vec} model is expected to work better on a data set that has commonly used words as labels.
+%TODO sowieso aanpassen maar ook aanpassen als ik 3e dataset heb.
+  \paragraph{}
+ The algorithm has been run on multiple data sets which are different.
+Despite that there is no significant difference in performance.
+For example, compare the Average precision for the medical dataset with the anatomy dataset.
+The [...] %TODO AP is between baseline en AML for both?
+ So the data does not cause the underperformance of the system.
+
+ %Ik heb bewust gekozen voor kleine data zodat het te vergelijken was met andere matchers. Want iedereen in OM gebruikt kleine datasets.
+ %Deepwalk paper ook kleine data
+ %Misschien heb ik te weinig data gebruikt maar er is geen grote dataset met ground truth beschikbaar.
+ %Further research: grote dataset maken door LOD te pakken, 10% weg te gooien en kijken of je dat reconstruct. 
+  \subsubsection{The system}
+  Since the system parts are connected in sequence, if any of the steps in the software system contains an error, the whole system fails.
+This could cause all algorithms to learn badly or the results to be misinterpreted.
+The system consists of a data loader, preprocessor, context extractor, the algorithm, the matcher and multiple visualizers.
+If all of these systems work properly, the system is not the reason for the underperformance.
+I will analyse every part except for the context extractor, which will be analysed in the next section.
+
+  \begin{figure}[H]
+  \includegraphics[width=0.9\textwidth]{plots/programdiagram}
+  \label{program}
+  \caption[Program diagram]{The program is structured in sequence, except the visualisers which are structured in parallel.}
+  \end{figure}
+
+  \paragraph{Preprocessing}
+%  The preprocessing works as described in Section \ref{preprocessing}. 
+  \paragraph{Matcher}The matcher is a simple KD-tree that finds the nearest neighbours of every node in the opposing Ontology. This is unlikely to contain errors.
+  \paragraph{Data loading}
+  Since the preprocessing and context extraction works, we can conclude that the data is also loaded properly.
+  \paragraph{Statistics and visualisation}
+  Since the visualizers work in parallel, errors in them would not cascade to the others, so they are all faulty or none of them are.
+  \paragraph{}
+  Since every part works, the system is not faulty. %TODO kan beter
+
+  Secondly, as an extra measure, the following steps have been replicated by another piece of software: the data loader, preprocessor, context extractor and the algorithm.
+The results of that system are titled "alternative DeepWalk" in the results Section.
+As this system has been used in other projects and is written by someone else, if the results match the ones from this study, the system from this study works.
+
+  \subsubsection{Context extraction}
+  There are different context extractors for some of the different algorithms.
+I will research every one: the sentence generator of DeepWalk, the context extractor for the graph-based models and the context extractor for the pre-trained model.
+If all three work well, the context extractors are not the cause of the underperformance.
+  \paragraph{}
+  The context extractor for DeepWalk works as generates sentences as described in Section \ref{sentences}.
+Since the sentences are generated properly and DeepWalk only requires sentences, the context extraction for DeepWalk works.
+  \paragraph{}
+  For the Node2vec algorithms, the context extraction is more advanced.
+All edges are extracted from the Ontology using Jena.
+Then, for every node the context is decided as every node it has an edge with.
+In the case of the bidirectional algorithm, both outgoing and ingoing edges count as being connected, whereas in the monodirectional algorithm only outgoing edges count as the connectedness.
+For the algorithms that also use the edge labels for context, double the context size is expected.
+  \paragraph{}
+  The context extraction of the pre-trained Word2vec consists of splitting up every label into multiple words which can be looked up.
+For example "Adrenal vein" can be split up into "Adrenal" and "vein".
+  The pre-trained model does not use any other form of context integration.
+  \paragraph{}
+  First, I obtained the number of edges from VOWLview\cite{vowlview}, an Ontology graphing program, which looks like Figure \ref{vowlfig}.
+This was necessary since the creators of the data did not share how many edges were in the database.
+With the actual number of edges, obtained, it is possible to compare them with the number of edges found.
+If these match, the context extraction works.
+
+  \begin{figure}
+  \includegraphics[width=0.7\textwidth]{vowlview}
+  \caption[]{}
+  \label{vowlfig}
+  \end{figure}
+
+  \begin{table}[H]
+  \caption[Edge comparison]{The number of edges compared to show that edge parsing was successful.}
+  \label{edgecounts}
+  \begin{tabular}{l|ll|ll}  
+  & \multicolumn{2}{c}{\#edges mice} & \multicolumn{2}{c|}{\#edges humans}\\
+  Algorithm & expected & actual & expected & actual\\
+  \hline
+  \textbf{Truth*} & \multicolumn{2}{c|}{\textbf{1810}} & \multicolumn{2}{c}{\textbf{3780}} \\
+  Monodirectional & 1810 & 1807 & 3780 & 3761\\
+  Bidirectional & 3620 & 3614 & 7560 & 7522\\
+  \end{tabular}
+  \end{table}
+
+  Since the expected number of edges and actual number of edges are very similar, we can conclude that the context extraction works.
+The difference can be explained by oddities in the VOWLview representation, as it contains edges that are not relevant to the ontology such as in Figure \ref{thing_edges}.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.6\textwidth]{plots/thing_edges}
+  \caption[Addition edges example]{An example of two edges that VOWLview renders that are not relevant to ontology matching.}
+  \label{thing_edges}
+  \end{figure}
+
+  \subsubsection{The algorithm}
+  At the beginning of this section, I reasoned that there are three possible causes of system failure, namely, bad data, bad code and bad context extraction.
+I have shown that all three are unlikely to cause problems.
+Since those three possibilities have been excluded, it is certain that the results of this study are actual results.
+
+ \subsubsection{Example: DeepWalk sentences} \label{sentences}
+
  \newpage
@@
 $Al=\{a_1,..,a_n\}$ and $T=\{a'_1,..,a'_m\}$, then the True Positives $TP=\{a|a\in Al, a\in T\}$, False Positives $FP=\{a|a\in Al, a\notin T\}$ and False Negatives $FN=\{a|a\in T, a\notin Al\}$ determine the performance of the alignment.
+
+ \paragraph{Jaccard similarity}
  The True Negatives do not matter, as there are extremely many, and the goal of ontology matching is to find True Positives.
 If we only care about True Positives, the Jaccard similarity is a prime candidate for the performance measure.
- \paragraph{}
+
  The Jaccard similarity is calculated as follows
@@
 
+ % Comparing the results.
+We want to compare to a baseline to ensure proper interpretation of the results.
+However, to test the hypothesis it is also required to compare the results to the best scoring algorithm on the same data set.
+
  \newpage
@@
 
- %TODO F measure noteren op pieken. Dan confidence vs F-measure bespreken in interpretation.
+ %TODO F-pieken aanwijzen. Dan confidence vs F-measure bespreken in interpretation.
  % Wat is de threshold van AML?
@@
   \begin{table}[H]
-  \begin{tabular}{l|l}
-  \textbf{Matcher} & \textbf{$F_1$-score}\\
+  \caption[$F_1$ mice]{The $F_1$-scores for the different matchers for the mice dataset compared to the result of AML at OAEI 2015 \cite{oaei2015}}
+  \label{fscores}
+  \begin{tabular}{l|ll}
+  \multirow{2}{*}{\textbf{Matcher}} & \multicolumn{2}{c}{\textbf{$F_1$-score}} \\
+  & Anatomy & Medical\\
   \hline
-  Alternative & 0.4244\\
-  Bidirectional & 0.4245\\
-  Untrained & 0.4245\\
-  Generic & 0.4245\\
-  \textbf{AML} & \textbf{0.94}\\ %http://disi.unitn.it/~pavel/om2015/
+  Alternative & 0.6372 & 0.2494 \\
+  Bidirectional & 0.8432 & 0.4946 \\
+  Label match + Random & 0.6926 & 0.3875 \\
+  Generic & 0.6372 & 0.2419 \\
+  \textbf{AML} & \textbf{0.94} & \textbf{0.81} \\ %http://disi.unitn.it/~pavel/om2015/
   %papers/om2015_proceedings.pdf#page=125
   \end{tabular}
-  \caption[$F_1$ mice]{The $F_1$-scores for the different matchers for the mice dataset}
-  \label{fscores}
   \end{table}
-  \subsection{Jaccard}
-  TBD
+  %\subsection{Jaccard}
+  %TBD
   \subsection{Examples to illustrate the differences}
@@
  \subsection{Discussion}
-  The system underperforms on the provided data. This can have one or more of the following four potential causes:
-  \begin{enumerate}
-  \item The data breaks the considered algorithms.
-  \item There are bugs in the developed system unrelated to the algorithms.
-  \item The considered context extraction does not work.
-  \item The considered algorithms are not suited for Ontology matching.
-  \end{enumerate}
-
-  I will investigate all four of these causes to see which is the most likely.
-If potential cause one is the case, the study is invalid and should be repeated on one or more different data sets.
-If either potential cause two or three is the actual cause, the study is invalid and the results should not be published until the system is fixed and the results do not change.
-If it is the case that none of these three potential causes is the actual cause, by elimination the fourth potential cause must be the actual cause.
-In that case the study is valid and it will be possible to draw the final conclusion.
-
-  \subsubsection{The data}
-  If the data set is the cause of the underperformance, switching to another data set will improve performance over the baseline.
-Possible reasons the data set causes underperformance include the data set being too small, labels that are not useful or the data set having a structure that does not work with the algorithm.
-For example, the pre-trained \emph{Word2vec} model is expected to work better on a data set that has commonly used words as labels.
-%Aanpassen als ik 3e dataset heb.
-  \paragraph{}
- The algorithm has been run on multiple data sets which are different.
-Despite that there is no significant difference in performance.
-For example, compare the Average precision for the medical dataset with the anatomy dataset.
-The %TODO AP is between baseline en AML for both?
- So the data does not cause the underperformance of the system.
-
- %Ik heb bewust gekozen voor kleine data zodat het te vergelijken was met andere matchers. Want iedereen in OM gebruikt kleine datasets.
- %Deepwalk paper ook kleine data
- %Misschien heb ik te weinig data gebruikt maar er is geen grote dataset met ground truth beschikbaar.
- %Further research: grote dataset maken door LOD te pakken, 10% weg te gooien en kijken of je dat reconstruct. 
-  \subsubsection{The system}
-  % Sectie maken waar ik het systeem beschrijf
-  If any of the steps in the software system contains an error, the whole system would fail.
-This could cause all algorithms to learn badly or the results to be misinterpreted.
-The system consists of a data loader, preprocessor, context extractor, the algorithm, the matcher and multiple visualizers.
-If all of these systems work properly, the system is not the reason for the underperformance.
-
-  \begin{figure}[H]
-  \includegraphics[width=0.9\textwidth]{plots/programdiagram}
-  \label{program}
-  \caption[Program diagram]{The program is structured in sequence, except the visualisers which are structured in parallel.}
-  \end{figure}
-
-  \paragraph{Data loading}
-  \paragraph{Preprocessing}
-  The preprocessing works, as described in Section \ref{preprocessing}.
-The matcher is a simple KD-tree that finds the nearest neighbours of every node in the opposing Ontology.
-This is unlikely to contain errors.
-  \paragraph{Matcher}
-  \paragraph{Statistics and visualisation}
-  Since the visualizers work in parallel, errors in them would not cascade to the others, so they are all faulty or none of them are.
-  \paragraph{}
-  Since every part works, the system is not faulty. %TODO kan beter
-
-  Secondly, all steps have been replicated by another piece of software that does the data loading, preprocessing, context extraction and the algorithm.
-The results of that system are titled "alternative DeepWalk" in the results Section.
-As system has been used in other projects and is written by someone else, it can be concluded that it works.
-This is more proof that the system indeed works as intended.
-
-  \subsubsection{Context extraction}
-  There are different context extractors for some of the different algorithms.
-I will research every one: the sentence generator of DeepWalk, the context extractor for the graph-based models and the context extractor for the pre-trained model.
-If all three work well, the context extractors are not the cause of the underperformance.
-  \paragraph{}
-  The context extractor for DeepWalk works as generates sentences as described in Section \ref{sentences}.
-Since the sentences are generated properly and DeepWalk only requires sentences, the context extraction for DeepWalk works.
-  \paragraph{}
-  For the Node2vec algorithms, the context extraction is more advanced.
-All edges are extracted from the Ontology using Jena.
-Then, for every node the context is decided as every node it has an edge with.
-In the case of the bidirectional algorithm, both outgoing and ingoing edges count as being connected, whereas in the monodirectional algorithm only outgoing edges count as the connectedness.
-For the algorithms that also use the edge labels for context, double the context size is expected.
-  \paragraph{}
-  The context extraction of the pre-trained Word2vec consists of splitting up every label into multiple words which can be looked up.
-For example "Adrenal vein" can be split up into "Adrenal" and "vein".
-  The pre-trained model does not use any other form of context integration.
-  \paragraph{}
-  First, I obtained the number of edges from VOWLview\cite{vowlview}, an Ontology graphing program.
-This was necessary since the creators of the data did not share how many edges were in the database.
-With the actual number of edges, obtained, it is possible to compare them with the number of edges found.
-If these match, the context extraction works.
-  \begin{table}[H]
-  \begin{tabular}{l|ll|ll}
-  & \multicolumn{2}{c}{\#edges mice} & \multicolumn{2}{c|}{\#edges humans}\\
-  Algorithm & expected & actual & expected & actual\\
-  \hline
-  \textbf{Truth}\cite{mice_ontology} & \multicolumn{2}{c|}{\textbf{1810}} & \multicolumn{2}{c}{\textbf{3780}} \\
-  Monodirectional & & & &\\
-  Bidirectional & & & &\\
-  Bidirectional \& edges & & & &\\
-  \end{tabular}
-  \caption[Edge comparison]{The number of edges compared to show that edge parsing was successful.}
-  \label{edgecounts}
-  \end{table}
-  Since the expected number of edges and actual number of edges match, we can conclude that the context extraction works.
-
-  \subsubsection{The algorithm}
-  At the beginning of this section, I reasoned that there are four possible causes for the underperformance of the system.
-The first three being bad data, bad code and bad context extraction.
-I have shown that all three are very unlikely to be the cause of the underperformance.
-Since those three possibilities have been excluded, the most likely conclusion is last remaining possibility: the set of distributed embedding algorithms do not work well on Ontology data.
-
-  % Uit mijn onderzoek blijkt dat McCallum's algoritme niet werkt op SW.
-Als ik terugkijk naar zijn keynote, is dat wel logisch, want in zijn voorbeeld heeft hij een dataset gegeven waar de KBs toevallig dezelfde Named Entities hebben (perfect zijn).
-In de echte wereld is dit met de meeste data niet zo, helemaal in het SW omdat veel ambiguiteit door auatomatscih maken.
-
- % Plaatje van mccallum matrix. Kijk, Steve heet Steven in alle drie de KBs. Dit is in het echt dus niet zo.
+ %TODO gooi weg wat niet meer waar is
+  This study shows that the algorithm of McCallum et al as shown in \cite{mccallumweblecture} does not help improve the results of ontology alignment over the straightforward baseline of simply pairing labels based on their syntactic similarity in the area of Ontology Matching.
+
+  The results show that one assumption that was made by the developers of the Universal Schema was incorrect, namely the assumption that when combining knowledge bases matching labels refer to the same entity and vice versa.
+For example, Bill Gates is called Bill Gates in FreeBase as well as retrieved from unstructured text.
+In reality, there may be multiple entities named Bill Gates and the same entity may be labelled differently.
+
+  This assumption will weaken further as an increasingly growing part of the Semantic Web is automatically generated and as such different labels can be assigned to the same entity.
+One of the goals of Ontology Matching is to link those differently labelled entities.
+
+  %In de presentatie zegt hij ook dat hij niet gaat proberen dingen meteen op elkaar te matchen maar gewoon alles houdt zoals het gelezen is/in de KB staat.
+Toch haalt hij goede resultaten met rule discovery e.d.
  \subsection{Future research}

### 2016-07-01 Paper/Draft.tex
No caps no more

@@
  %TODO Verbeteringen discussieren
- %TODO 
+ %TODO Verwijder ensemble uit evaluation
+ %TODO F-measure aan evluation
  \tableofcontents
@@
  %Vragen
- % Hypothese waarom ik dat denk?
- % extra hypothese
+ % Hypothese waarom ik dat denk? Antwoord see Arjen notes
+ % extra hypothese. Antwoord see Arjen notes (I think? otherwise its: don't add ensemble hypothesis)
 
@@
  \paragraph{}
- At the 14th International Semantic Web Conference McCallum presented his keynote on \emph{Representation and Reasoning with Universal Schema Embeddings}\cite{mccallumweblecture}.
+ At the 14th International Semantic Web Conference McCallum presented his keynote on \emph{Representation and Reasoning with Universal Schema embeddings}\cite{mccallumweblecture}.
 
@@
 The Universal Schema uses two steps.
-Firstly, the system learns embeddings of entities and relations found in text and Knowledge Bases\cite{universalschema}, see Figure \ref{McCallum_matrix}.
+Firstly, the system learns embeddings of entities and relations found in text and knowledge bases\cite{universalschema}, see Figure \ref{McCallum_matrix}.
 Secondly, these embeddings are then used to predict new relations for the knowledge bases.
@@
 This can be used to infer even more similarities by collaborative filtering.
-The technique had very promising results in Knowledge Base completion tasks.
+The technique had very promising results in knowledge kase completion tasks.
 
@@
  \includegraphics[width=0.8\textwidth]{plots/Skip-Gram}
- \caption[Skip-Gram Model]{The embedding of a row (in pink) is optimized to be close to its context embeddings (in purple) but far away from other embeddings (in red).}
+ \caption[Skip-Gram model]{The embedding of a row (in pink) is optimized to be close to its context embeddings (in purple) but far away from other embeddings (in red).}
  \label{Skip-Gram-img}
@@
  \includegraphics[width=0.8\linewidth]{plots/graaf}
- \caption[Ontology Matching graph example]{Similar to how the embeddings are used to predict relations within an ontology, ontology matching can be done by predicting relations between two ontologies.
+ \caption[Ontology matching graph example]{Similar to how the embeddings are used to predict relations within an ontology, ontology matching can be done by predicting relations between two ontologies.
 For example, since Gates and Bill will have very similar sets of embeddings (as their contexts are very similar) the system will recognise they are the same entity.}
@@
  McCallum plans on using these embeddings to predict new intra-knowledge base relations.
-However, from the keynote it is clear that this technique should work with multiple Knowledge Bases as the Universal Schema is applied to a set of Knowledge Bases including Freebase, knowledge extracted from text and the TAC Knowledge Bases Population Track Dataset.
-This means that inter-knowledge base relations can also be predicted using the Word Embedding Tensor Factorisation technique.
+However, from the keynote it is clear that this technique should work with multiple knowledge bases as the Universal Schema is applied to a set of knowledge bases including Freebase, knowledge extracted from text and the TAC knowledge base population track dataset.
+This means that inter-knowledge base relations can also be predicted using the word embedding tensor factorisation technique.
 
@@
  \paragraph{}
- The core of the Semantic Web are Knowledge Bases with the corresponding Ontologies.
-Ontology Matching is essential for the Semantic Web to work, as the information contained in the Knowledge Bases has to be combined.
+ The core of the Semantic Web are knowledge bases with the corresponding ontologies.
+Ontology matching is essential for the Semantic Web to work, as the information contained in the knowledge bases has to be combined.
 Since the Semantic Web will have many small knowledge bases, they will be combined at the moment information from them is required.
@@
  \paragraph{}
- The most important goal of this study is to find an Ontology Matcher that is able to deal with ambiguous concepts.
+ The most important goal of this study is to find an ontology matcher that is able to deal with ambiguous concepts.
 Since most of the knowledge on the Semantic Web is automatically gathered, it may be unreliable, ambiguous and even wrong.
 Therefore, ontology matching that is capable of handling this uncertain knowledge is required.
-Word Embeddings and especially multi-sense Word Embeddings should be able to handle a high amount of ambiguity, since multi-sense Word Embeddings are made to differentiate between different meanings of the same word.
+Word embeddings and especially multi-sense word embeddings should be able to handle a high amount of ambiguity, since multi-sense word embeddings are made to differentiate between different meanings of the same word.
  \paragraph{}
  Normally, the raw text representation of words is used for matching, for example to calculate the string distance.
-However, Word Embeddings Models use a vector representation, which should be more efficient.
+However, word embeddings models use a vector representation, which should be more efficient.
  Calculating the distance between vectors can be done very efficiently, therefore ontology matching with distributed concept representations fits that efficiency criteria. 
@@
 Everything that is mentioned in this section will be explained more in-depth further on.
- Firstly, I will give a short summary of the context by explaining why the Semantic Web requires Ontology Matching.
+ Firstly, I will give a short summary of the context by explaining why the Semantic Web requires ontology matching.
 Then I will illustrate the problem of ambiguity.
@@
  \paragraph{}
- On the Semantic Web, Ontologies are used to define knowledge\cite{fensel2001ontologies}.
+ On the Semantic Web, ontologies are used to define knowledge\cite{fensel2001ontologies}.
  The term ontology will be properly defined later on, but for now it suffices to know that an ontology is a set of rules that determine what relations are allowed and required in a given domain of discourse.
@@
  \paragraph{}
- The first option, using one single ontology, is infeasible. This is due to the fact that inference and search time scales with Ontology size\cite{complexity},
+ The first option, using one single ontology, is infeasible. This is due to the fact that inference and search time scales with ontology size\cite{complexity},
  and the number of concepts that are needed on the Semantic Web is enormous.
@@
 And all these concepts are related.
-Searching through this Ontology just to find one concept would be incredibly costly.
-And since every interaction on the Semantic Web requires lookups in an Ontology, these lookups need to be fast.
+Searching through this ontology just to find one concept would be incredibly costly.
+And since every interaction on the Semantic Web requires lookups in an ontology, these lookups need to be fast.
  \paragraph{}
  The second option, the one I address in this thesis, is the problem of combining ontologies from multiple domains.
-Combining in this sense means connecting the related concepts from the different Ontologies.
-Some research has focused on Ontology Merging, with promising results.
+Combining in this sense means connecting the related concepts from the different ontologies.
+Some research has focused on ontology merging, with promising results.
 However, recently research has been slowing to the point where there is little improvement.
  \paragraph{}
- One big problem in Ontology matching is the fact that in different domains, words can have different meanings.
+ One big problem in ontology matching is the fact that in different domains, words can have different meanings.
 Common examples are synonyms like author and writer, homonyms like bank (for money or by a river) and ambiguity.
@@
 There are a number of extensions that can deal with homonyms as well as data structured other than the continuous bag of words representation that the initial model was developed for.
-These facts show that it may be possible to make an embedding model for Ontologies and use the word relatedness to combine Ontologies\cite{multisense}.
+These facts show that it may be possible to make an embedding model for ontologies and use the word relatedness to combine ontologies\cite{multisense}.
  \paragraph{}
@@
  In this section I will discuss all concepts that are required to understand the study.
-Firstly, the Semantic Web, the key technology that depends very strongly on Ontology matching, will be discussed.
-Secondly, the concept of the Ontology itself will be addressed.
+Firstly, the Semantic Web, the key technology that depends very strongly on ontology matching, will be discussed.
+Secondly, the concept of the ontology itself will be addressed.
 Thirdly, current alignment strategies and their their problems are discussed.
@@
  \subsection{The Semantic Web}
-  The first concept I will discuss is the Semantic Web, also called Web 3.0, a vision of a Web that enhances the User Experience in ways that the current Web can not provide.
+  The first concept I will discuss is the Semantic Web, also called Web 3.0, a vision of a Web that enhances the user experience in ways that the current Web can not provide.
  \subsubsection{Progression of the Web}
@@
 In fact, the largest part of the job an agent has to carry out on the Semantic Web is finding relationships between pieces of information on the Web.
-Based on this observation, we can state that Ontology and Knowledge Base Alignment is the cornerstone  of the Semantic Web, since without this vital system the Web is merely a collection of separate pieces of information.
+Based on this observation, we can state that ontology and knowledge base alignment is the cornerstone  of the Semantic Web, since without this vital system the Web is merely a collection of separate pieces of information.
 Only when those pieces are aligned can we talk of knowledge, of semantics.
@@
  \includegraphics[width=0.5\linewidth]{plots/kb}
- \caption[Knowledge Base graph]{New information to be added to the Semantic Web.}
+ \caption[Knowledge base graph]{New information to be added to the Semantic Web.}
  \label{kb}
@@
  }
- \caption[Linking the Knowledge Base]{The new information is connected to the rest of the Semantic Web by connecting the new entities with entities in the Semantic Web.}
+ \caption[Linking the knowledge base]{The new information is connected to the rest of the Semantic Web by connecting the new entities with entities in the Semantic Web.}
  \label{combine}
@@
 For example, all people are in the same sub-graph, as are countries and the recently added foods.
-Every such sub-graph is one Knowledge Base that covers that specific domain.
-See Figure \ref{kbs} for the Knowledge Bases in the example.
+Every such sub-graph is one knowledge base that covers that specific domain.
+See Figure \ref{kbs} for the knowledge bases in the example.
 
@@
  }
- \caption[Semantic Web Knowledge Base view]{The different sub-graphs in the Semantic Web graph. They are contained in different Knowledge Bases and connected by URIs.}
+ \caption[Semantic Web knowledge base view]{The different sub-graphs in the Semantic Web graph. They are contained in different knowledge bases and connected by URIs.}
  \label{kbs}
@@
 The URI consists of a link to the knowledge base and then the identifier of the entity.
-For example, the people are connected to their country of origin, so in the people Knowledge Base there is a reference from Obama to \emph{countries\#USA}.
+For example, the people are connected to their country of origin, so in the people knowledge base there is a reference from Obama to \emph{countries\#USA}.
  \paragraph{}
  In this paragraph I will explain the use of ontologies on the Semantic Web.
-Ontologies describe the rules by which the Knowledge Bases must play.
+Ontologies describe the rules by which the knowledge bases must play.
 For example, every food must have a country of origin, and those countries of origin need to be of the Country \emph{Class}.
-This rule enables search algorithms to limit search to the countries Knowledge Base, as it is the only Knowledge Base that contains countries\cite{whyontologies}.
+This rule enables search algorithms to limit search to the countries knowledge base, as it is the only knowledge base that contains countries\cite{whyontologies}.
 This is just one example of a constraint that improves the work of one system.
@@
 Therefore the relationships are 'is-a' relationships: a bird \emph{is an} animal.
- Concepts can be instantiated, which is done in a Knowledge Base (KB).
-KBs and Ontologies are often confused, and are indeed very similar in structure.
-The Knowledge Base in our example can contain actually existing birds or fictional birds, and refers to the Ontology concept of bird to embed the instantiations with meaning\cite{ontologyGuru}.
+ Concepts can be instantiated, which is done in a knowledge base (KB).
+KBs and ontologies are often confused, and are indeed very similar in structure.
+The knowledge base in our example can contain actually existing birds or fictional birds, and refers to the ontology concept of bird to embed the instantiations with meaning\cite{ontologyGuru}.
 
@@
  \label{mouse_example}
- \caption[Mouse Ontology]{The different body parts of the mouse are connected as in this image.}
+ \caption[Mouse ontology]{The different body parts of the mouse are connected as in this image.}
  \end{figure}
@@
  \label{man_example}
- \caption[Human Ontology]{The different body parts of the man are connected as in this image.}
+ \caption[Human ontology]{The different body parts of the man are connected as in this image.}
  \end{figure}
@@
  \label{muis_man_example}
- \caption[Aligned Ontologies]{Humans and mice are connected as shown in this image.}
+ \caption[Aligned ontologies]{Humans and mice are connected as shown in this image.}
  \end{figure}
@@
 
- \subsubsection{Uses of Ontologies}
- There are three main reasons Ontologies are used.
+ \subsubsection{Uses of ontologies}
+ There are three main reasons ontologies are used.
 Firstly, it allows querying languages to optimize the search process.
 Secondly, it allows expansion of information on a node.
-Thirdly, it allows for consistency checking a Knowledge Base.
+Thirdly, it allows for consistency checking a knowledge base.
 Lastly, it allows merging of knowledge bases.
@@
  \subsection{Word representation} \label{w2v}
- An important area of research in Natural Language Process is the representation of words.
+ An important area of research in Natural Language Processing is the representation of words.
 The most obvious representation is the collection of characters humans are used to.
@@
 However, the representation is very sparse and the semantics or meaning of the word are not captured very well.
-Also, the method requires many discrete documents to train on, which are not available in Ontology matching.
+Also, the method requires many discrete documents to train on, which are not available in ontology matching.
  \paragraph{}
@@
 On the other hand, a concept in a single ontology can have multiple meanings and should therefore be matched with more than one concept from another ontology\cite{multisense}.
-This idea sparked the second reason why I started investigating semantic word representations for Ontology matching, since current methods do not allow for disambiguation.
+This idea sparked the second reason why I started investigating semantic word representations for ontology matching, since current methods do not allow for disambiguation.
  \paragraph{}
@@
 A different possible problem with this method is that the relation between a neighbour node and its corresponding edge may be lost, since they are just treated as independent contexts.
-  In the case of the mouse Ontology, the \emph{head} is above the \emph{torso} so \emph{isAbove} will be added to the context of \emph{head}.
+  In the case of the mouse ontology, the \emph{head} is above the \emph{torso} so \emph{isAbove} will be added to the context of \emph{head}.
 The same goes for the \emph{human head}, which will make them more similar.
@@
 Despite that there is no significant difference in performance.
-For example, compare the Average precision for the medical dataset with the anatomy dataset.
+For example, compare the Average Precision for the medical dataset with the anatomy dataset.
 The [...] %TODO AP is between baseline en AML for both?
@@
 %  The preprocessing works as described in Section \ref{preprocessing}. 
-  \paragraph{Matcher}The matcher is a simple KD-tree that finds the nearest neighbours of every node in the opposing Ontology. This is unlikely to contain errors.
+  \paragraph{Matcher}The matcher is a simple KD-tree that finds the nearest neighbours of every node in the opposing ontology. This is unlikely to contain errors.
   \paragraph{Data loading}
@@
   For the Node2vec algorithms, the context extraction is more advanced.
-All edges are extracted from the Ontology using Jena.
+All edges are extracted from the ontology using Jena.
 Then, for every node the context is decided as every node it has an edge with.
@@
   \paragraph{}
-  First, I obtained the number of edges from VOWLview\cite{vowlview}, an Ontology graphing program, which looks like Figure \ref{vowlfig}.
+  First, I obtained the number of edges from VOWLview\cite{vowlview}, an ontology graphing program, which looks like Figure \ref{vowlfig}.
 This was necessary since the creators of the data did not share how many edges were in the database.
@@
  %TODO gooi weg wat niet meer waar is
-  This study shows that the algorithm of McCallum et al as shown in \cite{mccallumweblecture} does not help improve the results of ontology alignment over the straightforward baseline of simply pairing labels based on their syntactic similarity in the area of Ontology Matching.
+  This study shows that the algorithm of McCallum et al as shown in \cite{mccallumweblecture} does not help improve the results of ontology alignment over the straightforward baseline of simply pairing labels based on their syntactic similarity in the area of ontology matching.
 
@@
   This assumption will weaken further as an increasingly growing part of the Semantic Web is automatically generated and as such different labels can be assigned to the same entity.
-One of the goals of Ontology Matching is to link those differently labelled entities.
+One of the goals of ontology matching is to link those differently labelled entities.
 

### 2016-07-02 Paper/Draft.tex
Added almost all results

@@
  %TODO Word index
- %TODO Fix hoofdletters (bv ontology, kb)
  %TODO spelling (database dataset)
@@
  %TODO Verwijder ensemble uit evaluation
- %TODO F-measure aan evluation
+ %TODO F-measure aan evaluation
  \tableofcontents
@@
   \begin{figure}
-  \includegraphics[width=0.7\textwidth]{vowlview}
+%  \includegraphics[width=0.7\textwidth]{vowlview}
   \caption[]{}
@@
   \hline
-  Alternative & 0.6372 & 0.2494 \\
+  Label Match & 0.6926 & 0.4905 \\
+  Random & 0.6926 & 0.4905 \\
+  Generic & 0.6372 & 0.3874 \\
   Bidirectional & 0.8432 & 0.4946 \\
-  Label match + Random & 0.6926 & 0.3875 \\
-  Generic & 0.6372 & 0.2419 \\
-  \textbf{AML} & \textbf{0.94} & \textbf{0.81} \\ %http://disi.unitn.it/~pavel/om2015/
+  Deepwalk &  & 0.4906 \\
+  Alternative & 0.6372 & 0.4905 \\
+  \textbf{AML ensemble} & \textbf{0.94} & \textbf{0.81} \\ %http://disi.unitn.it/~pavel/om2015/
   %papers/om2015_proceedings.pdf#page=125

### 2016-07-02 node_embedding/src/DeepWalkNodeEmbedding.scala
Committing to store everything in the cloud

@@ -10,7 +10,7 @@ import scala.collection.mutable.ArrayBuffer
 /**
   * Created by harmen on 16-6-16.
   */
-class DeepWalkNodeEmbedding extends NodeEmbeddingModel {
+class DeepWalkNodeEmbedding extends SkipGramNodeEmbedding {
 
   val URIs = Array("http://mouse.owl#",
                    "http://human.owl#")
@@ -114,7 +114,7 @@ class DeepWalkNodeEmbedding extends NodeEmbeddingModel {
       process(sentence.toString())
       if (ndoc % printAfterNDoc == 0 && id == 0) {
         printf("Progress: %d/%d%n", ndoc, nIts)
-        store()
+        //store()
       }
       work = check_finished(ndoc)
       curOnt = maybeSwitch(curOnt)
@@ -122,11 +122,11 @@ class DeepWalkNodeEmbedding extends NodeEmbeddingModel {
   }
 
   // Stuff copied from SkipGramNodeEmbedding
-  def getVector(node: RDFNode) : Array[Double] = {
+  override def getVector(node: RDFNode) : Array[Double] = {
     getVector(ontology.toString(node))
   }
 
-  def getVector(index: Int) : Array[Double] = {
+  override def getVector(index: Int) : Array[Double] = {
     if (vocab == null) {
       this.buildVocab()
     }
@@ -137,7 +137,7 @@ class DeepWalkNodeEmbedding extends NodeEmbeddingModel {
     Array.tabulate(weight.value.size)(i => weight.value(i))
   }
 
-  def getVector(name: String) : Array[Double] = {
+  override def getVector(name: String) : Array[Double] = {
     if (vocab == null) {
       this.buildVocab()
     }
@@ -148,12 +148,13 @@ class DeepWalkNodeEmbedding extends NodeEmbeddingModel {
   }
 
   // Stuff copied from SKipGramEmbeddingModel
-  val negative = opts.negative.value
-  val window = opts.window.value
-  val rng = new util.Random(5) // set rng seed
-  val sample = opts.sample.value.toDouble
+  // Probably can be removed now that it extends it
+  override val negative = opts.negative.value
+  override val window = opts.window.value
+  override val rng = new java.util.Random(5) // set rng seed
+  override val sample = opts.sample.value.toDouble
 
-  def process(doc: String): Int = {
+  override def process(doc: String): Int = {
[…]

### 2016-07-02 node_embedding/src/Evaluator.scala

@@ -14,7 +14,7 @@ import scala.util.Try
 object Evaluator {
 
   val opts = WordSenseOpts
-  val model = new SkipGramNodeEmbedding()
+  var model: NodeEmbeddingModel = null
 
   def get_compare_stats(alignment: Alignment, truth: Alignment, calc: (String, String) => Double = this.calc): (Int, Int, Int) = {
     val alignmentset = alignment.alignments.asScala.toSet[(String, String, Double)].map { case (s: String, o: String, v: Double) => (s, o) }
@@ -51,8 +51,8 @@ object Evaluator {
 
   def obtain_name(subj: String, predicate: String) : String = {
     val (o, uri) = predicate.endsWith("1") match {
-      case true  => (model.getOntologies(0), "http://mouse.owl#")
-      case false => (model.getOntologies(1), "http://human.owl#")
+      case true  => (model.getOntologies(0), "http://" + WordSenseOpts.corpusses.value.split(";").head.split("/").last + "#")
+      case false => (model.getOntologies(1), "http://" + WordSenseOpts.corpusses.value.split(";")(1).split("/").last + "#")
     }
     o match {
       case ontology: RDFOntology =>
@@ -92,9 +92,10 @@ object Evaluator {
     val rs = new ArrayBuffer[Double]()
     var i = 0
     var correct = 0
-    val truthset = truth.alignments.asScala.map(t => (t._1, t._2)).toSet
+    val truthset_ = truth.alignments.asScala.map(t => (t._1, t._2)).toSet
+    val truthset = truthset_.filterNot(t => calc(t._1, t._2) >= 100000)
     val N = truthset.size
-    for (trip <- alignment.alignments.iterator().asScala) {
+    for (trip <- alignment.alignments.asScala.toList.sortWith((t, t_) => t._3 < t_._3)) {
       i += 1
       if (truthset.contains((trip._1, trip._2)) || truthset.contains((trip._2, trip._1)))
         correct += 1
@@ -104,15 +105,19 @@ object Evaluator {
 
     //var mx = 0.toDouble
     //val ps_ = ps.map(v => {mx = math.max(mx, v); mx})
+    val fs = ps zip rs map {case (p, r) => 2*p*r / (p + r)}
+    val order = fs.zipWithIndex.sortWith((t, t_) => t._1 < t_._1).map(t => t._2).reverse
+    val sorted = order.map(fs(_))
[…]

### 2016-07-02 node_embedding/src/NodeEmbeddingModel.scala

@@ -1,8 +1,9 @@
 import cc.factorie.app.nlp.embeddings.{EmbeddingOpts, TensorUtils, WordEmbeddingModel, LiteHogwildTrainer => HogWildTrainer}
-import cc.factorie.model.Weights
+import cc.factorie.model.{Weights, Weights1}
 import cc.factorie.optimize.AdaGradRDA
 import cc.factorie.la.DenseTensor1
 import java.io._
+import java.util
 import java.util.zip.{GZIPInputStream, GZIPOutputStream}
 
 import scala.collection.JavaConverters._
@@ -148,16 +149,20 @@ abstract class NodeEmbeddingModel extends WordEmbeddingModel(WordSenseOpts) {
     // <word>[<space><embedding(word)(d)>]*dim-size<newline>
     in.readLine() // Skip header
     var line : String = ""
-    val weights = new Array[Weights](vocab.size)
+    val weights: util.ArrayList[Weights1] = new util.ArrayList((0 until V).map(i => Weights(TensorUtils.setToRandom1(new DenseTensor1(D, 0)))).asJava) // initialized using wordvec random
+    var i = 0
     while({line = in.readLine; line != null}) {
       val word_ = line.split(" ").apply(0)
       val word = if(mapping == null) word_ else mapping(word_)
       val weight : Array[String] = line.split(" ").drop(1)
       val weightTensor = new DenseTensor1(weight.length)
       weight.zipWithIndex foreach (t => weightTensor.update(t._2, t._1.toDouble))
-      weights(vocab.getId(word)) = Weights(weightTensor)
+      val i = vocab.getId(word)
+      if (i > 0) {
+        weights.add(vocab.getId(word), Weights(weightTensor))
+      }
     }
-    this.weights = weights
+    this.weights = weights.asScala.toList
     in.close()
   }
 
@@ -182,10 +187,11 @@ abstract class NodeEmbeddingModel extends WordEmbeddingModel(WordSenseOpts) {
     val threadIds = (0 until threads).map(i => i)
     //val fileLen = new File(current_corpus).length
     val fileLen = ontology.getEdges.size
-    for (it <- 0 to nIts) {
+    for (it <- 0 until nIts) {
       println("Iteration: " + it)
-      threadIds.par.foreach(workerThread(_, fileLen, 300))
-      store()
+      threadIds.par.foreach(workerThread(_, fileLen, 30))
+      //if (it % 10 == 0)
+        store()
     }
[…]

### 2016-07-02 node_embedding/src/Normal_W2V.scala

@@ -8,6 +8,7 @@ import cc.factorie.model.Weights
 import com.hp.hpl.jena.rdf.model.RDFNode
 
 import math.sqrt
+import scala.collection.mutable
 import scala.util.Try
 
 /**
@@ -21,18 +22,19 @@ object Normal_W2V {
 
   def main(args: Array[String]): Unit = {
     model.buildVocab()
-    model.loadEmbeddings()
+    model.learnEmbeddings()
+    Evaluator.model = model
     val alignment = align()
 
     //Visualizer.hist_alignment(alignment)
     //alignment.set_threshold(0.075)
     val truth = Evaluator.loadTruth()
-    Visualizer.compare_hist(alignment, truth, calc)
+    //Visualizer.compare_hist(alignment, truth, calc)
     val dice = Evaluator.compare(alignment, truth)
-    val synonyms = Evaluator.loadTruth(WordSenseOpts.synonyms.value)
-    val dice_ = Evaluator.compare(synonyms, truth)
+    //val synonyms = Evaluator.loadTruth(WordSenseOpts.synonyms.value)
+    //val dice_ = Evaluator.compare(synonyms, truth)
     printf("The result of what you have been working for for months: %s%n", dice)
-    printf("For reference, just the synonyms scores: %s%n", dice_)
+    //printf("For reference, just the synonyms scores: %s%n", dice_)
     //show_alignment(alignment, truth)
     Evaluator.plot_roc(alignment, truth, this.calc)
   }
@@ -41,7 +43,7 @@ object Normal_W2V {
     val o1 = model.getOntologies(0)
     val o2 = model.getOntologies(1)
     println("Building trees for aligning")
-    val synonyms = model.loadSynonyms()
+    val synonyms = mutable.HashMap[String, String]() //model.loadSynonyms()
 
     val nodes1 = o1.getNodes.map(model.getRootSynonym(_, synonyms)).toSet[String].toArray[String] // Don't grab all synonyms too
     val vectors1 : Array[Array[Double]] = nodes1.map(n => model.getVector(n))
@@ -69,6 +71,8 @@ object Normal_W2V {
   }
 
   def calc(node1: String, node2: String): Double = {
+    if (node1 == node2)
+      return -0.1
     val v1 = model.getVector(node1)
     val v2 = model.getVector(node2)
     val v = sqrt((v1 zip v2 map {case (x,y)=> (x - y) * (x - y)}).sum) // Euclidean vector distance
[…]

### 2016-07-02 node_embedding/src/Ontology.scala

@@ -1,17 +1,20 @@
 import cc.factorie.app.nlp.embeddings.FastLineReader
 import com.hp.hpl.jena.graph.Node_Literal
+import com.hp.hpl.jena.ontology.OntResource
+import com.hp.hpl.jena.ontology.impl.OntModelImpl
 import com.hp.hpl.jena.rdf.model._
 import com.hp.hpl.jena.rdf.model.impl.LiteralImpl
 import com.hp.hpl.jena.util.FileManager
+import com.hp.hpl.jena.vocabulary.RDFS
 
 import scala.collection.JavaConverters._
 import scala.collection.immutable.HashMap
 
 abstract class Ontology {
   val LABEL_URI = "http://www.w3.org/2000/01/rdf-schema#label"
-  val EDGE_URIS = Array(//"http://www.geneontology.org/formats/oboInOwl#hasRelatedSynonym",
-                        "http://www.w3.org/2000/01/rdf-schema#subClassOf"
-  )// "http://www.geneontology.org/formats/oboInOwl#hasDefinition")
+  val EDGE_URIS = Array("http://www.geneontology.org/formats/oboInOwl#hasRelatedSynonym",
+                        "http://www.w3.org/2000/01/rdf-schema#subClassOf",
+                        "http://www.geneontology.org/formats/oboInOwl#hasDefinition")
   val REF_URIS = Array("http://knowledgeweb.semanticweb.org/heterogeneity/alignmententity1",
                        "http://knowledgeweb.semanticweb.org/heterogeneity/alignmententity2",
                        "http://knowledgeweb.semanticweb.org/heterogeneity/alignmentmeasure")
@@ -52,6 +55,7 @@ abstract class Ontology {
 }
 
 class RDFOntology (filename: String, reference: Boolean = false) extends Ontology {
+  val LABEL_PROPERTY = RDFS.label
   def get_label(uri: String) : String = {
     val n = model.getResource(uri)
     val e = model.listStatements(n, model.getProperty(LABEL_URI), null).nextStatement()
@@ -60,21 +64,36 @@ class RDFOntology (filename: String, reference: Boolean = false) extends Ontolog
   }
 
   val model : Model = FileManager.get.loadModel(filename)
+  printf("%s contains %d nodes and %d edges%n", filename, getNodes.size, getEdges.size)
 
   def getNodes: Iterator[String] = {
     val nodes = getEdges.map(_.split(" ")).flatMap[String](a => Array(a(0),a(2)))
     if(this.reference)
       return nodes
     else
[…]

### 2016-07-02 node_embedding/src/WordSenseOpts.scala

@@ -12,7 +12,7 @@ object WordSenseOpts extends EmbeddingOpts{
   val nIts              = new CmdOption("n-its", 5, "INTEGER", "Number of times w2v should go over the corpus")
   val continue          = new CmdOption("continue", true, "BOOLEAN", "")
   nIts.setValue(0)//1000000)
-  threads.setValue(4)
+  threads.setValue(1)//4)
   continue.setValue(false)
   dimension.setValue(5)
 
@@ -28,9 +28,11 @@ object WordSenseOpts extends EmbeddingOpts{
   corpusses.setValue("Data/anatomy/mouse.owl;Data/anatomy/human.owl")
   //corpusses.setValue("Data/medical/oaei2013_SNOMED_small_overlapping_nci.owl;Data/medical/oaei2013_NCI_small_overlapping_snomed.owl")
   //truthfile.setValue("Data/medical/oaei2013_SNOMED2NCI_repaired_UMLS_mappings.rdf")
+  synonyms.setValue("")
   output.setValue("Data/output.csv")
   saveVocabFile.setValue("Data/vocab.csv")
   //loadVocabFile.setValue("Data/vocab.csv")
+  //inputFilename.setValue("embeddings.csv")
   //inputFilename.setValue("Data/output.csv")
   //inputFilename.setValue("Data/forthelongesttime.csv")
   //inputFilename.setValue("edgemappings.csv")

### 2016-07-03 Paper/Draft.tex
All results have been added

@@
  \item The algorithm finds relationships between concepts in ontologies.
- \item The algorithm has been compared to the currently best matchers.
  \item The algorithm performs better.
@@
  \subsubsection{Current state} %TODO This bit can use some work
+ Zijn alle losse technologien er al? Ja. Hoe? RDF en OWL worden al gebruikt. Google heeft al betere search door Knowledge gRaph (hummingbird) plaatje etc...
+ Door lack of adoption is het er niet.
+
  % Tip: google wie schreef Harry Potter
@@
  The many uses of ontology matching show that it is important to research all avenues that might improve ontology matching, as it will have a direct result in many other fields.
- \subsubsection{Technologies}
- %TODO Wil ik dit nog doen?
 
@@
  \subsubsection{Uses of ontologies}
- There are three main reasons ontologies are used.
+ There are four main reasons ontologies are used.
 Firstly, it allows querying languages to optimize the search process.
@@
  \subsection{Current alignment strategies} \label{strategies}
+ %TODO Meer voorbeelden meer plaatjes (uit hun papers). Eerst ga ik uitleggen..
  Many different alignment strategies have already been developed.
@@
  \subsubsection{Problems in ontology alignment}
+ %TODO Cite en in discussion of w2v dit kan helpen. Zo niet: weg
  How should the wildly differing demands the applications place on the ontology matching systems be satisfied by a single or just a few systems?
@@
  \subsection{Word representation} \label{w2v}
+ % Meer McCallum noemen. 80 plaatjes %TODO
  An important area of research in Natural Language Processing is the representation of words.
@@
  \subsubsection{Factorie} \label{factorie}
- Factorie is a toolkit that contains a number of tools which includes word-embedding models \cite{git-factorie}. \cite{w2v}.
+ Factorie is a toolkit that contains a number of tools which includes word-embedding models \cite{git-factorie, w2v}.
  \paragraph{}
@@
 For example, if the relationship has a certain confidence or more than two concepts are involved.
+
+ %TODO AML toevoegen
 
@@
 
- \subsection{Considered implementations}
+ \subsection{Algorithms}
+ %TODO Move sommige naar discussions
+ %TODO per algorithme uitleggen: hoe het werkt. Waarom gekozen. Plaatjes. Volgorde van kiezen (ik denk dat deze beter past) en bij resultaten bespreken of deze volgorde klopt.
  In this section, I will discuss the different implementations that were made of the algorithm.
@@
    \includegraphics[width=\textwidth]{plots/untrained_ROC}
-   \caption[Precision-recall curve untrained mice]{The precision and recall trade-off for the results of the untrained Node2vec. $AP = 0.04194$}
+   \caption[Precision-recall curve untrained mice]{The precision and recall trade-off for the results of the untrained Node2vec.}
    \label{ROC_untrained}
@@
   \begin{figure}[H]
+
+ \begin{subfigure}{.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{plots/Generic_ROC}
-   \caption[Precision-recall curve pre-trained mice]{The precision and recall trade-off for the results of the Word2vec algorithm. $AP: 0.04636$}
+   \caption[Precision-recall curve pre-trained mice]{Pretrained Word2vec algorithm.}
    \label{ROC_generic}
-  \end{figure}
-
-  \begin{figure}[H]
+   \end{subfigure}
+ \begin{subfigure}{.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{plots/trained_ROC}
-   \caption[Precision-recall curve trained mice model]{The precision and recall trade-off for the results of the bidirectional Node2vec. $AP = 0.04198$}
+   \caption[Precision-recall curve trained mice model]{bidirectional Node2vec.}
    \label{ROC_trained}
-  \end{figure}
-
-  \begin{figure}[H]
+  \end{subfigure}
+ \begin{subfigure}{.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{plots/Alternative_ROC}
-   \caption[Precision-recall curve DeepWalk mice]{The precision and recall trade-off for the results of the alternative DeepWalk algorithm. $AP = 0.04193$}
+   \caption[Precision-recall curve DeepWalk mice]{Alternative DeepWalk algorithm.}
    \label{ROC_alternative}
+  \end{subfigure}
+  \caption{Precision-recall trade-off curve for the results of three more algorithms.}
   \end{figure}
@@
   Bidirectional & 0.8432 & 0.4946 \\
-  Deepwalk &  & 0.4906 \\
+  Deepwalk & 0.6926 & 0.4906 \\
   Alternative & 0.6372 & 0.4905 \\
@@
  \textit{
- Can distributed representations of concepts be used to find relationships between concepts in ontologies better than existing matchers?
- }
+ Can distributed representations of concepts be used to find relationships between concepts in ontologies better than the best existing matcher?
+ } % Zelfde als sectie hypothese?
  \end{center}
 
- To answer this question I have examined the following points from Section \ref{hypotheses}:
-
-\paragraph{The algorithm uses distributed representations of concepts}
-\paragraph{The algorithm finds relationships between concepts in ontologies}
-\paragraph{The algorithm has been compared to the currently best matchers}
+ To answer this question I have examined the following points from Section \ref{hypotheses} for every algorithm (Pre-trained Word2vec, DeepWalk, Node2vec):
+
+\paragraph{The algorithm uses distributed representations of concepts} %TODO In de uitleg van het algoritme duidelijk maken dat dit zo is.
+
+Yes. They all use distributed representations since they all convert words into vectors:
+\begin{description} \item[pre-trained Word2vec] ... 
+\item[] ...
+\end{description}
+\paragraph{The algorithm finds relationships between concepts in ontologies} %TODO In de system check duidelijk maken.
+
+This is correct as the inputs are always two ontologies and the output is always a set relationships between the ontologies.
 \paragraph{The algorithm performs better}
- I performed empirical research where I made the algorithm, applied it to different datasets and compared the results with existing methods.
-
- Because the last point is not true, the answer is not in agreement with my hypothesis from Section \ref{hypotheses}:
-
- \begin{center}
- \textit{Matchers that use a distributed representation of concepts can find relationships between concepts in ontologies better than the best existing matchers.}
- \end{center}
-
+
+Not yet.
+
+I compared the results of the algorithms with AML, the best existing matcher.
+All algorithms perform below AML.
+However, there is potential for better performance as we can see in Section \ref{discussion}.
+\paragraph{}
+ Because the last point is not true, the answer is not in agreement with my hypothesis from Section \ref{hypotheses}.
+ \paragraph{}
 The results from all the different evaluation measures are in agreement. From those results we can conclude the following:
@@
 
- \subsection{Discussion}
+ %TODO Arjen vragen dit te bekijken
+
+ \subsection{Discussion} \label{discussion}
  %TODO gooi weg wat niet meer waar is
+
   This study shows that the algorithm of McCallum et al as shown in \cite{mccallumweblecture} does not help improve the results of ontology alignment over the straightforward baseline of simply pairing labels based on their syntactic similarity in the area of ontology matching.
@@
 Toch haalt hij goede resultaten met rule discovery e.d.
- \subsection{Future research}
-
- \subsection{Discarded implementations}
+
+  % Het was wel gelukt als ik ... (wat eerst future research was)
+
+ \subsection{Discarded algorithms}
 

### 2016-07-05 Paper/Draft.tex
Committing before a crash deletes another paragraph. Fixed a dozen TODOs

@@
 
- \title{Graphs of Mice and Men}
- %subtitle{Matching ontologies with distributed word embeddings}
+ \title{Matching ontologies with distributed word embeddings}
  \author{Harmen Prins}
@@
  %TODO Results interpretation: uitleg waarom hoger en lager
- %TODO Plaatje VOWL
  %TODO Verbeteringen discussieren
@@
 To do this you must either manually go through the list of movies playing this weekend and check if any movies on that list match your preferences.
+In Figure \ref{movies}, this is called "Filter based on movies".
 
@@
 You also have to filter the out time slots based on your availability, so you cross-reference the available movie showtimes with your agenda.
+This step is called "Filter based on availability" in Figure \ref{movies}
 
@@
 Once you contact your friends, most of them do not respond as they are not online at that time or they do not want to fill out an availability poll or movie choices.
+This is called "Filter based on friends" in Figure \ref{movies}.
  \paragraph{}
@@
 This last problem is the one that I will work on in this thesis.
-Once this problem has been solved, the Semantic Web is technically possible and only needs to be socially accepted before it will become the norm.
-%cite microformats.org
- %TODO per stap refereren naar plaatje
+Once this problem has been solved, the Semantic Web is technically possible and only needs to be socially accepted before it will become the norm\cite{microformats}.
  \subsection{Motivation}
@@
  \begin{figure}[H]
+ \centering
  \begin{subfigure}{.475\textwidth}
@@
  \begin{figure}[H]
+ \centering
  \begin{subfigure}{0.475\textwidth}
@@
 
-"" 
+ {\centering
   Matching ontologies and dealing with the ambiguity and homonymy contained in them.
-"" %TODO mooier
+ }
 
@@
 
- \subsection{Overview} %TODO rewrite
+ \subsection{Overview}
+ This report is structured as follows: firstly, I will give all the required background information required to understand the context and the algorithms I will use.
+Then, I will describe the method, which includes the design of the algorithm and the evaluation method.
+The last two sections are the results and the joint conclusion and discussion, which interpret the results.
 
@@
 Readers, however, could not change anything, merely read the sites and click on links.
-In this iteration of the Web there was no interaction.
+In this iteration of the Web there was no interaction\cite{web1}.
 See Figure \ref{web1}.
-%cite web1.0?
 
@@
  Web 2.0, the current Web, models the internet as \textit{hubs} (or sites) with a specific purpose and interaction between users, who can also add content, as in Figure \ref{web2}.
-However, there is only limited interconnectivity between those hubs\footnote{For example, Facebook is a hub for sharing content with people you consider friends, but if you want to share that content with more people you will have to go to another hub, like Imgur or Pinterest.}.
-%cite web2.0
+However, there is only limited interconnectivity between those hubs\footnote{For example, Facebook is a hub for sharing content with people you consider friends, but if you want to share that content with more people you will have to go to another hub, like Imgur or Pinterest.}\cite{web2}.
  It is possible to link to content from other hubs using URLs, but this moves the user to another hub, rather than connecting the content present in the hubs.
@@
 But humans will only accept the Semantic Web if it is useful to them, so the Semantic Web must show its applications and usefulness before it will be used in daily life.
- \subsubsection{Workings} % Technisch uitleg. Veel voorbeelden, veel citaties. Hoe komt er info in. Hoe eruit. Hoe gaat een mens om met de SW (visie). Tags: grafen, ontologien.
- %Dit is belangrijk voor mij want... 
+ \subsubsection{Workings}
  \begin{figure}[H]
@@
 
- \subsubsection{Current state} %TODO This bit can use some work
- Zijn alle losse technologien er al? Ja. Hoe? RDF en OWL worden al gebruikt. Google heeft al betere search door Knowledge gRaph (hummingbird) plaatje etc...
- Door lack of adoption is het er niet.
-
- % Tip: google wie schreef Harry Potter
+ \subsubsection{Current state}
  Currently, people are not aware of the Semantic Web.
@@
  \paragraph{}
- Semantic Web systems are currently divided into two groups: the systems that need high accuracy and the ones that need high recall.
-The first group are deployed in domains that require exact knowledge, whereas the second group are systems that must make available a big amount of data.
-In the past it was not possible to extract information from texts and other sources automatically, so all systems were hand-crafted and thus highly accurate but very small.
-This also impacted research, which did not focus on scaling ontologies until recently.
- \paragraph{}
- The group that requires high recall use hand-crafted knowledge bases, created by experts, containing only facts that are accurate, verified and relevant\cite{mika2015schema}.
+ The main languages W3C endorses are RDF, OWL and SKOS\cite{rdf, owl, skos}.
+They are important for the Semantic Web and are already in use.
+Most of this use, however, is for hand-crafted knowledge bases, created by experts, containing only facts that are accurate, verified and relevant\cite{mika2015schema}.
 This method of creating a knowledge base does not scale very well and usually consists of fewer than ten thousand facts.
 Because of this, the knowledge bases are restricted to small domains, including some parts of medicine and cultural heritage\cite{byrne, le2002}.
- \paragraph{}
- For the group that requires a high recall, or in other words a big amount of data, automated methods are required.
-These methods work fast, parsing thousands of websites a minute, but are inclined to make mistakes.
+As such it does not help regular uses of the Web but only people who are willing to become adept with the tools used in the knowledge bases.
+ \paragraph{} 
+ The Linked Open Data project, on the other hand, is building the foundation of the Semantic Web mostly automated.
+These automated methods work fast, parsing thousands of websites a minute, but are inclined to make mistakes.
 Often, these methods use crowd-sourcing to improve accuracy, using experts or the general public to suggest or check facts\cite{zhou2007}.
- \paragraph{}
- On way the W3C is fighting ambiguity is to ensure very few different languages are used for ontologies and knowledge bases.
-The main languages W3C endorses are RDF, OWL and SKOS\cite{rdf, owl, skos}.
- \paragraph{}
- Large ontologies already exist, with the largest, Freebase, boasting almost two billion triples and the three hundred combined Large Open Data databases contain over thirty billion\cite{dbpedia, lod}.
+
+ The largest knowledge base of the LOD project, Freebase, boasts almost two billion triples.
+The three hundred combined Large Open Data databases contain over thirty billion\cite{dbpedia, lod}.
 The LOD is simply a single alignment over many different knowledge bases.
  \paragraph{}
- Applications include improved web searching, question answering, product comparison, context merging, data integration, decision support, translation, all the way up to the intelligent softbot mentioned earlier.
-\cite{schreiber, future}
- \paragraph{}
- The many uses of ontology matching show that it is important to research all avenues that might improve ontology matching, as it will have a direct result in many other fields.
+ Applications include improved web searching, question answering, product comparison, context merging, data integration, decision support, translation, all the way up to the intelligent softbot mentioned earlier\cite{schreiber, future}.
+
+ An example: since the Hummingbird update, when someone Googles "Who is Barack Obama" they will find a part of the Knowledge Graph, see Figure \ref{hummingbird}..
+This system improves web searching by finding answers rather than pages.
+ \paragraph{}
+ The many uses of ontology matching and its role in the Semantic Web show that it is important to research all avenues that might improve ontology matching, as it will have a direct result in many fields.
 
@@
  \begin{figure}[H]
+ \centering
  \includegraphics[width=0.7\linewidth]{plots/muisman}
@@
  Aristotelian ontologies have the advantage of being easier to create.
-One could use statistical methods given a sample of all possible observations or crowd sourcing to create concepts and constraints.
-This would enable enormous ontologies and knowledge bases with the amount of data currently available and cheap mental labour with services like Amazon's Mechanical Turk.
+One can use statistical methods given a sample of all possible observations or crowd sourcing to create concepts and constraints.
+This enables enormous ontologies and knowledge bases, especially with the big amount of data currently available and cheap mental labour with services like Amazon's Mechanical Turk.
  \paragraph{}
@@
 The disadvantage is that creating such an ontology is much more costly than an Aristotelian ontology, since every concept and constraint needs to be correct in all cases.
- \paragraph{}
- Another way to represent this spectrum is the precision-recall trade-off.
-A Platonic ontology has maximum precision but its recall is limited since it can only represent very little if creation budget is limited, or paradoxes exist.
-The Aristotelian ontology on the other hand, can theoretically reach perfect recall given enough storage size and observations for its statistical methods.
-Again, in reality this is limited by a budget.
-All ontologies fall between these two extremes.
-Often, a combination of statistical methods with expert confirmation is used.
- \paragraph{}
- Platonic ontologies are often used in areas where precision is important, like medicine, where lives depend on the information contained in the ontology and its knowledge base.
+
+ These ontologies are often used in areas where precision is important, like medicine, where lives depend on the information contained in the ontology and its knowledge base.
 Aristotelian ontologies are more common on the Semantic Web, where massive amounts of data need to be represented and queried.
+ \paragraph{}
+ Currently, alignment strategies are focussed more on Platonic ontologies.
+In the Ontology Alignment Evaluation Challenge the datasets are relatively small Platonic ontologies.
+Since most of the ontology matching systems are produced to compete in the OAEI, almost all techniques focus on small, perfect knowledge, perfect ground truth ontologies.
+
+ The proposed method should scale to much larger datasets without effort, allowing for ontology matching that is suitable for the Semantic Web, rather than just for individual small knowledge bases.
 
  \subsection{Current alignment strategies} \label{strategies}
- %TODO Meer voorbeelden meer plaatjes (uit hun papers). Eerst ga ik uitleggen..
- Many different alignment strategies have already been developed.
-All strategies follow the same two-step approach.
-The two steps are independent and as such different methods can be used interchangeably.
-The first step is to generate an initial correspondence set, where correspondences between nodes are found based on just their labels and meta-data.
-The second step is to use this initial set and the structure of the ontology to find more correspondences.
-These steps are called the terminological and the structural steps.
-Some strategies also use extra steps like the extensional and semantic steps, which use vector space models and inference, respectively\cite{future}.
+ In this section I will give a more in-depth description of the ontology matchers that compete in the OAEI.
+
+ Many different ontology matchers have already been developed.
+All matchers can be divided into two groups: those that require just the labels of the concepts and those that require an initial correspondence set and the structure of the ontologies.
+The first group is always used first to generate the correspondence set of the second group.
+The first step is called a terminological matcher since it only uses the terms of the concepts.
+If it uses a vector space model it is also called an extensional matcher.
+
+ The second step is referred to as structural matching. If the matcher uses logic, it is also called an inference matcher\cite{future}.
  \paragraph{}
@@
 the number of edges between the concepts and their least general common superconcept\cite{lin2008}.
- For example, the distance between moustache and whiskers is 3, since their least general common superconcept is hair the distance between moustache and hair is 2 (with facial hair between them) and the distance between whisker and hair is 1 (direct).
+ For example, the distance between moustache and whiskers is 3, since their least general common superconcept is hair the distance between moustache and hair is 2 (with facial hair between them) and the distance between whisker and hair is 1.
  Edit distance is a purely string-based similarity measure.
@@
 Similar methods include substring matching and n-gram matching, which compare parts of the strings to find similarities\cite{singh2014, levenshtein}.
- For example, arm and front paw have an edit distance of 8, since they have 1 character in sequence in common (either the a or the r) and thus 8 characters that are different.
+ For example, arm and front paw have an edit distance of 8, since they have 1 character in sequence in common (either the a or the r) and thus 8 characters that are different, see Figure \ref{levenshteinfig}.
+
+ \begin{figure}[H]
+ \centering
+ \includegraphics[width=0.6\textwidth]{plots/editdistance}
+ \caption[Edit distance example]{The edit distance between \textit{arm} and \textit{front paw}.}
+ \label{levenshteinfig}
+ \end{figure}
+
+ An example of a structural matcher is the children matcher.
+It matches all children of a pair in the correspondence set with some low confidence.
+When two nodes are matched more often, their confidence is combined until it reaches some threshold.
+Then it is added to the correspondence set.
+
  \subsubsection{Problems in ontology alignment}
- %TODO Cite en in discussion of w2v dit kan helpen. Zo niet: weg
  How should the wildly differing demands the applications place on the ontology matching systems be satisfied by a single or just a few systems?
@@
  \paragraph{}
- Online matching would allow for updates in a knowledge base to be represented in the alignments of that knowledge base.
-This would be required on any ontology that tracks changing knowledge, like stores, movie theatres and social media, for example.
- \paragraph{}
- Based on the previous two points, we can state that it would also be useful to have different benchmarks to test those different types of challenges and matching systems.
+ Based on the previous point, it would also be useful to have different benchmarks to test those different types of challenges and matching systems.
 This would allow for better comparison of methods and better tracking of the improvements in the field.
@@
 The challenge is to all available ontologies and other sources rather than just WordNet.
- \paragraph{}
- Matchers should be able to explain the results it produces, i.e.
-making those results more interpretable.
-This would allow a number of other improvements to occur.
-Firstly, it would allow users of a system to have more confidence in the results and make better decisions based on the source of the result.
-Secondly, it would allow people manually aiding the alignment to check if the matcher did a good job, and thus improve the interaction between the system and the domain expert.
-Thirdly, it would allow researchers to improve the matching system because they are able to detect the source of errors.
- \paragraph{}
- When these problems are solved, ontology matching has matured enough to be used in Semantic Web applications. Then it is merely the challenge to have the public adopt these technologies.
+
+ Word embeddings should be good at using other ontologies, since they can very quickly learn embeddings for all concepts in those ontologies.
+These embeddings can then be used during matching as an a priori believe of the locations of the word embeddings in semantic space.
+ \paragraph{}
+ When these and other problems are solved, ontology matching has matured enough to be used in Semantic Web applications. Then it is merely the challenge to have the public adopt these technologies.
 
  \subsection{Word representation} \label{w2v}
- % Meer McCallum noemen. 80 plaatjes %TODO
  An important area of research in Natural Language Processing is the representation of words.
@@
 This semantic similarity property is very useful for ontology alignment, as parts of one ontology have to be aligned with parts of another ontology depending on their semantic relation.
- \paragraph{}
+
+ \begin{figure}[H]
+ \centering
+ \includegraphics[width=0.8\textwidth]{plots/Skip-Gram}
+ \caption[Skip-Gram model]{The embedding of a word (in pink) is optimized to be close to its context embeddings (in purple) but far away from other embeddings (in red).}
+ \label{Skip-Gram-img2}
+ \end{figure}
+
  Skip-gram models work by teaching a 3-layer neural network to predict the context of a word.
@@
 
+ \begin{figure}[H]
+ \centering
+ \includegraphics[width=\textwidth]{plots/ssg}
+ \caption[Syntax Skip-gram]{Rather than ranking the output of the network with respect to the whole context, one output per item in the context is computed and ranked.}
+ \label{syntax-skipgram}
+ \end{figure}
+
  \subsubsection{Multi-sense} \label{multisense}
- %TODO Voorbeeld uit McCallum's slides kopieren en uitleggen
  Another interesting development is the multi-sense \emph{Word2vec}, which allows for multiple vector representations per word, depending on the number of different definitions a word has.
@@
 This idea sparked the second reason why I started investigating semantic word representations for ontology matching, since current methods do not allow for disambiguation.
- \paragraph{}
- For example, string matchers only look at the phrases representing the concepts, and as such do not care about semantics.
+
+ \begin{figure}[H]
+ \centering
+ \includegraphics[width=\textwidth]{plots/ms-skipgram}
+ \caption[Multi-sense Skip-gram]{The context is first used to find the right sense, which is then optimized to match the context.}
+ \label{ms-skipgram}
+ \end{figure}
+
+ String matchers only look at the phrases representing the concepts, and as such do not care about semantics.
 Structural matchers use the context, but do not use the meaning of the concept since they only look at the location of the concept within the graph.
@@
 
- %TODO AML toevoegen
+ \subsubsection{AgreementMaker} \label{agreementmaker}
+ AgreementMaker is an ontology matching system that obtained the highest F-measure in 6 of the 7 ontology matching tracks of OAEI 2015 \cite{oaei2015}.
+The system has also been updated the most recent at the time of writing\cite{agreementmaker}.
+
+ The system will be used as a benchmark to compare the results of this study.
+It uses many matchers in ensemble and therefore it is more realistic to compare my single matcher with a single matcher from the system, so I will do that too.
+%TODO remove als niet echt gebeurd.
+
+ Ideally it would be possible to extend the Agreementmaker system with the matcher developed in this study.
+However, their claim that the system is easily extendible does not ring true, as it was too hard for the scope of this project to accomplish.
+%TODO see \ref{appendix}
 
@@
  \emph{Word2vec} is an unsupervised method that implicitly maps words to a vector space that has been shown to contain semantic properties.
-Explicitly, it predicts words from the context of that word.
-%cite
+Explicitly, it predicts words from the context of that word\cite{w2v}.
  It can be trained on large corpora quickly and the resulting vectors can easily be used to measure the distance between words.
@@
  The data used comes from a list of data sets that the OAEI provides\cite{euzenat2013ontology}.
-% OAEI en kleine data common in OM.
-Vergelijkbaar met andere resultaten.
-Kleine datasets zijn logisch want: oude tak van sport.
- % Ik heb gekeken naar DeepWalk (nieuwe tak van sport)(gebruikt ook NN) OOK kleine data.
+Although the data is not as big as the dataset McCallum will use, there are a few reasons to use these data sets.
+
+ Firstly, it allows comparison to the state-of-the-art matchers as they all competed in the OAEI.
+Secondly, DeepWalk, an alternative way to transform graphs into vector representations, works on small graphs.
+Consequently, it is likely that other embedding models should work on small graphs as well.
+ \paragraph{}
  Every data set contains two ontologies that need to be aligned and a ground truth alignment.
 The goal is straightforward: find the alignment given only the ontologies and whichever outside resources are needed.
-
- \subsubsection{Preprocessing} \label{preprocessing}
 
@@
 
- \subsection{Algorithms}
- %TODO Move sommige naar discussions
+ \subsection{Algorithms} \label{implementations}
  %TODO per algorithme uitleggen: hoe het werkt. Waarom gekozen. Plaatjes. Volgorde van kiezen (ik denk dat deze beter past) en bij resultaten bespreken of deze volgorde klopt.
@@
 This way, all improvements are recorded precisely.
- The explanations refer back to the example in Section \ref{example}.
+ All algorithms use word embeddings, though the way they use word embeddings is different.  The explanations refer back to the example in Section \ref{example}.
+  \subsubsection{Pre-trained models}
+  The simplest way to use node embeddings for ontology matching is to obtain a model already trained on normal text.
+This model should already have learned some semantic context, although neighbourhood in text is different from that in an ontology.
+Also, since the words it is trained on might not match the labels from the ontology, two things need to be done.
+Firstly, if a word is not in the model, it is ignored.
+Secondly, the labels are split up into separate words and the resulting vectors are averaged.
+  This model was chosen because of its ease of implementation and to see if the graph-based context improves ontology matching over the text-based context.
   \subsubsection{Node vectorisation}
@@
 It may even be competitive with more advanced string matchers (that look at substrings of labels).
-For example, \emph{whisker} and \emph{moustache} will be matched by a substring matcher, but are also semantically similar since they will often be mentioned in the same context.
-  \subsubsection{Combine with neighbours}
-  To improve the model, we can add context information from the neighbours of a node.
-The most basic context adaptation would be to create a vector as the average of the context vectors.
-The resulting vector should be combined with the node vector of the node that is being investigated.
-This can be done by averaging or weighted averaging where the context is weighed more if there are more neighbours, though not necessarily linearly.
-These possibilities were also investigated.
-  For example, since the \emph{front paws} and \emph{arms} are both attached to the \emph{torso}, their context vectors will be similar as well.
+For example, \emph{whisker} and \emph{moustache} may be matched by a substring matcher, but are also semantically similar since they will often be mentioned in the same context.
+  This method was chosen because it is the foundation of all other models that use the graph-context. It is required to see if the extensions improve results.
+  \subsubsection{Bidirectional connections}
+  More connections means bigger context. For neural networks more data is always a good things. Therefore it is likely that this will improve results somewhat.
   \subsubsection{Select from senses}
-  Another way to take into account the influence of neighbouring nodes is to train a multi-sense node embedding model as described in Section \ref{multisense}, and selecting from the different node senses based on which is closest to the context average.
-  \subsubsection{Adding edge labels}
-  To add more information to the model, edge labels can also be added to the context of a node.
-This method effectively doubles the training data and context size when creating the context average.
-This should make the model more robust, although edge labels may be duplicate (one has many unique family members) and less informative in general, so a lower weight may be appropriate.
-A different possible problem with this method is that the relation between a neighbour node and its corresponding edge may be lost, since they are just treated as independent contexts.
-  In the case of the mouse ontology, the \emph{head} is above the \emph{torso} so \emph{isAbove} will be added to the context of \emph{head}.
-The same goes for the \emph{human head}, which will make them more similar.
-  \subsubsection{Select from senses}
-  This method is exactly the same as the selecting from node senses with just the neighbour nodes except that you now also take into account the edge labels.
-  \subsubsection{Combining edges with nodes}
-  As can be read in Section \ref{wordorder}, it is possible to drop the bag-of-words assumption that the context is sequence invariant.
-  This means we can for example have the context be (previous word, next word) and those words will be treated differently.
-Similarly we can separate the edge and node labels and treat them differently.
-This ensures that the model will find any relationship between the edge and the node if it exists and will take this into account.
-For example, \emph{isBelow} and \emph{torso} will combine into a vector that is similar to \emph{tail} whereas \emph{isAbove} and \emph{torso} combine into a vector that is similar to \emph{head} since the edge and node labels are combined in the model, rather than considered separately.
+  %TODO implement
+  One way to take into account the influence of neighbouring nodes is to train a multi-sense node embedding model as described in Section \ref{multisense}, and selecting from the different node senses based on which is closest to the context average.
   \subsubsection{Hot start}
@@
 In the case of \emph{Node2vec} they are more likely to be matched, since their neighbourhoods are the same (the only neighbour of both \emph{arms} and \emph{paws} is \emph{connectedTo torso}).
- \subsubsection{Training corpus}
-  Word embedding models need to be trained on a large corpus.
-These corpora need to cover the concepts that are contained in the ontology, but also need to be large enough to build good embeddings.
-Since the ontologies themselves do not necessarily contain enough examples to embed the concepts properly, I need to use ontologies that are likely to contain the concepts I want to align.
-In the case of the mice and men ontologies, anatomical or medical ontologies can be useful, since they may list more anatomical relationships or common relationships (for example \emph{whisker} and \emph{moustache} are related to \emph{hair}).
-  As a benchmark, I will use the WordNet and NELL ontologies.
-To check if adding the ontologies that are to be aligned helps, I will also train a model on an ontology consisting of WordNet, NELL and the two alignment candidates.
  \subsubsection{DeepWalk}
-  An alternative way of increasing the number of examples that the algorithm considers is using DeepWalk.
-DeepWalk generates sentences by randomly walking through the ontology and processes those sentences using a normal embedding model.
+  It is possible to increase the number of examples that the algorithm considers by using DeepWalk.
+DeepWalk generates sentences by randomly walking through the ontology and processes those sentences using a normal word embedding model.
 This has the advantage of having a wider neighbourhood, as the neighbours of neighbours are also used as context, or even further neighbours depending on the scope of the algorithm.
 It also allows for weighting of edges to change the sampling rate of the random walk, which can be used to prioritize important nodes or highlight informative neighbours.
+%TODO ref sentences
 
@@
 Despite that there is no significant difference in performance.
-For example, compare the Average Precision for the medical dataset with the anatomy dataset.
-The [...] %TODO AP is between baseline en AML for both?
- So the data does not cause the underperformance of the system.
+For example, compare the F-measures for the medical dataset and the anatomy dataset.
+From Section \ref{results} we can see that both F-measures improve over the baselines, therefore the datasets used do not seem to influence the algorithm by too much.
 
@@
   \begin{figure}[H]
+  \centering
   \includegraphics[width=0.9\textwidth]{plots/programdiagram}
@@
 
-  \paragraph{Preprocessing}
-%  The preprocessing works as described in Section \ref{preprocessing}. 
-  \paragraph{Matcher}The matcher is a simple KD-tree that finds the nearest neighbours of every node in the opposing ontology. This is unlikely to contain errors.
+  \paragraph{Preprocessing} \label{preprocessing}
+  The preprocessing transforms the OWL graph into a graph with just the nodes and edges.
+Since OWL uses blank nodes to structure the ontology and connects everything to \textit{Thing} and \textit{Nothing}, two OWL concepts, those need to be resolved and removed, respectively.
+
+  We can conclude that this works if the context extraction works. Please refer to Section \ref{contextextraction} for those results.
+  \paragraph{Matcher} The matcher gets as input the embeddings generated obtained by the algorithm.
+It uses these to calculate the distance between nodes and output the most likely alignments.
+As such it completes the system so that it produces a set of alignments from the two ontologies.
+
+  The matcher is a simple KD-tree that finds the nearest neighbours of every node in the opposing ontology. The KD-tree has been tested by its creator and as such does not contain errors.
   \paragraph{Data loading}
@@
 
-  \subsubsection{Context extraction}
+  \subsubsection{Context extraction} \label{contextextraction}
   There are different context extractors for some of the different algorithms.
@@
 
-  \begin{figure}
-%  \includegraphics[width=0.7\textwidth]{vowlview}
+  \begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7\textwidth]{plots/vowlview}
   \caption[]{}
@@
   \begin{table}[H]
+  \centering
   \caption[Edge comparison]{The number of edges compared to show that edge parsing was successful.}
@@
 
+ %TODO
+
  \newpage
  \subsection{Evaluation}
- The goal of the research is to find an ontology alignment algorithm $A$ and prove that it performs better than current techniques.
-However, as current techniques may combine many different algorithms and sources of information, maybe such a comparison is not fair, nor is a comparison with individual algorithms as they may be optimised for being combined.
-So, instead we may want to see if performance is improved when adding $A$ to an ensemble of algorithms $E=(A_1,..,A_n)$.
+ The goal of this study is to see if the developed ontology matching algorithm performs better than the best existing matchers. In this section I will define better.
  \subsubsection{Evaluation methods} \label{EvaluationMethods}
- The evaluation should be done using a performance measure $P(Al,T)$ that takes the alignment an algorithm produces given an ontology and the ground truth.
-If both the alignment and truth are considered sets of alignments, i.e.
-$Al=\{a_1,..,a_n\}$ and $T=\{a'_1,..,a'_m\}$, then the True Positives $TP=\{a|a\in Al, a\in T\}$, False Positives $FP=\{a|a\in Al, a\notin T\}$ and False Negatives $FN=\{a|a\in T, a\notin Al\}$ determine the performance of the alignment.
-
- \paragraph{Jaccard similarity}
- The True Negatives do not matter, as there are extremely many, and the goal of ontology matching is to find True Positives.
-If we only care about True Positives, the Jaccard similarity is a prime candidate for the performance measure.
-
- The Jaccard similarity is calculated as follows
- \[
- J = \frac{TP}{TP + FP + FN}
- \]
- i.e. the fraction of the true positives over the sum of the true positives and mistakes.
- \paragraph{}
- The Jaccard similarity is a number between 0 and 1, with a higher number being better.
-Therefore if we compare two alignments, the one which is most similar to the truth, i.e.
-has a higher Jaccard similarity, is the better one.
- \paragraph{}
- However, if we want to find out if an algorithm improves an ensemble, we calculate the improvement as follows:
- \[
- I = J_{E\cup \{A\}} - J_E
- \]
- where $J_E$ is the Jaccard coefficient of an ensemble $E$.
- To see if an algorithm is useful to an ensemble, the improvement score $I$ has to be \emph{significantly} higher than zero.
-To check if a score is significant, a statistical significance test will have to be carried out, which works as follows: generate $N$ solutions randomly and score them.
-Then score the method you want to investigate.
-If the score is in the top p\%, it is significant, otherwise it is not.
-In this case the solutions are $E\cup \{R\}$, where $R$ is an algorithm that generates random alignments\cite{fisher1925statistical}.
- \paragraph{}
- It is in principle possible to weigh False Positives and False Negatives differently, but this is not done in practice.
-To make the results of this study easily comparable to others, equal weights will be used.
-
- % Comparing the results.
+ Since for the used data the ground truth is available, comparison is straightforward.
+Namely, the algorithm that finds the most items that are also in the ground truth in the lowest number of attempts.
+This definition, however, has two parts: the number of correct attempts and the total number of attempts.
+This makes it hard to compare two algorithms, as one may be better with few attempts allowed whereas the other may be better with more attempts allowed.
+
+ Precision represents the number of attempts: it is the ratio of the correct attempts divided by the total number of attempts.
+However, if you make only one attempt and it is correct, you cannot improve your precision by making more attempts.
+This solution is to balance precision with recall.
+Recall is the ratio of the correct attempts divided by the number of items in the ground truth.
+Often a higher recall results in lower precision as items from the ground truth become increasingly harder to recognise.
+For example, concepts with the same label are easy to link, but synonyms are much harder to link.
+
+ To balance precision and recall we use the $F$-measure.
+It uses a balance factor to favour either precision or recall.
+The $F_1$-measure is the harmonic mean of the two.
+The $F_1$-measure is used in this study.
+This is in correspondence to studies in the same area of research and thus allows for good comparison.
+
+ However there is still one problem remaining.
+The algorithm outputs a confidence measure for every possible alignment.
+This means that the $F$-measure depends on the confidence threshold to select which alignments become attempts.
+The optimal threshold can be decided by using a validation set to check the most likely thresholds.
+
  We want to compare to a baseline to ensure proper interpretation of the results.
-However, to test the hypothesis it is also required to compare the results to the best scoring algorithm on the same data set.
+For example, it is possible that a very simple baseline algorithm is already able to obtain a good score.
+In that case the results of the algorithm should be corrected.
+A higher score is still better, but an improvement from $0.1$ to $0.2$ is not as impactful as an improvement from $0.8$ to $0.9$.
+
+ To test the hypothesis it is also required to compare the results to the best scoring algorithm on the same data set.
+However, as the best scoring ontology alignment \textit{system} uses many algorithms in an ensemble, it would be an unfair comparison.
+There are two solutions.
+
+ Firstly, if the ensemble is extended with the algorithm of this study, it is possible to see if the algorithm improves the ensemble and thus can find alignments the other algorithms cannot find.
+ However, as the it is not possible to change the ensemble used in the best alignment system, this is not possible.
+
+ The second option is to compare the algorithm to every single algorithm in the ensemble.
+This is possible as the whole system is available and single algorithm can be separately used.
+This method was used in this study.
 
@@
 
- %TODO F-pieken aanwijzen. Dan confidence vs F-measure bespreken in interpretation.
- % Wat is de threshold van AML?
- % Extra rij met baseline literal string matcher
+ %TODO F-pieken aanwijzen.
  \subsection{Precision versus recall}
@@
   \begin{figure}[H]
+   \centering
 
@@
 
- %\subsection{Recap research question} % Maak 'figure' van
- %\subsection{Recap hypotheses}
  \subsection{Conclusions} \label{conclusions}
-
  The goal of this study was to answer the research question from Section \ref{researchquestion}:
+
  \begin{center}
  \textit{
- Can distributed representations of concepts be used to find relationships between concepts in ontologies better than the best existing matcher?
- } % Zelfde als sectie hypothese?
+ Can distributed representations of concepts be used to find relationships between concepts in ontologies?
+ }
  \end{center}
@@
 
-\paragraph{The algorithm uses distributed representations of concepts} %TODO In de uitleg van het algoritme duidelijk maken dat dit zo is.
-
-Yes. They all use distributed representations since they all convert words into vectors:
-\begin{description} \item[pre-trained Word2vec] ... 
-\item[] ...
+\paragraph{The algorithm uses distributed representations of concepts}
+ From Section \ref{implementations} it is clear that every single algorithm uses distributed representations. To summarize:
+\begin{description}
+\item[pre-trained Word2vec] Uses existing distributed representations on every word in a label.
+\item[Node2vec] All implementations of the Node2vec algorithms, monodirection, bidirectional and multi-sense, convert nodes into vectors.
+\item[DeepWalk] Trains a normal distributed representation model on labels with the context generated from a random walk.
 \end{description}
-\paragraph{The algorithm finds relationships between concepts in ontologies} %TODO In de system check duidelijk maken.
-
+\paragraph{The algorithm finds relationships between concepts in ontologies}
 This is correct as the inputs are always two ontologies and the output is always a set relationships between the ontologies.
-\paragraph{The algorithm performs better}
+\paragraph{The algorithm performs better than the best matcher}
 
@@
  \subsection{Discarded algorithms}
+  %TODO (her)schrijf
+  \subsubsection{Combine with neighbours}
+  To improve the model, we can add context information from the neighbours of a node.
+The most basic context adaptation would be to create a vector as the average of the context vectors.
+The resulting vector should be combined with the node vector of the node that is being investigated.
+This can be done by averaging or weighted averaging where the context is weighed more if there are more neighbours, though not necessarily linearly.
+These possibilities were also investigated.
+  For example, since the \emph{front paws} and \emph{arms} are both attached to the \emph{torso}, their context vectors will be similar as well.
+
+  \subsubsection{Adding edge labels}
+  To add more information to the model, edge labels can also be added to the context of a node.
+This method effectively doubles the training data and context size when creating the context average.
+This should make the model more robust, although edge labels may be duplicate (one has many unique family members) and less informative in general, so a lower weight may be appropriate.
+A different possible problem with this method is that the relation between a neighbour node and its corresponding edge may be lost, since they are just treated as independent contexts.
+  In the case of the mouse ontology, the \emph{head} is above the \emph{torso} so \emph{isAbove} will be added to the context of \emph{head}.
+The same goes for the \emph{human head}, which will make them more similar.
+
+  \subsubsection{Combining edges with nodes}
+  As can be read in Section \ref{wordorder}, it is possible to drop the bag-of-words assumption that the context is sequence invariant.
+  This means we can for example have the context be (previous word, next word) and those words will be treated differently.
+Similarly we can separate the edge and node labels and treat them differently.
+This ensures that the model will find any relationship between the edge and the node if it exists and will take this into account.
+For example, \emph{isBelow} and \emph{torso} will combine into a vector that is similar to \emph{tail} whereas \emph{isAbove} and \emph{torso} combine into a vector that is similar to \emph{head} since the edge and node labels are combined in the model, rather than considered separately.
+
+ \subsubsection{Training corpus}
+  Word embedding models need to be trained on a large corpus.
+These corpora need to cover the concepts that are contained in the ontology, but also need to be large enough to build good embeddings.
+Since the ontologies themselves do not necessarily contain enough examples to embed the concepts properly, I need to use ontologies that are likely to contain the concepts I want to align.
+In the case of the mice and men ontologies, anatomical or medical ontologies can be useful, since they may list more anatomical relationships or common relationships (for example \emph{whisker} and \emph{moustache} are related to \emph{hair}).
+  As a benchmark, I will use the WordNet and NELL ontologies.
+To check if adding the ontologies that are to be aligned helps, I will also train a model on an ontology consisting of WordNet, NELL and the two alignment candidates.
 

### 2016-07-06 Paper/Draft.tex
All TODOs except intro and conclusion done

@@
  \usepackage{multirow}
+ \usepackage[dvipsnames]{xcolor}
+ \usepackage[nottoc,numbib]{tocbibind}
 
@@
  \section*{Acknowledgements}
+ Arjen de Vries, professor at the Radboud University of Nijmegen and my mentor - Kennis enthusiasme en als het tegenzat kon hij me toch motiveren.
+ Sanna Dinh, my partner - Nachtenlang opgebleven om het schrijfwerk en plaatjes
+ Jeroen Vuurens, Delft University of Technology - Sparren over word2vec
+ Xander Wilcke - Inspireren over het Semantisch Web
+ Marianne - op de gekste tijdstippen skypen en proof-readen
+ Suzan Verberne, professor at the Radboud University of Nijmegen - Nakijken
+ Flynn, my pug - For the fresh air when I needed a minute to relax
+
  \section*{Abstract}
+ McCallum proposed using distributed word embeddings for knowledge base completion, the problem of finding relations \textit{within} a knowledge base.
+In this study distributed word embeddings were used for ontology matching, the problem of finding relations \textit{between} knowledge bases.
+To test if distributed word embeddings also work on ontology matching, multiple algorithms that adapt these embeddings to ontology graphs were implemented.
+
+ The conclusion is that distributed word embeddings can be applied to ontology matching.
+The performance is not as good as the state-of-the-art methods yet.
+However, distributed word embeddings have potential to improve with more data as opposed to current methods which are hand-crafted.
 
@@
 
+ %TODO leg uit waarom intra implies inter
+ %TODO maak duidelijk dat het \textit{mijn} idee was om inter te doen
+
  McCallum plans on using these embeddings to predict new intra-knowledge base relations.
@@
  Currently, knowledge base and ontology alignment techniques do not make use of embeddings.
-Since embedding models have good performance on intra-knowledge base relation prediction, they should also work well on ontology alignment.
+Since embedding models have good performance on knowledge base reconstruction\cite{universalschema}, they should also work well on ontology alignment.
 
@@
 
- \subsection{Hypothesis} \label{hypotheses}
-
- \begin{center}
- \textit{Matchers that use a distributed representation of concepts can find relationships between concepts in ontologies better than the best existing matchers.}
- \end{center}
-
- To prove this hypothesis, I must proof the following points:
+ To answer the research question, I must investigate the following points:
  \begin{itemize}
@@
  \item The algorithm finds relationships between concepts in ontologies.
- \item The algorithm performs better.
+ \item The algorithm performs well.
  \end{itemize}
 
- \paragraph{}
- This hypothesis is true for distributed representations matching in general if it is true for one distributed representation matcher.
-Therefore to test the hypothesis, I must test it for every distinct implementation of the matcher.
+ The answer is positive for distributed representations matching in general if it is positive for one distributed representation matcher.
 
@@
 The last two sections are the results and the joint conclusion and discussion, which interpret the results.
+ %TODO dieper of weg
 
@@
  \subsubsection{Example} \label{example}
- In this section I will give an example of a pair of anatomical ontologies with their alignment. This example will be used throughout this work.
+ In this section I will give an example of a pair of anatomical ontologies with their alignment, which will be used throughout this work.
 
@@
 The two concepts may also have different labels in their context even though their contexts refer to the same concepts.
-  \item The size of the training corpus should be large enough for proper representation to be learned for every concept.
-It should also be relevant to the labels that are in the ontologies.
-This is a problem since the ontologies may be relatively small, so they need to be extended while keeping relevance.
+  \item The size of the training corpus should be large enough for proper representation to be learned for every concept. This is a problem since the ontologies may be relatively small. 
+  \item The representations should also be relevant to the labels that are in the ontologies.
+For example, a model pre-trained on text will likely have very different embeddings than trained on an ontology, and may as such not be very useful.
   \item Some labels may be ambiguous, for example homonyms, which are concepts that have the same label but represent a different context.
@@
 Since they are similar creatures, there are many correspondences between the anatomy.
-The ontologies contain X and Y nodes, and X and Y edges, respectively.
-There are Z correspondences between the two ontologies.
+The ontologies contain 1838 and 3298 nodes, and 1807 and 3761 edges, respectively.
+There are 1516 correspondences between the two ontologies.
  \paragraph{}
@@
  \subsubsection{Medical}
- The second data set is larger, boasting X and Y medical concepts with X and Y relations. There are Z correspondences between the two ontologies. This data set has N different edge labels.
+ The second data set is larger, boasting 23692 and 16923 medical concepts with 31289 and 18932 relations. There are 18476 correspondences between the two ontologies.
 
  \subsection{Algorithms} \label{implementations}
- %TODO per algorithme uitleggen: hoe het werkt. Waarom gekozen. Plaatjes. Volgorde van kiezen (ik denk dat deze beter past) en bij resultaten bespreken of deze volgorde klopt.
  In this section, I will discuss the different implementations that were made of the algorithm.
@@
   This model was chosen because of its ease of implementation and to see if the graph-based context improves ontology matching over the text-based context.
+  \subsubsection{DeepWalk}
+  DeepWalk generates sentences by randomly walking through the ontology and processes those sentences using a normal word embedding model.
+This means it is possible to have a wide neighbourhood, as the neighbours of neighbours are also used as context, or even further neighbours depending on the scope of the algorithm.
+It also allows for weighting of edges to change the sampling rate of the random walk, which can be used to prioritize important nodes or highlight informative neighbours.
+  One adaptation over normal Deepwalk that was considered is switching between ontologies when on a concept from the correspondence set.
+For example, if both ontologies contain \textit{eye}, when the algorithm lands on the corresponding node, it will have a chance to switch to the other ontology.
+As such the sentence will contain concepts from both ontologies and they will move closer together.
+See \ref{sentences} for an example of the sentences generated by DeepWalk.
   \subsubsection{Node vectorisation}
@@
   \subsubsection{Select from senses}
-  %TODO implement
   One way to take into account the influence of neighbouring nodes is to train a multi-sense node embedding model as described in Section \ref{multisense}, and selecting from the different node senses based on which is closest to the context average.
@@
 In the case of \emph{Node2vec} they are more likely to be matched, since their neighbourhoods are the same (the only neighbour of both \emph{arms} and \emph{paws} is \emph{connectedTo torso}).
- \subsubsection{DeepWalk}
-  It is possible to increase the number of examples that the algorithm considers by using DeepWalk.
-DeepWalk generates sentences by randomly walking through the ontology and processes those sentences using a normal word embedding model.
-This has the advantage of having a wider neighbourhood, as the neighbours of neighbours are also used as context, or even further neighbours depending on the scope of the algorithm.
-It also allows for weighting of edges to change the sampling rate of the random walk, which can be used to prioritize important nodes or highlight informative neighbours.
-%TODO ref sentences
 
@@
 For example, compare the F-measures for the medical dataset and the anatomy dataset.
-From Section \ref{results} we can see that both F-measures improve over the baselines, therefore the datasets used do not seem to influence the algorithm by too much.
-
- %Ik heb bewust gekozen voor kleine data zodat het te vergelijken was met andere matchers. Want iedereen in OM gebruikt kleine datasets.
- %Deepwalk paper ook kleine data
- %Misschien heb ik te weinig data gebruikt maar er is geen grote dataset met ground truth beschikbaar.
- %Further research: grote dataset maken door LOD te pakken, 10% weg te gooien en kijken of je dat reconstruct. 
+From Section \ref{results} we can see that both F-measures improve over the baselines, therefore the datasets used do not seem to influence the algorithm by much.
   \subsubsection{The system}
@@
   \paragraph{}
-  Since every part works, the system is not faulty. %TODO kan beter
+  Since every part works, the system is not faulty.
 
@@
   \paragraph{}
-  First, I obtained the number of edges from VOWLview\cite{vowlview}, an ontology graphing program, which looks like Figure \ref{vowlfig}.
+  First, I obtained the number of edges from VOWLview\cite{vowlview}, an ontology graphing program, represented in Figure \ref{vowlfig}.
 This was necessary since the creators of the data did not share how many edges were in the database.
@@
   \includegraphics[width=0.7\textwidth]{plots/vowlview}
-  \caption[]{}
+  \caption[VOWLview of mice dataset]{The mice dataset visualized in VOWLview.
+It shows the hierarchical nature of the data, as subclasses circle their superclass.
+It also shows that many individual classes are not connected, and as such structure cannot be used in the matching process.}
   \label{vowlfig}
@@
  \subsubsection{Example: DeepWalk sentences} \label{sentences}
-
- %TODO
-
+ Sentence lengths vary from 1 to about a hundred.
+The lower limit is due to the fact that some nodes do not have neighbours and as such the sentence is cut short.
+The upper limit not precise since the sentence end is random.
+
+ Below are some examples of sentences.
+ \begin{figure}[H]
+ \paragraph{}
+ \textcolor{Plum}{incus} \textcolor{red}{auditory\_bone} \textcolor{Plum}{\underline{incus}} \textcolor{blue}{ auditory\_ossicle ear\_part cymba\_conchae}
+ \paragraph{}
+  \textcolor{red}{brain\_nucleus brainstem\_nucleus red\_nucleus brainstem\_nucleus raphe\_pallidus\_nucleus brainstem\_nucleus trochlear\_iv\_nucleus brainstem\_nucleus nucleus\_of\_trapezoid\_body}
+  \paragraph{}
+  \textcolor{red}{hip\_joint hindlimb\_joint} \textcolor{Plum}{\underline{ankle\_joint}} \textcolor{blue}{joint\_by\_site cricoarytenoid\_joint}
+  \label{jumpingsentence}
+  \caption[Sentence that runs over both ontologies]{Example of a sentences that run over both ontologies.
+The words are color coded according to which ontology they occur in.
+Red is the mice ontology, blue the human ontology and purple words occur in both ontologies.
+Underlined words indicate a point at which the walker switches between the ontologies.}
+ \end{figure}
+
+ The first and third sentence both contain words that are in both ontologies.
+However, in the first sentence the switch does not occur immediately.
+The second sentence contains words from just one ontology.
+This will improve the embeddings for that ontology, but will not teach the algorithm about the mapping from one ontology to the other.
+
+ \begin{figure}[H]
+ \paragraph{}
+ \textbf{thyroid\_gland\_left\_lobe}
+ \label{singlesentence}
+ \caption[Sentence with single word]{Some sentences contain only one word. Often these words refer to nodes with no neighbours.}
+ \end{figure}
  \newpage
@@
    \centering
-   \includegraphics[width=\textwidth]{plots/untrained_ROC}
-   \caption[Precision-recall curve untrained mice]{The precision and recall trade-off for the results of the untrained Node2vec.}
-   \label{ROC_untrained}
+   \includegraphics[width=\textwidth]{plots/trained_ROC}
+   \caption[Precision-recall curve trained mice model]{bidirectional Node2vec.}
+   \label{ROC_trained}
   \end{figure}
@@
  \begin{subfigure}{.3\textwidth}
-   \centering
-   \includegraphics[width=\textwidth]{plots/trained_ROC}
-   \caption[Precision-recall curve trained mice model]{bidirectional Node2vec.}
-   \label{ROC_trained}
+   \centering\includegraphics[width=\textwidth]{plots/untrained_ROC}
+   \caption[Precision-recall curve untrained mice]{Random for comparison.}
+   \label{ROC_untrained}
   \end{subfigure}
@@
   \end{subfigure}
-  \caption{Precision-recall trade-off curve for the results of three more algorithms.}
+  \caption[Three more precision-recall curves]{Precision-recall trade-off curve for the results of three more algorithms.}
   \end{figure}
@@
   \begin{table}[H]
-  \caption[$F_1$ mice]{The $F_1$-scores for the different matchers for the mice dataset compared to the result of AML at OAEI 2015 \cite{oaei2015}}
+  \caption[$F_1$]{The $F_1$-scores for the different matchers for the mice and medical datasets compared to the result of AML at OAEI 2015 \cite{oaei2015}}.
   \label{fscores}
@@
   Random & 0.6926 & 0.4905 \\
-  Generic & 0.6372 & 0.3874 \\
+  Pre-trained & 0.6372 & 0.3874 \\
   Bidirectional & 0.8432 & 0.4946 \\
+  Multi-sense & 0.6926 & 0.4905 \\
   Deepwalk & 0.6926 & 0.4906 \\
-  Alternative & 0.6372 & 0.4905 \\
-  \textbf{AML ensemble} & \textbf{0.94} & \textbf{0.81} \\ %http://disi.unitn.it/~pavel/om2015/
-  %papers/om2015_proceedings.pdf#page=125
+  Alternative DeepWalk & 0.6372 & 0.4905 \\
+  \textbf{AML ensemble} & \textbf{0.94} & \textbf{0.81} \\
   \end{tabular}
   \end{table}
-  %\subsection{Jaccard}
-  %TBD
-  \subsection{Examples to illustrate the differences}
-  TBD
+
+  \subsection{Example }
+  (cortical\_layer\_iii,external\_pyramidal\_cell\_layer)
 
@@
  \subsection{Interpretation}
+
  \subsubsection{Unexpected results}
@@
  \subsection{Conclusions} \label{conclusions}
+ %TODO conclusie: het werkt. Alleen niet beter dan de beste.
  The goal of this study was to answer the research question from Section \ref{researchquestion}:
@@
 This is correct as the inputs are always two ontologies and the output is always a set relationships between the ontologies.
-\paragraph{The algorithm performs better than the best matcher}
-
-Not yet.
-
-I compared the results of the algorithms with AML, the best existing matcher.
-All algorithms perform below AML.
-However, there is potential for better performance as we can see in Section \ref{discussion}.
+\paragraph{The algorithm performs well}
+%TODO ook bij hypotheses weghalen
+ One of the algorithms finds new relations. Therefore we can conclude that the algorithm can be used for ontology matching.
+
+ All algorithms perform worse than the full AML ensemble. However, as detailed further in Section \ref{discussion}, there is potential for embedding methods.
 \paragraph{}
@@
  %TODO gooi weg wat niet meer waar is
+  %TODO Duidelijk maken waarom algoritme nog potentie heeft
 
@@
 
- \section{Bibliography} %Fix
-
  \newpage

### 2016-07-06 Paper/Draft.tex
All TODOs finished except big dataset, AML singles and AML review

@@
  \section*{Summary}
- %TODO Definitions
- %TODO Word index
- %TODO spelling (database dataset)
- %TODO volgorde bieb (APA?)
- %TODO Results interpretation: uitleg waarom hoger en lager
- %TODO Verbeteringen discussieren
- %TODO Verwijder ensemble uit evaluation
- %TODO F-measure aan evaluation
  \tableofcontents
@@
 
- %TODO leg uit waarom intra implies inter
- %TODO maak duidelijk dat het \textit{mijn} idee was om inter te doen
-
  McCallum plans on using these embeddings to predict new intra-knowledge base relations.
@@
 
+ Applying the embedding tensor factorisation to inter-knowledge base relation finding (i.e.
+ontology aligning) makes it objective.
+This is because for ontology aligning there is a ground truth possible and available.
+There are also many projects on ontology aligning so it is possible to compare the results with the best methods available.
+This means ontology aligning is a good test for this algorithm.
+
  An example of an inter-knowledge base relation is shown in Figure \ref{merge_graph}.
 If these relations can be predicted, multiple knowledge bases can be aligned.
-Doing ontology alignment using these word embeddings is the goal of this work.
- \paragraph{}
- Currently, knowledge base and ontology alignment techniques do not make use of embeddings.
-Since embedding models have good performance on knowledge base reconstruction\cite{universalschema}, they should also work well on ontology alignment.
+Testing if this word embedding algorithm is versatile enough to work in the field of ontology aligning is the goal of this work.
 
@@
 Distributed word representations, specifically multi-sense \emph{Word2vec}, should be used for this problem since multi-sense \emph{Word2vec} is specifically designed to combat homonymy while the neural networks in distributed word representations use the context to deal with ambiguity.
-  %TODO vraag Arjen of dit 'antwoord' in problem hoort
 
@@
  \subsection{Overview}
- This report is structured as follows: firstly, I will give all the required background information required to understand the context and the algorithms I will use.
-Then, I will describe the method, which includes the design of the algorithm and the evaluation method.
-The last two sections are the results and the joint conclusion and discussion, which interpret the results.
- %TODO dieper of weg
+ This report is structured as follows: firstly, I will give all the background information required to understand the context and the algorithms I will use.
+This includes the history and future of the Semantic Web, the roles of ontologies in the Semantic Web, ontology aligning and the recent developments in word embeddings.
+
+ Secondly, I will describe the method, which includes the design of the algorithm, the whole system and the evaluation method.
+Multiple algorithms will be described that all use word embeddings differently.
+
+ Thirdly, the results. These show how the algorithms perform when applied to ontology aligning. The results will be compared to a baseline and the best performing system so far.
+
+ Lastly, the conclusion and discussion, which interpret the results and give recommendations for future research.
 
@@
 
- \subsection{Implementation}
- The foundation the algorithm has been build and tested on is Factorie, described in \ref{factorie}.
-Earlier work on a forked branch of factorie was done by \cite{multisensecode} to implement multi-sense \emph{Word2vec}.
-
- % Hier de pipeline omschrijven zoals in discussie.system
-
  \subsection{System check}
@@
  \paragraph{}
- \textcolor{Plum}{incus} \textcolor{red}{auditory\_bone} \textcolor{Plum}{\underline{incus}} \textcolor{blue}{ auditory\_ossicle ear\_part cymba\_conchae}
- \paragraph{}
-  \textcolor{red}{brain\_nucleus brainstem\_nucleus red\_nucleus brainstem\_nucleus raphe\_pallidus\_nucleus brainstem\_nucleus trochlear\_iv\_nucleus brainstem\_nucleus nucleus\_of\_trapezoid\_body}
-  \paragraph{}
-  \textcolor{red}{hip\_joint hindlimb\_joint} \textcolor{Plum}{\underline{ankle\_joint}} \textcolor{blue}{joint\_by\_site cricoarytenoid\_joint}
+ 1) \textcolor{Plum}{incus} \textcolor{red}{auditory\_bone} \textcolor{Plum}{\underline{incus}} \textcolor{blue}{ auditory\_ossicle ear\_part cymba\_conchae}
+ \paragraph{}
+ 2) \textcolor{red}{brain\_nucleus brainstem\_nucleus red\_nucleus brainstem\_nucleus raphe\_pallidus\_nucleus brainstem\_nucleus trochlear\_iv\_nucleus brainstem\_nucleus nucleus\_of\_trapezoid\_body}
+  \paragraph{}
+ 3) \textcolor{red}{hip\_joint hindlimb\_joint} \textcolor{Plum}{\underline{ankle\_joint}} \textcolor{blue}{joint\_by\_site cricoarytenoid\_joint}
   \label{jumpingsentence}
@@
 
- %TODO F-pieken aanwijzen.
  \subsection{Precision versus recall}
@@
    \includegraphics[width=\textwidth]{plots/trained_ROC}
-   \caption[Precision-recall curve trained mice model]{bidirectional Node2vec.}
+   \caption[Precision-recall curve trained mice model]{Precision-recall trade-off curve for the results of bidirectional Node2vec. Red indicates the maximum $F_1$-score.}
    \label{ROC_trained}
@@
    \subsubsection{Medical data}
-   TBD
+
+  \begin{figure}
+    \begin{subfigure}{.45\textwidth}
+   \centering\includegraphics[width=\textwidth]{plots/medical_generic_ROC}
+   \caption[Precision-recall curve pre-trained medical]{Pre-trained}
+   \label{ROC_pretrained_medical}
+  \end{subfigure}
+ \begin{subfigure}{.45\textwidth}
+   \centering
+   \includegraphics[width=\textwidth]{plots/medical_trained_ROC}
+   \caption[Precision-recall curve trained medical]{Bidirectional}
+   \label{ROC_trained_medical}
+  \end{subfigure}
+  \caption[Medical precision-recall curves]{Precision-recall trade-off curve for the results of two algorithms on the medical dataset.}
+  \end{figure}
 
@@
   Random & 0.6926 & 0.4905 \\
-  Pre-trained & 0.6372 & 0.3874 \\
+  Pre-trained & 0.6926 & 0.3874 \\
   Bidirectional & 0.8432 & 0.4946 \\
@@
   Deepwalk & 0.6926 & 0.4906 \\
-  Alternative DeepWalk & 0.6372 & 0.4905 \\
+  Alternative DeepWalk & 0.6926 & 0.4905 \\
   \textbf{AML ensemble} & \textbf{0.94} & \textbf{0.81} \\
@@
 
-  \subsection{Example }
-  (cortical\_layer\_iii,external\_pyramidal\_cell\_layer)
-
  \newpage
  \subsection{Interpretation}
-
- \subsubsection{Unexpected results}
- \subsubsection{Expected results}
 
@@
  \subsection{Conclusions} \label{conclusions}
- %TODO conclusie: het werkt. Alleen niet beter dan de beste.
  The goal of this study was to answer the research question from Section \ref{researchquestion}:
@@
 \paragraph{The algorithm performs well}
-%TODO ook bij hypotheses weghalen
  One of the algorithms finds new relations. Therefore we can conclude that the algorithm can be used for ontology matching.
@@
  All algorithms perform worse than the full AML ensemble. However, as detailed further in Section \ref{discussion}, there is potential for embedding methods.
-\paragraph{}
- Because the last point is not true, the answer is not in agreement with my hypothesis from Section \ref{hypotheses}.
- \paragraph{}
-The results from all the different evaluation measures are in agreement. From those results we can conclude the following:
-
- \begin{center}
- \textit{
- The distributed word representations system is currently \textbf{not} able to find relationships between concepts in ontologies better than existing matchers.
- }
- \end{center}
-
- %TODO Arjen vragen dit te bekijken
 
  \subsection{Discussion} \label{discussion}
- %TODO gooi weg wat niet meer waar is
-  %TODO Duidelijk maken waarom algoritme nog potentie heeft
-
-  This study shows that the algorithm of McCallum et al as shown in \cite{mccallumweblecture} does not help improve the results of ontology alignment over the straightforward baseline of simply pairing labels based on their syntactic similarity in the area of ontology matching.
+  This study shows that the algorithm of McCallum et al as shown in \cite{mccallumweblecture} does not help improve the results of ontology alignment more than current methods already do.
 
   The results show that one assumption that was made by the developers of the Universal Schema was incorrect, namely the assumption that when combining knowledge bases matching labels refer to the same entity and vice versa.
-For example, Bill Gates is called Bill Gates in FreeBase as well as retrieved from unstructured text.
+For example, the assumption that Bill Gates is called Bill Gates in FreeBase as well as in all unstructured text does not hold up.
 In reality, there may be multiple entities named Bill Gates and the same entity may be labelled differently.
 
-  This assumption will weaken further as an increasingly growing part of the Semantic Web is automatically generated and as such different labels can be assigned to the same entity.
+  This assumption become even weaker as an increasingly growing part of the Semantic Web is automatically generated and as such different labels can be assigned to the same entity.
 One of the goals of ontology matching is to link those differently labelled entities.
 
-  %In de presentatie zegt hij ook dat hij niet gaat proberen dingen meteen op elkaar te matchen maar gewoon alles houdt zoals het gelezen is/in de KB staat.
-Toch haalt hij goede resultaten met rule discovery e.d.
-
-  % Het was wel gelukt als ik ... (wat eerst future research was)
+  In the following sections I will describe a number of extensions that might improve the algorithm further such that it may one day rival hand-crafted methods in their domain and be unparalleled in the big data domain.
 
  \subsection{Discarded algorithms}
-  %TODO (her)schrijf
   \subsubsection{Combine with neighbours}
-  To improve the model, we can add context information from the neighbours of a node.
+  To improve the model, context information from the neighbours of a node can be added.
 The most basic context adaptation would be to create a vector as the average of the context vectors.
@@
 This can be done by averaging or weighted averaging where the context is weighed more if there are more neighbours, though not necessarily linearly.
-These possibilities were also investigated.
   For example, since the \emph{front paws} and \emph{arms} are both attached to the \emph{torso}, their context vectors will be similar as well.
@@
 For example, \emph{isBelow} and \emph{torso} will combine into a vector that is similar to \emph{tail} whereas \emph{isAbove} and \emph{torso} combine into a vector that is similar to \emph{head} since the edge and node labels are combined in the model, rather than considered separately.
+As the datasets used in this study did not provide any edge labels, the method could not be studied.
 
@@
 These corpora need to cover the concepts that are contained in the ontology, but also need to be large enough to build good embeddings.
-Since the ontologies themselves do not necessarily contain enough examples to embed the concepts properly, I need to use ontologies that are likely to contain the concepts I want to align.
-In the case of the mice and men ontologies, anatomical or medical ontologies can be useful, since they may list more anatomical relationships or common relationships (for example \emph{whisker} and \emph{moustache} are related to \emph{hair}).
-  As a benchmark, I will use the WordNet and NELL ontologies.
-To check if adding the ontologies that are to be aligned helps, I will also train a model on an ontology consisting of WordNet, NELL and the two alignment candidates.
-
-  \subsubsection{Just context nodes}
-
-  \subsubsection{Just edges}
-
-  \subsubsection{Context matrix representation}
+Since the ontologies themselves do not necessarily contain enough examples to embed the concepts properly, other ontologies that contain the same concepts can be useful.
+In the case of the mice and men ontologies, anatomical or medical ontologies may be used, since they may list more anatomical relationships or common relationships (for example \emph{whisker} and \emph{moustache} are related to \emph{hair}).
+  Since no such ontologies exist for the OAEI datasets, this extension could not be investigated.
 

### 2016-07-07 Paper/Draft.tex
Added acknowledgements

@@
  \section*{Acknowledgements}
- Arjen de Vries, professor at the Radboud University of Nijmegen and my mentor - Kennis enthusiasme en als het tegenzat kon hij me toch motiveren.
- Sanna Dinh, my partner - Nachtenlang opgebleven om het schrijfwerk en plaatjes
- Jeroen Vuurens, Delft University of Technology - Sparren over word2vec
- Xander Wilcke - Inspireren over het Semantisch Web
- Marianne - op de gekste tijdstippen skypen en proof-readen
- Suzan Verberne, professor at the Radboud University of Nijmegen - Nakijken
- Flynn, my pug - For the fresh air when I needed a minute to relax
+ Arjen de Vries, professor at the Radboud University of Nijmegen and my mentor, for his limitless pool of knowledge and enthusiasm.
+For getting me out of the mud when I was stuck and motivating me to push on.
+Suzan Verberne, professor at the Radboud University of Nijmegen, for co-reading
+ Jeroen Vuurens, from Delft University of Technology, for helping me figure out Word2vec.
+ Xander Wilcke, from the VU Amsterdam, for inspiring me to combine Machine Learning with the Semantic Web.
+ Sanna Dinh, my partner, for spending countless hours in the night making this thesis readable and designing many of the images, making this thesis understandable.
+ Marianne, my mother-in-law, for being available on Skype at the most unconventional times to advise and proof-read. Flynn, my pug - For the fresh air when I needed a minute to relax.
 
@@
  \subsection{Interpretation}
+ %TODO interpretation
 

### 2016-07-07 Paper/Draft.tex
Added images to algorithms

--- 2016-07-06 Paper/Draft.tex
@@
 
+ \hfuzz=20pt % No more overfull hboxes!
+
  \title{Matching ontologies with distributed word embeddings}
@@
  }\footnote{Credit: Sanna Dinh}
+
  \newpage
@@
  \section*{Acknowledgements}
- Arjen de Vries, professor at the Radboud University of Nijmegen and my mentor - Kennis enthusiasme en als het tegenzat kon hij me toch motiveren.
- Sanna Dinh, my partner - Nachtenlang opgebleven om het schrijfwerk en plaatjes
- Jeroen Vuurens, Delft University of Technology - Sparren over word2vec
- Xander Wilcke - Inspireren over het Semantisch Web
- Marianne - op de gekste tijdstippen skypen en proof-readen
- Suzan Verberne, professor at the Radboud University of Nijmegen - Nakijken
- Flynn, my pug - For the fresh air when I needed a minute to relax
-
- \section*{Abstract}
+ I would like to thank the following people:
+ \paragraph{}
+ \paragraph{}
+ Arjen de Vries, professor at the Radboud University of Nijmegen and my mentor, for his limitless pool of knowledge and enthusiasm.
+For getting me out of the mud when I was stuck and motivating me to push on.
+ \paragraph{}
+ Suzan Verberne, professor at the Radboud University of Nijmegen and co-reader, for helping me start and finish this thesis.
+ \paragraph{}
+ Jeroen Vuurens, from Delft University of Technology, for helping me figure out Word2vec.
+ \paragraph{}
+ Xander Wilcke, from the VU Amsterdam, for inspiring me to combine Machine Learning with the Semantic Web.
+ \paragraph{}
+ Sanna Dinh, my partner, for spending countless late hours making this thesis readable and designing many of the images, making this thesis understandable.
+ \paragraph{}
+ Marianne, my mother-in-law, for being available on Skype at the most unconventional times to advise and proof-read. 
+  \paragraph{}
+ Flynn, my pug, for the fresh air during our walks when I needed a minute to relax.
+
+ \newpage 
+ \begin{abstract}
  McCallum proposed using distributed word embeddings for knowledge base completion, the problem of finding relations \textit{within} a knowledge base.
@@
 However, distributed word embeddings have potential to improve with more data as opposed to current methods which are hand-crafted.
-
- \section*{Summary}
+ \end{abstract}
+
+ \newpage
  \tableofcontents
  \newpage
-
- %Vragen
- % Hypothese waarom ik dat denk? Antwoord see Arjen notes
- % extra hypothese. Antwoord see Arjen notes (I think? otherwise its: don't add ensemble hypothesis)
 
@@
 
- An example: since the Hummingbird update, when someone Googles "Who is Barack Obama" they will find a part of the Knowledge Graph, see Figure \ref{hummingbird}..
+ An example: since the Hummingbird update, when someone Googles "How old is Barack Obama" they will find a part of the Knowledge Graph, see Figure \ref{hummingbird}.
 This system improves web searching by finding answers rather than pages.
- \paragraph{}
+
+ \begin{figure}
+ \includegraphics[width=\textwidth]{plots/hummingbird}
+ \caption[Hummingbird search]{A google search after the Hummingbird update returns a triple from Google's knowledge base, the Knowledge Graph.}
+ \label{hummingbird}
+ \end{figure}
+
  The many uses of ontology matching and its role in the Semantic Web show that it is important to research all avenues that might improve ontology matching, as it will have a direct result in many fields.
@@
 As such the sentence will contain concepts from both ontologies and they will move closer together.
-See \ref{sentences} for an example of the sentences generated by DeepWalk.
+See Section \ref{sentences} for an example of the sentences generated by DeepWalk.
+See Figure \ref{embedding_alignment} for an example of two ontology graphs being mapped to the same space.
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.6\textwidth]{plots/embedding_alignment}
+  \caption[Two graphs embedded]{Two graphs with a few corresponding nodes are embedded into vector space.
+Because of the known correspondences the latent correspondences are also mapped close to each other.}
+  \label{embedding_alignment}
+  \end{figure}
+
   \subsubsection{Node vectorisation}
@@
 It may even be competitive with more advanced string matchers (that look at substrings of labels).
-For example, \emph{whisker} and \emph{moustache} may be matched by a substring matcher, but are also semantically similar since they will often be mentioned in the same context.
+See Figure \ref{ontology_matrix}.
+
+  \begin{figure}
+  \begin{subfigure}{0.45\textwidth}
+  \includegraphics[width=\textwidth]{plots/ontology_matching_matrix}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.45\textwidth}
+    \includegraphics[width=\textwidth]{plots/ontology_matching_matrix2}
+  \end{subfigure}
+  \caption[Tensor with multiple ontologies]{The ontologies represented as a tensor.
+The connections (in green) are only within the ontologies, not between.
+The embeddings are used to predict new connections between the ontologies (in light green)}
+  \label{ontology_matrix}
+  \end{figure}
+
+  An example, \emph{whisker} and \emph{moustache} may be matched by a substring matcher, but are also semantically similar since they will often be mentioned in the same context.
   This method was chosen because it is the foundation of all other models that use the graph-context. It is required to see if the extensions improve results.
@@
   Random & 0.6926 & 0.4905 \\
-  Pre-trained & 0.6926 & 0.3874 \\
+  Pre-trained & 0.6926 & 0.4905 \\
   Bidirectional & 0.8432 & 0.4946 \\
@@
  \newpage
- \subsection{Interpretation}
-
- \newpage
  \section{Conclusion and discussion}
@@
 
- To answer this question I have examined the following points from Section \ref{hypotheses} for every algorithm (Pre-trained Word2vec, DeepWalk, Node2vec):
+ To answer this question I have examined the following points from Section \ref{researchquestion} for every algorithm (Pre-trained Word2vec, DeepWalk, Node2vec):
 
@@
  \newpage
- \bibliographystyle{plain}
+ \bibliographystyle{unsrt}
  \bibliography{bibliography}{}
